### 2014-01-15 Draft/abstract.tex
Initial Commit

\begin{abstract}

Recently many popular websites such as Twitter and Flickr expose their data through web service APIs, enabling third-party 
organizations to develop client applications that provide functionalities beyond what the original websites offer. These client applications should follow certain constraints in order to correctly interact with the web services.
Violations of such constraints can cause fatal errors 
or incorrect results in the client applications. However, these constraints are often not formally specified and thus not available for 
automatic verification of client applications. To address this issue, 
we propose a novel approach, called \tool,
%to automatically 
%infer dependency constraints on parameters for web services, via a 
%hybrid analysis of heterogeneous web service artifacts, including 
%the service documentation, the service SDKs, and the web services themselves. To evaluate our approach, we applied INDICATOR to infer dependency constraints for four popular web services. 
%The results showed that INDICATOR effectively infers constraints 
%with an average precision of 94.4\% and recall of 95.5\%.

\end{abstract}

### 2014-01-15 Draft/approach.tex
Initial Commit

\section{\tool\ Design}
\label{sec:approach}
%\vspace{-2mm}

\begin{figure}
	\centering
		\includegraphics[scale=0.45]{approach.eps}
	\caption{Overview of \tool\ framework}
	\label{fig:approachOverview}
\end{figure}

We next present our framework for inferring specifications from the method descriptions in API Documents. Figure~\ref{fig:approachOverview} gives an overview of our framework. Our framework consists of four major components: a parser, a preprocessor, an text-analysis engine, and a postprocessor.

The parser accepts online API description and parser them into an intermediate representation. The pre-processor accepts method descriptions and preprocesses the sentences in the descriptions, such as annotating sentence boundaries and reducing lexical tokens. 
The text-analysis engine accepts the pre-processed sentences and parses them using an NLP parser. The text-analysis engine further transforms the parsed sentences into the first-order-logic (FOL) representation and then leverages the FOL representation of a sentence to infer specifications. Finally, the postprocessor undoes any modifications done by the preprocessor to get refined specifications.

Besides the previously described major components the framework also consists of a an external component, namely target specification generator. This component accepts the specification generated by our framework and using mapping functions to a target specification language generates specifications in the target language of choice. We next describe each component in detail.

\subsection{Parser}
\label{sub:parser}

Our parser accepts the online API documents and parses them into predefined categories. In particular, our parser extracts the following contents: 1) Summary of the API method, 2)Summary of request elements of the method, and 3) Summary of response elements of the method inclusive of error responses.

This step is required to extract the desired descriptive text from the various presentation styles of the API documents. In particular, deferential API documents may have styles of presenting information to developers inclusive of different levels of details, we chose very generic fields that are found across all documents.

Currently our prototype implementation extracts this information from \amazon. However almost all of the REST API developer documents are provided on-line as structured webpages, thus the parser can be easily extended to extract desired information from any REST API developer documents in general.

\subsection{Preprocessor}
\label{sub:Preprocessor}

The preprocessor accepts method application descriptions extracted by the parser and preprocesses the natural language text, to be further analyzed by the text-analysis engine. In particular, the preprocessor annotates special words and reduces the number of lexical tokens using semantic information. The preprocessing steps are required to increase the accuracy of the subsequent phases of \tool\ framework, described in detail in Section~\ref{sub:TAE}. We next describe in detail the preprocessing steps:

\textbf{1. Special word annotation}.
Since the exiting NLP techniques rely on accurate annotation of POS tags in a sentence, the accuracy of \tool\ to infer constraints is dependent on the accurate annotation of POS tags. While existing techniques work well on general linguistics, that does not necessary entail that they work well with domain specific text as well. In particular, with respect to API documents certain words have a very different semantic meaning, in contrast to general linguistics that causes incorrect annotation of POS tags.

Consider the word ``POST'' for instance. The online Oxford dictionary~\footnote{\url{http://oxforddictionaries.com/us/definition/american_english/post?q=POST}} has 8 different definition of word ``POST'', and none of them describes POST as a HTTP method supported by REST API meaning: \textit{``Creates a new entry in the collection. The new entry's URI is assigned automatically and is usually returned by the operation''}. Thus existing NLP techniques fail to accurately annotate the POS tags of the sentences involving word ``POST''.

This preprocessing step identifies such words from the sentences based on a domain-specific dictionary, and annotates them appropriately. This special annotation forces the underlying POS tagger to accurately annotate the POS tags of the words involving domain specific keywords.

From implementations perspective, we manually built the domain-specific dictionary using the glossary of terms collected from the web pertaining to REST API. We further leveraged the HTML style information in \amazon\ to look for words that were highlighted in code like format.

\textbf{2. Lexical tokens reduction}.

The reduction of lexical tokens greatly increases the accuracy of the analysis in the subsequent components of our framework. In particular, the preprocessor reduces lexical tokens by performing following subtasks

\textbf{1. Period Handling}. Besides marking the end of a sentence in simplistic English, the character period (`.') has other legal usages as well such as decimal representation (periods between numbers). Although legal, such usage hinder detection of sentence boundaries, thus forcing the subsequent components to return incorrect or imprecise results. We pre-process the sentences by annotating these usages for accurate detection of sentence boundaries. We achieve so by looking up known shorthand words from WordNet~\cite{wordnet} and detecting decimals, which are also the period character, by using regular expressions. From an implementation perspective, we have maintained a static lookup table of shorthand words observed in WordNet.

\textbf{2. Named Entity Handling}. Sometimes a sequence of words correspond to the name of entities that have a specific meaning collectively. For instance, consider the phrases \textit{``Amazon S3'', ``Amazon simple storage service''}, which are the names of the service. Further resolution of these phrases using grammatical syntax is unnecessary and would not bring forth any semantic value. Also these phrases contribute to length of a sentence that in turn negatively affects the accuracy of POS tagger. Thus, we identify such phrases and annotate them as single lexical units. We achieve so by maintaining a static lookup table.

\textbf{3. Abbreviation Handling}. Natural-language sentences often consist of abbreviations mixed with text. This can result in subsequent components to incorrectly parse a sentence. We find such instances and annotate them as a single entity. For example, text followed by abbreviations such as \textit{``Access Control Lists (ACL)''} is treated as single lexical unit. Detecting such abbreviations is achieved by using the common structure of abbreviations and encoding such structures into regular expressions. Typically, regular expressions provide a reasonable approximation for handling abbreviations.

\textbf{4. Frequent Phrases} Although the previous steps assist in bringing down the number of lexical tokens in a sentence, some sentences may still contain a considerable number of lexical tokens to overwhelm the underlying POS tagger. To address this issue we propose to further reduce the number of lexical tokens in a sentence  by annotating frequent phrases as a single lexical unit.

In particular, we use n-gram based approach as means to achieve this reduction. In the fields of computational linguistics and probability, an n-gram is a contiguous sequence of n words from a given sequence of text or speech. We first calculate the most frequently occurring n-grams in the text body. In particular, we are interested in the n-grams of length 4 or greater to achieve a reasonable reduction. We then prune the list of n-grams based on a subsumption. We consider a n-gram of length k ($n_k$) to subsume n-gram of length k-1 ($n_{k-1}$) iff $n_{k-1}$ is a substring of ($n_k$) and the frequency of occurrence of $n_{k-1}$ equals frequency of occurrence of $n_{k}$ . Finally, we rank the list of n-grams based on the frequency of their occurrence in the text, and select top-k n-grams for reduction.

From an implementation perspective we used Apache Lucene$^{\textregistered}$~\cite{lucene} to achieve n-gram reduction. Apache Lucene is a high-performance, full-featured text search engine library written entirely in Java. It is a technology suitable for nearly any application that requires full-text search, especially cross-platform.

Although a POS tagger can be retrained to achieve these pre-processing steps, we prefer annotations to make our approach independent of any specific NLP infrastructure, thus ensuring interoperability with various POS taggers.

\subsection{NLP Parser}

The NLP parser accepts the pre-processed documents and annotates every sentence within each document using standard NLP techniques. From an implementation perspective, we chose the Stanford Parser~\cite{SNLP}. However, this component can be implemented using any other existing NLP libraries or frameworks. In particular, we annotate each sentence with POS annotations, Named-Entity Annotations and Stanford-Typed Dependencies. For more details on these tehniques and their application, please refer to ~\cite{Marneffe06LREC,Marneffe08COLING,pandita12:inferring, pandita13:WHYPER}.

%\begin{figure}
%	\centering
%%		\includegraphics[scale=0.6]{stanfordAnnotated.eps}
%	\caption{Sentence annotated with Stanford dependencies}
%	\label{fig:standep}
%\end{figure}
%
%Next we use an example to illustrate the annotations added by the NLP Parser. Consider the example sentence \textbf{\textit{``Also you can share the yoga exercise to your friends via Email and SMS.''}}, that indirectly refers to the READ\_CONTACTS permission. Figure~\ref{fig:standep} shows the sentence annotated with Stanford-typed dependencies. The words in red are the names of dependencies connecting the actual words of the sentence (in black). Each word is followed by the Part-Of-Speech (POS) tag of the word (in green). For more details on Stanford-typed dependencies and POS tags, please refer to ~\cite{Marneffe06LREC,Marneffe08COLING}.

\subsection{Text Analysis Engine}
\label{sub:TAE}
%
%\begin{figure}
%	\centering
%	%	\includegraphics[scale=0.65]{taeRep.eps}
%	\caption{First-order logic representation of annotated sentence in Figure~\ref{fig:standep}}
%	\label{fig:FOLRep}
%\end{figure}

The text analysis engine component accepts the annotated documents and creates an intermediate representation of each sentence. We define our representation as a tree structure that is essentially a First-Order-Logic (FOL) expression. Research literature provides evidence of the the adequacy of using FOL for NLP related analysis tasks~\cite{Sinha2009,Sinha2010,pandita12:inferring, pandita13:WHYPER}.

In our representation, every node in the tree except for the leaf nodes is a predicate node. The leaf nodes represent the entities. The children of the predicate nodes are the participating entities in the relationship represented by the predicate. The first or the only child of a predicate node is the governing entity and the second child is the dependent entity. Together the governing entity, predicate and the dependent entity node form a tuple.

In particular, the process of generation of intermediate-representation is an extension of the intermediate-representation generator component of \emph{WHYPER}~\cite{pandita13:WHYPER} with additional steps. In \emph{WHYPER}, the intermediate representation is generated based on principle of shallow parsing~\cite{Branimir2000}. They implemented their parser as a function of Stanford-typed dependencies~\cite{Marneffe06LREC,Marneffe08COLING,SNLP,KleinNIPS03}, to leverage the semantic information encoded in Stanford-typed dependencies.

However, we observed that intermediate-representation generator component of \emph{WHYPER}~\cite{pandita13:WHYPER} is overwhelmed by wordy sentences.This limitation mandates the use of additional novel technique of \textit{`Frequent Phrases Reduction'} in preprocessing phase. We further improve the accuracy of  parser by adopting a hybrid (leveraging both POS tags as well as Stanford-typed dependencies) approach.

Our implementation of shallow parser is a two phase process:

\begin{enumerate}
	\item{\textbf{POS Tags}}: We first parse a sentence based on the function of POS tags. In particular, we use semantic templates to logically break a sentences into smaller constituent sentences. For instance, consider the sentence \scriptsize``All objects (including all object versions and Delete Markers) in the bucket must be deleted before the bucket itself can be deleted.''. \normalsize The Stanford parser inaccurately annotates the Stanford-typed dependencies of the sentence because of presence of different clauses acting on different subject-object pairs. We thus break down the sentence into two smaller tractable sentences:

	 \scriptsize All objects in the bucket must be deleted before the bucket itself can be deleted.

	 All objects including all object versions and Delete Markers.\normalsize

	 Table~\ref{tab:semanticTemplates} shows a list the semantic templates. Column ``Template'' describes conditions where the template is applicable and Column ``Summary'' describes the action taken by our shallow parser when the template is applicable. All of these semantic templates are publicly available on our project website~\cite{projectweb}. With respect to the previous example the template no. 3 \textit{( A noun phrase followed by another noun/pronoun/verb phrase in brackets)} is applicable. Thus our shallow parser breaks the sentence into two individual sentences.

	\item{\textbf{Stanford-typed Dependencies}}: This phase is equivalent to the intermediate-representation generator component of the \emph{WHYPER}~\cite{pandita13:WHYPER}.

\end{enumerate}

\begin{table*}
\begin{center}

\caption{Semantic Templates}
    \begin{tabular}{ | l | p{5cm} |p{10cm} |}
    \hline
    \textbf{S No.} 	& \textbf{Template} & \textbf{Summary} \\ \hline

    1. 		& Two sentences joined by a conjunction & Sentence is broken down into two individual sentences with the conjunction term serving as the connector between two. \\ \hline
    2. 		& Two sentences joined by a ``,''& Sentence is broken down to individual independent sentences \\ \hline
    3.		& A noun phrase followed by another noun/pronoun/verb phrase in brackets & Two individual sentences are formed. The first sentence is  the same as the parent sentence sans the noun/pronoun.verb phrase in bracket. The second sentence constitutes of the noun phrase followed by  noun/pronoun/verb phrase without the brackets.\\ \hline
    4.		& A noun phrase by a conditional phrase in brackets & Two individual sentences are formed. The first sentence is the same as the parent sentence sans the conditional phrase in bracket. The second sentence constitutes of noun phrases followed by conditional in the bracket.\\ \hline
    5.		& A conditional phrase followed by a sentence & Two dependent sentences are formed. The first sentence constitutes the conditional phrase. The second sentence constitutes rest of the sentence.\\ \hline
    6.		& A sentence in which the parent verb phrase is over two child verb phrases joined by a conjunction & Two dependent sentences are formed where the dependency is the conjunction. The first sentence is formulated by removing conjunction and second child verb phrase. The second sentence is formulated by removing conjunction and first child verb phrase. \\ \hline
    \end{tabular}
	\label{tab:semanticTemplates}
\end{center}
\end{table*}

%The FOL representation helps us effectively deal with the problem of \emph{confounding effects} of keywords as described in Section~\ref{sec:overview}. In particular, the FOL assists in distinguishing between a resource that would be a leaf node and an action that would be a predicate node in the intermediate representation of a sentence. The generated FOL representation of the sentence is then provided as an input to the semantic engine for further processing.
%
%
%
%\subsection{Semantic Engine (SE)}
%\label{sub:SE}
%The Semantic Engine (SE) accepts the FOL representation of a sentence and based on the semantic graphs of Android permissions annotates a sentence if it matches the criteria. A semantic graph is basically a semantic representation of the resources which are governed by a permission. For instance, the READ\_CONTACTS permission governs the resource ``CONTACTS'' in Android system.
%
%
%Figure~\ref{fig:knowledge} shows the semantic graph for the permission READ\_CONTACTS. A semantic graph primarily constitutes of subordinate resources of a permission (represented in rectangular boxes) and a set of available actions on the resource itself (represented in curved boxes). Section~\ref{sub:ACA} elaborates on how we build such graphs systematically.
%
%Our SE accepts the semantic graph pertaining to a permission and annotates a sentence based on the algorithm shown in Algorithm~\ref{alg:SenAnnotaator}. The Algorithm accepts the FOL representation of a sentence $rep$, the semantic graph associated with the resource of a permission $g$ and a boolean value $recursion$ that governs the recursion. The algorithm outputs a boolean value $isPStmt$, which is \CodeIn{true} if the statement describes the permission associated with a semantic graph ($g$), otherwise \CodeIn{false}. 
%
%Our algorithm systematically explores the FOL representation of the sentence to determine if a sentence describes the need for a permission. First, our algorithm attempts to locate the occurrence of associated resource name within the leaf node of the FOL representation of the sentence (Line 3). The method \CodeIn{findLeafContaining(name)} explores the FOL representation to find a leaf node that contains term \CodeIn{name}. Furthermore, we use WordNet and Lemmatisation~\cite{Do09:Robust} to deal with synonyms of a word in question to find appropriate matches. Once a leaf node is found, we systematically traverse the tree from the leaf node to the root, matching all parent predicates as well as immediate child predicates [Lines 5-16].
%
%Our algorithm matches each of the traversed predicate with the actions associated with the resource defined in semantic graph. Similar to matching entities, we also employ WordNet and Lemmatisation~\cite{Do09:Robust} to deal with synonyms to find appropriate matches. If a match is found, then the value \CodeIn{isPStmt} is set to  \CodeIn{true}, indicating that the statement describes a permission.
%
%In case no match is found, our algorithms recursively search all the associated subordinate resources in the semantic graph of current resource. A subordinate resource may further have its own subordinate resources. Currently, our algorithm considers only immediate subordinate resources of a resource to limit the false positives.
%
%%We limit the exploration to depth 1 to limit the false positives. That means only immediate subordinate resources of a resource will be explored.
%
%In the context of the FOL representation shown in Figure~\ref{fig:FOLRep}, we invoke Algorithm~\ref{alg:SenAnnotaator} with the semantic graph shown in Figure~\ref{fig:knowledge}. Our algorithm attempts to find a leaf node containing term ``CONTACT'' or some of its synonym. Since the FOL representation does not contain such a leaf node, algorithm calls itself with semantic graphs of subordinate resources (Line 17-25), namely `NUMBER', `EMAIL', `LOCATION', `BIRTHDAY', `ANNIVERSARY'. 
%
%The subsequent invocation will find the leaf-node ``email'' (annotated 9 in Figure~\ref{fig:FOLRep}). Our algorithm then explores the preceding predicates and finds predicate ``share'' (annotated 2 in Figure~\ref{fig:FOLRep}). The Algorithm matches the word ``share'' with action ``send'' (using Lemmatisation and WordNet similarity), one of the actions available in the semantic graph of resource `EMAIL' and returns \CodeIn{true}. Thus, the sentence is appropriately identified as describing the need for permission READ\_CONTACT. 
%
%
%\algsetup{indent=1em}
%\begin{algorithm}[t!]
%\begin{algorithmic}[1]
%\begin{scriptsize}
%\REQUIRE K\_Graph $g$, FOL\_rep $rep$, Boolean $recursion$ 
%\ENSURE Boolean $isPStmt$
%\STATE $Boolean\ isPStmt\ =\ false$
%\STATE $String\ r\_name\ =\ g.resource\_Name$
%\STATE $FOL\_rep\ r'\ =\ rep.findLeafContaining(r\_name)$
%\STATE $List\ actionList\ =\ g.actionList$
%\WHILE{$(r'.hasParent)$}
%	\IF{$actionList.contains(r'.parent.predicate)$}
%		\STATE $isPStmt\ =\ true$
%		\STATE $break$
%	\ELSE
%		\IF{$actionList.contains(r'.leftSibling.predicate)$}
%			\STATE $isPStmt\ =\ true$
%			\STATE $break$
%		\ENDIF
%	\ENDIF
%	\STATE $r'\ =\ r'.parent$
%\ENDWHILE
%\IF{$((NOT(isPStmt))\ AND\ recursion)$}
%	\STATE $List\ resourceList\ =\ g.resourceList$
%	\FORALL{$(Resource\ res\ in\ resourceList)$}
%		\STATE $isPStmt\ =\ Sentence\_Annotator(getKGraph(res),\ rep,\ false)$
%		\IF{$isPStmt$}
%			\STATE $break$
%		\ENDIF
%	\ENDFOR
%\ENDIF
%\RETURN $isPStmt$
%\end{scriptsize}
%\end{algorithmic}
%\caption{Sentence\_Annotator}
%\label{alg:SenAnnotaator}
%\end{algorithm} 
%
%\begin{figure}
%	\centering
%%		\includegraphics[scale=0.4]{knowledge.eps}
%	\caption{Semantic Graph for the READ\_CONTACT permission}
%	\label{fig:knowledge}
%\end{figure} 
%  
%
%

### 2014-01-15 Draft/background.tex
Initial Commit

\section{Background}
\label{sec:background}

Although, well suited for human communication, converting natural language into unambiguous specifications that can be processed and understood by computers is very difficult.  Recently, a lot of exciting work has been carried out in the area of Natural Language Processing (NLP), with existing NLP techniques proving to be fairly accurate in highlighting grammatical structure of a natural language sentence. However, existing NLP techniques are still in the processing phase and not in understanding phase.  We briefly introduce the NLP techniques used in this work.

\textbf{Parts Of Speech (POS) tagging}~\cite{Klein03,KleinNIPS03}. Also known as \textit{`word tagging'}, \textit{`grammatical tagging'} and \textit{`word-sense disambiguation'}, these techniques aim to identify the part of speech (such as noun, verbs, etc.), a particular word in a sentence belongs to. The most commonly used technique is to train a classification parser over a previously known data set. Current state of the art approaches been have demonstrated to achieve 97\%~\cite{SNLP1} accuracy in classifying POS tags for well written news articles.

\textbf{Phrase and clause parsing}. Also known as chunking, this technique divides a sentence into a constituent set of words (or phrases) that logically belong together (such as a Noun Phrase and Verb Phrase). Chunking thus further enhances the syntax of a sentence on top of POS tagging. Current state-of-the-art approaches can achieve around 90\%~\cite{SNLP1} accuracy in classifying phrases and clauses over well written news articles.

\textbf{Typed Dependencies}~\cite{Marneffe06LREC,Marneffe08COLING}. The Stanford typed dependencies representation  is designed to provide a simple description of grammatical relationships directed towards non-linguistics experts to perform NLP related tasks. It provides a hierarchical structure for the dependencies with precise definitions of what each dependency means, thus facilitating machine based manipulation of natural language text.

\textbf{Named Entity Recognition}~\cite{Finkel05ACL}. Also known as \textit{`entity identification'} and \textit{`entity extraction'}, these techniques are a subtask of IE that aims to classify words in a sentence into predefined categories such as names, quantities, expression of times, etc. These techniques help in associating predefined semantic meaning to a word or a group of words (phrase), thus facilitating semantic processing of named entities.

\textbf{Co-reference Resolution}~\cite{RaghunathanEMNLP10,LeeCoNLL11}. Also known as \textit{`anaphora resolution'}, these techniques aim to identify multiple expressions present across (or within) the sentences, that point out to the same thing or \textit{`referant'}. These techniques are useful for extracting information; especially if the information encompasses many sentences in a document.

### 2014-01-15 Draft/conclusion.tex
Initial Commit

\section{Conclusion}
\label{sec:conclusion}

%API documents provide specification information about how to use a particular method within a class by means of method descriptions. However, specifications described in natural Language in API documents are not amenable to formal verification by existing verification tools.

%Specifications described in natural language in API documents are not amenable to formal verification by existing verification tools. In this paper, we have presented a novel approach for inferring formal specifications from API documents targeted towards code contract generation. Our evaluation results show that our approach has an average of 92\% precision and 93\% recall in identifying sentences describing code contracts from over 2500 sentences. Furthermore, our results also show that our approach has an average of 83.4\% accuracy in inferring specifications from sentences describing code contracts out of over 1600 sentences.

### 2014-01-15 Draft/evaluation.tex
Initial Commit

\section{Evaluation}
\label{sec:evaluation}

We conducted an evaluation to assess the effectiveness of our approach. In our evaluation, we address three main research questions:

\begin{itemize}

\item\textbf{RQ1}: What are the precision and recall of \tool\ in inferring usage constraints?

%\item\textbf{RQ2}: What is the accuracy of our approach in inferring specifications from contract sentences in the API documents?

\item\textbf{RQ2}: How does our approach fares in comparison to previous NLP approaches?

\end{itemize}

\subsection{Subjects}
\label{sub:subject}

We used the API documents of the following two libraries as subjects for our evaluation.

\amazon\ provides a simple REST based web services interface that can be used to store and retrieve data on the web. Furthermore, \CodeIn{Amazon S3} also empowers a developer with rich set of API methods to access a highly scalable, reliable, secure, fast, inexpensive infrastructure. \textbf{may be a little detail of usage statistics etc....}

\textbf{TBD}.

\subsection{Summary}
\label{sub:summary}

\subsection{Threats to Validity}
\label{sub:threats_to_validity}
Threats to external validity primarily include the degree to which the subject documents used in our evaluations are representative of true practice. To minimize the threat, we used API documents of two representative commercial REST API: one dealing with online storage and the other \textbf{TBD}. The \amazon documents describe one of the most popularly used and online storage APIs. We also used the \textbf{TBD}. Furthermore, the difference in the functionalities provided by the two projects also address the issue of over fitting our approach to a particular type of API. The threat can be further reduced by evaluating our approach on more subjects.

Threats to internal validity include the correctness of our implementation in extracting usage constraints and labelling a statement as a constraint statement. To reduce the threat, we manually inspected all the constraints inferred against the API method descriptions in our evaluation. Furthermore, we ensured that the results were individually verified and agreed
upon by two authors.

### 2014-01-15 Draft/example.tex
Initial Commit

\section{Examples}
\label{sec:example}

%We now present a series progressing in complexity to demonstrate our approach. Our examples are from real Java Platform, Micro Edition (JME) formerly known as J2ME and Android API. Both JME and Android use Java as the language of implementation and targeted towards hand-held devices. However, our approach is independent of language of implementation and thus can be used for any similar source and target API.

%First we parse the API documents of source and target API library and store it in intermediate representation for analysis. In particular, we extract class, interface and corresponding method descriptions from API documents. Second, we then create a term vector representation of each class description and method descriptions. Vector space model or term vector model is an algebraic model for representing text documents (and any objects, in general) as vectors of identifiers, such as, for example, index terms. In our case, each word is considered as a term barring the stop words such as (a, the, and ...).

%Finally we use the term vector representation of a method description in a source API to query term vector representation of the the method description in target API. The results are ranked based on the Term Frequency-Inverse Document Frequency (TF-IDF) measure. TF-IDF is a numerical statistic which reflects how important a word is to a document in a collection or corpus. It is often used as a weighting factor in information retrieval and text mining.

%We then collect the top 10 results from target API methods for each source API method. Figure~\ref{fig:excpAPIJ2ME} and Figure~\ref{fig:excpAPIAndroid} shows example of trivially similar API methods. Our search results return the Android API method shown in Figure~\ref{fig:excpAPIAndroid} as a first match for the JME method shown in Figure~\ref{fig:excpAPIJ2ME}. Notice the slightly different description for the methods in JME and Android API. Although, correct this is very trivial mapping. We next present a more complex example.

\begin{figure}[t]
\begin{CodeOut}
\begin{alltt}
\includegraphics[scale=0.4]{Stackoverflow.eps}
\end{alltt}
\end{CodeOut}
\caption{\label{fig:Stackoverflow} The Query posted on Stackoverflow form regrading Amazon S3 REST API}
\end{figure}

\begin{figure}[t]
\begin{CodeOut}
\begin{alltt}
\includegraphics[scale=0.4]{AmzonS3DeleteBucketAPI.eps}
\end{alltt}
\end{CodeOut}
\caption{\label{fig:AmzonS3DeleteBucketAPI} The online API document for \CodeIn{DELETE Bucket} operation in Amazon S3 REST API}
\end{figure}

%Figure~\ref{fig:drawCharAPIJ2ME} and Figure~\ref{fig:drawTextAPIJ2ME} shows example of non-trivially similar API methods. Although, the textual description is similar using text analytics (TF-IDF similarity using term frequency vector), there is difference in type of arguments.

### 2014-01-15 Draft/introduction.tex
Initial Commit

\section{Introduction}
\label{sec:introduction}

%These constraints are mainly expressed in natural language in the service documentation. A widely-adopted strategy [7] by developers to build correct client applications is to first read through the service documentation, trying to memorize the constraints, and then develop client applications accordingly. However, conformance to constraints cannot be assured. In fact, a recent study [14] showed that developers may still make mistakes even when they have been rather familiar with the documentation. 
%
%
%Therefore, it is desirable that client applications are formally verified against these constraints, and violations of each constraint are detected as bugs. However, these verification techniques [8, 9, 14] require formally specified constraints, which are often not readily available, due to the large amount of effort needed to manually specify them. For example, it took one of the authors more than 10 hours to only browse the documentation of the Ebay2 web service operation “AddFixedPriceItem”, let alone the time needed to extract and formalize the constraints
%
%To address these shortcomings we propose a different approach for inferring likely mapping between API's. In particular, we propose the use of Natural Language processing of API documents to infer such mapping.  
%
%  
%API documentation provides developers with useful information about class/interface hierarchies within the software. Additionally, API documents also provides information about how to use a particular method within a class by means of method descriptions. Method descriptions typically describe specifications in terms of the expectations of the method arguments and functionality of method in general.
%
%
%We plan to leverage these method descriptions to find the likely mapping. However, it is not trivial to use natural langauge processing on API documents to infer likely mappings. In particular, our technique addresses the following technical challenges to infer likely mappings:
%
%\begin{enumerate}
%	\item \textit{Programming Keywords}. Method descriptions often contain programming keywords (e.g., \CodeIn{true, null, buffer}), which have a different meaning in the context of programs, in contrast to general linguistics. For instance,\textit{``This method also returns false if path is null''}. In this sentence, words `false' and `null' are nouns in the context of object-oriented languages such as Java and C\#, whereas in general linguistics these words are adjectives. Thus, these keywords need to be handled differently.
%		
%	\item \textit{Semantic Equivalence}. A legal usage in natural language can be described in different words and semantic structures. For instance, consider the following two fragments that describe the similar functionality specification: \textit{``Flushes this data output stream. This forces any buffered output bytes to be written out to the stream.'}' and \textit{``Writes buffered data to the target stream and calls the flush method of the target stream.''}. Thus, there is a need to identify the semantic equivalence of legal usage described in different ways.
%		
%		To address this challenge, we propose a new technique called \textit{equivalence analysis} based on identified grammatical relationships (main nouns and verbs) of a sentence.
%	
%	\item \textit {Partial Functionality}. There are significant number of cases when the functionality in a source API method is broken across multiple methods in target API. For instance \CodeIn{Graphics.drawChar()} method in J2ME API is mapped to methods \CodeIn{Paint.setColor();Canvas.drawText()}in Android API.
%	
%		To address this challenge, we propose a lightweight \CodeIn{Type} analysis.
%		
%\end{enumerate}
%
%
%
%
%In summary, our approach leverages natural language description of API's to infer likely mapping thus facilitating cross API migration of applications. As our approach analyzes API documents in natural language, it can be reused independent of the programming language of the library. To the best of our knowledge, ours is the first approach that analyzes natural language API descriptions to infer likely mapping across API's.
%
%Our paper makes the following major contributions:
%\begin{itemize}
%	\item A technique that effectively infers mapping across source and target API.
%	\item A prototype implementation of our approach based on extending the Stanford Parser~\cite{SNLP,SNLP1}, which is a natural language parser to derive the grammatical structure of sentences. An open source implementation of our prototype can be found at our website\footnote{\url{http://research.csc.ncsu.edu/ase/projects/pint/}}. 
%	\item An evaluation of our approach on J2ME and Android API
%\end{itemize}

The rest of the paper is organized as follows. Section~\ref{sec:background} presents the  background on code contracts as well as NLP. Section~\ref{sec:example} presents an real world examples that motivate our approach. Section~\ref{sec:approach} presents our approach. Section~\ref{sec:evaluation} presents evaluation of our approach. Section~\ref{sec:discussion} presents a brief discussion and future work. Section~\ref{sec:related} discusses related work. Finally, Section~\ref{sec:conclusion} concludes.

### 2014-01-15 Draft/related.tex
Initial Commit

\section{Related work}
\label{sec:related}

Design by contracts has been an influential concept in the area of software engineering in the past decade. A significant amount of work has been done in automated inference of code contracts. There are existing approaches that statically or dynamically extract code contracts~\cite{csallner08dysy, NimmerE02:ISSTA, Tillmann:2006:DLM:2105385.2105433}. However, a combination of developer written and automatically inferred contracts seems to be the most effective approach~\cite{FrakesIEEETran05,Polikarpova2009ISSTA}. Since developers describe the specifications in the method descriptions, we believe that our approach can work in conjunction with existing approaches towards extracting a comprehensive set of code contracts for a method. Furthermore, Wei et al.~\cite{WeiICSE11}demonstrated that dynamic contract inference performed better when provided with an initial set of seed contracts.

There are existing approaches that infer code-contract-like specifications (such as behavioral model, algebraic specifications, and exception specifications) either dynamically~\cite{Ghezzi:2009:SIB:1555001.1555057,Henkel07documentation,Henkel:2008:DDA:1363102.1363105} or statically~\cite{Buse:2008:ADI:1390630.1390664,FrakesIEEETran05} from source code and binaries. In contrast, our approach infers specifications from the natural language text in API documents, thus complementing these existing approaches when the source code or binaries of the API library is not available.

NLP techniques are increasingly applied in the software engineering domain. NLP techniques have been shown to be useful in requirements engineering~\cite{Gervasi2005,Sinha2009,Sinha2010}, usability of API documents~\cite{Dekel2009}, and other areas~\cite{Little2009,Zhou2008}. We next describe most relevant approaches.

Xiao et al.~\cite{XiaoFSE2012} use shallow parsing techniques to infer Access Control Policy (ACP) rules from natural language text in use cases. The use of shallow parsing techniques works well on natural language texts in use cases, owing to well formed nature of sentences in use case descriptions. In contrast, often the sentences in API documents are not well formed. Additionally, their approach does not deal with programming keywords or identifiers, which are often mixed within the method descriptions in API documents.

\
~\cite{pandita12:inferring}
~\cite{pandita13:WHYPER}

Zhong et al.~\cite{zhong09SE} employ NLP and ML techniques to infer resource specifications from API documents. Their approach uses machine learning to automatically classify such rules. In contrast, we attempt to parse sentences based on semantic templates and demonstrate that such an approach preforms reasonably well. Tan et al.~\cite{TanSOSP07} applied an NLP and Machine Learning (ML) based approach to test Javadoc comments against implementations. However, their approach specifically focuses on null values and related exceptions, thus limiting the application scope. In contrast, our approach infers generic specifications from API documents. In particular, our approach already produces FOL representation of the specifications that can be used to test implementations. Furthermore, the performance of the preceding ML-based approaches is dependent on the quality of the training sets used for ML. In contrast, our approach is independent of such training set and thus can be easily extended to target respective problems addressed by these approaches.

Among other works described in ~\cite{RobillardIEEEtranSE13}, Mining API Mapping (MAM)~\cite{Zhong2010ICSE} is most directly related to our work. MAM mines API mapping relations across different languages for language migration, however they do little in terms of mining usage constraints of methods.

%Web Query~\cite{Zheng2011FSE}

%\textbf{Library migration}. With evolution of libraries, some APIs may become incompatible across library versions. To address this problem, Henkel and Diwan ~\cite{csallner08dysy} proposed an approach that captures and replays API refactoring actions to update the client code. Xing and Stroulia [17] proposed an approach that recognizes the changes of APIs by comparing the differences between two versions of libraries. Balaban et al. [2] proposed an approach to migrate client code when mapping relations of libraries are available. In contrast to these approaches, our approach focuses on mapping relations of APIs across different languages. In addition, since our approach uses ATGs to mine API mapping relations, our approach can also mine mapping relations between API methods with different parameters or between API methods whose functionalities are split among several API methods in the other language.

### 2014-01-16 Draft/abstract.tex
added new version

@@
 \begin{abstract}
+Formal specifications of an Application Programming Interface (API) usage are highly desirable,
+because they are the precursor to the formal analysis tools such as model checkers and runtime verifiers.
+However, most API's do not have formal specifications.
+In contrast documentation of methods contain detailed specifications of the usage in natural language text.
+However, formal analysis tools are not designed to work on specifications in natural languages.
+Manually writing formal specifications based on natural language text in API documents can be prohibitively time consuming and error prone.
+To address this issue, we propose a natural language processing based novel approach \tool\ to precisely infer constraints from natural language text of API documents.
+In particular, we focus on temporal constraints, that are defined as constraints on the
+\textit{allowed sequence of invocations of methods within an API}.
+To evaluate our proposed approach, we applied \tool\ to infer temporal constraints from 
+commonly used package \CodeIn{java.io} from JDK API and Amazon S3 REST API.
+Our evaluation results show that \tool\ achieves an average of PP\% precision and RR\% recall
+in inferring TT temporal constraints from more than ZZZZ sentences of API sentences.
 
-Recently many popular websites such as Twitter and Flickr expose their data through web service APIs, enabling third-party 
-organizations to develop client applications that provide functionalities beyond what the original websites offer.
-These client applications should follow certain constraints in order to correctly interact with the web services.
-Violations of such constraints can cause fatal errors 
-or incorrect results in the client applications. However, these constraints are often not formally specified and thus not available for 
-automatic verification of client applications. To address this issue, 
-we propose a novel approach, called \tool,
-%to automatically 
-%infer dependency constraints on parameters for web services, via a 
-%hybrid analysis of heterogeneous web service artifacts, including 
-%the service documentation, the service SDKs, and the web services themselves. To evaluate our approach, we applied INDICATOR to infer dependency constraints for four popular web services. 
-%The results showed that INDICATOR effectively infers constraints 
-%with an average precision of 94.4\% and recall of 95.5\%.
+%IS the approach automated
+%precursor too strong word
+% need to explain why moving from formal specifications to temporal constraints
+
+% Goal statement
+% The goal of this research is to facilitate the correct usage API methods by identifying temporal constraints etc..
+% Is the approach automated ? Make a line about how you gonna
+% conclusion of numbers 
+% make it consistent APi documents, descriptions and sentences
 

### 2014-01-16 Draft/approach.tex
added new version

@@
 Figure~\ref{fig:approachOverview} gives an overview of our framework.
-Our framework consists of four major components: a parser, a preprocessor, an text-analysis engine, and a postprocessor.
+Our framework consists of four major components: an API parser, a preprocessor, a text-analysis engine, and a postprocessor.
 
-The parser accepts online API description and parser them into an intermediate representation.
+The API parser accepts online API description and extracts method descriptions.
 The pre-processor accepts method descriptions and preprocesses the sentences in the descriptions, such as annotating sentence boundaries and reducing lexical tokens. 
-The text-analysis engine accepts the pre-processed sentences and parses them using an NLP parser.
-The text-analysis engine further transforms the parsed sentences into the first-order-logic (FOL) representation and then leverages the FOL representation of a sentence to infer specifications.
+The text-analysis engine accepts the pre-processed sentences and annotates them using an NLP parser.
+The text-analysis engine further transforms the annotated sentences into the first-order-logic (FOL) representation and then leverages the FOL representation of a sentence to infer specifications.
 Finally, the postprocessor undoes any modifications done by the preprocessor to get refined specifications.
@@
 
-\subsection{Parser}
+\subsection{API Parser}
 \label{sub:parser}
 
-Our parser accepts the online API documents and parses them into predefined categories.
-In particular, our parser extracts the following contents: 1) Summary of the API method, 2)Summary of request elements of the method, and 3) Summary of response elements of the method inclusive of error responses.
+Our API parser accepts the online API documents and extracts method descriptions from it.
+In particular, our parser extracts the following fields within method descriptions: 
+1) \textit{Summary of the API method},
+2) \textit{Summary of request elements of the API method}, and 
+3) \textit{Summary of response elements of the method (inclusive of error responses)}.
 
 This step is required to extract the desired descriptive text from the various presentation styles of the API documents.
-In particular, deferential API documents may have styles of presenting information to developers inclusive of different levels of details, we chose very generic fields that are found across all documents.
+In particular, different API documents may have different styles of presenting information to developers.
+This difference in style may include the difference in the level of detail presented to the developer.
+We thus chose very only generic fields that are essential to API methods.
 
-Currently our prototype implementation extracts this information from \amazon.
-However almost all of the REST API developer documents are provided on-line as structured webpages, thus the parser can be easily extended to extract desired information from any REST API developer documents in general.
+Currently our prototype implementation extracts this information from online \amazon\ only. 
+However, almost all of the REST API developer documents are provided online as structured webpages.
+Thus, current implementation of parser can be easily extended to extract desired information from any REST API developer documents.
 
@@
 
-The preprocessor accepts method application descriptions extracted by the parser and preprocesses the natural language text, to be further analyzed by the text-analysis engine.
-In particular, the preprocessor annotates special words and reduces the number of lexical tokens using semantic information.
-The preprocessing steps are required to increase the accuracy of the subsequent phases of \tool\ framework, described in detail in Section~\ref{sub:TAE}.
-We next describe in detail the preprocessing steps:
+The preprocessor accepts API method descriptions extracted by the parser and preprocesses the natural language text, to be further analyzed by the text-analysis engine.
+The preprocessing steps are required to increase the accuracy core NLP techniques (described in Section~\ref{sub:CoreNLPback}) that are used in the subsequent phases of \tool\ framework.
+In particular, the preprocessor first employs the noun boosting followed by heuristics listed under lexical token reduction, as introduced in Section~\ref{sub:SENLPback}.
 
-\textbf{1. Special word annotation}.
-Since the exiting NLP techniques rely on accurate annotation of POS tags in a sentence, the accuracy of \tool\ to infer constraints is dependent on the accurate annotation of POS tags.
-While existing techniques work well on general linguistics, that does not necessary entail that they work well with domain specific text as well.
-In particular, with respect to API documents certain words have a very different semantic meaning, in contrast to general linguistics that causes incorrect annotation of POS tags.
+From an implementation perspective, we manually built the domain dictionaries for the preprocessing using the glossary of terms collected from the websites pertaining to REST API.
+We further leveraged the HTML style information in \amazon\ to look for words that were highlighted in code like format.
+We further leveraged WordNet to maintain a static lookup table of shorthand words to aid named entity handling and abbreviation handling.
 
-Consider the word ``POST'' for instance.
-The online Oxford dictionary~\footnote{\url{http://oxforddictionaries.com/us/definition/american_english/post?q=POST}} has 8 different definition of word ``POST'', and none of them describes POST as a HTTP method supported by REST API meaning: \textit{``Creates a new entry in the collection.
-The new entry's URI is assigned automatically and is usually returned by the operation''}.
-Thus existing NLP techniques fail to accurately annotate the POS tags of the sentences involving word ``POST''.
-
-This preprocessing step identifies such words from the sentences based on a domain-specific dictionary, and annotates them appropriately.
-This special annotation forces the underlying POS tagger to accurately annotate the POS tags of the words involving domain specific keywords.
-
-From implementations perspective, we manually built the domain-specific dictionary using the glossary of terms collected from the web pertaining to REST API.
-We further leveraged the HTML style information in \amazon\ to look for words that were highlighted in code like format.
-
-\textbf{2. Lexical tokens reduction}.
-
-The reduction of lexical tokens greatly increases the accuracy of the analysis in the subsequent components of our framework.
-In particular, the preprocessor reduces lexical tokens by performing following subtasks
-
-\textbf{1.
-Period Handling}.
-Besides marking the end of a sentence in simplistic English, the character period (`.') has other legal usages as well such as decimal representation (periods between numbers).
-Although legal, such usage hinder detection of sentence boundaries, thus forcing the subsequent components to return incorrect or imprecise results.
-We pre-process the sentences by annotating these usages for accurate detection of sentence boundaries.
-We achieve so by looking up known shorthand words from WordNet~\cite{wordnet} and detecting decimals, which are also the period character, by using regular expressions.
-From an implementation perspective, we have maintained a static lookup table of shorthand words observed in WordNet.
-
-\textbf{2.
-Named Entity Handling}.
-Sometimes a sequence of words correspond to the name of entities that have a specific meaning collectively.
-For instance, consider the phrases \textit{``Amazon S3'', ``Amazon simple storage service''}, which are the names of the service.
-Further resolution of these phrases using grammatical syntax is unnecessary and would not bring forth any semantic value.
-Also these phrases contribute to length of a sentence that in turn negatively affects the accuracy of POS tagger.
-Thus, we identify such phrases and annotate them as single lexical units.
-We achieve so by maintaining a static lookup table.
-
-\textbf{3.
-Abbreviation Handling}.
-Natural-language sentences often consist of abbreviations mixed with text.
-This can result in subsequent components to incorrectly parse a sentence.
-We find such instances and annotate them as a single entity.
-For example, text followed by abbreviations such as \textit{``Access Control Lists (ACL)''} is treated as single lexical unit.
-Detecting such abbreviations is achieved by using the common structure of abbreviations and encoding such structures into regular expressions.
-Typically, regular expressions provide a reasonable approximation for handling abbreviations.
-
-\textbf{4.
-Frequent Phrases} Although the previous steps assist in bringing down the number of lexical tokens in a sentence, some sentences may still contain a considerable number of lexical tokens to overwhelm the underlying POS tagger.
-To address this issue we propose to further reduce the number of lexical tokens in a sentence  by annotating frequent phrases as a single lexical unit.
+Although the previous techniques and heuristics significantly lower the number of lexical tokens in a sentence, some sentences may still contain a considerable number of lexical tokens to overwhelm the POS tagger.
+To address this issue, we propose a novel technique (\textit{`Frequent Phrases Reduction'}) to further reduce the number of lexical tokens in a sentence by annotating frequent phrases as a single lexical unit.
 
@@
 We then prune the list of n-grams based on a subsumption. 
-We consider a n-gram of length k ($n_k$) to subsume n-gram of length k-1 ($n_{k-1}$) iff $n_{k-1}$ is a substring of ($n_k$) and the frequency of occurrence of $n_{k-1}$ equals frequency of occurrence of $n_{k}$ .
+We consider a n-gram of length k ($n_k$) to subsume n-gram of length k-1 ($n_{k-1}$) iff $n_{k-1}$ is a substring of ($n_k$) and the frequency of occurrence of $n_{k-1}$ equals frequency of occurrence of $n_{k}$.
 Finally, we rank the list of n-grams based on the frequency of their occurrence in the text, and select top-k n-grams for reduction.
@@
 
-Although a POS tagger can be retrained to achieve these pre-processing steps, we prefer annotations to make our approach independent of any specific NLP infrastructure, thus ensuring interoperability with various POS taggers.
+%Although a POS tagger can be retrained to achieve these pre-processing steps, we prefer annotations to make our approach independent of any specific NLP infrastructure, thus ensuring interoperability with various POS taggers.
 
@@
 
-The NLP parser accepts the pre-processed documents and annotates every sentence within each document using standard NLP techniques.
-From an implementation perspective, we chose the Stanford Parser~\cite{SNLP}.
+The NLP parser accepts the pre-processed documents and annotates every sentence within each document using core NLP techniques described in Section~\ref{sub:CoreNLPback}.
+From an implementation perspective, we chose the Stanford parser~\cite{SNLP}.
 However, this component can be implemented using any other existing NLP libraries or frameworks.
-In particular, we annotate each sentence with POS annotations, Named-Entity Annotations and Stanford-Typed Dependencies.
-For more details on these tehniques and their application, please refer to ~\cite{Marneffe06LREC,Marneffe08COLING,pandita12:inferring, pandita13:WHYPER}.
+In particular, we annotate each sentence with POS tags, named-entity Annotations and Stanford-typed dependencies.
+For more details on these techniques and their application, please refer to ~\cite{Marneffe06LREC, Marneffe08COLING, pandita12:inferring, pandita13:WHYPER, thummalapentaICSE12}.
 
@@
 %	\centering
-%%		\includegraphics[scale=0.6]{stanfordAnnotated.eps}
+%%		\includegraphics[scale=0.6]{StanfordAnnotated.eps}
 %	\caption{Sentence annotated with Stanford dependencies}
@@
 We define our representation as a tree structure that is essentially a First-Order-Logic (FOL) expression.
-Research literature provides evidence of the the adequacy of using FOL for NLP related analysis tasks~\cite{Sinha2009,Sinha2010,pandita12:inferring, pandita13:WHYPER}.
+Research literature provides evidence of the adequacy of using FOL for NLP related analysis tasks~\cite{Sinha2009,Sinha2010,pandita12:inferring, pandita13:WHYPER}.
 
@@
 
-In particular, the process of generation of intermediate-representation is an extension of the intermediate-representation generator component of \emph{WHYPER}~\cite{pandita13:WHYPER} with additional steps.
-In \emph{WHYPER}, the intermediate representation is generated based on principle of shallow parsing~\cite{Branimir2000}.
-They implemented their parser as a function of Stanford-typed dependencies~\cite{Marneffe06LREC,Marneffe08COLING,SNLP,KleinNIPS03}, to leverage the semantic information encoded in Stanford-typed dependencies.
+As described in Section~\ref{sub:SENLPback} the intermediate representation generation technique is based on the principle of shallow parsing~\cite{Branimir2000}. 
+In particular, the intermediate-representation technique is implemented as a function of Stanford-typed dependencies~\cite{Marneffe06LREC,Marneffe08COLING,SNLP,KleinNIPS03}, to leverage the semantic information encoded in Stanford-typed dependencies.
 
-However, we observed that intermediate-representation generator component of \emph{WHYPER}~\cite{pandita13:WHYPER} is overwhelmed by wordy sentences.This limitation mandates the use of additional novel technique of \textit{`Frequent Phrases Reduction'} in preprocessing phase.
-We further improve the accuracy of  parser by adopting a hybrid (leveraging both POS tags as well as Stanford-typed dependencies) approach.
+However, we observed that such implementation is overwhelmed by complex sentences.
+This limitation mandates the use of additional novel technique of \textit{`Frequent Phrases Reduction'} in preprocessing phase.
+We further improve the accuracy of intermediate-representation generation by proposing an hybrid approach, i.e. taking into consideration both the POS tags as well as Stanford-typed dependencies.
+The POS tags which annotate the syntactical structure of a sentence are used to further simplify the constituent elements in a sentence. 
+We then use the Stanford-typed dependencies that annotate the grammatical relationships between words to construct our FOL representation.
+Thus, the intermediate representation generator used in this work is two phase process as opposed to previous work~\cite{pandita12:inferring, pandita13:WHYPER}. 
+We next describe these two phases:
 
-Our implementation of shallow parser is a two phase process:
+\textbf{POS Tags}: We first parse a sentence based on the function of POS tags. 
+In particular, we use semantic templates to logically break a sentences into smaller constituent sentences. 
+For instance, consider the sentence:
 
-\begin{enumerate}
-	\item{\textbf{POS Tags}}: We first parse a sentence based on the function of POS tags.
-In particular, we use semantic templates to logically break a sentences into smaller constituent sentences.
-For instance, consider the sentence \scriptsize``All objects (including all object versions and Delete Markers) in the bucket must be deleted before the bucket itself can be deleted.''.
-\normalsize The Stanford parser inaccurately annotates the Stanford-typed dependencies of the sentence because of presence of different clauses acting on different subject-object pairs.
+\begin{center}
+\scriptsize``All objects (including all object versions and Delete Markers) in the bucket must be deleted before the bucket itself can be deleted.''. \normalsize
+\end{center}
+
+The Stanford parser inaccurately annotates the Stanford-typed dependencies of the sentence because of presence of different clauses acting on different subject-object pairs.
 We thus break down the sentence into two smaller tractable sentences:
 
-	 \scriptsize All objects in the bucket must be deleted before the bucket itself can be deleted.
+\begin{center}
+\scriptsize \textit{``All objects in the bucket must be deleted before the bucket itself can be deleted.}''
 
-	 All objects including all object versions and Delete Markers.\normalsize
+\textit{``All objects including all object versions and Delete Markers.''}\normalsize 
+\end{center}
 
-	 Table~\ref{tab:semanticTemplates} shows a list the semantic templates.
+Table~\ref{tab:semanticTemplates} shows a list the semantic templates used in this phase.
 Column ``Template'' describes conditions where the template is applicable and Column ``Summary'' describes the action taken by our shallow parser when the template is applicable.
 All of these semantic templates are publicly available on our project website~\cite{projectweb}.
-With respect to the previous example the template no.
-3 \textit{( A noun phrase followed by another noun/pronoun/verb phrase in brackets)} is applicable.
+With respect to the previous example the template no. 3 \textit{( A noun phrase followed by another noun/pronoun/verb phrase in brackets)} is applicable.
 Thus our shallow parser breaks the sentence into two individual sentences.
 
-	\item{\textbf{Stanford-typed Dependencies}}: This phase is equivalent to the intermediate-representation generator component of the \emph{WHYPER}~\cite{pandita13:WHYPER}.
+\textbf{Stanford-typed Dependencies}: This phase is equivalent to the intermediate-representation technique described in Section~\ref{sub:SENLPback}.
 
-\end{enumerate}
+\subsection{Specification Extractor}
+\label{sub:SE}
+
+This component accepts the FOL representation of the sentence.
+
+\begin{itemize}
+\item Extracts Specifications from FOL representation. 
+\item Specifically looking for modal modifies ``can, could, may, must, should'' 
+\item Takes into consideration the negative quantifiers.
+\item Algorithm to infer the sequence of operations.
+\end{itemize}
+
+\subsection{Postprocessor}
+\label{sub:postpro}
+undoing pre-processing and Hybrid intermediate representation generation.
 
@@
 \end{table*}
+
+\subsection{Semantic-Graph Generator}
+\label{sub:ACA}
+
+A key way of identifying reference to a method within the API in our proposed framework is the employment of a semantic graph of an API.
+In particular, we propose to initially infer such graphs from API documents.
+Manually creating a semantic graph is prohibitively time consuming and may be error prone.
+We thus employ a systematic methodology (proposed previously in ~\cite{pandita13:WHYPER}) to infer such semantic graphs from API documents that can potentially be automated.
+We first consider the name of the class.
+We then find the synonyms terms used refer to the class in question.
+The synonym terms are listed as by breaking down the camel-case notation in the class name.
+This list is further augmented by listing the name of the parent classes and implemented interfaces if any.
+
+\begin{figure}
+	\centering
+		\includegraphics[scale=0.4]{KnowledgeGraph.eps}
+	\caption{Semantic Graph for the \CodeIn{BufferedInputStream} class in Java}
+	\label{fig:knowledge}
+\end{figure}
+
+We then systematically inspect the member methods to identify actions applicable to the objects represented by the class.
+From the name of a public method (describing a possible action on the object), we extract verb phrases.
+The verb phrases are used as the associated actions applicable on the object.
+For instance, \CodeIn{BufferedInputReader} defines operations available, close, mark, and so on.
+We associate these operations with the objects of type \CodeIn{BufferedInputReader}.
+Figure~\ref{fig:knowledge} shows a sub-graph of  graph for \CodeIn{BufferedInputReader} class.
+The phrases in solid rectangles are synonyms of the class name \CodeIn{BufferedInputReader}.
+The phrases in rounded rectangle are the actions applicable on \CodeIn{BufferedInputReader} class.
+
+\algsetup{indent=1em}
+\begin{algorithm}[t!]
+\begin{algorithmic}[1]
+\begin{scriptsize}
+\REQUIRE K\_Graph $g$, FOL\_rep $rep$ 
+\ENSURE String $action$
+\STATE $String\ action\ =\ \phi$
+\STATE $List\ r\_name\_list\ =\ g.resource\_Names$
+\STATE $FOL\_rep\ r'\ =\ rep.findLeafContaining(r\_nam\_list)$
+\STATE $List\ actionList\ =\ g.actionList$
+\WHILE{$(r'.hasParent)$}
+	\IF{$actionList.contains(r'.parent.predicate)$}
+		\STATE $action\ =\ actionList.matching(r'.parent.predicate)$
+		\STATE $break$
+	\ELSE
+		\IF{$actionList.contains(r'.leftSibling.predicate)$}
+			\STATE $action\ =\ actionList.matching(r'.leftSibling.predicate)$
+			\STATE $break$
+		\ENDIF
+	\ENDIF
+	\STATE $r'\ =\ r'.parent$
+\ENDWHILE
+\RETURN $action$
+\end{scriptsize}
+\end{algorithmic}
+\caption{Action\_Extractor}
+\label{alg:SenAnnotaator}
+\end{algorithm}
+
+\begin{algorithm}[t!]
+\begin{algorithmic}[1]
+\begin{scriptsize}
+\REQUIRE List $methodList$ 
+\ENSURE Graph $seq\_Graph$
+\STATE $Graph\ seq\_Graph\ =\ \phi$
+\STATE $Map\ idx\ = createIdx(methodList)$
+
+\FORALL{$Method\ mtd\ in\ methodList$} 
+	\STATE $seq\_Graph.addVertex(mtd)$
+\ENDFOR
+
+\FORALL{$Method\ mtd\ in\ methodList$} 
+	\IF{$mtd.isPublic()$}
+		\IF{$!mtd.isStatic()$}
+			\STATE $List\ preList\ =\ idx.query(mtd.declaringType)$
+			\FORALL{$Method\ mtd'\ in\ preList$}
+				\STATE $seq\_Graph.addEdge(mtd',mtd)$
+			\ENDFOR
+		\ENDIF
+		\FORALL{$Parameter\ param\ in\ mtd.getParameters()$}
+			\IF{$!isBasicType(param.Type)$}
+				\STATE $List\ preList\ =\ idx.query(paramType)$
+				\FORALL{$Method\ mtd'\ in\ preList$}
+					\STATE $seq\_Graph.addEdge(mtd',mtd)$
+				\ENDFOR				
+			\ENDIF
+		\ENDFOR
+	\ENDIF
+\ENDFOR
+\RETURN $seq\_Graph$
+\end{scriptsize}
+\end{algorithmic}
+\caption{Type\_Sequence\_Builder}
+\label{alg:SeqAnnotaator}
+\end{algorithm}
 
@@
 %
-%\algsetup{indent=1em}
-%\begin{algorithm}[t!]
-%\begin{algorithmic}[1]
-%\begin{scriptsize}
-%\REQUIRE K\_Graph $g$, FOL\_rep $rep$, Boolean $recursion$ 
-%\ENSURE Boolean $isPStmt$
-%\STATE $Boolean\ isPStmt\ =\ false$
-%\STATE $String\ r\_name\ =\ g.resource\_Name$
-%\STATE $FOL\_rep\ r'\ =\ rep.findLeafContaining(r\_name)$
-%\STATE $List\ actionList\ =\ g.actionList$
-%\WHILE{$(r'.hasParent)$}
-%	\IF{$actionList.contains(r'.parent.predicate)$}
-%		\STATE $isPStmt\ =\ true$
-%		\STATE $break$
-%	\ELSE
-%		\IF{$actionList.contains(r'.leftSibling.predicate)$}
-%			\STATE $isPStmt\ =\ true$
-%			\STATE $break$
-%		\ENDIF
-%	\ENDIF
-%	\STATE $r'\ =\ r'.parent$
-%\ENDWHILE
-%\IF{$((NOT(isPStmt))\ AND\ recursion)$}
-%	\STATE $List\ resourceList\ =\ g.resourceList$
-%	\FORALL{$(Resource\ res\ in\ resourceList)$}
-%		\STATE $isPStmt\ =\ Sentence\_Annotator(getKGraph(res),\ rep,\ false)$
-%		\IF{$isPStmt$}
-%			\STATE $break$
-%		\ENDIF
-%	\ENDFOR
-%\ENDIF
-%\RETURN $isPStmt$
-%\end{scriptsize}
-%\end{algorithmic}
-%\caption{Sentence\_Annotator}
-%\label{alg:SenAnnotaator}
-%\end{algorithm} 
-%
-%\begin{figure}
-%	\centering
-%%		\includegraphics[scale=0.4]{knowledge.eps}
-%	\caption{Semantic Graph for the READ\_CONTACT permission}
-%	\label{fig:knowledge}
-%\end{figure} 
-%  
-%
-%

### 2014-01-16 Draft/background.tex
added new version

@@
 
-Although, well suited for human communication, converting natural language into unambiguous specifications that can be processed and understood by computers is very difficult.
-Recently, a lot of exciting work has been carried out in the area of Natural Language Processing (NLP), with existing NLP techniques proving to be fairly accurate in highlighting grammatical structure of a natural language sentence.
+Natural language is well suited for human communication, but converting natural language into unambiguous specifications that can be processed and understood by computers is difficult.
+However, research advances~\cite{Marneffe06LREC,Marneffe08COLING,Klein03,KleinNIPS03} have increased the accuracy of existing NLP techniques to annotate the grammatical structure of a sentence.
+These advances in NLP have inspired researchers/practitioners~\cite{pandita12:inferring, pandita13:WHYPER, johnSlankasPASSAT13, XiaoFSE2012, thummalapentaICSE12} to adapt/apply NLP techniques to solve problems in software engineering domain.
+
+In particular, this work proposes novel techniques on top of previously proposed techniques~\cite{pandita12:inferring, pandita13:WHYPER} to demonstrate the effectiveness of applying NLP on API documents.
+We next briefly introduce the techniques used in this work that have been grouped into broad categories.
+We first introduce the core NLP techniques used in this work.
+We then introduce the software engineering specific NLP techniques proposed in previous work~\cite{pandita12:inferring,pandita13:WHYPER} that have been used in this work.
+
+\subsection{Core NLP techniques}
+\label{sub:CoreNLPback}
+
+%Recently, a lot of exciting work has been carried out in the area of Natural Language Processing (NLP), with existing NLP techniques proving to be fairly accurate in highlighting grammatical structure of a natural language sentence.
 However, existing NLP techniques are still in the processing phase and not in understanding phase.
@@
 
-\textbf{Phrase and clause parsing}.
+\textbf{Phrase and Clause Parsing}.
 Also known as chunking, this technique divides a sentence into a constituent set of words (or phrases) that logically belong together (such as a Noun Phrase and Verb Phrase).
@@
 These techniques are useful for extracting information; especially if the information encompasses many sentences in a document.
+
+\subsection{Software engineering specific NLP techniques}
+\label{sub:SENLPback}
+
+\textbf{Noun Boosting}~\cite{pandita12:inferring}. Accurate annotation of POS tags in a sentence is fundamental to effectiveness of any advanced NLP technique.
+However, as mentioned earlier, POS tagging work well on well written news articles which does not necessary entail that they work well with domain specific text as well.
+Thus, noun boosting is a necessary precursor to application of POS tagging on domain specific text.
+In particular, with respect to API documents certain words have a very different semantic meaning, in contrast to general linguistics that causes incorrect annotation of POS tags.
+
+Consider the word \CodeIn{POST} for instance. 
+The online Oxford dictionary~\footnote{\url{http://oxforddictionaries.com/us/definition/american_english/post?q=POST}} has 8 different definition of word \CodeIn{POST}, and none of them describes \CodeIn{POST} as a HTTP method
+~\footnote{In HTTP vocabulary \CodeIn{POST} means: ''Creates a new entry in the collection.
+The new entry's URI is assigned automatically and is usually returned by the operation''}
+supported by REST API.
+Thus existing POS tagging techniques fail to accurately annotate the POS tags of the sentences involving word \CodeIn{POST}.
+
+Noun Boosting identifies such words from the sentences based on a domain-specific dictionaries, and annotates them appropriately.
+The annotation assists the POS tagger to accurately annotate the POS tags of the words thus inturn increasing accuracy of advanced NLP techniques such as chunking and typed dependency annotation.
+
+\textbf{Lexical Token Reduction}~\cite{pandita13:WHYPER}.
+These are a group of generic preprocessing heuristics to further improve the accuracy of core NLP techniques.
+The accuracy of core NLP techniques is inversely proportional to the number of lexical tokens in a sentence.
+Thus, the reduction in the number of lexical tokens greatly increases the accuracy of core NLP techniques. 
+In particular, following heuristics have been used in previous work to achieve the desired reduction of lexical tokens:
+
+\begin{itemize}
+
+\item \textbf{Period Handling}.
+Besides marking the end of a sentence in simplistic English, the character period (`.') has other legal usages as well such as decimal representation (periods between numbers).
+Although legal, such usage hinder detection of sentence boundaries, thus causing core NLP techniques to return incorrect or imprecise results.
+The text is pre-processed by annotating these usages for accurate detection of sentence boundaries.
+
+\item \textbf{Named Entity Handling}. Sometimes a sequence of words correspond to the name of entities that have a specific meaning collectively.
+For instance, consider the phrases \textit{``Amazon S3'', ``Amazon simple storage service''}, which are the names of the service.
+Further resolution of these phrases using grammatical syntax is unnecessary and would not bring forth any semantic value.
+Also these phrases contribute to length of a sentence that in turn negatively affects the accuracy of core NLP techniques.
+This heuristic annotates the phrase representing the name of the entities as a single lexical token.
+
+\item \textbf{Abbreviation Handling}. Natural-language sentences often consist of abbreviations mixed with text.
+This can result in subsequent components to incorrectly parse a sentence.
+This heuristic finds such instances and annotates them as a single lexical unit.
+For example, text followed by abbreviations such as \textit{``Access Control Lists (ACL)''} is treated as single lexical unit.
+Detecting such abbreviations is achieved by using the common structure of abbreviations and encoding such structures into regular expressions.
+Typically, regular expressions provide a reasonable approximation for handling abbreviations.
+
+\end{itemize}
+
+\textbf{Intermediate-Representation Generation}~\cite{pandita13:WHYPER}.
+This technique accepts the syntax-annotated sentences and builds a First-Order-Logic(FOL) representation of the sentence.
+Earlier researches have shown the adequacy using FOL for NLP related analysis tasks~\cite{Sinha2009,Sinha2010,pandita12:inferring}.
+In particular, WHYPER~\cite{pandita13:WHYPER} demonstrates the effectiveness of this technique, by constructing an intermediate representation generator based on shallow parsing~\cite{Branimir2000} techniques.
+The shallow parser itself is implemented as sequence of cascading finite state machines based on the functions of stanford-typed dependencies~\cite{Marneffe06LREC,Marneffe08COLING,Klein03,KleinNIPS03}.
+
+In next section we describe our proposed generic approach to infer constraints from API documents.

### 2014-01-16 Draft/conclusion.tex
added new version

@@
 
-%API documents provide specification information about how to use a particular method within a class by means of method descriptions.
-However, specifications described in natural Language in API documents are not amenable to formal verification by existing verification tools.
-
-%Specifications described in natural language in API documents are not amenable to formal verification by existing verification tools.
-In this paper, we have presented a novel approach for inferring formal specifications from API documents targeted towards code contract generation.
-Our evaluation results show that our approach has an average of 92\% precision and 93\% recall in identifying sentences describing code contracts from over 2500 sentences.
-Furthermore, our results also show that our approach has an average of 83.4\% accuracy in inferring specifications from sentences describing code contracts out of over 1600 sentences.
+Although highly desirable, most API's do not have formal specifications.
+In contrast documentation of methods contain detailed specifications of the usage in natural language text.
+However, formal analysis tools are not designed to work on specifications in natural languages.
+Manually writing formal specifications based on natural language text in API documents is prohibitively time consuming and error prone.
+To address this issue, we proposed a novel approach \tool\ to infer temporal constraints from natural language text of API documents.
+We applied \tool\ to infer temporal constraints from 
+commonly used package \CodeIn{java.io} from JDK API and Amazon S3 REST API.
+Our evaluation results show that \tool\ achieves an average of PP\% precision and RR\% recall
+in inferring TT temporal constraints from more than ZZZZ sentences of API documents.

### 2014-01-16 Draft/example.tex
added new version

@@
-\section{Examples}
+\section{Motivating Example}
 \label{sec:example}
 
-%We now present a series progressing in complexity to demonstrate our approach.
-Our examples are from real Java Platform, Micro Edition (JME) formerly known as J2ME and Android API.
-Both JME and Android use Java as the language of implementation and targeted towards hand-held devices.
-However, our approach is independent of language of implementation and thus can be used for any similar source and target API.
-
-%First we parse the API documents of source and target API library and store it in intermediate representation for analysis.
-In particular, we extract class, interface and corresponding method descriptions from API documents.
-Second, we then create a term vector representation of each class description and method descriptions.
-Vector space model or term vector model is an algebraic model for representing text documents (and any objects, in general) as vectors of identifiers, such as, for example, index terms.
-In our case, each word is considered as a term barring the stop words such as (a, the, and ...).
-
-%Finally we use the term vector representation of a method description in a source API to query term vector representation of the the method description in target API.
-The results are ranked based on the Term Frequency-Inverse Document Frequency (TF-IDF) measure.
-TF-IDF is a numerical statistic which reflects how important a word is to a document in a collection or corpus.
-It is often used as a weighting factor in information retrieval and text mining.
-
-%We then collect the top 10 results from target API methods for each source API method.
-Figure~\ref{fig:excpAPIJ2ME} and Figure~\ref{fig:excpAPIAndroid} shows example of trivially similar API methods.
-Our search results return the Android API method shown in Figure~\ref{fig:excpAPIAndroid} as a first match for the JME method shown in Figure~\ref{fig:excpAPIJ2ME}.
-Notice the slightly different description for the methods in JME and Android API.
-Although, correct this is very trivial mapping.
-We next present a more complex example.
+We now present some real world examples to motivate our approach.
+In particular, through these examples we demonstrate that developers often overlook the documentation.
+Thus, the resultant system is inconsistent with the intentions that a developer had in mind initially.
+This inconsistency oftentimes result in undesirable consequences ranging from developer frustration, customer dissatisfaction, to actual financial losses.
 
 \begin{figure}[t]
-\begin{CodeOut}
-\begin{alltt}
+\begin{center}
 \includegraphics[scale=0.4]{Stackoverflow.eps}
-\end{alltt}
-\end{CodeOut}
+\end{center}
 \caption{\label{fig:Stackoverflow} The Query posted on Stackoverflow form regrading Amazon S3 REST API}
@@
 
+For example consider the question asked in \textit{Stack Overflow}~\footnote{\url{http://stackoverflow.com/}} as shown in Figure~\ref{fig:Stackoverflow}.
+Stack Overflow is a question and answer site for professional and enthusiast programmers.
+The query is about the delete functionality of a third-party software \CodeIn{S3Fox} to interact with \amazonAPI.
+In particular, the query complains about an issue in delete bucket functionality of the \CodeIn{S3Fox}.
+In particular, the issue was because the \CodeIn{S3Fox} developers overlooked the specifications in \amazon.
+Figure~\ref{fig:AmzonS3DeleteBucketAPI} shows the documentation of delete bucket method.
+The documents clearly states (outlined in red for clarity) that before deleting the bucket the objects in the buckets must be deleted.
+Although the issue was fixed but notice that the response on the \textit{Stack Overflow} encouraged the person asking query to switch to another product, thus potentially resulting in a loss of revenue attributed to customer dissatisfaction.
+
 \begin{figure}[t]
-\begin{CodeOut}
-\begin{alltt}
+\begin{center}
 \includegraphics[scale=0.4]{AmzonS3DeleteBucketAPI.eps}
-\end{alltt}
-\end{CodeOut}
+\end{center}
 \caption{\label{fig:AmzonS3DeleteBucketAPI} The online API document for \CodeIn{DELETE Bucket} operation in Amazon S3 REST API}
@@
 
-%Figure~\ref{fig:drawCharAPIJ2ME} and Figure~\ref{fig:drawTextAPIJ2ME} shows example of non-trivially similar API methods.
-Although, the textual description is similar using text analytics (TF-IDF similarity using term frequency vector), there is difference in type of arguments.
+In yet another example a developer points out the financial losses he suffered because he was incorrectly using the previously described delete bucket functionality as shown in Figure~\ref{fig:example2}.
+The problems in the previously described examples could have been alleviated if developers paid more attention to the documentation.
+However, as pointed out by Novick et.
+al~\cite{Novick2006WDP} that developers often overlook the documentation.
+Furthermore, since these documents are written in natural language they cannot be subjected to machine based verification.
+Thus, there is need for an approach to translate the constraints described in natural language into a more formal notation.
+Although, we only use examples from the developer forums and blogs for \amazon\ to motivate our approach.
+In next section, we briefly discuss the related work in this area.
+
+\begin{figure}[t]
+\begin{center}
+\includegraphics[scale=0.4]{Example2.eps}
+\end{center}
+\caption{\label{fig:example2} The experience article posted by a developer regarding Amazon S3 REST API}
+\end{figure}

### 2014-01-16 Draft/introduction.tex
added new version

@@
 
-%These constraints are mainly expressed in natural language in the service documentation.
-A widely-adopted strategy [7] by developers to build correct client applications is to first read through the service documentation, trying to memorize the constraints, and then develop client applications accordingly.
-However, conformance to constraints cannot be assured.
-In fact, a recent study [14] showed that developers may still make mistakes even when they have been rather familiar with the documentation.
-%
-%
-%Therefore, it is desirable that client applications are formally verified against these constraints, and violations of each constraint are detected as bugs.
-However, these verification techniques [8, 9, 14] require formally specified constraints, which are often not readily available, due to the large amount of effort needed to manually specify them.
-For example, it took one of the authors more than 10 hours to only browse the documentation of the Ebay2 web service operation “AddFixedPriceItem”, let alone the time needed to extract and formalize the constraints
-%
-%To address these shortcomings we propose a different approach for inferring likely mapping between API's.
-In particular, we propose the use of Natural Language processing of API documents to infer such mapping.
-%
-%  
-%API documentation provides developers with useful information about class/interface hierarchies within the software.
-Additionally, API documents also provides information about how to use a particular method within a class by means of method descriptions.
-Method descriptions typically describe specifications in terms of the expectations of the method arguments and functionality of method in general.
-%
-%
-%We plan to leverage these method descriptions to find the likely mapping.
-However, it is not trivial to use natural langauge processing on API documents to infer likely mappings.
-In particular, our technique addresses the following technical challenges to infer likely mappings:
-%
-%\begin{enumerate}
-%	\item \textit{Programming Keywords}.
-Method descriptions often contain programming keywords (e.g., \CodeIn{true, null, buffer}), which have a different meaning in the context of programs, in contrast to general linguistics.
-For instance,\textit{``This method also returns false if path is null''}.
-In this sentence, words `false' and `null' are nouns in the context of object-oriented languages such as Java and C\#, whereas in general linguistics these words are adjectives.
-Thus, these keywords need to be handled differently.
-%		
-%	\item \textit{Semantic Equivalence}.
-A legal usage in natural language can be described in different words and semantic structures.
-For instance, consider the following two fragments that describe the similar functionality specification: \textit{``Flushes this data output stream.
-This forces any buffered output bytes to be written out to the stream.'}' and \textit{``Writes buffered data to the target stream and calls the flush method of the target stream.''}.
-Thus, there is a need to identify the semantic equivalence of legal usage described in different ways.
-%		
-%		To address this challenge, we propose a new technique called \textit{equivalence analysis} based on identified grammatical relationships (main nouns and verbs) of a sentence.
-%	
-%	\item \textit {Partial Functionality}.
-There are significant number of cases when the functionality in a source API method is broken across multiple methods in target API.
-For instance \CodeIn{Graphics.drawChar()} method in J2ME API is mapped to methods \CodeIn{Paint.setColor();Canvas.drawText()}in Android API.
-%	
-%		To address this challenge, we propose a lightweight \CodeIn{Type} analysis.
-%		
-%\end{enumerate}
-%
-%
-%
-%
-%In summary, our approach leverages natural language description of API's to infer likely mapping thus facilitating cross API migration of applications.
-As our approach analyzes API documents in natural language, it can be reused independent of the programming language of the library.
-To the best of our knowledge, ours is the first approach that analyzes natural language API descriptions to infer likely mapping across API's.
-%
-%Our paper makes the following major contributions:
-%\begin{itemize}
-%	\item A technique that effectively infers mapping across source and target API.
-%	\item A prototype implementation of our approach based on extending the Stanford Parser~\cite{SNLP,SNLP1}, which is a natural language parser to derive the grammatical structure of sentences.
-An open source implementation of our prototype can be found at our website\footnote{\url{http://research.csc.ncsu.edu/ase/projects/pint/}}.
-%	\item An evaluation of our approach on J2ME and Android API
-%\end{itemize}
+% Introduction needs to tightned up a bit
+% Paragraph about typed languages must be moved to background or methodology
+% Example might appropriately go in background as well
+% Try to fit the goal statement in the introduction
+% too long an abstract
+% Names of exact tools and citations to them for verification
+% Over use of however,
+% J2EE document seems to be out of place
+
+Specifications of using an Application Programming Interface (API) of a library play an important role in software reuse.
+In addition to guiding the development process by outlining what and how to reuse, 
+usage specifications also help in verification process by allowing quality assurance practitioners to test the expected outcome.
+Furthermore, if the specifications are formal (machine-readable such as code-contracts),
+they can be used in conjunction with the formal analysis tools such as model checkers and runtime verifiers
+to automatically reason about the quality of the software.
+
+%Formal specifications of an Application Programming Interface (API) usage are highly desirable.
+%because they are the precursor to the formal analysis tools such as model checkers and runtime verifiers.
+
+However, most API's do not have formal specifications.
+In contrast, API developers commonly describe correct usage in natural language text in API documents.
+Typically, such documents are provided to client-code developers through online access, or are shipped with the API code.
+For example, J2EE's API documentation\footnote{\url{http:\\download.oracle.com/javaee/1.7/api/}} is one of the popular API documents.
+Typically, an API document will describe the both the constraints on that method parameters as well as the constraints in terms of the methods the must be invoked pre/post the current method.
+However, formal analysis tools are not designed to work on specifications written in natural languages.
+
+%May be strike out the first sentence 
+%May be strike out the term prohibitevely
+
+A na{\"i}ve solution to address the issue, is to manually convert the natural language API description into formal specifications. 
+However, manually writing formal specifications based on natural language text in API documents can be prohibitively time consuming and error prone~\cite{wu2013inferring,RubingerWEB10}. 
+For instance, Wu et al.~\cite{wu2013inferring} report that it took one of the authors more than 10 hours to browse the documentation of one method of a web Service API, even before they attempted to formalize the constraints on the method.
+
+%Strike out ``To address the aforementioned issue''
+To address the aforementioned issue, we propose a novel approach to infer usage constraints from natural language text of API documents.
+We propose new techniques that apply Natural Language Processing (NLP) on natural language text API documents to automatically infer usage constraints.
+In particular, we focus on specific type of constraints namely temporal constraints.
+A generic temporal relation is defined as \textit{an interpropositional relation that communicates the simultaneity or ordering in time of events or states.}
+In terms of API method invocations, we interpret temporal relationships as \textit{`the allowed sequence of invocations of methods'}.
+For example, consider the following statement in \amazonAPI\ ``You must initiate a multipart upload before you can upload any part.''
+This statement can be interpreted as multipart-upload method must be invoked before invoking any part-upload method in the API.
+
+%Move this paragraph to later sections or may be push later in intro
+% make example flow in next paragraph
+% Make consistent terminology approach or technique 
+Although, in typed languages some sequencing constraints are enforced by type system. 
+For instances a method ($m$) accepting input parameter ($i$) of type ($t$) mandates that (at least one) method ($m'$) be invoked whose return value is of type ($t$).  
+However, most temporal constraints are not limited by the type definitions (i.e, requirements on the type of input parameters),
+and are currently expressed mostly in natural language in API documents, as described in the example previously.
+In a manual investigation, we observed that roughly 12\% of the sentences describing some sort of specification constraints in \amazonAPI\ documentations are temporal constraints related.
+%Background on out of how many sentences
+
+% Combine first two sentences
+% In contrast, temporal constraints are beyond these parameter constraints. may be use difficult to express using parameter constraints
+% Amazon S3 is popularly used web service for simple cloud based storage
+Most of the existing approaches focus in inferring method pre-post conditions~\cite{Henkel07discoveringdocumentation,Ghezzi:2009:SIB:1555001.1555057,Henkel:2008:DDA:1363102.1363105,Flanagan:2001:HAA:647540.730008,Buse:2008:ADI:1390630.1390664} in terms of parameter constraints either using static or dynamic analysis techniques.
+Furthermore, there is a class of NLP based approaches~\cite{pandita12:inferring, wu2013inferring} that infer constraints from API documents.
+However, similar to static and dynamic analysis techniques these approaches focus on parameter constraints as well.  
+In contrast, temporal constraints are beyond these parameter constraints.
+Temporal constraints, in general focus on rules related to orchestration of methods within an API rather than focusing on the requirements on the input parameters of these methods.   
+In particular, our proposed techniques address the following challenges to infer temporal constraints automatically from natural language text.
+
+First, relying just on type information will result in a incomplete list of temporal constraints. 
+Furthermore, such constraints although valuable but are already checked by any advanced Integrated Development Environment(IDE) such as eclipse
+for a strongly typed language.
+The problem is exacerbated in web based API's such as \amazonAPI\ where most of the types are either \CodeIn{integer} or \CodeIn{strings}.
+
+%identified in previous work~\cite{pandita12:inferring} delete and leave the reference
+% Add a sentnce stating that we extend previous technique to address the issues 
+Second, inferring temporal constraints from the natural language text itself is challenging. 
+There are existing challenges in NLP for software engineering domain namely \textit{ambiguity}, \textit{programming keywords}, and \textit{semantic equivalence} identified in previous work~\cite{pandita12:inferring}.
+In addition to these challenges, we have an added challenge of identifying the method referenced in the natural language text to infer temporal constraint.
+Recall, the description sentence ``You must initiate a multipart upload before you can upload any part.''
+In this sentence, phrases ``multipart upload'' and ``upload any part'' refer to individual methods in the API.
+Identifying these phrases as method invocation instances require domain dictionaries.
+Ad-hoc constructing these dictionaries is prohibitively time and resources intensive.
+To address this challenge we propose to build domain-dictionaries systematically from API documents themselves.
+
+%Furthermore, I propose to evaluate the effectiveness of proposed work on real world API's: 1) Java 7 and 2) Amazon S3 REST API.
+The former is generic language API, while the later is a web based API directed towards cloud-based data storage.
+The temporal constraints inferred for Java 7 will be compared with the existing approaches to evaluate the effectiveness of proposed work.
+In contrast, Amazon S3 REST API (relatively recent) representative of the class of API's where neither source code of API nor enough usage examples are available.
+
+%To evaluate our proposed approach, we applied \tool\ to infer temporal constraints from 
+%commonly used package \CodeIn{java.io} from JDK API and Amazon S3 REST API.
+%Our evaluation results show that \tool\ achieves an average of PP\% precision and RR\% recall
+%in inferring TT temporal constraints from more than ZZZZ sentences of API documents.
+
+%Software reuse is commonly practiced since the advent of software development~\cite{FrakesIEEETran05}.
+Software reuse facilitates development of larger, more complex, and timely-delivered software systems~\cite{GaffneySE92}.
+To determine what and how to reuse, specifications of reusable software libraries play an important role.
+In the absence of specifications, developers may write code that is inconsistent with the expectations of libraries.
+As a result, not only such code is of inferior quality and contains faults, the added cost of debugging and correcting such faulty code could also defeat the purpose of reusing software.
+
+% talk about mining approaches 
+In summary, the proposed work leverages natural language description of API's to infer temporal constraints of method invocations.
+As the proposed work analyzes API documents in natural language, it can be reused independent of the programming language of the library.
+Additionally, our approach complements existing mining based approaches~\cite{buse2012synthesizing, thummalapenta07parseweb, Wang:2013:MSR, Zhong:2009:MMR} that partially address the problem by mining for common usage patterns.
+The proposed work in general, makes the following contributions:
+%However, all of these approaches rely on the availability of the source code that use API methods under investigation.
+%Furthermore, these approaches are limited by both the quantity as well as quality of data set (source code) available.
+%To address the limitation we propose to extend the natural language infrastructure developed previously~\cite{pandita12:inferring,pandita2013whyper} to focus specifically on the temporal constraints.
+
+%Use consistent term technique or approach
+%Methodology for generating domain dictionaries 
+\begin{itemize}
+	\item A NLP based approach that infers temporal constraints of method invocations.
+	\item A prototype implementation of our approach based on extending the Stanford Parser~\cite{Klein03,SNLP1}, which is a natural language parser to derive the grammatical structure of sentences.
+	An open source implementation of the prototype will be made available publicly. 
+	\item An evaluation of proposed approach on Java 7 and Amazon S3 REST API
+\end{itemize}
 
 The rest of the paper is organized as follows.
+Section~\ref{sec:example} presents an real world examples that motivate our approach.
+Section~\ref{sec:related} discusses related work in this area.
 Section~\ref{sec:background} presents the  background on code contracts as well as NLP.
-Section~\ref{sec:example} presents an real world examples that motivate our approach.
 Section~\ref{sec:approach} presents our approach.
@@
 Section~\ref{sec:discussion} presents a brief discussion and future work.
-Section~\ref{sec:related} discusses related work.
 Finally, Section~\ref{sec:conclusion} concludes.
+
+% how well does the NLP based technique augument the type based temporal constraints

### 2014-01-16 Draft/related.tex
added new version

@@
 
+// "In contrast" switch up the wording a little bit
+
+Our proposed approach touches a few research areas such as software verification,  NLP on software engineering artifacts, and document augmentation.
+We next discuss relevant work pertinent to our proposed approach in these areas.
+
+\textbf{Code Contracts - Formal Specifications}
+// Define temporal constraints distinction
 Design by contracts has been an influential concept in the area of software engineering in the past decade.
 A significant amount of work has been done in automated inference of code contracts.
-There are existing approaches that statically or dynamically extract code contracts~\cite{csallner08dysy, NimmerE02:ISSTA, Tillmann:2006:DLM:2105385.2105433}.
-However, a combination of developer written and automatically inferred contracts seems to be the most effective approach~\cite{FrakesIEEETran05,Polikarpova2009ISSTA}.
-Since developers describe the specifications in the method descriptions, we believe that our approach can work in conjunction with existing approaches towards extracting a comprehensive set of code contracts for a method.
-Furthermore, Wei et al.~\cite{WeiICSE11}demonstrated that dynamic contract inference performed better when provided with an initial set of seed contracts.
+There are existing approaches that statically or dynamically extract code contracts~\cite{csallner08dysy,NimmerE02:ISSTA,Tillmann:2006:DLM:2105385.2105433}.
+However, a combination of developer written and automatically inferred contracts seems to be the most effective approach~\cite{Polikarpova2009ISSTA,Flanagan:2001:HAA:647540.730008}.
+Furthermore, there are existing approaches that infer code-contract-like specifications (such as behavioral model, algebraic specifications, and exception specifications) either dynamically\cite{Henkel07discoveringdocumentation,Ghezzi:2009:SIB:1555001.1555057,Henkel:2008:DDA:1363102.1363105} or statically~\cite{Flanagan:2001:HAA:647540.730008,Buse:2008:ADI:1390630.1390664} from source code and binaries.
+In contrast, the approach presented in this work infers specifications from the natural language text in API documents, thus complementing these existing approaches when the source code or binaries of the API library is not available.
 
-There are existing approaches that infer code-contract-like specifications (such as behavioral model, algebraic specifications, and exception specifications) either dynamically~\cite{Ghezzi:2009:SIB:1555001.1555057,Henkel07documentation,Henkel:2008:DDA:1363102.1363105} or statically~\cite{Buse:2008:ADI:1390630.1390664,FrakesIEEETran05} from source code and binaries.
-In contrast, our approach infers specifications from the natural language text in API documents, thus complementing these existing approaches when the source code or binaries of the API library is not available.
+\textbf{NLP in Software Engineering}
 
 NLP techniques are increasingly applied in the software engineering domain.
-NLP techniques have been shown to be useful in requirements engineering~\cite{Gervasi2005,Sinha2009,Sinha2010}, usability of API documents~\cite{Dekel2009}, and other areas~\cite{Little2009,Zhou2008}.
-We next describe most relevant approaches.
+NLP techniques have been shown to be useful in requirements engineering ~\cite{Sinha2009,Sinha2010,Gervasi2005}, usability of API documents~\cite{Dekel2009}, and other areas~\cite{Zhou2008,Little2009,pandita13:WHYPER}.
+We next describe the most relevant approaches.
 
-Xiao et al.~\cite{XiaoFSE2012} use shallow parsing techniques to infer Access Control Policy (ACP) rules from natural language text in use cases.
-The use of shallow parsing techniques works well on natural language texts in use cases, owing to well formed nature of sentences in use case descriptions.
+\textit{1.
+Access Control Policies}: Xiao et al.~\cite{XiaoFSE2012} and Slankas et al.~\cite{johnSlankasPASSAT13} use shallow parsing techniques to infer Access Control Policy (ACP) rules from natural language text in use cases.
+The use of shallow parsing techniques works well on natural language texts in use cases, owing to well formed structure of sentences in use case descriptions.
 In contrast, often the sentences in API documents are not well formed.
-Additionally, their approach does not deal with programming keywords or identifiers, which are often mixed within the method descriptions in API documents.
+Additionally, these approaches do not deal with programming keywords or identifiers, which are often mixed within the method descriptions in API documents.
 
-\
-~\cite{pandita12:inferring}
-~\cite{pandita13:WHYPER}
-
-Zhong et al.~\cite{zhong09SE} employ NLP and ML techniques to infer resource specifications from API documents.
+\textit{2.
+Resource Specifications}: Zhong et al.~\cite{zhong09SE} employ NLP and  Machine Learning (ML) techniques to infer resource specifications from API documents.
 Their approach uses machine learning to automatically classify such rules.
 In contrast, we attempt to parse sentences based on semantic templates and demonstrate that such an approach preforms reasonably well.
-Tan et al.~\cite{TanSOSP07} applied an NLP and Machine Learning (ML) based approach to test Javadoc comments against implementations.
-However, their approach specifically focuses on null values and related exceptions, thus limiting the application scope.
-In contrast, our approach infers generic specifications from API documents.
-In particular, our approach already produces FOL representation of the specifications that can be used to test implementations.
-Furthermore, the performance of the preceding ML-based approaches is dependent on the quality of the training sets used for ML.
-In contrast, our approach is independent of such training set and thus can be easily extended to target respective problems addressed by these approaches.
+Furthermore, the performance of the approach is dependent on the quality of the training sets used for ML.
+In contrast, approach presented in this work is independent of such training set and thus can be easily extended to target respective problems addressed by these approaches.
 
-Among other works described in ~\cite{RobillardIEEEtranSE13}, Mining API Mapping (MAM)~\cite{Zhong2010ICSE} is most directly related to our work.
-MAM mines API mapping relations across different languages for language migration, however they do little in terms of mining usage constraints of methods.
+\textit{3.
+Code Comments}: Tan et al.~\cite{TanSOSP07} and Hwei-Tan et al.~\cite{tcomment} applied an NLP and ML  based approach on code comments/ Javadoc comments to detect mismatches between these comments and implementations.
+They rely on predefined rule templates targeted towards method invocation and lock related comments, thus limiting their scope both in terms of application area as well as language used in the comments.
+In contrast, approach presented in this report relies on generic natural language based templates thus relaxing the restriction on the style of the language used to describe specifications.
 
-%Web Query~\cite{Zheng2011FSE}
+\textit{4.
+API Description}: Most closely related work to the approach presented here is Pandita et al.~\cite{pandita12:inferring} work on inferring parameter constraints from method descriptions in the API documents.
+In contrast this approach deals with the temporal constraints.
+The approach presented here is a significant extension to the infrastructure used in the previous work as documented in Section~\ref{sec:approach}.
 
-%\textbf{Library migration}.
-With evolution of libraries, some APIs may become incompatible across library versions.
-To address this problem, Henkel and Diwan ~\cite{csallner08dysy} proposed an approach that captures and replays API refactoring actions to update the client code.
-Xing and Stroulia [17] proposed an approach that recognizes the changes of APIs by comparing the differences between two versions of libraries.
-Balaban et al.
-[2] proposed an approach to migrate client code when mapping relations of libraries are available.
-In contrast to these approaches, our approach focuses on mapping relations of APIs across different languages.
-In addition, since our approach uses ATGs to mine API mapping relations, our approach can also mine mapping relations between API methods with different parameters or between API methods whose functionalities are split among several API methods in the other language.
+\textbf{Augmented Documentation}
+
+Another related field has been that of improving the documentation related to an software API~\cite{Dekel2009,tan2011acomment}.
+We next describe most relevant approaches.
+Dekel et al.~\cite{Dekel2009}, were the first to create a tool namely eMoose, an Eclipse~\footnote{\url{http://www.eclipse.org/}} based plug-in that allowed developers to create directives( way of marking the specification sentences) in the default documentation.
+These directives are highlighted whenever they are displayed in the eclipse environment.
+Lee et al.~\cite{lee2012towards} improved upon their work by providing a formalism to the directives proposed by Dekel et al.~\cite{Dekel2009}, thus allowing tool based verification.
+However, a developer has to manually annotate such directives.
+In contrast, our proposed approach both identifies the sentences pertaining to temporal constraints and infers the temporal constraints automatically.
+
+In next section, we briefly introduce the NLP techniques used by our approach.
+
+%\textbf{Program Comprehension}
+%
+%With respect to program comprehension there are existing techniques that assist in building domain specific ontologies~\cite{Zhou2008}.
+Furthermore, there are existing approaches~\cite{sridhara2011ICPC,robillard1986schematic} that automatically infer natural language documentation from source code.
+These approaches would immensely help in comprehension of the functionality of an application.
+However inherent dependency on source code to generate such documents poses a problem in cases, where source code is not available.
+We next describe some of these approaches
+%
+%\begin{itemize}
+% \item Sridhara et al.~\cite{sridhara2011ICPC} use data-flow analysis on the method variables to determine the set of statements that represent the computational intent of the method.
+The data flow analysis is then used to determine the relation of these statements to the method parameters.
+These realtions are then thn used to generate the natural language parameter documentation using predefined templates.
+%
+% \item Zhang et al.~\cite{zhang2011automated} present an approach to generate the explanatory document in the form of code comments explaining the failure of the test case.
+They first instrument the failing test case.
+They then use statistical algorithm on the different execution traces of the failing test case to determine a relatively small subset of the suspicious statements along with the objects that need correction for successful execution of test case.
+Finally, the identified objects that need correction for successful execution of the test case are used to generate the explanatory comments using predefined templates on the generalized properties of the object.
+For instance, \CodeIn{x == null} becomes \textit{x is set to:null}.
+%
+% \item Buse et al.~\cite{Buse:2008:ADI:1390630.1390664} use source mining source code repositories to generate usage patterns of an API.
+They argue that availability of actual usable code examples serves as a better documentation assisting developers in understating the usage of API.
+They propose the clustering of the uses of an API in the open source repositories based on path information.
+They then propose type abstraction on the clusters to come up with a usage document.
+%\end{itemize}

### 2014-01-17 Draft/abstract.tex
Fixed reading group comments on abstract

@@
 \begin{abstract}
-Formal specifications of an Application Programming Interface (API) usage are highly desirable,
-because they are the precursor to the formal analysis tools such as model checkers and runtime verifiers.
-However, most API's do not have formal specifications.
-In contrast documentation of methods contain detailed specifications of the usage in natural language text.
+Formal specifications of using a libraries Application Programming Interface (API)
+can be used in conjunction with formal analysis tools such as
+model checkers and runtime verifiers to assess the quality of a software.
+Despite being highly desirable, most API's do not have formal specifications.
+In contrast, API documents contain valuable information about the usage in natural language.
 However, formal analysis tools are not designed to work on specifications in natural languages.
-Manually writing formal specifications based on natural language text in API documents can be prohibitively time consuming and error prone.
-To address this issue, we propose a natural language processing based novel approach \tool\ to precisely infer constraints from natural language text of API documents.
+Manually writing formal specifications based on natural language text in API documents
+can be prohibitively time consuming and error prone.
+To address this issue, we propose a natural language processing based automated approach \tool ,
+to infer formal specifications from natural language text of API documents.
 In particular, we focus on temporal constraints, that are defined as constraints on the
@@
 Our evaluation results show that \tool\ achieves an average of PP\% precision and RR\% recall
-in inferring TT temporal constraints from more than ZZZZ sentences of API sentences.
+in inferring TT temporal constraints from more than ZZZZ sentences of API documents.
 
-%IS the approach automated
-%precursor too strong word
 % need to explain why moving from formal specifications to temporal constraints
@@
 % The goal of this research is to facilitate the correct usage API methods by identifying temporal constraints etc.. 
-% Is the approach automated ? Make a line about how you gonna
-% conclusion of numbers 
-% make it consistent APi documents, descriptions and sentences
-
 \end{abstract}

### 2014-01-17 Draft/introduction.tex
fixed some reading group comments.

@@
 
-However, most API's do not have formal specifications.
+Despite being desirable, most API's do not have formal specifications.
 In contrast, API developers commonly describe correct usage in natural language text in API documents.
@@
 
-%May be strike out the first sentence 
-%May be strike out the term prohibitevely
-
-A na{\"i}ve solution to address the issue, is to manually convert the natural language API description into formal specifications. 
+One way of addressing the issue, is to manually convert the natural language API description into formal specifications. 
 However, manually writing formal specifications based on natural language text in API documents can be prohibitively time consuming and error prone~\cite{wu2013inferring,RubingerWEB10}. 
@@
 
-%Furthermore, I propose to evaluate the effectiveness of proposed work on real world API's: 1) Java 7 and 2) Amazon S3 REST API.
-The former is generic language API, while the later is a web based API directed towards cloud-based data storage.
-The temporal constraints inferred for Java 7 will be compared with the existing approaches to evaluate the effectiveness of proposed work.
-In contrast, Amazon S3 REST API (relatively recent) representative of the class of API's where neither source code of API nor enough usage examples are available.
-
-%To evaluate our proposed approach, we applied \tool\ to infer temporal constraints from 
-%commonly used package \CodeIn{java.io} from JDK API and Amazon S3 REST API.
-%Our evaluation results show that \tool\ achieves an average of PP\% precision and RR\% recall
-%in inferring TT temporal constraints from more than ZZZZ sentences of API documents.
-
-%Software reuse is commonly practiced since the advent of software development~\cite{FrakesIEEETran05}.
-Software reuse facilitates development of larger, more complex, and timely-delivered software systems~\cite{GaffneySE92}.
-To determine what and how to reuse, specifications of reusable software libraries play an important role.
-In the absence of specifications, developers may write code that is inconsistent with the expectations of libraries.
-As a result, not only such code is of inferior quality and contains faults, the added cost of debugging and correcting such faulty code could also defeat the purpose of reusing software.
-
 % talk about mining approaches 

### 2014-01-17 Draft/related.tex
fixed some reading group comments.

@@
 
-// "In contrast" switch up the wording a little bit
+% "In contrast" switch up the wording a little bit
 
-Our proposed approach touches a few research areas such as software verification,  NLP on software engineering artifacts, and document augmentation.
-We next discuss relevant work pertinent to our proposed approach in these areas.
+Our proposed approach touches a few research areas such as software verification,
+NLP on software engineering artifacts, and document augmentation.
+We next discuss the relevant work pertinent to our proposed approach in these areas.
 
-\textbf{Code Contracts - Formal Specifications}
-// Define temporal constraints distinction
+\subsection{Code Contracts - Formal Specifications}
+% Define temporal constraints distinction
 Design by contracts has been an influential concept in the area of software engineering in the past decade.
@@
 However, a combination of developer written and automatically inferred contracts seems to be the most effective approach~\cite{Polikarpova2009ISSTA,Flanagan:2001:HAA:647540.730008}.
-Furthermore, there are existing approaches that infer code-contract-like specifications (such as behavioral model, algebraic specifications, and exception specifications) either dynamically\cite{Henkel07discoveringdocumentation,Ghezzi:2009:SIB:1555001.1555057,Henkel:2008:DDA:1363102.1363105} or statically~\cite{Flanagan:2001:HAA:647540.730008,Buse:2008:ADI:1390630.1390664} from source code and binaries.
-In contrast, the approach presented in this work infers specifications from the natural language text in API documents, thus complementing these existing approaches when the source code or binaries of the API library is not available.
+Furthermore, there are existing approaches that infer code-contract-like specifications
+(such as behavioral model, algebraic specifications, and exception specifications) either dynamically\cite{Henkel07discoveringdocumentation,Ghezzi:2009:SIB:1555001.1555057,Henkel:2008:DDA:1363102.1363105} or statically~\cite{Flanagan:2001:HAA:647540.730008,Buse:2008:ADI:1390630.1390664} from source code and binaries.
+In contrast, the approach presented in this work infers specifications from the natural language text in API documents,
+thus complementing these existing approaches when the source code or binaries of the API library is not available.
 
-\textbf{NLP in Software Engineering}
+\subsection{NLP in Software Engineering}
 
 NLP techniques are increasingly applied in the software engineering domain. 
-NLP techniques have been shown to be useful in requirements engineering ~\cite{Sinha2009,Sinha2010,Gervasi2005}, usability of API documents~\cite{Dekel2009}, and other areas~\cite{Zhou2008,Little2009,pandita13:WHYPER}.
+NLP techniques have been shown to be useful in requirements engineering ~\cite{Sinha2009,Sinha2010,Gervasi2005},
+usability of API documents~\cite{Dekel2009}, and other areas~\cite{Zhou2008,Little2009,pandita13:WHYPER}.
 We next describe the most relevant approaches.
@@
 
-\textit{2.
-Resource Specifications}: Zhong et al.~\cite{zhong09SE} employ NLP and  Machine Learning (ML) techniques to infer resource specifications from API documents.
+\textit{2. Resource Specifications}: Zhong et al.~\cite{zhong09SE} employ NLP and  Machine Learning (ML) techniques to infer resource specifications from API documents.
 Their approach uses machine learning to automatically classify such rules.
 In contrast, we attempt to parse sentences based on semantic templates and demonstrate that such an approach preforms reasonably well.
-Furthermore, the performance of the approach is dependent on the quality of the training sets used for ML.
-In contrast, approach presented in this work is independent of such training set and thus can be easily extended to target respective problems addressed by these approaches.
+Furthermore, the performance of the proposed approach is dependent on the quality of the training sets used for ML.
+In contrast, approach presented in this work is independent of such training set and thus can be easily extended to target respective problems addressed by them.
 
@@
 
-\textbf{Augmented Documentation}
+\subsection{Augmented Documentation}
 
@@
 We next describe most relevant approaches.
-Dekel et al.~\cite{Dekel2009}, were the first to create a tool namely eMoose, an Eclipse~\footnote{\url{http://www.eclipse.org/}} based plug-in that allowed developers to create directives( way of marking the specification sentences) in the default documentation.
+Dekel et al.~\cite{Dekel2009}, were the first to create a tool namely eMoose, an Eclipse~\footnote{\url{http://www.eclipse.org/}} based plug-in that allowed developers to create directives (way of marking the specification sentences) in the default API documentation.
 These directives are highlighted whenever they are displayed in the eclipse environment.
@@
 In next section, we briefly introduce the NLP techniques used by our approach.
-
-%\textbf{Program Comprehension}
-%
-%With respect to program comprehension there are existing techniques that assist in building domain specific ontologies~\cite{Zhou2008}.
-Furthermore, there are existing approaches~\cite{sridhara2011ICPC,robillard1986schematic} that automatically infer natural language documentation from source code.
-These approaches would immensely help in comprehension of the functionality of an application.
-However inherent dependency on source code to generate such documents poses a problem in cases, where source code is not available.
-We next describe some of these approaches
-%
-%\begin{itemize}
-% \item Sridhara et al.~\cite{sridhara2011ICPC} use data-flow analysis on the method variables to determine the set of statements that represent the computational intent of the method.
-The data flow analysis is then used to determine the relation of these statements to the method parameters.
-These realtions are then thn used to generate the natural language parameter documentation using predefined templates.
-%
-% \item Zhang et al.~\cite{zhang2011automated} present an approach to generate the explanatory document in the form of code comments explaining the failure of the test case.
-They first instrument the failing test case.
-They then use statistical algorithm on the different execution traces of the failing test case to determine a relatively small subset of the suspicious statements along with the objects that need correction for successful execution of test case.
-Finally, the identified objects that need correction for successful execution of the test case are used to generate the explanatory comments using predefined templates on the generalized properties of the object.
-For instance, \CodeIn{x == null} becomes \textit{x is set to:null}.
-%
-% \item Buse et al.~\cite{Buse:2008:ADI:1390630.1390664} use source mining source code repositories to generate usage patterns of an API.
-They argue that availability of actual usable code examples serves as a better documentation assisting developers in understating the usage of API.
-They propose the clustering of the uses of an API in the open source repositories based on path information.
-They then propose type abstraction on the clusters to come up with a usage document.
-%\end{itemize}

### 2014-01-22 Draft/introduction.tex
Changed Intro

@@
 
-Specifications of using an Application Programming Interface (API) of a library play an important role in software reuse.
-In addition to guiding the development process by outlining what and how to reuse, 
-usage specifications also help in verification process by allowing quality assurance practitioners to test the expected outcome.
-Furthermore, if the specifications are formal (machine-readable such as code-contracts),
-they can be used in conjunction with the formal analysis tools such as model checkers and runtime verifiers
-to automatically reason about the quality of the software.
+Temporal specifications~\cite{slam-2002} of an Application Programming Interface (API) 
+describe allowed sequences of invocations of methods within an API. 
+These specifications govern the secure and robust operation of client software 
+using these APIs.
+If these specifications are formal (machine-readable such as code-contracts),
+they can be used  as a basis of formal analysis tools such 
+as model checker and runtime verifiers
+in detecting the violations of these temporal constraints as defects.
+
+%Specifications of using an Application Programming Interface (API) of a library play an important role in software reuse.
+%In addition to guiding the development process by outlining what and how to reuse, 
+%usage specifications also help in verification process by allowing quality assurance practitioners to test the expected outcome.
+%Furthermore, if the specifications are formal (machine-readable such as code-contracts),
+%they can be used in conjunction with the formal analysis tools such as model checkers and runtime verifiers
+%to automatically reason about the quality of software.
 
@@
 Despite being desirable, most API's do not have formal specifications.
-In contrast, API developers commonly describe correct usage in natural language text in API documents.
+In contrast, API developers commonly describe correct temporal usage in natural language text in API documents.
 Typically, such documents are provided to client-code developers through online access, or are shipped with the API code.
-For example, J2EE's API documentation\footnote{\url{http:\\download.oracle.com/javaee/1.7/api/}} is one of the popular API documents.
-Typically, an API document will describe the both the constraints on that method parameters as well as the constraints in terms of the methods the must be invoked pre/post the current method.
-However, formal analysis tools are not designed to work on specifications written in natural languages.
+%For example, J2EE's API documentation\footnote{\url{http:\\download.oracle.com/javaee/1.7/api/}} is one of the popular API documents.
+Typically, an API document describes both the constraints on that method parameters as well as the temporal constraints in terms of the methods must be invoked pre/post the current method.
+We observed that roughly 12\% of the sentences describing some sort of specification constraints in \amazonAPI\ documentations describe temporal constraints.
+Although API documents contain temporal constraints in natural language, formal analysis tools are not designed to work on specifications written in natural languages.
 
@@
 %Strike out ``To address the aforementioned issue''
-To address the aforementioned issue, we propose a novel approach to infer usage constraints from natural language text of API documents.
-We propose new techniques that apply Natural Language Processing (NLP) on natural language text API documents to automatically infer usage constraints.
-In particular, we focus on specific type of constraints namely temporal constraints.
+We propose a novel approach to infer temporal usage constraints from natural language text of API documents.
+We propose new techniques that apply Natural Language Processing (NLP) on natural language text API documents to automatically infer temporal usage constraints.
+%In particular, we focus on specific type of constraints namely temporal constraints.
 A generic temporal relation is defined as \textit{an interpropositional relation that communicates the simultaneity or ordering in time of events or states.}
@@
 % Make consistent terminology approach or technique
-Although, in typed languages some sequencing constraints are enforced by type system. 
-For instances a method ($m$) accepting input parameter ($i$) of type ($t$) mandates that (at least one) method ($m'$) be invoked whose return value is of type ($t$).  
-However, most temporal constraints are not limited by the type definitions (i.e, requirements on the type of input parameters),
-and are currently expressed mostly in natural language in API documents, as described in the example previously.
-In a manual investigation, we observed that roughly 12\% of the sentences describing some sort of specification constraints in \amazonAPI\ documentations are temporal constraints related.
+
 %Background on out of how many sentences
@@
 % Amazon S3 is popularly used web service for simple cloud based storage
-Most of the existing approaches focus in inferring method pre-post conditions~\cite{Henkel07discoveringdocumentation,Ghezzi:2009:SIB:1555001.1555057,Henkel:2008:DDA:1363102.1363105,Flanagan:2001:HAA:647540.730008,Buse:2008:ADI:1390630.1390664} in terms of parameter constraints either using static or dynamic analysis techniques.
+Existing approaches focus in inferring method pre-post conditions~\cite{Henkel07discoveringdocumentation,Ghezzi:2009:SIB:1555001.1555057,Henkel:2008:DDA:1363102.1363105,Flanagan:2001:HAA:647540.730008,Buse:2008:ADI:1390630.1390664} in terms of parameter constraints either using static or dynamic analysis techniques.
 Furthermore, there is a class of NLP based approaches~\cite{pandita12:inferring, wu2013inferring} that infer constraints from API documents.
@@
 Temporal constraints, in general focus on rules related to orchestration of methods within an API rather than focusing on the requirements on the input parameters of these methods.
-In particular, our proposed techniques address the following challenges to infer temporal constraints automatically from natural language text.
 
+Although, in typed languages some sequencing constraints are enforced by type system. 
+For instances a method ($m$) accepting input parameter ($i$) of type ($t$) mandates that (at least one) method ($m'$) be invoked whose return value is of type ($t$).
+However, most temporal constraints are not limited by the type definitions (i.e, requirements on the type of input parameters), and are currently expressed mostly in natural language in API documents, as described in the example previously.
+
+Our proposed techniques address the following challenges to infer temporal constraints automatically from natural language text.
 First, relying just on type information will result in a incomplete list of temporal constraints. 
@@
 The problem is exacerbated in web based API's such as \amazonAPI\ where most of the types are either \CodeIn{integer} or \CodeIn{strings}.
+Our proposed approach extends the existing techniques to address the challenge.
 
 %identified in previous work~\cite{pandita12:inferring} delete and leave the reference
-% Add a sentnce stating that we extend previous technique to address the issues 
+% Add a sentence stating that we extend previous technique to address the issues 
 Second, inferring temporal constraints from the natural language text itself is challenging. 
@@
 Ad-hoc constructing these dictionaries is prohibitively time and resources intensive.
-To address this challenge we propose to build domain-dictionaries systematically from API documents themselves.
+To address this challenge, we propose to build domain-dictionaries systematically from API documents themselves.
 
@@
 As the proposed work analyzes API documents in natural language, it can be reused independent of the programming language of the library.
-Additionally, our approach complements existing mining based approaches~\cite{buse2012synthesizing, thummalapenta07parseweb, Wang:2013:MSR, Zhong:2009:MMR} that partially address the problem by mining for common usage patterns.
+Additionally, our approach complements existing mining based approaches~\cite{buse2012synthesizing, thummalapenta07parseweb, Wang:2013:MSR, Zhong:2009:MMR} that partially address the problem by mining for common usage patterns among client software that use the API.
 The proposed work in general, makes the following contributions:
@@
 	\item A NLP based approach that infers temporal constraints of method invocations. 
+	To the best of our knowledge, our approach is the first one to apply NLP for the goal of inferring temporal specifications from API documents.
 	\item A prototype implementation of our approach based on extending the Stanford Parser~\cite{Klein03,SNLP1}, which is a natural language parser to derive the grammatical structure of sentences.
-	An open source implementation of the prototype will be made available publicly. 
-	\item An evaluation of proposed approach on Java 7 and Amazon S3 REST API
+	An open source implementation of the prototype is publicly available on our project website\footnote{\url{https://sites.google.com/site/icon}}. 
+	\item An evaluation of proposed approach on Java 7 and Amazon S3 REST API.
 \end{itemize}

### 2014-01-22 Draft/introduction.tex
Changed technique->approach in Intro

@@
 We propose a novel approach to infer temporal usage constraints from natural language text of API documents.
-We propose new techniques that apply Natural Language Processing (NLP) on natural language text API documents to automatically infer temporal usage constraints.
+We propose a new approach that apply Natural Language Processing (NLP) on natural language text API documents to automatically infer temporal usage constraints.
 %In particular, we focus on specific type of constraints namely temporal constraints.
@@
 Furthermore, there is a class of NLP based approaches~\cite{pandita12:inferring, wu2013inferring} that infer constraints from API documents.
-However, similar to static and dynamic analysis techniques these approaches focus on parameter constraints as well.  
+However, similar to static and dynamic analysis techniques, these approaches focus on parameter constraints as well.  
 In contrast, temporal constraints are beyond these parameter constraints.
@@
 
-Our proposed techniques address the following challenges to infer temporal constraints automatically from natural language text.
+Our proposed approach address the following challenges to infer temporal constraints automatically from natural language text.
 First, relying just on type information will result in a incomplete list of temporal constraints. 
@@
 The problem is exacerbated in web based API's such as \amazonAPI\ where most of the types are either \CodeIn{integer} or \CodeIn{strings}.
-Our proposed approach extends the existing techniques to address the challenge.
+Our proposed approach extends the existing approaches to address the challenge.
 

### 2014-01-22 Draft/abstract.tex
fixed some reading group comments.
Fixed comments more comments

@@
 model checkers and runtime verifiers to assess the quality of a software.
-Despite being highly desirable, most API's do not have formal specifications.
+Despite being desirable, most API's do not have formal specifications.
 In contrast, API documents contain valuable information about the usage in natural language.
@@
 commonly used package \CodeIn{java.io} from JDK API and Amazon S3 REST API.
-Our evaluation results show that \tool\ achieves an average of PP\% precision and RR\% recall
-in inferring TT temporal constraints from more than ZZZZ sentences of API documents.
+Our evaluation results show that \tool\ achieves an average of 60\% precision and 80\% recall
+in inferring 63 temporal constraints from more than 2400 sentences of API documents.
 

### 2014-01-22 Draft/approach.tex
Fixed comments more comments

@@
 		\includegraphics[scale=0.45]{approach.eps}
-	\caption{Overview of \tool\ framework}
+	\caption{Overview of \tool\ approach}
 	\label{fig:approachOverview}
@@
 
-We next present our framework for inferring specifications from the method descriptions in API Documents.
-Figure~\ref{fig:approachOverview} gives an overview of our framework.
-Our framework consists of four major components: an API parser, a preprocessor, a text-analysis engine, and a postprocessor.
+We next present our approach for inferring specifications from the method descriptions in API Documents.
+Figure~\ref{fig:approachOverview} gives an overview of our approach.
+Our approach consists of five major components: a preprocessor, a text-analysis engine, a semantic graph generator, specification extractor, and a type analyzer.
 
-The API parser accepts online API description and extracts method descriptions.
-The pre-processor accepts method descriptions and preprocesses the sentences in the descriptions, such as annotating sentence boundaries and reducing lexical tokens. 
+The pre-processor accepts API documents and preprocesses the sentences in the method description, such as annotating sentence boundaries and reducing lexical tokens.
 The text-analysis engine accepts the pre-processed sentences and annotates them using an NLP parser.
-The text-analysis engine further transforms the annotated sentences into the first-order-logic (FOL) representation and then leverages the FOL representation of a sentence to infer specifications.
+The text-analysis engine further transforms the annotated sentences into the first-order-logic (FOL) representation.
+Finally, the specification extractor then leverages the FOL representation of a sentence to infer specifications.
 Finally, the postprocessor undoes any modifications done by the preprocessor to get refined specifications.
 
-Besides the previously described major components the framework also consists of a an external component, namely target specification generator.
-This component accepts the specification generated by our framework and using mapping functions to a target specification language generates specifications in the target language of choice.
+Besides the previously described major components the approach also consists of a an external component, namely target specification generator.
+This component accepts the specification generated by our approach and using mapping functions to a target specification language generates specifications in the target language of choice.
 We next describe each component in detail.
@@
 The preprocessor accepts API method descriptions extracted by the parser and preprocesses the natural language text, to be further analyzed by the text-analysis engine.
-The preprocessing steps are required to increase the accuracy core NLP techniques (described in Section~\ref{sub:CoreNLPback}) that are used in the subsequent phases of \tool\ framework.
+The preprocessing steps are required to increase the accuracy core NLP techniques (described in Section~\ref{sub:CoreNLPback}) that are used in the subsequent phases of \tool\ approach.
 In particular, the preprocessor first employs the noun boosting followed by heuristics listed under lexical token reduction, as introduced in Section~\ref{sub:SENLPback}.
@@
 From an implementation perspective, we chose the Stanford parser~\cite{SNLP}.
-However, this component can be implemented using any other existing NLP libraries or frameworks.
+However, this component can be implemented using any other existing NLP libraries or approachs.
 In particular, we annotate each sentence with POS tags, named-entity Annotations and Stanford-typed dependencies.
@@
 
-A key way of identifying reference to a method within the API in our proposed framework is the employment of a semantic graph of an API.
+A key way of identifying reference to a method within the API in our proposed approach is the employment of a semantic graph of an API.
 In particular, we propose to initially infer such graphs from API documents.

### 2014-01-22 Draft/background.tex
Fixed comments more comments

@@
 
-\textbf{Co-reference Resolution}~\cite{RaghunathanEMNLP10,LeeCoNLL11}.
+%\textbf{Co-reference Resolution}~\cite{RaghunathanEMNLP10,LeeCoNLL11}.
 Also known as \textit{`anaphora resolution'}, these techniques aim to identify multiple expressions present across (or within) the sentences, that point out to the same thing or \textit{`referant'}.
@@
 \textbf{Noun Boosting}~\cite{pandita12:inferring}. Accurate annotation of POS tags in a sentence is fundamental to effectiveness of any advanced NLP technique.
-However, as mentioned earlier, POS tagging work well on well written news articles which does not necessary entail that they work well with domain specific text as well.
+However, as mentioned earlier, POS tagging work well on well written news articles which does not necessary entail that the tagging works well on domain specific text as well.
 Thus, noun boosting is a necessary precursor to application of POS tagging on domain specific text.

### 2014-01-22 Draft/introduction.tex
Fixed comments more comments

@@
 
-Temporal specifications~\cite{slam-2002} of an Application Programming Interface (API) 
+Temporal specifications~\cite{ball2002s} of an Application Programming Interface (API) 
 describe allowed sequences of invocations of methods within an API. 
@@
 using these APIs.
-If these specifications are formal (machine-readable such as code-contracts),
+If these specifications are formal (machine-readable such as linear temporal logic),
 they can be used  as a basis of formal analysis tools such 
@@
 % Amazon S3 is popularly used web service for simple cloud based storage
-Existing approaches focus in inferring method pre-post conditions~\cite{Henkel07discoveringdocumentation,Ghezzi:2009:SIB:1555001.1555057,Henkel:2008:DDA:1363102.1363105,Flanagan:2001:HAA:647540.730008,Buse:2008:ADI:1390630.1390664} in terms of parameter constraints either using static or dynamic analysis techniques.
-Furthermore, there is a class of NLP based approaches~\cite{pandita12:inferring, wu2013inferring} that infer constraints from API documents.
-However, similar to static and dynamic analysis techniques, these approaches focus on parameter constraints as well.  
+There are existing approaches focus on inferring just the method pre-post conditions in terms of parameter constraints either using program analysis techniques~\cite{Henkel07discoveringdocumentation,Ghezzi:2009:SIB:1555001.1555057,Henkel:2008:DDA:1363102.1363105,Flanagan:2001:HAA:647540.730008,Buse:2008:ADI:1390630.1390664} or using NLP~\cite{pandita12:inferring, wu2013inferring}.
 In contrast, temporal constraints are beyond these parameter constraints.
 Temporal constraints, in general focus on rules related to orchestration of methods within an API rather than focusing on the requirements on the input parameters of these methods.
+Our proposed approach addresses the following challenges to infer temporal constraints automatically from API documents.
 
-Although, in typed languages some sequencing constraints are enforced by type system. 
+First, relying just on type information will result in a incomplete list of temporal constraints. 
+Although, in typed languages some temporal constraints are enforced by type system. 
 For instances a method ($m$) accepting input parameter ($i$) of type ($t$) mandates that (at least one) method ($m'$) be invoked whose return value is of type ($t$).
-However, most temporal constraints are not limited by the type definitions (i.e, requirements on the type of input parameters), and are currently expressed mostly in natural language in API documents, as described in the example previously.
-
-Our proposed approach address the following challenges to infer temporal constraints automatically from natural language text.
-First, relying just on type information will result in a incomplete list of temporal constraints. 
-Furthermore, such constraints although valuable but are already checked by any advanced Integrated Development Environment(IDE) such as eclipse
-for a strongly typed language.
-The problem is exacerbated in web based API's such as \amazonAPI\ where most of the types are either \CodeIn{integer} or \CodeIn{strings}.
-Our proposed approach extends the existing approaches to address the challenge.
+However, temporal constraints are not limited by the type definitions (i.e, requirements on the type of input parameters), and are currently expressed mostly in natural language in API documents, as described in the example previously.
+We propose to address the issue by augmenting the type definitions based temporal constraints with the the constraints inferred from
+the natural language text in API documents.
+%Furthermore, such constraints although valuable but are already checked by any advanced Integrated Development Environment(IDE) such as eclipse
+%for a strongly typed language.
+%The problem is exacerbated in web based API's such as \amazonAPI\ where most of the types are either \CodeIn{integer} or \CodeIn{strings}.
+%Our proposed approach extends the existing approaches to address the challenge.
 

### 2014-01-23 Draft/approach.tex
Fixed approach into para

@@
 
-The pre-processor accepts API documents and preprocesses the sentences in the method description, such as annotating sentence boundaries and reducing lexical tokens.
+The preprocessor accepts API documents and preprocesses the sentences in the method description, such as annotating sentence boundaries and reducing lexical tokens.
 The text-analysis engine accepts the pre-processed sentences and annotates them using an NLP parser.
 The text-analysis engine further transforms the annotated sentences into the first-order-logic (FOL) representation.
-Finally, the specification extractor then leverages the FOL representation of a sentence to infer specifications.
-Finally, the postprocessor undoes any modifications done by the preprocessor to get refined specifications.
-
-Besides the previously described major components the approach also consists of a an external component, namely target specification generator.
-This component accepts the specification generated by our approach and using mapping functions to a target specification language generates specifications in the target language of choice.
+Finally, the specification extractor then leverages the semantic graphs to infer temporal constraints from the FOL representation of a sentence.
+Besides the previously described components the approach also consists of a semantic graph generator and type analyzer.
+The semantic graph generator accepts the API documents and generates the semantic graphs that are leveraged by specification extractor component.
+The type analyzer components infers temporal constraints encoded in the type system of a language by analyzing the API methods parameter and return types.
 We next describe each component in detail.
 
-\subsection{API Parser}
+\subsection{Preprocessor}
 \label{sub:parser}
 
-Our API parser accepts the online API documents and extracts method descriptions from it.
-In particular, our parser extracts the following fields within method descriptions: 
+The preprocessor accepts the API documents and first extracts method descriptions from it.
+In particular, the preprocessor extracts the following fields within method descriptions: 
 1) \textit{Summary of the API method},
-2) \textit{Summary of request elements of the API method}, and 
-3) \textit{Summary of response elements of the method (inclusive of error responses)}.
+2) \textit{Summary and type information of parameters of the API method}, 
+3) \textit{Summary and type information of return values of the method}, and
+4) \textit{Summary and type information of exceptions thrown by the methods}.
 
@@
 This difference in style may include the difference in the level of detail presented to the developer.
-We thus chose very only generic fields that are essential to API methods.
+Our approach thus relies on only basic fields that are trivially available for API methods across different presentation styles.
 
-Currently our prototype implementation extracts this information from online \amazon\ only. 
-However, almost all of the REST API developer documents are provided online as structured webpages.
-Thus, current implementation of parser can be easily extended to extract desired information from any REST API developer documents.
-
-\subsection{Preprocessor}
-\label{sub:Preprocessor}
-
-The preprocessor accepts API method descriptions extracted by the parser and preprocesses the natural language text, to be further analyzed by the text-analysis engine.
+After extracting desired information, the natural language text is further preprocessed to be analyzed by the text-analysis engine.
 The preprocessing steps are required to increase the accuracy core NLP techniques (described in Section~\ref{sub:CoreNLPback}) that are used in the subsequent phases of \tool\ approach.

### 2014-01-23 Draft/approach.tex
Refines pre-processor component

@@
 \subsection{Preprocessor}
-\label{sub:parser}
+\label{sub:prep}
 
@@
 
-After extracting desired information, the natural language text is further preprocessed to be analyzed by the text-analysis engine.
+After extracting desired information, the natural language text is further preprocessed to be analyzed by subsequent components.
 The preprocessing steps are required to increase the accuracy core NLP techniques (described in Section~\ref{sub:CoreNLPback}) that are used in the subsequent phases of \tool\ approach.
 In particular, the preprocessor first employs the noun boosting followed by heuristics listed under lexical token reduction, as introduced in Section~\ref{sub:SENLPback}.
-
-From an implementation perspective, we manually built the domain dictionaries for the preprocessing using the glossary of terms collected from the websites pertaining to REST API.
-We further leveraged the HTML style information in \amazon\ to look for words that were highlighted in code like format.
-We further leveraged WordNet to maintain a static lookup table of shorthand words to aid named entity handling and abbreviation handling.
 
@@
 Finally, we rank the list of n-grams based on the frequency of their occurrence in the text, and select top-k n-grams for reduction.
+For instance, \textit{Amazon Simple Storage Service}, \textit{an I/O Error Occurs}, and \textit{end of stream} are the examples of such n-grams detected by our approach.
 
-From an implementation perspective we used Apache Lucene$^{\textregistered}$~\cite{lucene} to achieve n-gram reduction.
+%\begin{figure}[t]
+%\begin{CodeOut}
+%\begin{alltt}
+%01: 
+%04:
+%\end{alltt}
+%\end{CodeOut}\vspace*{-2ex}
+%\caption{\label{fig:methodAPI} The method description of the \CodeIn{DefineObjectProperty} method in Facebook API}\vspace*{-4ex}
+%\end{figure}
+
+\textbf{Prototype Implementation}
+
+Currently our prototype implementation works with online \amazon\ and JDK API. 
+However, almost all of the developer documents are provided online as structured webpages.
+Thus, current implementation of preprocessor can be easily extended to extract the desired information from any API developer documents.
+
+Additionally, in current implementation we have manually built the domain dictionaries for the preprocessing using the glossary of terms collected from the websites pertaining to REST and Java API.
+We further leveraged the HTML style information in \amazon\ to look for words that were highlighted in code like format.
+We further leveraged WordNet to maintain a static lookup table of shorthand words to aid named entity handling and abbreviation handling.
+
+Finally, to achieve  n-gram reduction we used Apache Lucene$^{\textregistered}$~\cite{lucene} to achieve.
 Apache Lucene is a high-performance, full-featured text search engine library written entirely in Java.
@@
 The NLP parser accepts the pre-processed documents and annotates every sentence within each document using core NLP techniques described in Section~\ref{sub:CoreNLPback}.
-From an implementation perspective, we chose the Stanford parser~\cite{SNLP}.
+From an implementation perspective, we chose the Stanford parser~\cite{Manning:01}.
 However, this component can be implemented using any other existing NLP libraries or approachs.

### 2014-01-23 Draft/evaluation.tex
publishing local file changes

@@
 
-We conducted an evaluation to assess the effectiveness of our approach. In our evaluation, we address three main research questions:
+We conducted an evaluation to assess the effectiveness of our approach. In our evaluation, we address two main research questions:
 
 \begin{itemize}
-
-\item\textbf{RQ1}: What are the precision and recall of \tool\ in inferring usage constraints?
-
+	\item\textbf{RQ1}: What are the precision and recall of \tool\  in
+	identifying temporal contraints from sentences written in natural language?
 	%\item\textbf{RQ2}: What is the accuracy of our approach in inferring specifications from contract sentences in the API documents? 
-
 	\item\textbf{RQ2}: How does our approach fares in comparison to previous NLP approaches?
-
 \end{itemize}
@@
 We used the API documents of the following two libraries as subjects for our evaluation. 
+\begin{itemize}
+	\item{Amazon S3}.
+\amazon\ provides a REST based web services interface that can be used to store and retrieve data on the web.
+Furthermore, \CodeIn{Amazon S3} also empowers a developer with rich set of API methods to access a highly scalable, reliable, secure, fast, inexpensive infrastructure.
+\CodeIn{Amazon S3} is reported to store more than 2 trillion objects as of April 2013 and gets over 1.1 million requests per second at peak time~\cite{amazons3stats}.
 
-\amazon\ provides a simple REST based web services interface that can be used to store and retrieve data on the web.
-Furthermore, \CodeIn{Amazon S3} also empowers a developer with rich set of API methods to access a highly scalable, reliable, secure, fast, inexpensive infrastructure.
-\textbf{may be a little detail of usage statistics etc....}
+	\item{java.io}. \CodeIn{java.io} is a popular packacge in \CodeIn{Java} programming language that provides APIs for system input and output through data streams, serialization and the file system.
+\end{itemize}
+We chose \CodeIn{Amazon S3} and \CodeIn{java.io} APIs as our subjects because they are popular and contain decent documentation.
 
-\textbf{TBD}.
+\subsection{Experimental Setup.} 
+We apply our approach on the API documents of the two APIs.
+To determine the precision and recall, 
+two authors manually label each sentence in the API documentation as sentence containing 
+temporal constraints or not. After the authors have classified all the sentences, they 
+talk to each ther to reach a consensus on the sentences they classified differently. 
+We use this classified scentes as the golden set for calculating precision and recall.
+
+\CodeIn{cohen kappa} score of the two authors was 6.6
 
@@
 upon by two authors.
+
+If any in-memory buffering is being done by the application (for example, by a BufferedOutputStream object), those buffers must be flushed into the FileDescriptor (for example, by invoking OutputStream.flush) before that data will be affected by sync.
+
+If markposMM is -1MM (no mark has been set or the mark has been invalidated), an IOExceptionMM is thrown.

### 2014-01-23 Draft/approach.tex
publishing local file changes
Changed approach, Introduction

@@
 As described in Section~\ref{sub:SENLPback} the intermediate representation generation technique is based on the principle of shallow parsing~\cite{Branimir2000}. 
-In particular, the intermediate-representation technique is implemented as a function of Stanford-typed dependencies~\cite{Marneffe06LREC,Marneffe08COLING,SNLP,KleinNIPS03}, to leverage the semantic information encoded in Stanford-typed dependencies.
+In particular, the intermediate-representation technique is implemented as a function of Stanford-typed dependencies~\cite{Marneffe06LREC,Marneffe08COLING,KleinNIPS03}, to leverage the semantic information encoded in Stanford-typed dependencies.
 
@@
 
-\textbf{Stanford-typed Dependencies}: This phase is equivalent to the intermediate-representation technique described in Section~\ref{sub:SENLPback}.
-
-\subsection{Specification Extractor}
-\label{sub:SE}
-
-This component accepts the FOL representation of the sentence.
-
-\begin{itemize}
-\item Extracts Specifications from FOL representation. 
-\item Specifically looking for modal modifies ``can, could, may, must, should'' 
-\item Takes into consideration the negative quantifiers.
-\item Algorithm to infer the sequence of operations.
-\end{itemize}
-
-\subsection{Postprocessor}
-\label{sub:postpro}
-undoing pre-processing and Hybrid intermediate representation generation.
-
 \begin{table*}
@@
 
-\subsection{Semantic-Graph Generator}
-\label{sub:ACA}
+\textbf{Stanford-typed Dependencies}: This phase is equivalent to the intermediate-representation technique described in Section~\ref{sub:SENLPback}.
 
-A key way of identifying reference to a method within the API in our proposed approach is the employment of a semantic graph of an API.
-In particular, we propose to initially infer such graphs from API documents.
-Manually creating a semantic graph is prohibitively time consuming and may be error prone.
-We thus employ a systematic methodology (proposed previously in ~\cite{pandita13:WHYPER}) to infer such semantic graphs from API documents that can potentially be automated.
-We first consider the name of the class.
-We then find the synonyms terms used refer to the class in question.
-The synonym terms are listed as by breaking down the camel-case notation in the class name.
-This list is further augmented by listing the name of the parent classes and implemented interfaces if any.
+\subsection{Specification Extractor}
+\label{sub:SE}
 
-\begin{figure}
-	\centering
-		\includegraphics[scale=0.4]{KnowledgeGraph.eps}
-	\caption{Semantic Graph for the \CodeIn{BufferedInputStream} class in Java}
-	\label{fig:knowledge}
-\end{figure}
+This component accepts the FOL representation of the sentence from the previous component,
+then extracts the temporal constraints if present in a sentence. 
+Specification Extractor then classifies the sentence as a specification 
+sentence (containing temporal constraint) candidate based on following ordered set of rules:
 
-We then systematically inspect the member methods to identify actions applicable to the objects represented by the class.
-From the name of a public method (describing a possible action on the object), we extract verb phrases.
-The verb phrases are used as the associated actions applicable on the object.
-For instance, \CodeIn{BufferedInputReader} defines operations available, close, mark, and so on.
-We associate these operations with the objects of type \CodeIn{BufferedInputReader}.
+\begin{enumerate}
+	\item The sentence is not from parameter summary or return variable summary.
+	Typically such sentences describe pre-post conditions as opposed to temporal constraints this approach addresses.
+	\item The sentences contains modal modifiers such as ``can, could, may, must, should'' expressing necessity.
+	Typically, presence of such modal modifier is a strong indicator of presence of constraints imposed by an API developer
+	\item If the sentence does not contain modal modifiers described previously, sentence must contain temporal modifier relationship, identified by Stanford-typed dependency parser.
+	Typically, presence of temporal modifier is an indicator of presence of temporal information.  
+	\item If rules 2 and 3 don't apply then the sentences should be a conditional sentence, identified by the presence of keywords such as ``if''.
+\end{enumerate}
+
+Once a candidate sentence is identified, this component selects an semantic graph.
+In particular, the semantic graph of the API class to which the candidate sentence belongs to selected.
+A semantic graph constitutes the keyword representation of the classes and the corresponding applicable actions. 
 Figure~\ref{fig:knowledge} shows a sub-graph of  graph for \CodeIn{BufferedInputReader} class.
@@
 The phrases in rounded rectangle are the actions applicable on \CodeIn{BufferedInputReader} class.
+Section~\ref{sub:ACA} further describes how these graphs are generated.
+
+Specification extractor then uses the semantic graph to determine
+if a candidate sentence is a specification sentence and if so extract
+the action that is should be performed prior to the method the sentence
+belongs to. Algorithm~\ref{alg:SenAnnotaator} describes this action extraction
+process.
 
@@
 \end{algorithm}
+
+Our algorithm systematically explores the FOL representation
+of the candidate sentence to determine if a sentence
+describes a temporal specification. First, our algorithm
+attempts to locate the occurrence of class name or its synonym
+within the leaf nodes of the FOL
+representation of the sentence (Line 3). The method
+findLeafContaining(r\_name\_list) explores the FOL representation
+to find a leaf node that contains either the class name
+or one of its synonyms.
+In particular, we use WordNet~\cite{wordnet} and Lemmatisation
+to deal with synonyms of a word in question to find appropriate
+matches. Once a leaf node is found, we systematically
+traverse the tree from the leaf node to the root,
+matching all parent predicates as well as immediate child
+predicates [Lines 5-16].
+
+Our algorithm matches each of the traversed predicate
+with the actions associated with the class defined in
+semantic graph. Similar to matching entities, we also
+employ WordNet and Lemmatisation to deal with
+synonyms to find appropriate matches. If a match is
+found, then the matching action name is returned.
+
+\subsection{Semantic-Graph Generator}
+\label{sub:ACA}
+
+A key way of identifying reference to a method within the API in our proposed approach is the employment of a semantic graph of an API.
+In particular, we propose to initially infer such graphs from API documents.
+Manually creating a semantic graph is prohibitively time consuming and may be error prone.
+We thus employ a systematic methodology (proposed previously in ~\cite{pandita13:WHYPER}) to infer such semantic graphs from API documents that can potentially be automated.
+We first consider the name of the class for the API document in question.
+We then find the synonyms terms used refer to the class in question.
+The synonym terms are listed as by breaking down the camel-case notation in the class name.
+This list is further augmented by listing the name of the parent classes and implemented interfaces if any.
+
+\begin{figure}
+	\centering
+		\includegraphics[scale=0.4]{KnowledgeGraph.eps}
+	\caption{Semantic Graph for the \CodeIn{BufferedInputStream} class in Java}
+	\label{fig:knowledge}
+\end{figure}
+
+We then systematically inspect the member methods to identify actions applicable to the objects represented by the class.
+From the name of a public method (describing a possible action on the object), we extract verb phrases.
+The verb phrases are used as the associated actions applicable on the object.
+For instance, \CodeIn{BufferedInputReader} defines operations available, close, mark, and so on.
+We associate these operations with the objects of type \CodeIn{BufferedInputReader}.
+Figure~\ref{fig:knowledge} shows a sub-graph of  graph for \CodeIn{BufferedInputReader} class.
+The phrases in solid rectangles are synonyms of the class name \CodeIn{BufferedInputReader}.
+The phrases in rounded rectangle are the actions applicable on \CodeIn{BufferedInputReader} class.
+
+\subsection{Type Analysis}
+
+As mentioned earlier that some temporal constraints are enforced by the type system in typed Languages.
+For instances a method ($m$) accepting input parameter ($i$) of type ($t$) mandates that (at least one) method ($m'$) be invoked whose return value is of type ($t$).
+To extend the temporal constraints inferred by the analyzing the natural language text, this component infers additional constraints that are encoded
+in the type system. Algorithm~\ref{alg:TypeAnalysis} lists the steps followed to infer type based temporal constraints.
+
+The algorithm accepts the list of methods as an input produces a graph with
+the nodes representing methods in an API and the directed edges representing temporal constraints.
+First, a index is created based on the return types of the method (Line 2).
+Second, all methods in an API are added to an unconnected graph (Line 3-4).
+Then, for every public method in the input list, the algorithm checks the types
+of the input parameters and constructs and directed edge from all the methods that whose return value
+have the same type to the method in question (Line 14- 20).
+The algorithm does not take into consideration the basic parameter types such as integer, string (Line 15)
+Additionally, an edge is created from the constructors of a class to the non static members methods of a class (Line 8 -13).
+The resultant graph is then returned by the algorithm.
+
+The temporal constraints based on the type information can be extracted by querying the graph. 
+The incoming edges to a node denoting a method represents the set of pre-requisite methods.
+The temporal constraint being, at least one of the pre-requisite methods must be invoked before invoking the method in question.
 
@@
 \caption{Type\_Sequence\_Builder}
-\label{alg:SeqAnnotaator}
+\label{alg:TypeAnalysis}
 \end{algorithm}
-
-%The FOL representation helps us effectively deal with the problem of \emph{confounding effects} of keywords as described in Section~\ref{sec:overview}.
-In particular, the FOL assists in distinguishing between a resource that would be a leaf node and an action that would be a predicate node in the intermediate representation of a sentence.
-The generated FOL representation of the sentence is then provided as an input to the semantic engine for further processing.
-%
-%
-%
-%\subsection{Semantic Engine (SE)}
-%\label{sub:SE}
-%The Semantic Engine (SE) accepts the FOL representation of a sentence and based on the semantic graphs of Android permissions annotates a sentence if it matches the criteria.
-A semantic graph is basically a semantic representation of the resources which are governed by a permission.
-For instance, the READ\_CONTACTS permission governs the resource ``CONTACTS'' in Android system.
-%
-%
-%Figure~\ref{fig:knowledge} shows the semantic graph for the permission READ\_CONTACTS.
-A semantic graph primarily constitutes of subordinate resources of a permission (represented in rectangular boxes) and a set of available actions on the resource itself (represented in curved boxes).
-Section~\ref{sub:ACA} elaborates on how we build such graphs systematically.
-%
-%Our SE accepts the semantic graph pertaining to a permission and annotates a sentence based on the algorithm shown in Algorithm~\ref{alg:SenAnnotaator}.
-The Algorithm accepts the FOL representation of a sentence $rep$, the semantic graph associated with the resource of a permission $g$ and a boolean value $recursion$ that governs the recursion.
-The algorithm outputs a boolean value $isPStmt$, which is \CodeIn{true} if the statement describes the permission associated with a semantic graph ($g$), otherwise \CodeIn{false}.
-%
-%Our algorithm systematically explores the FOL representation of the sentence to determine if a sentence describes the need for a permission.
-First, our algorithm attempts to locate the occurrence of associated resource name within the leaf node of the FOL representation of the sentence (Line 3).
-The method \CodeIn{findLeafContaining(name)} explores the FOL representation to find a leaf node that contains term \CodeIn{name}.
-Furthermore, we use WordNet and Lemmatisation~\cite{Do09:Robust} to deal with synonyms of a word in question to find appropriate matches.
-Once a leaf node is found, we systematically traverse the tree from the leaf node to the root, matching all parent predicates as well as immediate child predicates [Lines 5-16].
-%
-%Our algorithm matches each of the traversed predicate with the actions associated with the resource defined in semantic graph.
-Similar to matching entities, we also employ WordNet and Lemmatisation~\cite{Do09:Robust} to deal with synonyms to find appropriate matches.
-If a match is found, then the value \CodeIn{isPStmt} is set to  \CodeIn{true}, indicating that the statement describes a permission.
-%
-%In case no match is found, our algorithms recursively search all the associated subordinate resources in the semantic graph of current resource.
-A subordinate resource may further have its own subordinate resources.
-Currently, our algorithm considers only immediate subordinate resources of a resource to limit the false positives.
-%
-%%We limit the exploration to depth 1 to limit the false positives. That means only immediate subordinate resources of a resource will be explored.
-%
-%In the context of the FOL representation shown in Figure~\ref{fig:FOLRep}, we invoke Algorithm~\ref{alg:SenAnnotaator} with the semantic graph shown in Figure~\ref{fig:knowledge}.
-Our algorithm attempts to find a leaf node containing term ``CONTACT'' or some of its synonym.
-Since the FOL representation does not contain such a leaf node, algorithm calls itself with semantic graphs of subordinate resources (Line 17-25), namely `NUMBER', `EMAIL', `LOCATION', `BIRTHDAY', `ANNIVERSARY'.
-%
-%The subsequent invocation will find the leaf-node ``email'' (annotated 9 in Figure~\ref{fig:FOLRep}).
-Our algorithm then explores the preceding predicates and finds predicate ``share'' (annotated 2 in Figure~\ref{fig:FOLRep}).
-The Algorithm matches the word ``share'' with action ``send'' (using Lemmatisation and WordNet similarity), one of the actions available in the semantic graph of resource `EMAIL' and returns \CodeIn{true}.
-Thus, the sentence is appropriately identified as describing the need for permission READ\_CONTACT.
-%
-%

### 2014-01-23 Draft/evaluation.tex
Changed approach, Introduction

--- 2014-01-23 Draft/evaluation.tex
@@
 
-We conducted an evaluation to assess the effectiveness of our approach. In our evaluation, we address two main research questions:
+We conducted an evaluation to assess the effectiveness of \tool. In our evaluation, we address two main research questions:
 
@@
 	\item\textbf{RQ1}: What are the precision and recall of \tool\  in
-	identifying temporal contraints from sentences written in natural language?
-	%\item\textbf{RQ2}: What is the accuracy of our approach in inferring specifications from contract sentences in the API documents? 
-	\item\textbf{RQ2}: How does our approach fares in comparison to previous NLP approaches?
+	identifying temporal constraints from sentences written in natural language?
+	\item\textbf{RQ2}: What is the accuracy of \tool\ in inferring temporal constraints from specification sentences in the API documents? 
 \end{itemize}
@@
 \subsection{Experimental Setup.} 
-We apply our approach on the API documents of the two APIs.
-To determine the precision and recall, 
-two authors manually label each sentence in the API documentation as sentence containing 
-temporal constraints or not. After the authors have classified all the sentences, they 
-talk to each ther to reach a consensus on the sentences they classified differently. 
-We use this classified scentes as the golden set for calculating precision and recall.
+We first manually annotated the sentences in the API documents of the two APIs.
+Two authors manually labeled each sentence in the API documentation as sentence containing 
+temporal constraints or not.
+We used \CodeIn{cohen kappa}~\cite{carletta1996assessing} score to statistically measure
+the inter-rater agreement.
+The \CodeIn{cohen kappa} score of the two authors was .66 (on a scale of 0 to 1), 
+which denotes a statically significant agreement. 
+After the authors classified all the sentences, they 
+discussed with each other to reach a consensus on the sentences they classified differently. 
+We use this classified sentences as the golden set for calculating precision and recall.
 
-\CodeIn{cohen kappa} score of the two authors was 6.6
+To answer RQ1, we measure the number of true positives ($TP$), false positives ($FP$), true negative ($TN$), and false negatives ($FN$)
+in identifying the specification sentences by \tool.
+We define specification sentence as a sentence describing a temporal constraints.
+We define the $TP$, $FP$, $TN$, and $FN$ of \tool\ as follows:
+
+\begin{enumerate}
+	\item $TP$: A sentence correctly identified by \tool\ as specification sentence.
+	\item $FP$: A sentence incorrectly identified by \tool as specification sentence.
+	\item $TN$: A sentence correctly identified by \tool\ as not a specification sentence.
+	\item $FN$: A sentence incorrectly identified by \tool\ as not a specification sentence.
+\end{enumerate}
+
+In statistical classification~\cite{Olson08}, $Precision$ is defined as a ratio of
+number of true positives to the total number of items reported to be true,
+$Recall$ is defined as a ratio of number of true positives to the total number
+of items that are true. $F-score$ is defined as the weighted harmonic mean of 
+$Precision$ and $Recall$. Higher value of $Precision$, $Recall$, and $F-Score$
+are indicative of higher quality of the specification statements inferred using 
+\tool. based on the calculation of $TP$, $FP$, $TN$, and $FN$ of \tool\ defined
+previously we computed the $Precision$, $Recall$, and $F-Score$ of \tool\ as follows:
+
+\begin{center}
+
+$Precision$ = $\frac{TP}{TP + FP}$
+
+$Recall$ = $\frac{FN}{TP + FP}$
+
+$F-Score$ = $\frac{2 X Precison X Recall}{Precision + Recall}$
+
+\end{center}
+
+To answer RQ2, we checked the temporal constraints inferred from specification sentences by \tool.
+We measure $accuracy$ of \tool as the ratio of the total number of temporal constraints that
+are correctly inferred by \tool to the total number of specification sentences.
+
+\subsection{Results}
+
+We next describe our evaluation results to demonstrate the effectiveness of \tool\ in identifying temporal constraints.
+
+\subsubsection{RQ1: Effectiveness in Identifying Specification Sentences}
+
+In this section, we evaluate the effectiveness of \tool\ in identifying specification sentences from API documents.
+
+We next describe how
+
+\subsubsection{RQ2: Accuracy in Inferring Temporal Constraints}
+
+In this section, we evaluate the effectiveness of \tool\ in inferring specification sentences from API documents.
 

### 2014-01-23 Draft/abstract.tex
Changed Abstract and Intro

@@
 \begin{abstract}
-Formal specifications of using a libraries Application Programming Interface (API)
-can be used in conjunction with formal analysis tools such as
-model checkers and runtime verifiers to assess the quality of a software.
-Despite being desirable, most API's do not have formal specifications.
+Temporal specifications of an Application Programming
+Interface (API) describe allowed sequences of invocations
+of methods within an API. Despite being desirable for 
+software testing and verification (through formal analysis tools),
+most API's do not have formal temporal specifications.
 In contrast, API documents contain valuable information about the usage in natural language.
@@
 To address this issue, we propose a natural language processing based automated approach \tool ,
-to infer formal specifications from natural language text of API documents.
-In particular, we focus on temporal constraints, that are defined as constraints on the
-\textit{allowed sequence of invocations of methods within an API}.
+to infer formal temporal specifications from natural language text of API documents.
 To evaluate our proposed approach, we applied \tool\ to infer temporal constraints from 

### 2014-01-23 Draft/introduction.tex
Changed Abstract and Intro

@@
 	An open source implementation of the prototype is publicly available on our project website\footnote{\url{https://sites.google.com/site/icon}}. 
-	\item An evaluation of proposed approach on Java 7 and Amazon S3 REST API.
+	\item An evaluation of proposed approach on 
+commonly used package \CodeIn{java.io} from JDK API and Amazon
+S3 REST API. Our evaluation results show that \CodeIn{ICON} achieves
+an average of 60\% precision and 80\% recall in inferring 63
+temporal constraints from more than 2400 sentences of API
+documents.
 \end{itemize}

### 2014-01-23 Draft/example.tex
Changed Example Mativation

@@
 Thus, the resultant system is inconsistent with the intentions that a developer had in mind initially.
-This inconsistency oftentimes result in undesirable consequences ranging from developer frustration, customer dissatisfaction, to actual financial losses.
+We suspect the reason for this phenomena is that API documentation is often verbose and information is distributed across various
+pages.
+For example, the PDF version of the documentation for Amazon S3 API\footnote{\url{http://awsdocs.s3.amazonaws.com/S3/latest/s3-api.pdf}} spans 278 pages.
+Developers do not have time and patience to go through all the documentation and miss various temporal specifications of the API, which often result in defective applications that do not follow temporal specifications.
+If we have the formal temporal specifications such kinds of defects can be detected by formal verification tools.
 
@@
 
-For example consider the question asked in \textit{Stack Overflow}~\footnote{\url{http://stackoverflow.com/}} as shown in Figure~\ref{fig:Stackoverflow}.
+Consider the question asked in \textit{Stack Overflow}~\footnote{\url{http://stackoverflow.com/}} as shown in Figure~\ref{fig:Stackoverflow}.
 Stack Overflow is a question and answer site for professional and enthusiast programmers.

### 2014-01-23 Draft/example.tex
More changes in Example

@@
 We now present some real world examples to motivate our approach.
-In particular, through these examples we demonstrate that developers often overlook the documentation.
-Thus, the resultant system is inconsistent with the intentions that a developer had in mind initially.
+In particular, through these examples, we demonstrate that developers often ignore the tempral specifications of an API present in its documentation.
 We suspect the reason for this phenomena is that API documentation is often verbose and information is distributed across various
@@
 For example, the PDF version of the documentation for Amazon S3 API\footnote{\url{http://awsdocs.s3.amazonaws.com/S3/latest/s3-api.pdf}} spans 278 pages.
-Developers do not have time and patience to go through all the documentation and miss various temporal specifications of the API, which often result in defective applications that do not follow temporal specifications.
+Developers do not have time and patience to go through all the documentation and miss various temporal specifications of the API, resulting in defective applications that do not follow temporal specifications.
 If we have the formal temporal specifications such kinds of defects can be detected by formal verification tools.
@@
 Figure~\ref{fig:AmzonS3DeleteBucketAPI} shows the documentation of delete bucket method.
-The documents clearly states (outlined in red for clarity) that before deleting the bucket the objects in the buckets must be deleted.
-Although the issue was fixed but notice that the response on the \textit{Stack Overflow} encouraged the person asking query to switch to another product, thus potentially resulting in a loss of revenue attributed to customer dissatisfaction.
+The documents states (outlined in red for clarity) that before deleting the bucket the objects in the buckets must be deleted.
+Although the issue was fixed but notice that one of the responses on the \textit{Stack Overflow} encouraged the person asking query to switch to another product, thus potentially resulting in a loss of revenue attributed to customer dissatisfaction.
+In yet another example a developer points out the financial losses he suffered because he was incorrectly using the previously described delete bucket functionality as shown in Figure~\ref{fig:example2}.
 
@@
 
-In yet another example a developer points out the financial losses he suffered because he was incorrectly using the previously described delete bucket functionality as shown in Figure~\ref{fig:example2}.
-The problems in the previously described examples could have been alleviated if developers paid more attention to the documentation.
-However, as pointed out by Novick et.
-al~\cite{Novick2006WDP} that developers often overlook the documentation.
-Furthermore, since these documents are written in natural language they cannot be subjected to machine based verification.
-Thus, there is need for an approach to translate the constraints described in natural language into a more formal notation.
-Although, we only use examples from the developer forums and blogs for \amazon\ to motivate our approach.
-In next section, we briefly discuss the related work in this area.
+Formal verification tools can be used to find such kind of defects. However, formal analysis
+tools are not designed to work on specifications in natural languages (such as API Documents) and require the specifications in a more formal machine understandable form. 
+Thus, there is need for an approach to translate the constraints described in natural language into a more formal notation. In next section, we briefly discuss the related work in this area.
 

### 2014-01-24 Draft/background.tex
Fixed background

@@
 We first introduce the core NLP techniques used in this work.
-We then introduce the software engineering specific NLP techniques proposed in previous work~\cite{pandita12:inferring,pandita13:WHYPER} that have been used in this work.
+We then introduce the software engineering specific NLP techniques proposed in previous work~\cite{pandita12:inferring,pandita13:WHYPER} that are used in this work.
 
@@
 The most commonly used technique is to train a classification parser over a previously known data set.
-Current state of the art approaches been have demonstrated to achieve 97\%~\cite{SNLP1} accuracy in classifying POS tags for well written news articles.
+Current state of the art approaches have demonstrated to achieve 97\%~\cite{SNLP1} accuracy in classifying POS tags for well written news articles.
 
@@
 \textbf{Named Entity Recognition}~\cite{Finkel05ACL}.
-Also known as \textit{`entity identification'} and \textit{`entity extraction'}, these techniques are a subtask of IE that aims to classify words in a sentence into predefined categories such as names, quantities, expression of times, etc.
+Also known as \textit{`entity identification'} and \textit{`entity extraction'}, these techniques are a subtask of information extraction that aims to classify words in a sentence into predefined categories such as names, quantities, expression of times, etc.
 These techniques help in associating predefined semantic meaning to a word or a group of words (phrase), thus facilitating semantic processing of named entities.
@@
 \textbf{Noun Boosting}~\cite{pandita12:inferring}. Accurate annotation of POS tags in a sentence is fundamental to effectiveness of any advanced NLP technique.
-However, as mentioned earlier, POS tagging work well on well written news articles which does not necessary entail that the tagging works well on domain specific text as well.
+However, as mentioned earlier, POS tagging works well on well written news articles which does not necessary entail that the tagging works well on domain specific text as well.
 Thus, noun boosting is a necessary precursor to application of POS tagging on domain specific text.
@@
 Consider the word \CodeIn{POST} for instance. 
-The online Oxford dictionary~\footnote{\url{http://oxforddictionaries.com/us/definition/american_english/post?q=POST}} has 8 different definition of word \CodeIn{POST}, and none of them describes \CodeIn{POST} as a HTTP method
-~\footnote{In HTTP vocabulary \CodeIn{POST} means: ''Creates a new entry in the collection.
+The online Oxford dictionary\footnote{\url{http://oxforddictionaries.com/us/definition/american_english/post?q=POST}} has 8 different definition of word \CodeIn{POST}, and none of them describes \CodeIn{POST} as a HTTP method\footnote{In HTTP vocabulary \CodeIn{POST} means: ''Creates a new entry in the collection.
 The new entry's URI is assigned automatically and is usually returned by the operation''}
@@
 Noun Boosting identifies such words from the sentences based on a domain-specific dictionaries, and annotates them appropriately.
-The annotation assists the POS tagger to accurately annotate the POS tags of the words thus inturn increasing accuracy of advanced NLP techniques such as chunking and typed dependency annotation.
+The annotation assists the POS tagger to accurately annotate the POS tags of the words thus in turn increasing accuracy of advanced NLP techniques such as chunking and typed dependency annotation.
 
@@
 \item \textbf{Abbreviation Handling}. Natural-language sentences often consist of abbreviations mixed with text.
-This can result in subsequent components to incorrectly parse a sentence.
+This phenomenon can result in subsequent components to incorrectly parse a sentence.
 This heuristic finds such instances and annotates them as a single lexical unit.
@@
 In particular, WHYPER~\cite{pandita13:WHYPER} demonstrates the effectiveness of this technique, by constructing an intermediate representation generator based on shallow parsing~\cite{Branimir2000} techniques.
-The shallow parser itself is implemented as sequence of cascading finite state machines based on the functions of stanford-typed dependencies~\cite{Marneffe06LREC,Marneffe08COLING,Klein03,KleinNIPS03}.
+The shallow parser itself is implemented as a sequence of cascading finite state machines based on the functions of stanford-typed dependencies~\cite{Marneffe06LREC,Marneffe08COLING,Klein03,KleinNIPS03}.
 

### 2014-01-24 Draft/approach.tex
Changed Approach

@@
 The text-analysis engine further transforms the annotated sentences into the first-order-logic (FOL) representation.
+The semantic graph generator accepts the API documents and generates the semantic graphs that are leveraged by specification extractor component.
+The type analyzer component infers temporal constraints encoded in the type system of a language by analyzing the API methods parameter and return types.
 Finally, the specification extractor then leverages the semantic graphs to infer temporal constraints from the FOL representation of a sentence.
-Besides the previously described components the approach also consists of a semantic graph generator and type analyzer.
-The semantic graph generator accepts the API documents and generates the semantic graphs that are leveraged by specification extractor component.
-The type analyzer components infers temporal constraints encoded in the type system of a language by analyzing the API methods parameter and return types.
+
 We next describe each component in detail.
@@
 After extracting desired information, the natural language text is further preprocessed to be analyzed by subsequent components.
-The preprocessing steps are required to increase the accuracy core NLP techniques (described in Section~\ref{sub:CoreNLPback}) that are used in the subsequent phases of \tool\ approach.
+The preprocessing steps are required to increase the accuracy of core NLP techniques (described in Section~\ref{sub:CoreNLPback}) that are used in the subsequent phases of \tool\ approach.
 In particular, the preprocessor first employs the noun boosting followed by heuristics listed under lexical token reduction, as introduced in Section~\ref{sub:SENLPback}.
@@
 For instance, \textit{Amazon Simple Storage Service}, \textit{an I/O Error Occurs}, and \textit{end of stream} are the examples of such n-grams detected by our approach.
-
 %\begin{figure}[t]
@@
 %\end{figure}
-
-\textbf{Prototype Implementation}
-
+\\
+\textbf{Prototype Implementation.}
 Currently our prototype implementation works with online \amazon\ and JDK API. 
@@
 
-Additionally, in current implementation we have manually built the domain dictionaries for the preprocessing using the glossary of terms collected from the websites pertaining to REST and Java API.
+Additionally, in current implementation we have manually built the domain dictionaries for preprocessing using the glossary of terms collected from the websites pertaining to REST and Java API.
 We further leveraged the HTML style information in \amazon\ to look for words that were highlighted in code like format.
@@
 
-Finally, to achieve  n-gram reduction we used Apache Lucene$^{\textregistered}$~\cite{lucene} to achieve.
+Finally, to achieve  n-gram reduction we used Apache Lucene$^{\textregistered}$~\cite{lucene}.
 Apache Lucene is a high-performance, full-featured text search engine library written entirely in Java.
@@
 This limitation mandates the use of additional novel technique of \textit{`Frequent Phrases Reduction'} in preprocessing phase.
-We further improve the accuracy of intermediate-representation generation by proposing an hybrid approach, i.e. taking into consideration both the POS tags as well as Stanford-typed dependencies.
+We further improve the accuracy of intermediate-representation generation by proposing a hybrid approach, i.e. taking into consideration both the POS tags as well as Stanford-typed dependencies.
 The POS tags which annotate the syntactical structure of a sentence are used to further simplify the constituent elements in a sentence. 
 We then use the Stanford-typed dependencies that annotate the grammatical relationships between words to construct our FOL representation.
-Thus, the intermediate representation generator used in this work is two phase process as opposed to previous work~\cite{pandita12:inferring, pandita13:WHYPER}. 
+Thus, the intermediate representation generator used in this work is a two phase process as opposed to previous work~\cite{pandita12:inferring, pandita13:WHYPER}. 
 We next describe these two phases:
@@
 if a candidate sentence is a specification sentence and if so extract
-the action that is should be performed prior to the method the sentence
+the action that should be performed prior to the method the sentence
 belongs to. Algorithm~\ref{alg:SenAnnotaator} describes this action extraction
@@
 Then, for every public method in the input list, the algorithm checks the types
-of the input parameters and constructs and directed edge from all the methods that whose return value
+of the input parameters and constructs and directed edge from all the methods whose return value
 have the same type to the method in question (Line 14- 20).
-The algorithm does not take into consideration the basic parameter types such as integer, string (Line 15)
+The algorithm does not take into consideration the basic parameter types such as integer, string (Line 15).
 Additionally, an edge is created from the constructors of a class to the non static members methods of a class (Line 8 -13).

### 2014-02-19 Draft/abstract.tex
Updated some  reading group comments

@@
 commonly used package \CodeIn{java.io} from JDK API and Amazon S3 REST API.
-Our evaluation results show that \tool\ achieves an average of 60\% precision and 80\% recall
+Our evaluation results show that \tool\ achieves an average of 70\% precision and 80\% recall
 in inferring 63 temporal constraints from more than 2400 sentences of API documents.
 
+% Goal Statement
+% Negating everything as we go along
+% Instead of despite 
 % need to explain why moving from formal specifications to temporal constraints
+% bridging
+% Goal statement
+% The goal of this research is to facilitate the correct usage API methods by identifying temporal constraints.
+% to support tool based verfication
+% Avoid starting the abstarct with a definition
+% bridge the gap
+% There is an order that API documents tell 
+% but they are 
+% Adhering to temporal constraints is mandatory for correct usage of API
+% However, it not starightforward to 
+% Motivation
+% Goal
+% Evaluation
+% Structured Abstract
+% what is the significance of this prescison i/p o/p
+% expresses 
+% makes end to end summary.
 
-% Goal statement
-% The goal of this research is to facilitate the correct usage API methods by identifying temporal constraints etc.. 
+% where do you loose precision and recall.
 \end{abstract}

### 2014-02-19 Draft/approach.tex
Updated some  reading group comments

@@
 Finally, the specification extractor then leverages the semantic graphs to infer temporal constraints from the FOL representation of a sentence.
-
 We next describe each component in detail.
@@
 However, this component can be implemented using any other existing NLP libraries or approachs.
-In particular, we annotate each sentence with POS tags, named-entity Annotations and Stanford-typed dependencies.
+In particular, we annotate each sentence with POS tags, named-entity annotations and Stanford-typed dependencies.
 For more details on these techniques and their application, please refer to ~\cite{Marneffe06LREC, Marneffe08COLING, pandita12:inferring, pandita13:WHYPER, thummalapentaICSE12}.
@@
 The text analysis engine component accepts the annotated documents and creates an intermediate representation of each sentence.
-We define our representation as a tree structure that is essentially a First-Order-Logic (FOL) expression.
+We define our representation as a tree structure that is essentially a FOL expression.
 Research literature provides evidence of the adequacy of using FOL for NLP related analysis tasks~\cite{Sinha2009,Sinha2010,pandita12:inferring, pandita13:WHYPER}.
@@
 All of these semantic templates are publicly available on our project website~\cite{projectweb}.
-With respect to the previous example the template no. 3 \textit{( A noun phrase followed by another noun/pronoun/verb phrase in brackets)} is applicable.
+With respect to the previous example the template 3 \textit{( A noun phrase followed by another noun/pronoun/verb phrase in brackets)} is applicable.
 Thus our shallow parser breaks the sentence into two individual sentences.
@@
 	Typically such sentences describe pre-post conditions as opposed to temporal constraints this approach addresses.
-	\item The sentences contains modal modifiers such as ``can, could, may, must, should'' expressing necessity.
+	\item The sentences contains modal modifiers such as ``\textit{can, could, may, must, should}'' expressing necessity.
 	Typically, presence of such modal modifier is a strong indicator of presence of constraints imposed by an API developer
@@
 	Typically, presence of temporal modifier is an indicator of presence of temporal information.  
-	\item If rules 2 and 3 don't apply then the sentences should be a conditional sentence, identified by the presence of keywords such as ``if''.
+	\item If rules 2 and 3 don't apply then the sentences should be a conditional sentence, identified by the presence of keywords such as ``\textit{if}''.
 \end{enumerate}

### 2014-02-19 Draft/background.tex
Updated some  reading group comments

@@
 Consider the word \CodeIn{POST} for instance. 
-The online Oxford dictionary\footnote{\url{http://oxforddictionaries.com/us/definition/american_english/post?q=POST}} has 8 different definition of word \CodeIn{POST}, and none of them describes \CodeIn{POST} as a HTTP method\footnote{In HTTP vocabulary \CodeIn{POST} means: ''Creates a new entry in the collection.
-The new entry's URI is assigned automatically and is usually returned by the operation''}
+The online Oxford dictionary\footnote{\url{http://oxforddictionaries.com/us/definition/american_english/post?q=POST}} has 8 different definition of word \CodeIn{POST}, and none of them describes \CodeIn{POST} as a HTTP method\footnote{In HTTP vocabulary \CodeIn{POST} means: \textit{``Creates a new entry in the collection.
+The new entry's URI is assigned automatically and is usually returned by the operation''}}
 supported by REST API.

### 2014-02-19 Draft/example.tex
Updated some  reading group comments

@@
 For example, the PDF version of the documentation for Amazon S3 API\footnote{\url{http://awsdocs.s3.amazonaws.com/S3/latest/s3-api.pdf}} spans 278 pages.
-Developers do not have time and patience to go through all the documentation and miss various temporal specifications of the API, resulting in defective applications that do not follow temporal specifications.
+Developers do not have time and patience to go through all the documentation and miss various temporal specifications of the API, resulting in defective applications that invoke API methods in sequences prohibited by documentation.
 If we have the formal temporal specifications such kinds of defects can be detected by formal verification tools.
@@
 \begin{center}
-\includegraphics[scale=0.4]{Stackoverflow.eps}
+\includegraphics[scale=0.45]{Stackoverflow.eps}
 \end{center}
@@
 The query is about the delete functionality of a third-party software \CodeIn{S3Fox} to interact with \amazonAPI.
-In particular, the query complains about an issue in delete bucket functionality of the \CodeIn{S3Fox}.
+The inquisitor complains about an issue in delete bucket functionality of the \CodeIn{S3Fox}.
 In particular, the issue was because the \CodeIn{S3Fox} developers overlooked the specifications in \amazon.
-Figure~\ref{fig:AmzonS3DeleteBucketAPI} shows the documentation of delete bucket method.
-The documents states (outlined in red for clarity) that before deleting the bucket the objects in the buckets must be deleted.
+The document clearly states that before deleting the bucket, the objects in the buckets must be deleted.
+\textit{``All objects (including all objects versions and Delete Markers) in the bucket must be deleted before the bucket itself can be deleted''}.
 Although the issue was fixed but notice that one of the responses on the \textit{Stack Overflow} encouraged the person asking query to switch to another product, thus potentially resulting in a loss of revenue attributed to customer dissatisfaction.
-In yet another example a developer points out the financial losses he suffered because he was incorrectly using the previously described delete bucket functionality as shown in Figure~\ref{fig:example2}.
+In yet another example a developer points out the financial losses he suffered because he was incorrectly using the previously described delete bucket functionality as shown in Figure~\ref{fig:example2}, \textit{(``...paying for excess stuff you don't need is simply idiotic...'')}.
+
+%\begin{figure}[t]
+%\begin{center}
+%\includegraphics[scale=0.5]{AmzonS3DeleteBucketAPI.eps}
+%\end{center}
+%\caption{\label{fig:AmzonS3DeleteBucketAPI} The online API document for \CodeIn{DELETE Bucket} operation in Amazon S3 REST API}
+%\end{figure}
+
+Formal verification tools can be used to easily find such kind of defects.
+However, formal analysis tools are not designed to work on specifications in natural languages (such as API Documents) and require the specifications in a more formal or machine understandable format.
+Thus, there is need for an approach to automatically translate the constraints described in natural language into a more formal notation.
+In next section, we briefly discuss the related work in this area.
 
@@
 \begin{center}
-\includegraphics[scale=0.4]{AmzonS3DeleteBucketAPI.eps}
-\end{center}
-\caption{\label{fig:AmzonS3DeleteBucketAPI} The online API document for \CodeIn{DELETE Bucket} operation in Amazon S3 REST API}
-\end{figure}
-
-Formal verification tools can be used to find such kind of defects. However, formal analysis
-tools are not designed to work on specifications in natural languages (such as API Documents) and require the specifications in a more formal machine understandable form. 
-Thus, there is need for an approach to translate the constraints described in natural language into a more formal notation. In next section, we briefly discuss the related work in this area.
-
-\begin{figure}[t]
-\begin{center}
-\includegraphics[scale=0.4]{Example2.eps}
+\includegraphics[scale=0.6]{Example2.eps}
 \end{center}

### 2014-02-19 Draft/introduction.tex
Updated some  reading group comments

@@
 %For example, J2EE's API documentation\footnote{\url{http:\\download.oracle.com/javaee/1.7/api/}} is one of the popular API documents.
-Typically, an API document describes both the constraints on that method parameters as well as the temporal constraints in terms of the methods must be invoked pre/post the current method.
-We observed that roughly 12\% of the sentences describing some sort of specification constraints in \amazonAPI\ documentations describe temporal constraints.
-Although API documents contain temporal constraints in natural language, formal analysis tools are not designed to work on specifications written in natural languages.
+For a method under consideration, an API document may describe both the constraints on that method parameters as well as the temporal constraints in terms of the methods must be invoked pre/post the method.
+We observed that roughly 12\% of the sentences (that describe some sort of specification constraints) in \amazonAPI\ documentations describe temporal constraints.
+Although API documents contain temporal constraints, existing formal analysis tools are not designed to work on specifications written in natural language.
 
@@
 However, manually writing formal specifications based on natural language text in API documents can be prohibitively time consuming and error prone~\cite{wu2013inferring,RubingerWEB10}. 
-For instance, Wu et al.~\cite{wu2013inferring} report that it took one of the authors more than 10 hours to browse the documentation of one method of a web Service API, even before they attempted to formalize the constraints on the method.
+For instance, Wu et al.~\cite{wu2013inferring} report that it took one of the authors more than 10 hours to browse the documentation of one method of a web service API, even before they attempted to formalize the constraints on the method.
 
 %Strike out ``To address the aforementioned issue''
-We propose a novel approach to infer temporal usage constraints from natural language text of API documents.
-We propose a new approach that apply Natural Language Processing (NLP) on natural language text API documents to automatically infer temporal usage constraints.
+%We propose a novel approach to infer temporal usage constraints from natural language text of API documents. 
+In contrast to manual approach, we propose an automated approach that applies Natural Language Processing (NLP) techniques on natural language text in API documents to infer temporal usage constraints.
 %In particular, we focus on specific type of constraints namely temporal constraints.
@@
 % Amazon S3 is popularly used web service for simple cloud based storage
-There are existing approaches focus on inferring just the method pre-post conditions in terms of parameter constraints either using program analysis techniques~\cite{Henkel07discoveringdocumentation,Ghezzi:2009:SIB:1555001.1555057,Henkel:2008:DDA:1363102.1363105,Flanagan:2001:HAA:647540.730008,Buse:2008:ADI:1390630.1390664} or using NLP~\cite{pandita12:inferring, wu2013inferring}.
+\textbf{There are} existing approaches focus on inferring just the method pre-post conditions in terms of parameter constraints either using program analysis techniques~\cite{Henkel07discoveringdocumentation,Ghezzi:2009:SIB:1555001.1555057,Henkel:2008:DDA:1363102.1363105,Flanagan:2001:HAA:647540.730008,Buse:2008:ADI:1390630.1390664} or using NLP~\cite{pandita12:inferring, wu2013inferring}.
 In contrast, temporal constraints are beyond these parameter constraints.
@@
 
-First, relying just on type information will result in a incomplete list of temporal constraints. 
-Although, in typed languages some temporal constraints are enforced by type system. 
+First, relying just on type information will result in an incomplete list of temporal constraints. 
+In typed languages some temporal constraints are enforced by type system. 
 For instances a method ($m$) accepting input parameter ($i$) of type ($t$) mandates that (at least one) method ($m'$) be invoked whose return value is of type ($t$).
 However, temporal constraints are not limited by the type definitions (i.e, requirements on the type of input parameters), and are currently expressed mostly in natural language in API documents, as described in the example previously.
-We propose to address the issue by augmenting the type definitions based temporal constraints with the the constraints inferred from
+We propose to address the issue by augmenting the type definitions based temporal constraints with the constraints inferred from
 the natural language text in API documents.
@@
 In addition to these challenges, we have an added challenge of identifying the method referenced in the natural language text to infer temporal constraint.
-Recall, the description sentence ``You must initiate a multipart upload before you can upload any part.''
+Recall the description sentence ``You must initiate a multipart upload before you can upload any part.''
 In this sentence, phrases ``multipart upload'' and ``upload any part'' refer to individual methods in the API.
-Identifying these phrases as method invocation instances require domain dictionaries.
-Ad-hoc constructing these dictionaries is prohibitively time and resources intensive.
-To address this challenge, we propose to build domain-dictionaries systematically from API documents themselves.
+Identifying these phrases as method invocation instances requires domain dictionaries.
+Ad-hoc construction of such dictionaries is prohibitively time and resources intensive.
+To address this challenge, we propose to build domain-dictionaries systematically from API documents and generic English dictionaries.
 
@@
 \begin{itemize}
-	\item A NLP based approach that infers temporal constraints of method invocations. 
+	\item An NLP based approach that infers temporal constraints of method invocations. 
 	To the best of our knowledge, our approach is the first one to apply NLP for the goal of inferring temporal specifications from API documents.
@@
 S3 REST API. Our evaluation results show that \CodeIn{ICON} achieves
-an average of 60\% precision and 80\% recall in inferring 63
+an average of 70\% precision and 80\% recall in inferring 63
 temporal constraints from more than 2400 sentences of API
@@
 The rest of the paper is organized as follows.
-Section~\ref{sec:example} presents an real world examples that motivate our approach.
+Section~\ref{sec:example} presents real world examples that motivate our approach.
 Section~\ref{sec:related} discusses related work in this area.
-Section~\ref{sec:background} presents the  background on code contracts as well as NLP.
+Section~\ref{sec:background} presents the  background on NLP techniques used in this work.
 Section~\ref{sec:approach} presents our approach.

### 2014-03-02 Draft/evaluation.tex
Updated some  reading group comments
updated evaluation

@@
 
-$Recall$ = $\frac{FN}{TP + FP}$
+$Recall$ = $\frac{TP}{TP + FN}$
 
@@
 
-In this section, we evaluate the effectiveness of \tool\ in identifying specification sentences from API documents.
+In this section, we quantify the effectiveness of \tool\ in identifying specification sentences by answering RQ1.
+Our results show that, out of 2,414 sentences, \tool\ effectively identifies specification sentences with the average precision, recall, F-score, and accuracy of 65.0\%, 71.8\%, 68.7\%, and 97.9\%, respectively.
 
-We next describe how
+We next present an example to illustrate how \tool\ incorrectly identifies a sentence as a specification sentence.
+
+We next present an example to illustrate how \tool\ incorrectly identifies a sentence as a specification sentence (producing false positives).
+For instance, consider the sentence ``\textit{This is done by flushing the stream and then closing the underlying output stream.}'' from  \CodeIn{close} method description from \CodeIn{PrintStream} class.
+\tool\ fails to make the distinction
+
+Another major source of FPs is the incorrect parsing of sentences by the underlying NLP infrastructure and/or inadequacy of generic dictionaries for synonym analysis.
+For instance, consider the sentence ``\textit{If this stream has an associated channel then the channel is closed as well.}'' from the \CodeIn{close} method description from \CodeIn{FileOutputStream}.
+The sentence describes an effect that happens as a result of calling the \CodeIn{close} method and does not describe any temporal constraint.
+However, \tool\ annotates the sentence as a specification sentence because underlying Wordnet dictionaries matches the word ``has'' as a synonym of ``get''.
+This incorrect matching in turn causes \tool to incorrectly annotate the sentence as specification sentence because ``has'' is matched against \CodeIn(get) method in \CodeIn{FileOutputStream}.
+We observed 8 instances of previously described example in our results.
+
+If we manually fixed the Wordnet dictionaries to match ``has'' and ``get'' as synonyms, our precision is further increased to 70.8\% effectively increasing the F-Score of \tool to 71.2\%.
+We refrained from including such modifications for reporting the results to stay true to our proposed framework.
+In the future, we plan to investigate techniques to construct better domain dictionaries for software API.
+
+We next present an example to illustrate how \tool\ fails identify a specification sentence (producing false negative).
+False negatives are particularly undesirable in the context of our problem domain, because they can mislead the users of \tool\ into believing that no other temporal constraint exists in the API document.
+Furthermore, an overwhelming number of false negatives works against the usefulness of \tool.
+For instance, consider the sentence ``\textit{This is done by flushing the stream and then closing the underlying output stream.}'' from  \CodeIn{close} method description from \CodeIn{PrintStream} class.
+The sentence describes the constraint in terms of invoking the same method again.
+Although \tool\ correctly identifies the method \CodeIn{close} in the sentence, \tool\ currently does not support temporal constraint on the same method.
+Aforementioned, limitation causes \tool\ to not identify the statement as a specification constraint.
+
+Another major source of false negatives (similar to reasons for false positives) is the incorrect parsing of sentences by the underlying NLP infrastructure.
+For instance, consider the sentence ``\textit{If any in-memory buffering is being done by the application (for example, by a BufferedOutputStream object), those buffers must be flushed into the FileDescriptor (for example, by invoking OutputStream.flush) before that data will be affected by sync.}'' The sentence describes that the \CodeIn{OutputStream.flush()} must be invoked before invoking the current method if in-memory buffering is performed.
+However, the length and complexity in terms of number of clauses causes the underlying Stanford parser to inaccurately annotate the dependencies, which eventually results into incorrect classification.
+
+Overall, a significant number of false positives and false negatives will be reduced as the current NLP research advances the underlying NLP infrastructure.
+Furthermore, use of domain specific dictionaries as opposed to generic dictionaries used in current prototype implementation will further improve the precision and recall of \tool.
 

### 2014-03-12 Draft/abstract.tex
Changed to new ACM Format
+ added sig-alternate class for new ACM format
+ fixed abstract as per Dr. Xie's comments
+ added eval results Table in evaluation

@@
 Temporal specifications of an Application Programming
-Interface (API) describe allowed sequences of invocations
+Interface (API) describe allowed sequence of invocations
 of methods within an API. Despite being desirable for 
@@
 In contrast, API documents contain valuable information about the usage in natural language.
-However, formal analysis tools are not designed to work on specifications in natural languages.
+Although existing techniques infer from API documents method specifications (such as method precondition and postconditions) or resource specifications (such as constraints on creating/releasing resources), such techniques fail to explicitly infer temporal constraints.
 Manually writing formal specifications based on natural language text in API documents
 can be prohibitively time consuming and error prone.
-To address this issue, we propose a natural language processing based automated approach \tool ,
+To address this issue, we propose a natural language processing based automated approach \tool,
 to infer formal temporal specifications from natural language text of API documents.
+\tool\ uses 
 To evaluate our proposed approach, we applied \tool\ to infer temporal constraints from 
-commonly used package \CodeIn{java.io} from JDK API and Amazon S3 REST API.
-Our evaluation results show that \tool\ achieves an average of 70\% precision and 80\% recall
-in inferring 63 temporal constraints from more than 2400 sentences of API documents.
+commonly used package \CodeIn{java.io} from JDK API and \amazonAPI.
+Our evaluation results show that \tool\ achieves an average of 66\% precision and 70\% recall
+in inferring 69 temporal constraints from more than 3900 sentences of API documents.
 

### 2014-03-12 Draft/evaluation.tex
updated to ACM style
Changed to new ACM Format
+ added sig-alternate class for new ACM format
+ fixed abstract as per Dr. Xie's comments
+ added eval results Table in evaluation

@@
 $F-Score$ = $\frac{2 X Precison X Recall}{Precision + Recall}$
-
 \end{center}
@@
 
+\begin{table*}
+\begin{center}
+
+\caption{Evaluation Results}
+
+\begin{tabular}{|c|c|c|c|c|c|c|c|c|c|c|}
+\hline API & Methods & No. of Sentences & Spec Sentences & ICON Ann & TP & FP & FN & P & R & F-Score \\ 
+\hline java.io &  & 2417 & 78 & 87 & 56 & 31 & 22 & 64.4 & 71.8 & 67.9 \\ 
+\hline AMAZON S3 REST & 51 & 1492 & 12 & 12 & 8 & 4 & 4 & 66.7 & 66.7 & 66.7 \\ 
+\hline Total &  & 3909 & 90 & 99 & 64 & 35 & 26 & 64.6$^*$ & 71.1$^*$ & 67.7$^*$ \\ 
+\hline
+%----------------- END TABLE DATA ------------------------ 
+\multicolumn{11}{p{6.5in}}{\footnotesize $^*$ Column average; TP: Total number of True Positives; 
+FP: Total number of False Positives; FN: Total number of False Negatives; P: Precision; R: Recall} \\ 
+\end{tabular}
+\end{center}
+\end{table*}
+
 \subsubsection{RQ1: Effectiveness in Identifying Specification Sentences}
@@
 
-We next present an example to illustrate how \tool\ incorrectly identifies a sentence as a specification sentence.
+We next present an example to illustrate how \tool\ incorrectly identifies a sentence as a specification sentence. \textbf{A example goes here}
 
@@
 For instance, consider the sentence ``\textit{This is done by flushing the stream and then closing the underlying output stream.}'' from  \CodeIn{close} method description from \CodeIn{PrintStream} class.
-\tool\ fails to make the distinction
+\tool\ incorrectly identifies the action ``flush'' being performed before the action ``close''.
+However \tool\ fails to make the distinction that it happens internally (enforced within the body) in the method.
+\tool, thus incorrectly identifies the sentence as a specification sentence.
 

### 2014-03-13 Draft/evaluation.tex
Added parts of evaluation

@@
 	\item\textbf{RQ2}: What is the accuracy of \tool\ in inferring temporal constraints from specification sentences in the API documents?
+	\item\textbf{RQ3}: How do the constraints inferred by our approach compare with the typed-enforced temporal constraints?
+
 \end{itemize}
@@
 \begin{tabular}{|c|c|c|c|c|c|c|c|c|c|c|}
-\hline API & Methods & No. of Sentences & Spec Sentences & ICON Ann & TP & FP & FN & P & R & F-Score \\ 
-\hline java.io &  & 2417 & 78 & 87 & 56 & 31 & 22 & 64.4 & 71.8 & 67.9 \\ 
+\hline API & Methods & Sentences & Spec Sentences & \tool\ Ann & TP & FP & FN & P(\%) & R(\%) & F-Score(\%) \\
+\hline 
+\hline java.io &  & 2417 & 78 & 88 & 57 & 31 & 21 & 64.8 & 73.1 & 68.8 \\ 
 \hline AMAZON S3 REST & 51 & 1492 & 12 & 12 & 8 & 4 & 4 & 66.7 & 66.7 & 66.7 \\ 
-\hline Total &  & 3909 & 90 & 99 & 64 & 35 & 26 & 64.6$^*$ & 71.1$^*$ & 67.7$^*$ \\ 
+\hline Total &  & 3909 & 90 & 100 & 65 & 35 & 25 & 65.0$^*$ & 72.2$^*$ & 68.4$^*$ \\ 
 \hline
@@
 \end{tabular}
+\label{tab:results}
 \end{center}
@@
 In this section, we quantify the effectiveness of \tool\ in identifying specification sentences by answering RQ1.
-Our results show that, out of 2,414 sentences, \tool\ effectively identifies specification sentences with the average precision, recall, F-score, and accuracy of 65.0\%, 71.8\%, 68.7\%, and 97.9\%, respectively.
+Table~\ref{tab:results} shows the effectiveness of \tool\ in identifying specification sentences.
+Column ``API'' lists the names of the subject API. 
+Column ``Methods'' and ``Sentences'' lists the number of methods and sentences in each subject API's.
+Column ``\tool\ Ann'' lists the number of sentences identified by \tool\ as constraint sentences. 
+Columns ``TP'', ``FP'', ``TN'', and ``FN'' represent the number of \CodeIn{true positives}, \CodeIn{false positives}, \CodeIn{true negatives}, and \CodeIn{false negatives}, respectively. 
+Columns ``P(\%)'', ``R(\%)'', and ``F-Score(\%)'' list percentage values of \CodeIn{precision}, \CodeIn{recall}, and \CodeIn{F-score} respectively. 
+Our results show that, out of 3,909 sentences, \tool\ effectively identifies specification sentences with the average precision, recall, and F-score of 65.0\%, 72.2\%, and 68.4\%, respectively.
 
-We next present an example to illustrate how \tool\ incorrectly identifies a sentence as a specification sentence. \textbf{A example goes here}
-
+%We next present an example to illustrate how \tool\ incorrectly identifies a sentence as a specification sentence. \textbf{A example goes here}
 We next present an example to illustrate how \tool\ incorrectly identifies a sentence as a specification sentence (producing false positives).
@@
 We next present an example to illustrate how \tool\ fails identify a specification sentence (producing false negative).
-False negatives are particularly undesirable in the context of our problem domain, because they can mislead the users of \tool\ into believing that no other temporal constraint exists in the API document.
+False negatives are undesirable in the context of our problem domain, because they can mislead the users of \tool\ into believing that no other temporal constraint exists in the API documents.
 Furthermore, an overwhelming number of false negatives works against the usefulness of \tool.
@@
 
+If any in-memory buffering is being done by the application (for example, by a BufferedOutputStream object), those buffers must be flushed into the FileDescriptor (for example, by invoking OutputStream.flush) before that data will be affected by sync.
+
+If markposMM is -1MM (no mark has been set or the mark has been invalidated), an IOExceptionMM is thrown.
+
+\subsubsection{RQ3: Comparison to Typed-Enforced Constraints}
+
+In this section, we compared the temporal constraints inferred from the natural language API descriptions to those enforced by the type-system.
+For answering this question we used the constraints inferred by the Algorithm~\ref{alg:TypeAnalysis} presented in Section~\ref{sec:approach} on classes in \CodeIn{java.io} package.
+
+We observed that the constraints inferred by our \tool\ from natural language text were distinct from the constraints enforced by the type system.
+
 \subsection{Summary}
@@
 upon by two authors.
-
-If any in-memory buffering is being done by the application (for example, by a BufferedOutputStream object), those buffers must be flushed into the FileDescriptor (for example, by invoking OutputStream.flush) before that data will be affected by sync.
-
-If markposMM is -1MM (no mark has been set or the mark has been invalidated), an IOExceptionMM is thrown.

### 2014-03-13 Draft/evaluation.tex
Added Skelton for Kunal

@@
 \begin{itemize}
-	\item\textbf{RQ1}: What are the precision and recall of \tool\  in
-	identifying temporal constraints from sentences written in natural language?
-	\item\textbf{RQ2}: What is the accuracy of \tool\ in inferring temporal constraints from specification sentences in the API documents?
+	\item\textbf{RQ1}: What are the precision and recall of \tool\ in identifying temporal constraints from sentences written in natural language?
+	\item\textbf{RQ2}: What is the accuracy of \tool\ in inferring temporal constraints from constraint sentences in the API documents?
 	\item\textbf{RQ3}: How do the constraints inferred by our approach compare with the typed-enforced temporal constraints?
@@
 To answer RQ1, we measure the number of true positives ($TP$), false positives ($FP$), true negative ($TN$), and false negatives ($FN$)
-in identifying the specification sentences by \tool.
-We define specification sentence as a sentence describing a temporal constraints.
+in identifying the constraint sentences by \tool.
+We define constraint sentence as a sentence describing a temporal constraints.
 We define the $TP$, $FP$, $TN$, and $FN$ of \tool\ as follows:
@@
 \begin{enumerate}
-	\item $TP$: A sentence correctly identified by \tool\ as specification sentence.
-	\item $FP$: A sentence incorrectly identified by \tool as specification sentence.
-	\item $TN$: A sentence correctly identified by \tool\ as not a specification sentence.
-	\item $FN$: A sentence incorrectly identified by \tool\ as not a specification sentence.
+	\item $TP$: A sentence correctly identified by \tool\ as constraint sentence.
+	\item $FP$: A sentence incorrectly identified by \tool as constraint sentence.
+	\item $TN$: A sentence correctly identified by \tool\ as not a constraint sentence.
+	\item $FN$: A sentence incorrectly identified by \tool\ as not a constraint sentence.
 \end{enumerate}
@@
 $Precision$ and $Recall$. Higher value of $Precision$, $Recall$, and $F-Score$
-are indicative of higher quality of the specification statements inferred using 
+are indicative of higher quality of the constraint statements inferred using 
 \tool. based on the calculation of $TP$, $FP$, $TN$, and $FN$ of \tool\ defined
@@
 
-To answer RQ2, we checked the temporal constraints inferred from specification sentences by \tool.
+To answer RQ2, we checked the temporal constraints inferred from constraint sentences by \tool.
 We measure $accuracy$ of \tool as the ratio of the total number of temporal constraints that
-are correctly inferred by \tool to the total number of specification sentences.
+are correctly inferred by \tool to the total number of constraint sentences.
 
@@
 
-In this section, we quantify the effectiveness of \tool\ in identifying specification sentences by answering RQ1.
-Table~\ref{tab:results} shows the effectiveness of \tool\ in identifying specification sentences.
+In this section, we quantify the effectiveness of \tool\ in identifying constraint sentences by answering RQ1.
+Table~\ref{tab:results} shows the effectiveness of \tool\ in identifying constraint sentences.
 Column ``API'' lists the names of the subject API. 
@@
 Columns ``P(\%)'', ``R(\%)'', and ``F-Score(\%)'' list percentage values of \CodeIn{precision}, \CodeIn{recall}, and \CodeIn{F-score} respectively. 
-Our results show that, out of 3,909 sentences, \tool\ effectively identifies specification sentences with the average precision, recall, and F-score of 65.0\%, 72.2\%, and 68.4\%, respectively.
+Our results show that, out of 3,909 sentences, \tool\ effectively identifies constraint sentences with the average precision, recall, and F-score of 65.0\%, 72.2\%, and 68.4\%, respectively.
 
-%We next present an example to illustrate how \tool\ incorrectly identifies a sentence as a specification sentence. \textbf{A example goes here}
-We next present an example to illustrate how \tool\ incorrectly identifies a sentence as a specification sentence (producing false positives).
+%We next present an example to illustrate how \tool\ incorrectly identifies a sentence as a constraint sentence. \textbf{A example goes here}
+We next present an example to illustrate how \tool\ incorrectly identifies a sentence as a constraint sentence (producing false positives).
 For instance, consider the sentence ``\textit{This is done by flushing the stream and then closing the underlying output stream.}'' from  \CodeIn{close} method description from \CodeIn{PrintStream} class.
@@
 However \tool\ fails to make the distinction that it happens internally (enforced within the body) in the method.
-\tool, thus incorrectly identifies the sentence as a specification sentence.
+\tool, thus incorrectly identifies the sentence as a constraint sentence.
 
@@
 The sentence describes an effect that happens as a result of calling the \CodeIn{close} method and does not describe any temporal constraint.
-However, \tool\ annotates the sentence as a specification sentence because underlying Wordnet dictionaries matches the word ``has'' as a synonym of ``get''.
-This incorrect matching in turn causes \tool to incorrectly annotate the sentence as specification sentence because ``has'' is matched against \CodeIn(get) method in \CodeIn{FileOutputStream}.
+However, \tool\ annotates the sentence as a constraint sentence because underlying Wordnet dictionaries matches the word ``has'' as a synonym of ``get''.
+This incorrect matching in turn causes \tool to incorrectly annotate the sentence as constraint sentence because ``has'' is matched against \CodeIn(get) method in \CodeIn{FileOutputStream}.
 We observed 8 instances of previously described example in our results.
@@
 
-We next present an example to illustrate how \tool\ fails identify a specification sentence (producing false negative).
+We next present an example to illustrate how \tool\ fails identify a constraint sentence (producing false negative).
 False negatives are undesirable in the context of our problem domain, because they can mislead the users of \tool\ into believing that no other temporal constraint exists in the API documents.
@@
 Although \tool\ correctly identifies the method \CodeIn{close} in the sentence, \tool\ currently does not support temporal constraint on the same method.
-Aforementioned, limitation causes \tool\ to not identify the statement as a specification constraint.
+Aforementioned, limitation causes \tool\ to not identify the statement as a constraint constraint.
 
@@
 
-In this section, we evaluate the effectiveness of \tool\ in inferring specification sentences from API documents.
+In this section, we evaluate the effectiveness of \tool\ in inferring constraint sentences from API documents.
 
@@
 Threats to external validity primarily include the degree to which the subject documents used in our evaluations are representative of true practice.
-To minimize the threat, we used API documents of two representative commercial REST API: one dealing with online storage and the other \textbf{TBD}.
-The \amazon documents describe one of the most popularly used and online storage APIs.
-We also used the \textbf{TBD}.
-Furthermore, the difference in the functionalities provided by the two projects also address the issue of over fitting our approach to a particular type of API.
+To minimize the threat, we used API documents of two different API's: JDK \CodeIn{java.io} and \amazon.
+On one hand Java is a widely used programming language and \CodeIn{java.io} and is one of the main packages.
+In contrast, \amazon\ provides HTTP based access to online storage allowing developers the freedom to write clients applications in any programming language.
+Furthermore, the difference in the functionalities provided by the two API's also address the issue of over fitting our approach to a particular type of API.
 The threat can be further reduced by evaluating our approach on more subjects.
@@
 To reduce the threat, we manually inspected all the constraints inferred against the API method descriptions in our evaluation.
-Furthermore, we ensured that the results were individually verified and agreed
-upon by two authors.
+Furthermore, we ensured that the results were individually verified and agreed upon by two authors.

### 2014-03-13 Draft/abstract.tex
Updated abstract, Intro, eval

@@
 In contrast, API documents contain valuable information about the usage in natural language.
-Although existing techniques infer from API documents method specifications (such as method precondition and postconditions) or resource specifications (such as constraints on creating/releasing resources), such techniques fail to explicitly infer temporal constraints.
-Manually writing formal specifications based on natural language text in API documents
+However, manually writing formal specifications based on natural language text in API documents
 can be prohibitively time consuming and error prone.
+There are existing techniques that infer from API documents resource specifications 
+(such as constraints based on phases: creating, manipulating, and releasing resources).
+However, such techniques are limited to finding temporal specification of resources.
+Furthermore, such techniques do not make a distinction between explicit ordering of methods
+within each phases. 
 To address this issue, we propose a natural language processing based automated approach \tool,
 to infer formal temporal specifications from natural language text of API documents.
-\tool\ uses 
 To evaluate our proposed approach, we applied \tool\ to infer temporal constraints from 
 commonly used package \CodeIn{java.io} from JDK API and \amazonAPI.
-Our evaluation results show that \tool\ achieves an average of 66\% precision and 70\% recall
-in inferring 69 temporal constraints from more than 3900 sentences of API documents.
+Our evaluation results show that \tool\ achieves an average of 65\% precision and 72\% recall
+in inferring 63 temporal constraints from more than 3900 sentences of API documents.
 

### 2014-03-13 Draft/conclusion.tex
Updated abstract, Intro, eval

@@
 commonly used package \CodeIn{java.io} from JDK API and Amazon S3 REST API.
-Our evaluation results show that \tool\ achieves an average of PP\% precision and RR\% recall
-in inferring TT temporal constraints from more than ZZZZ sentences of API documents.
+Our evaluation results show that \tool\ achieves an average of 65\% precision and 72\% recall
+in inferring 63 temporal constraints from more than 3900 sentences of API documents.

### 2014-03-13 Draft/evaluation.tex
Updated abstract, Intro, eval

@@
 	\item $TP$: A sentence correctly identified by \tool\ as constraint sentence.
-	\item $FP$: A sentence incorrectly identified by \tool as constraint sentence.
+	\item $FP$: A sentence incorrectly identified by \tool\ as constraint sentence.
 	\item $TN$: A sentence correctly identified by \tool\ as not a constraint sentence.
@@
 
-\begin{tabular}{|c|c|c|c|c|c|c|c|c|c|c|}
-\hline API & Methods & Sentences & Spec Sentences & \tool\ Ann & TP & FP & FN & P(\%) & R(\%) & F-Score(\%) \\
+\begin{tabular}{|l|c|c|c|c|c|c|c|c|c|c|c|c|}
+\hline API & Mtds & Sen & Sen$_C$ & Sen$_{ICON}$ & TP & FP & FN & P(\%) & R(\%) & F$_S$(\%) & Spec$_{ICON}$ & Acc(\%)\\
 \hline 
-\hline java.io &  & 2417 & 78 & 88 & 57 & 31 & 21 & 64.8 & 73.1 & 68.8 \\ 
-\hline AMAZON S3 REST & 51 & 1492 & 12 & 12 & 8 & 4 & 4 & 66.7 & 66.7 & 66.7 \\ 
-\hline Total &  & 3909 & 90 & 100 & 65 & 35 & 25 & 65.0$^*$ & 72.2$^*$ & 68.4$^*$ \\ 
+\hline java.io &  & 2417 & 78 & 88 & 57 & 31 & 21 & 64.8 & 73.1 & 68.8 & 56 & 71.8\\ 
+\hline AMAZON S3 REST & 51 & 1492 & 12 & 12 & 8 & 4 & 4 & 66.7 & 66.7 & 66.7 & 7 & 58.3\\ 
+\hline Total &  & 3909 & 90 & 100 & 65 & 35 & 25 & 65.0$^*$ & 72.2$^*$ & 68.4$^*$ & 63 & 70.0$^*$\\ 
 \hline
 %----------------- END TABLE DATA ------------------------ 
-\multicolumn{11}{p{6.5in}}{\footnotesize $^*$ Column average; TP: Total number of True Positives; 
-FP: Total number of False Positives; FN: Total number of False Negatives; P: Precision; R: Recall} \\ 
+\multicolumn{13}{p{6.5in}}{\small
+$^*$ Column average;
+Mtds: Total no. of Methods; Sen: Total no. of Sentences; Sen$_C$: Total no. of constraint Sentences;
+Sen$_{ICON}$: Total no. of constraint Sentences identified by \tool; 
+TP: Total no. of True Positives; FP: Total no. of False Positives; FN: Total no. of False Negatives;
+P: Precision; R: Recall; F$_S$: F-Score; Acc: Accuracy
+Spec$_{ICON}$: Total no. of temporal constraint correctly identified by \tool;
+} \\ 
 \end{tabular}
@@
 
-\subsubsection{RQ1: Effectiveness in Identifying Specification Sentences}
+\subsubsection{RQ1: Effectiveness in Identifying Constraint Sentences}
 
@@
 Column ``API'' lists the names of the subject API. 
-Column ``Methods'' and ``Sentences'' lists the number of methods and sentences in each subject API's.
-Column ``\tool\ Ann'' lists the number of sentences identified by \tool\ as constraint sentences. 
+Columns ``Mtds'' and ``Sen'' lists the number of methods and sentences in each subject API's.
+Column ``Sen$_C$'' list the number of manually identified constraint sentences.
+Column ``Sen$_{ICON}$'' lists the number of sentences identified by \tool\ as constraint sentences. 
 Columns ``TP'', ``FP'', ``TN'', and ``FN'' represent the number of \CodeIn{true positives}, \CodeIn{false positives}, \CodeIn{true negatives}, and \CodeIn{false negatives}, respectively. 
-Columns ``P(\%)'', ``R(\%)'', and ``F-Score(\%)'' list percentage values of \CodeIn{precision}, \CodeIn{recall}, and \CodeIn{F-score} respectively. 
+Columns ``P(\%)'', ``R(\%)'', and ``F$_S$(\%)'' list percentage values of \CodeIn{precision}, \CodeIn{recall}, and \CodeIn{F-score} respectively. 
 Our results show that, out of 3,909 sentences, \tool\ effectively identifies constraint sentences with the average precision, recall, and F-score of 65.0\%, 72.2\%, and 68.4\%, respectively.
@@
 However, \tool\ annotates the sentence as a constraint sentence because underlying Wordnet dictionaries matches the word ``has'' as a synonym of ``get''.
-This incorrect matching in turn causes \tool to incorrectly annotate the sentence as constraint sentence because ``has'' is matched against \CodeIn(get) method in \CodeIn{FileOutputStream}.
+This incorrect matching in turn causes \tool\ to incorrectly annotate the sentence as constraint sentence because ``has'' is matched against \CodeIn(get) method in \CodeIn{FileOutputStream}.
 We observed 8 instances of previously described example in our results.
 
-If we manually fixed the Wordnet dictionaries to match ``has'' and ``get'' as synonyms, our precision is further increased to 70.8\% effectively increasing the F-Score of \tool to 71.2\%.
+If we manually fixed the Wordnet dictionaries to match ``has'' and ``get'' as synonyms, our precision is further increased to 70.8\% effectively increasing the F-Score of \tool\ to 71.2\%.
 We refrained from including such modifications for reporting the results to stay true to our proposed framework.
@@
 Furthermore, an overwhelming number of false negatives works against the usefulness of \tool.
-For instance, consider the sentence ``\textit{This is done by flushing the stream and then closing the underlying output stream.}'' from  \CodeIn{close} method description from \CodeIn{PrintStream} class.
-The sentence describes the constraint in terms of invoking the same method again.
-Although \tool\ correctly identifies the method \CodeIn{close} in the sentence, \tool\ currently does not support temporal constraint on the same method.
-Aforementioned, limitation causes \tool\ to not identify the statement as a constraint constraint.
+For instance, consider the sentence ``\textit{This implementation of the PUT operation creates a copy of an object that is already stored in Amazon S3.}'' from  \CodeIn{PUT Object-Copy} method description in \amazonAPI.
+The sentence describes the constraint that the object must already be stored (invocation of \CodeIn{PUT Object}) before calling the current method.
+However, \tool cannot make the connection owing to the limitation of the semantic graphs that do not list ``already stored'' as a ``valid operation'' on object.
 
@@
 
-In this section, we evaluate the effectiveness of \tool\ in inferring constraint sentences from API documents.
+In this section, we evaluate the effectiveness of \tool\ in inferring temporal constraints from the identified constraint sentences from API documents.
+To answer RQ2, we ran the sentences manually identified as constraint sentences against \tool.
+We then manually verified the correctness of temporal constraints inferred by our \tool.
+We define the \CodeIn{accuracy} of \tool\ as the ratio of constraint sentences with correctly inferred temporal constraints to the total number of constraint sentences.
 
-If any in-memory buffering is being done by the application (for example, by a BufferedOutputStream object), those buffers must be flushed into the FileDescriptor (for example, by invoking OutputStream.flush) before that data will be affected by sync.
+Table~\ref{tab:results} shows the effectiveness of \tool\ in inferring temporal constraints from the identified constraint sentences.
+Column ``API'' lists the names of the subject API. 
+Columns ``Mtds'' and ``Sen'' list the number of methods and sentences in each subject API's.
+Column ``Sen$_C$'' lists the number of manually identified constraint sentences.
+Column ``Spec$_{ICON}$'' lists the number of sentences with correctly inferred temporal constraints by \tool. 
+Column ``Acc(\%)'' list percentage values of accuracy. 
+Our results show that, out of 90 manually identified constraint sentences, \tool\ correctly infers temporal constraints with the average accuracy of 70.0\%.
 
-If markposMM is -1MM (no mark has been set or the mark has been invalidated), an IOExceptionMM is thrown.
+We next present an example to illustrate how \tool\ incorrectly infers temporal constraints from a constraint sentence.
+Consider the sentence ``if the stream does not support seek, or if this input stream has been closed by invoking its close method, or an I/O error occurs.'' from \CodeIn{skip} method of \CodeIn{java.io.FilterInputStream} class.
+Although \tool\ correctly infers that close cannot be called before current method, \tool\ incorrectly associates the phrase ``support seek'' with method \CodeIn{markSupported} in the class.
+The faulty association happens due to incorrect parsing of the sentence by the underlying NLP infrastructure.
+Such issues will be alleviated as the underlying NLP infrastructure improves.
+
+Another, major cause of failure for \tool\ in inferring temporal constraints from sentences is the failure to identify the sentence as a constraint sentences at the first place (false negatives).
+Overall, accuracy of \tool\ can be significantly improved by lowering the false negative rate in identifying the constraint sentences.
 
@@
 
+In summary, we demonstrate that \tool\ effectively identifies constraint sentences (from over 3900 API sentences) with the average precision, recall, and F-score of 65.0\%, 72.2\%, and 68.4\% respectively.
+Furthermore, we also show that \tool\ infers temporal constraints from the constraint sentences an average accuracy of 70\%.
+Furthermore, also provide discussion that a false positives rate and false negatives rate can be further improved by improving the underlying NLP infrastructure.
+Finally, we provide a comparison of the temporal constraints inferred from natural language description against the temporal constraints enforced by a type system.
+
 \subsection{Threats to Validity}
@@
 
-Threats to internal validity include the correctness of our implementation in extracting usage constraints and labelling a statement as a constraint statement.
+Threats to internal validity include the correctness of our implementation in extracting usage constraints and labeling a statement as a constraint statement.
 To reduce the threat, we manually inspected all the constraints inferred against the API method descriptions in our evaluation.

### 2014-03-13 Draft/example.tex
Updated abstract, Intro, eval

@@
 
-We now present some real world examples to motivate our approach.
-In particular, through these examples, we demonstrate that developers often ignore the tempral specifications of an API present in its documentation.
+We now present a real world example to motivate our approach.
+In particular, through the example, we demonstrate that developers often ignore the temporal specifications of an API present in its documentation.
 We suspect the reason for this phenomena is that API documentation is often verbose and information is distributed across various
@@
 For example, the PDF version of the documentation for Amazon S3 API\footnote{\url{http://awsdocs.s3.amazonaws.com/S3/latest/s3-api.pdf}} spans 278 pages.
-Developers do not have time and patience to go through all the documentation and miss various temporal specifications of the API, resulting in defective applications that invoke API methods in sequences prohibited by documentation.
+Developers may not have time and patience to go through all the documentation and may miss various temporal specifications of the API, resulting in defective applications that invoke API methods in sequences prohibited by documentation.
 If we have the formal temporal specifications such kinds of defects can be detected by formal verification tools.
@@
 Although the issue was fixed but notice that one of the responses on the \textit{Stack Overflow} encouraged the person asking query to switch to another product, thus potentially resulting in a loss of revenue attributed to customer dissatisfaction.
-In yet another example a developer points out the financial losses he suffered because he was incorrectly using the previously described delete bucket functionality as shown in Figure~\ref{fig:example2}, \textit{(``...paying for excess stuff you don't need is simply idiotic...'')}.
+%In yet another example a developer points out the financial losses he suffered because he was incorrectly using the previously described delete bucket functionality as shown in Figure~\ref{fig:example2}, \textit{(``...paying for excess stuff you don't need is simply idiotic...'')}.
 
@@
 
-Formal verification tools can be used to easily find such kind of defects.
+Formal verification tools can be used to easily find such defects.
 However, formal analysis tools are not designed to work on specifications in natural languages (such as API Documents) and require the specifications in a more formal or machine understandable format.
+For instance, a rule can be added to a static checker to ensure presence of a call to delete objects before the call to delete bucket.
 Thus, there is need for an approach to automatically translate the constraints described in natural language into a more formal notation.
@@
 
-\begin{figure}[t]
-\begin{center}
-\includegraphics[scale=0.6]{Example2.eps}
-\end{center}
-\caption{\label{fig:example2} The experience article posted by a developer regarding Amazon S3 REST API}
-\end{figure}
+%\begin{figure}[t]
+%\begin{center}
+%\includegraphics[scale=0.6]{Example2.eps}
+%\end{center}
+%\caption{\label{fig:example2} The experience article posted by a developer regarding Amazon S3 REST API}
+%\end{figure}

### 2014-03-13 Draft/introduction.tex
updated evaluation
Updated abstract, Intro, eval

@@
 % Amazon S3 is popularly used web service for simple cloud based storage
-\textbf{There are} existing approaches focus on inferring just the method pre-post conditions in terms of parameter constraints either using program analysis techniques~\cite{Henkel07discoveringdocumentation,Ghezzi:2009:SIB:1555001.1555057,Henkel:2008:DDA:1363102.1363105,Flanagan:2001:HAA:647540.730008,Buse:2008:ADI:1390630.1390664} or using NLP~\cite{pandita12:inferring, wu2013inferring}.
-In contrast, temporal constraints are beyond these parameter constraints.
+Although, existing approaches focus on inferring just the method pre-post conditions in terms of parameter constraints either using program analysis techniques~\cite{Henkel07discoveringdocumentation,Ghezzi:2009:SIB:1555001.1555057,Henkel:2008:DDA:1363102.1363105,Flanagan:2001:HAA:647540.730008,Buse:2008:ADI:1390630.1390664} or using NLP~\cite{pandita12:inferring, wu2013inferring}, temporal constraints are beyond these parameter constraints.
 Temporal constraints, in general focus on rules related to orchestration of methods within an API rather than focusing on the requirements on the input parameters of these methods.
-Our proposed approach addresses the following challenges to infer temporal constraints automatically from API documents.
 
-First, relying just on type information will result in an incomplete list of temporal constraints. 
-In typed languages some temporal constraints are enforced by type system. 
-For instances a method ($m$) accepting input parameter ($i$) of type ($t$) mandates that (at least one) method ($m'$) be invoked whose return value is of type ($t$).
-However, temporal constraints are not limited by the type definitions (i.e, requirements on the type of input parameters), and are currently expressed mostly in natural language in API documents, as described in the example previously.
-We propose to address the issue by augmenting the type definitions based temporal constraints with the constraints inferred from
-the natural language text in API documents.
+Apart from method specifications, Zhong et al.~\cite{zhong09SE} leverage machine learning and type information to infer constraints on resources based on phases of resource usage: creating, manipulating, and releasing.
+However, temporal specification are not limited to resource usage.
+Furthermore, their technique fails to make the finer grained distinction on the ordering of the methods within a phase.
+For the description mentioned in previously, assuming that the method calls are associated with resource ``part'', both the methods referenced are logically associated with the creation phase of resource.
+Zhong et al.~\cite{zhong09SE} approach fails to make a distinction in ordering of such methods.
+In contrast our proposed approach leverages natural language processing to infer generic temporal specifications (not limited to resource related constraints) and also improves upon existing work for making finer grained distinction between ordering of methods within a phase of a resource.
+
+%First, relying just on type information will result in an incomplete list of temporal constraints. 
+%In typed languages some temporal constraints are enforced by type system. 
+%For instances a method ($m$) accepting input parameter ($i$) of type ($t$) mandates that (at least one) method ($m'$) be invoked whose return value is of type ($t$).
+%However, temporal constraints are not limited by the type definitions (i.e, requirements on the type of input parameters), and are currently expressed mostly in natural language in API documents, as described in the example previously.
+%We propose to address the issue by augmenting the type definitions based temporal constraints with the constraints inferred from
+%the natural language text in API documents.
 %Furthermore, such constraints although valuable but are already checked by any advanced Integrated Development Environment(IDE) such as eclipse
@@
 % Add a sentence stating that we extend previous technique to address the issues 
-Second, inferring temporal constraints from the natural language text itself is challenging. 
+However, inferring temporal constraints from the natural language text is challenging. 
 There are existing challenges in NLP for software engineering domain namely \textit{ambiguity}, \textit{programming keywords}, and \textit{semantic equivalence} identified in previous work~\cite{pandita12:inferring}.
-In addition to these challenges, we have an added challenge of identifying the method referenced in the natural language text to infer temporal constraint.
+In addition to these challenges, we have an added challenge of 
+implicit method referencing: identifying the method referenced in the natural language text to infer temporal constraint.
 Recall the description sentence ``You must initiate a multipart upload before you can upload any part.''
@@
 In summary, the proposed work leverages natural language description of API's to infer temporal constraints of method invocations.
-As the proposed work analyzes API documents in natural language, it can be reused independent of the programming language of the library.
+As the proposed work analyzes API documents in natural language, it can be reused independent of the programming language of the API library.
 Additionally, our approach complements existing mining based approaches~\cite{buse2012synthesizing, thummalapenta07parseweb, Wang:2013:MSR, Zhong:2009:MMR} that partially address the problem by mining for common usage patterns among client software that use the API.

### 2014-03-13 Draft/introduction.tex
Updated the project Web

@@
 	\item A prototype implementation of our approach based on extending the Stanford Parser~\cite{Klein03,SNLP1}, which is a natural language parser to derive the grammatical structure of sentences.
-	An open source implementation of the prototype is publicly available on our project website\footnote{\url{https://sites.google.com/site/icon}}. 
-	\item An evaluation of proposed approach on 
-commonly used package \CodeIn{java.io} from JDK API and Amazon
-S3 REST API. Our evaluation results show that \CodeIn{ICON} achieves
-an average of 70\% precision and 80\% recall in inferring 63
-temporal constraints from more than 2400 sentences of API
-documents.
+	An open source implementation of the prototype is publicly available on our project website\footnote{\url{https://sites.google.com/site/temporalspec}}. 
+	\item An evaluation of proposed approach on commonly used package \CodeIn{java.io} from JDK API and \amazonAPI. 
 \end{itemize}

### 2014-03-14 Draft/evaluation.tex
Adding RQ3

@@
 
-In this section, we compared the temporal constraints inferred from the natural language API descriptions to those enforced by the type-system.
-For answering this question we used the constraints inferred by the Algorithm~\ref{alg:TypeAnalysis} presented in Section~\ref{sec:approach} on classes in \CodeIn{java.io} package.
+In this section, we compared the temporal constraints inferred from the natural language API descriptions to those enforced by the type-system (referred to as type-enforced constraint).
+The constraints that are enforced by the type-system can be enforced by IDEs.
+Hence, for such types of constraints, we do not require sophisticated techniques like ICON.
+For \CodeIn{java.io}, we define a type-enforced constraint as a constraint that mandates a method M accepting input parameter I of type T to be invoked after (at least one) a method M0 whose return value is of type T.
+Since there are no types in REST APIs, for \CodeIn{Amazon S3}, we consider a constraint as a type-enforced constraint if it is implicit in the \CodeIn{CRUD} naming convention followed by REST operations.
+In particular, we consider a constraint as a type-enforced constraint, if the constraint mandates a DELETE, GET, or PUT operation on a resource to be invoked after a GET operation on the same resource.
 
-We observed that the constraints inferred by our \tool\ from natural language text were distinct from the constraints enforced by the type system.
+To address this question, we manually inspect each of the constraints reported by ICON and classify it as a type-enforced constraint or a non type-enforced constraint. 
+We observed that none of the constraints inferred by our \tool\ from natural language text were classified as a type-enforced constraint.
+Hence, the constraints detected by \tool\ are not trivial enough to be enforced by a type system.
 

### 2014-03-14 Draft/introduction.tex
Fixed bib entries and references

@@
 % Amazon S3 is popularly used web service for simple cloud based storage
-Although, existing approaches focus on inferring just the method pre-post conditions in terms of parameter constraints either using program analysis techniques~\cite{Henkel07discoveringdocumentation,Ghezzi:2009:SIB:1555001.1555057,Henkel:2008:DDA:1363102.1363105,Flanagan:2001:HAA:647540.730008,Buse:2008:ADI:1390630.1390664} or using NLP~\cite{pandita12:inferring, wu2013inferring}, temporal constraints are beyond these parameter constraints.
+Although, existing approaches focus on inferring just the method pre-post conditions in terms of parameter constraints either using program analysis techniques~\cite{Henkel07discoveringdocumentation,Ghezzi:2009:SIB:1555001.1555057,Henkel:2008:DDA:1363102.1363105,Flanagan2001:HAA,Buse:2008:ADI:1390630.1390664} or using NLP~\cite{pandita12:inferring, wu2013inferring}, temporal constraints are beyond these parameter constraints.
 Temporal constraints, in general focus on rules related to orchestration of methods within an API rather than focusing on the requirements on the input parameters of these methods.
@@
 	To the best of our knowledge, our approach is the first one to apply NLP for the goal of inferring temporal specifications from API documents.
-	\item A prototype implementation of our approach based on extending the Stanford Parser~\cite{Klein03,SNLP1}, which is a natural language parser to derive the grammatical structure of sentences.
+	\item A prototype implementation of our approach based on extending the Stanford Parser~\cite{Klein03}, which is a natural language parser to derive the grammatical structure of sentences.
 	An open source implementation of the prototype is publicly available on our project website\footnote{\url{https://sites.google.com/site/temporalspec}}. 

### 2014-03-14 Draft/related.tex
Fixed bib entries and references

@@
 There are existing approaches that statically or dynamically extract code contracts~\cite{csallner08dysy,NimmerE02:ISSTA,Tillmann:2006:DLM:2105385.2105433}.
-However, a combination of developer written and automatically inferred contracts seems to be the most effective approach~\cite{Polikarpova2009ISSTA,Flanagan:2001:HAA:647540.730008}.
+However, a combination of developer written and automatically inferred contracts seems to be the most effective approach~\cite{Polikarpova2009ISSTA,Flanagan2001:HAA}.
 Furthermore, there are existing approaches that infer code-contract-like specifications
-(such as behavioral model, algebraic specifications, and exception specifications) either dynamically\cite{Henkel07discoveringdocumentation,Ghezzi:2009:SIB:1555001.1555057,Henkel:2008:DDA:1363102.1363105} or statically~\cite{Flanagan:2001:HAA:647540.730008,Buse:2008:ADI:1390630.1390664} from source code and binaries.
+(such as behavioral model, algebraic specifications, and exception specifications) either dynamically\cite{Henkel07discoveringdocumentation,Ghezzi:2009:SIB:1555001.1555057,Henkel:2008:DDA:1363102.1363105} or statically~\cite{Flanagan2001:HAA,Buse:2008:ADI:1390630.1390664} from source code and binaries.
 In contrast, the approach presented in this work infers specifications from the natural language text in API documents,

### 2014-03-14 Draft/approach.tex
Fixed bib entries and references
Minor Fixes

@@
 Column ``Template'' describes conditions where the template is applicable and Column ``Summary'' describes the action taken by our shallow parser when the template is applicable.
-All of these semantic templates are publicly available on our project website~\cite{projectweb}.
+All of these semantic templates are publicly available on our project website\footnote{\url{https://sites.google.com/site/temporalspec}}.
 With respect to the previous example the template 3 \textit{( A noun phrase followed by another noun/pronoun/verb phrase in brackets)} is applicable.
@@
 \caption{Semantic Templates}
-    \begin{tabular}{ | l | p{5cm} |p{10cm} |}
-    \hline
-    \textbf{S No.} 	& \textbf{Template} & \textbf{Summary} \\ \hline
+    \begin{tabular}{  l  p{5cm} p{10cm} }
+    \topline
+    \headcol  \textbf{S No.} 	& \textbf{Template} & \textbf{Summary} \\
+    \midline
 
-    1. 		& Two sentences joined by a conjunction & Sentence is broken down into two individual sentences with the conjunction term serving as the connector between two. \\ \hline
-    2. 		& Two sentences joined by a ``,''& Sentence is broken down to individual independent sentences \\ \hline
+    1. 		& Two sentences joined by a conjunction & Sentence is broken down into two individual sentences with the conjunction term serving as the connector between two. \\
+\rowcol    2. 		& Two sentences joined by a ``,''& Sentence is broken down to individual independent sentences \\
     3.		& A noun phrase followed by another noun/pronoun/verb phrase in brackets & Two individual sentences are formed.
 The first sentence is  the same as the parent sentence sans the noun/pronoun.verb phrase in bracket.
-The second sentence constitutes of the noun phrase followed by  noun/pronoun/verb phrase without the brackets.\\ \hline
-    4.		& A noun phrase by a conditional phrase in brackets & Two individual sentences are formed.
+The second sentence constitutes of the noun phrase followed by  noun/pronoun/verb phrase without the brackets.\\
+\rowcol    4.		& A noun phrase by a conditional phrase in brackets & Two individual sentences are formed.
 The first sentence is the same as the parent sentence sans the conditional phrase in bracket.
-The second sentence constitutes of noun phrases followed by conditional in the bracket.\\ \hline
+The second sentence constitutes of noun phrases followed by conditional in the bracket.\\
     5.		& A conditional phrase followed by a sentence & Two dependent sentences are formed.
 The first sentence constitutes the conditional phrase.
-The second sentence constitutes rest of the sentence.\\ \hline
-    6.		& A sentence in which the parent verb phrase is over two child verb phrases joined by a conjunction & Two dependent sentences are formed where the dependency is the conjunction.
+The second sentence constitutes rest of the sentence.\\
+\rowcol    6.		& A sentence in which the parent verb phrase is over two child verb phrases joined by a conjunction & Two dependent sentences are formed where the dependency is the conjunction.
 The first sentence is formulated by removing conjunction and second child verb phrase.
 The second sentence is formulated by removing conjunction and first child verb phrase.
-\\ \hline
+\\
+\bottomlinec
     \end{tabular}

### 2014-03-14 Draft/abstract.tex
Fixed comments in abstract

@@
 \begin{abstract}
-Temporal specifications of an Application Programming
+Temporal specifications  or constraints of an Application Programming
 Interface (API) describe allowed sequence of invocations
-of methods within an API. Despite being desirable for 
+of methods within an API. These constraints govern the secure and robust
+operation of client software using these APIs.
+Despite being desirable for 
 software testing and verification (through formal analysis tools),
-most API's do not have formal temporal specifications.
-In contrast, API documents contain valuable information about the usage in natural language.
-However, manually writing formal specifications based on natural language text in API documents
+most API's do not have formal temporal constraints.
+In contrast, API documents contain valuable information (including temporal constraints) about the usage in natural language.
+However, manually writing formal constraints based on natural language text in API documents
 can be prohibitively time consuming and error prone.
-There are existing techniques that infer from API documents resource specifications 
-(such as constraints based on phases: creating, manipulating, and releasing resources).
-However, such techniques are limited to finding temporal specification of resources.
-Furthermore, such techniques do not make a distinction between explicit ordering of methods
-within each phases. 
-To address this issue, we propose a natural language processing based automated approach \tool,
-to infer formal temporal specifications from natural language text of API documents.
+
+On the other hand, automatically inferring temporal constraints from API documents faces is challenging.
+In particular, it is challenging to automatically 
+identify the methods referenced in the natural language text to infer temporal constraints.
+
+% There are existing techniques that infer from API documents resource specifications 
+% (such as constraints based on phases: creating, manipulating, and releasing resources).
+% However, such techniques are limited to finding temporal specification of resources.
+% Furthermore, such techniques do not make a distinction between explicit ordering of methods
+% within each phases.
+
+To address the preceding challenge, we propose an natural-language-processing-based approach \tool,
+to infer formal temporal constraints from natural language text of API documents. These constraints can be used (as input)
+by various software testing and verification tools to detect defects in client code the APIs.
+Our approach 
+addresses the preceding challenge by building (and leveraging) domain-dictionaries systematically from API
+documents and generic English dictionaries.
 To evaluate our proposed approach, we applied \tool\ to infer temporal constraints from 
 commonly used package \CodeIn{java.io} from JDK API and \amazonAPI.
-Our evaluation results show that \tool\ achieves an average of 65\% precision and 72\% recall
+Our evaluation results are promising. In particular, \tool\ achieves an average of 65\% precision and 72\% recall
 in inferring 63 temporal constraints from more than 3900 sentences of API documents.

### 2014-03-14 Draft/background.tex

@@
 The most commonly used technique is to train a classification parser over a previously known data set.
-Current state of the art approaches have demonstrated to achieve 97\%~\cite{SNLP1} accuracy in classifying POS tags for well written news articles.
+Current state of the art approaches have demonstrated to achieve 97\%~\cite{KleinNIPS03} accuracy in classifying POS tags for well written news articles.
 
@@
 Chunking thus further enhances the syntax of a sentence on top of POS tagging.
-Current state-of-the-art approaches can achieve around 90\%~\cite{SNLP1} accuracy in classifying phrases and clauses over well written news articles.
+Current state-of-the-art approaches can achieve around 90\%~\cite{KleinNIPS03} accuracy in classifying phrases and clauses over well written news articles.
 

### 2014-03-14 Draft/related.tex

@@
 Our proposed approach touches a few research areas such as software verification,
-NLP on software engineering artifacts, and document augmentation.
+NLP in software engineering, and document augmentation.
 We next discuss the relevant work pertinent to our proposed approach in these areas.
 
-\subsection{Code Contracts - Formal Specifications}
+%\subsection{Code Contracts - Formal Specifications}
 % Define temporal constraints distinction
-Design by contracts has been an influential concept in the area of software engineering in the past decade.
+Formal specifications such as code contracts have been an active area of research.
+Notably, code contracts that are the heart of design by contract approach have been very influential in the area of software engineering.
 A significant amount of work has been done in automated inference of code contracts.
-There are existing approaches that statically or dynamically extract code contracts~\cite{csallner08dysy,NimmerE02:ISSTA,Tillmann:2006:DLM:2105385.2105433}.
+Existing approaches statically or dynamically extract code contracts~\cite{csallner08dysy,NimmerE02:ISSTA,Tillmann:2006:DLM:2105385.2105433}.
 However, a combination of developer written and automatically inferred contracts seems to be the most effective approach~\cite{Polikarpova2009ISSTA,Flanagan2001:HAA}.

### 2014-03-15 Draft/introduction.tex
Fixing Partial Comments on Introduction

@@
 
-Temporal specifications~\cite{ball2002s} of an Application Programming Interface (API) 
+Temporal specifications or constraints~\cite{ball2002s} of an Application Programming Interface (API) 
 describe allowed sequences of invocations of methods within an API. 
-These specifications govern the secure and robust operation of client software 
+These constraints govern the secure and robust operation of client software 
 using these APIs.
-If these specifications are formal (machine-readable such as linear temporal logic),
+If these constraints are formal (machine-readable such as linear temporal logic),
 they can be used  as a basis of formal analysis tools such 
@@
 
-Despite being desirable, most API's do not have formal specifications.
+Despite being desirable, most API's do not have formal constraints.
 In contrast, API developers commonly describe correct temporal usage in natural language text in API documents.
@@
 For a method under consideration, an API document may describe both the constraints on that method parameters as well as the temporal constraints in terms of the methods must be invoked pre/post the method.
-We observed that roughly 12\% of the sentences (that describe some sort of specification constraints) in \amazonAPI\ documentations describe temporal constraints.
-Although API documents contain temporal constraints, existing formal analysis tools are not designed to work on specifications written in natural language.
+We observed that a eminent portion (roughly 12\%) of the sentences (that describe some sort of constraints) in \amazonAPI\ documentations describe temporal constraints.
+Although API documents contain temporal constraints, existing formal analysis tools accept only formal constraints but not informal constraints written in natural language.
 
-One way of addressing the issue, is to manually convert the natural language API description into formal specifications. 
-However, manually writing formal specifications based on natural language text in API documents can be prohibitively time consuming and error prone~\cite{wu2013inferring,RubingerWEB10}. 
+One way of addressing the issue, is to manually convert the natural language API description into formal constraints. 
+However, manually writing formal constraints based on natural language text in API documents can be prohibitively time consuming and error prone~\cite{wu2013inferring,RubingerWEB10}. 
 For instance, Wu et al.~\cite{wu2013inferring} report that it took one of the authors more than 10 hours to browse the documentation of one method of a web service API, even before they attempted to formalize the constraints on the method.
@@
 %We propose a novel approach to infer temporal usage constraints from natural language text of API documents. 
-In contrast to manual approach, we propose an automated approach that applies Natural Language Processing (NLP) techniques on natural language text in API documents to infer temporal usage constraints.
+To reduce the manual effort, we propose an automated approach that applies Natural Language Processing (NLP) techniques on natural language text in API documents to infer formal temporal constraints. 
 %In particular, we focus on specific type of constraints namely temporal constraints.
-A generic temporal relation is defined as \textit{an interpropositional relation that communicates the simultaneity or ordering in time of events or states.}
-In terms of API method invocations, we interpret temporal relationships as \textit{`the allowed sequence of invocations of methods'}.
+A generic temporal constraint is defined as \textit{an interpropositional constraint that communicates the ordering in time of events or states.}
+In terms of API method constraints, we interpret temporal constraints as \textit{`the allowed sequence of invocations of methods'}.
 For example, consider the following statement in \amazonAPI\ ``You must initiate a multipart upload before you can upload any part.''
-This statement can be interpreted as multipart-upload method must be invoked before invoking any part-upload method in the API.
+We can interpret this sentence stating that a multipart-upload method must be invoked before invoking any part-upload method in the API.
 
@@
 % Amazon S3 is popularly used web service for simple cloud based storage
-Although, existing approaches focus on inferring just the method pre-post conditions in terms of parameter constraints either using program analysis techniques~\cite{Henkel07discoveringdocumentation,Ghezzi:2009:SIB:1555001.1555057,Henkel:2008:DDA:1363102.1363105,Flanagan2001:HAA,Buse:2008:ADI:1390630.1390664} or using NLP~\cite{pandita12:inferring, wu2013inferring}, temporal constraints are beyond these parameter constraints.
+Although, existing approaches focus on inferring method pre-post conditions (in terms of parameter constraints) using either program analysis techniques~\cite{Henkel07discoveringdocumentation,Ghezzi:2009:SIB:1555001.1555057,Henkel:2008:DDA:1363102.1363105,Flanagan2001:HAA,Buse:2008:ADI:1390630.1390664} or NLP~\cite{pandita12:inferring, wu2013inferring}, temporal constraints are beyond these parameter constraints.
 Temporal constraints, in general focus on rules related to orchestration of methods within an API rather than focusing on the requirements on the input parameters of these methods.
@@
 Apart from method specifications, Zhong et al.~\cite{zhong09SE} leverage machine learning and type information to infer constraints on resources based on phases of resource usage: creating, manipulating, and releasing.
-However, temporal specification are not limited to resource usage.
-Furthermore, their technique fails to make the finer grained distinction on the ordering of the methods within a phase.
+However, temporal constraints are not limited to resource usage.
+Furthermore, their approach fails to make the finer grained distinction on the ordering of the methods within a phase.
 For the description mentioned in previously, assuming that the method calls are associated with resource ``part'', both the methods referenced are logically associated with the creation phase of resource.
 Zhong et al.~\cite{zhong09SE} approach fails to make a distinction in ordering of such methods.
-In contrast our proposed approach leverages natural language processing to infer generic temporal specifications (not limited to resource related constraints) and also improves upon existing work for making finer grained distinction between ordering of methods within a phase of a resource.
+In contrast our proposed approach leverages natural language processing to infer generic temporal constraints (not limited to resource related constraints) and also improves upon existing work for making finer grained distinction between ordering of methods within a phase of a resource.
 
@@
 	\item An NLP based approach that infers temporal constraints of method invocations. 
-	To the best of our knowledge, our approach is the first one to apply NLP for the goal of inferring temporal specifications from API documents.
+	To the best of our knowledge, our approach is the first one to apply NLP for the goal of inferring temporal constraints from API documents.
 	\item A prototype implementation of our approach based on extending the Stanford Parser~\cite{Klein03}, which is a natural language parser to derive the grammatical structure of sentences.

### 2014-03-15 Draft/example.tex
Revised Example Section

--- 2014-02-19 Draft/example.tex
@@
 
-We now present some real world examples to motivate our approach.
-In particular, through these examples, we demonstrate that developers often ignore the tempral specifications of an API present in its documentation.
-We suspect the reason for this phenomena is that API documentation is often verbose and information is distributed across various
-pages.
-For example, the PDF version of the documentation for Amazon S3 API\footnote{\url{http://awsdocs.s3.amazonaws.com/S3/latest/s3-api.pdf}} spans 278 pages.
-Developers do not have time and patience to go through all the documentation and miss various temporal specifications of the API, resulting in defective applications that invoke API methods in sequences prohibited by documentation.
-If we have the formal temporal specifications such kinds of defects can be detected by formal verification tools.
+We next present a real world example to motivate our approach.
+In particular, through the example, we demonstrate that developers often ignore the temporal constraints of an API described in the documentation.
+We suspect the reason for this phenomena is that the documentation is often verbose and the information is distributed across various pages.
+For instance, the PDF version of the documentation for \amazonAPI\footnote{\url{http://awsdocs.s3.amazonaws.com/S3/latest/s3-api.pdf}} spans 278 pages.
+Developers often may not have time (and/or patience) to go through all the documentation and may overlook some temporal constraints of the API,
+resulting in defective client applications that invoke API methods in sequences prohibited by documentation.
 
@@
 \end{center}
-\caption{\label{fig:Stackoverflow} The Query posted on Stackoverflow form regrading Amazon S3 REST API}
+\caption{\label{fig:Stackoverflow} The Query posted on Stack Overflow forum regrading Amazon S3 REST API}
 \end{figure}
@@
 Consider the question asked in \textit{Stack Overflow}~\footnote{\url{http://stackoverflow.com/}} as shown in Figure~\ref{fig:Stackoverflow}.
-Stack Overflow is a question and answer site for professional and enthusiast programmers.
+Stack Overflow is an online question and answer forum for professional and enthusiast programmers.
 The query is about the delete functionality of a third-party software \CodeIn{S3Fox} to interact with \amazonAPI.
-The inquisitor complains about an issue in delete bucket functionality of the \CodeIn{S3Fox}.
-In particular, the issue was because the \CodeIn{S3Fox} developers overlooked the specifications in \amazon.
-The document clearly states that before deleting the bucket, the objects in the buckets must be deleted.
+The inquisitor complains about an issue in the delete bucket functionality of the \CodeIn{S3Fox}.
+In particular, the issue was because the \CodeIn{S3Fox} developers overlooked the constraints in \amazon.
+The API document pertaining to the  delete bucket functionality clearly states that before deleting the bucket, the objects in the buckets must be deleted.
 \textit{``All objects (including all objects versions and Delete Markers) in the bucket must be deleted before the bucket itself can be deleted''}.
-Although the issue was fixed but notice that one of the responses on the \textit{Stack Overflow} encouraged the person asking query to switch to another product, thus potentially resulting in a loss of revenue attributed to customer dissatisfaction.
-In yet another example a developer points out the financial losses he suffered because he was incorrectly using the previously described delete bucket functionality as shown in Figure~\ref{fig:example2}, \textit{(``...paying for excess stuff you don't need is simply idiotic...'')}.
+Although the issue was fixed but one of the responses on the forum encouraged the person asking query to switch to another product,
+thus potentially resulting in a loss of revenue attributed to customer dissatisfaction.
 
-%\begin{figure}[t]
-%\begin{center}
-%\includegraphics[scale=0.5]{AmzonS3DeleteBucketAPI.eps}
-%\end{center}
-%\caption{\label{fig:AmzonS3DeleteBucketAPI} The online API document for \CodeIn{DELETE Bucket} operation in Amazon S3 REST API}
-%\end{figure}
-
-Formal verification tools can be used to easily find such kind of defects.
-However, formal analysis tools are not designed to work on specifications in natural languages (such as API Documents) and require the specifications in a more formal or machine understandable format.
+The preceding issue can be easily detected using formal analysis tools.
+For instance, a specification rule (a temporal constraint) can be added to a static checker to verify
+the presence of a call to delete object functionality before the call to delete bucket functionality.
+However, existing formal analysis accept only formal specifications but not informal constraints described in natural language.
 Thus, there is need for an approach to automatically translate the constraints described in natural language into a more formal notation.
-In next section, we briefly discuss the related work in this area.
-
-\begin{figure}[t]
-\begin{center}
-\includegraphics[scale=0.6]{Example2.eps}
-\end{center}
-\caption{\label{fig:example2} The experience article posted by a developer regarding Amazon S3 REST API}
-\end{figure}
+In next section, we briefly discuss the related work pertinent to our proposed approach.

### 2014-03-15 Draft/background.tex
Revised Example, Related work, and background Section

--- 2014-02-19 Draft/background.tex
@@
 However, research advances~\cite{Marneffe06LREC,Marneffe08COLING,Klein03,KleinNIPS03} have increased the accuracy of existing NLP techniques to annotate the grammatical structure of a sentence.
-These advances in NLP have inspired researchers/practitioners~\cite{pandita12:inferring, pandita13:WHYPER, johnSlankasPASSAT13, XiaoFSE2012, thummalapentaICSE12} to adapt/apply NLP techniques to solve problems in software engineering domain.
+These advances in NLP have inspired researchers/ practitioners~\cite{pandita12:inferring, pandita13:WHYPER, johnSlankasPASSAT13, XiaoFSE2012, thummalapentaICSE12} to adapt/apply NLP techniques to solve problems in SE domain.
 
@@
 We first introduce the core NLP techniques used in this work.
-We then introduce the software engineering specific NLP techniques proposed in previous work~\cite{pandita12:inferring,pandita13:WHYPER} that are used in this work.
+We then introduce the SE specific NLP techniques proposed in previous work~\cite{pandita12:inferring,pandita13:WHYPER} that are used in this work.
 
@@
 The most commonly used technique is to train a classification parser over a previously known data set.
-Current state of the art approaches have demonstrated to achieve 97\%~\cite{SNLP1} accuracy in classifying POS tags for well written news articles.
+Current state of the art approaches have demonstrated to be effective in classifying POS tags for well written news articles.
 
@@
 Chunking thus further enhances the syntax of a sentence on top of POS tagging.
-Current state-of-the-art approaches can achieve around 90\%~\cite{SNLP1} accuracy in classifying phrases and clauses over well written news articles.
+Current state-of-the-art approaches can effectively classify phrases and clauses over well written news articles.
 
@@
 
-\textbf{Named Entity Recognition}~\cite{Finkel05ACL}.
+%\textbf{Named Entity Recognition}~\cite{Finkel05ACL}.
 Also known as \textit{`entity identification'} and \textit{`entity extraction'}, these techniques are a subtask of information extraction that aims to classify words in a sentence into predefined categories such as names, quantities, expression of times, etc.
@@
 
-\subsection{Software engineering specific NLP techniques}
+\subsection{SE specific NLP techniques}
 \label{sub:SENLPback}
@@
 \textbf{Noun Boosting}~\cite{pandita12:inferring}. Accurate annotation of POS tags in a sentence is fundamental to effectiveness of any advanced NLP technique.
-However, as mentioned earlier, POS tagging works well on well written news articles which does not necessary entail that the tagging works well on domain specific text as well.
+However, as mentioned previously, POS tagging works well on well written news articles which does not necessary entail that the tagging works well on domain specific text as well.
 Thus, noun boosting is a necessary precursor to application of POS tagging on domain specific text.
@@
 Consider the word \CodeIn{POST} for instance. 
-The online Oxford dictionary\footnote{\url{http://oxforddictionaries.com/us/definition/american_english/post?q=POST}} has 8 different definition of word \CodeIn{POST}, and none of them describes \CodeIn{POST} as a HTTP method\footnote{In HTTP vocabulary \CodeIn{POST} means: \textit{``Creates a new entry in the collection.
+The online Oxford dictionary\footnote{\url{http://oxforddictionaries.com/us/definition/american_english/post?q=POST}} has eight different definition of word \CodeIn{POST}, and none of them describes \CodeIn{POST} as a HTTP method\footnote{In HTTP vocabulary \CodeIn{POST} means: \textit{``Creates a new entry in the collection.
 The new entry's URI is assigned automatically and is usually returned by the operation''}}

### 2014-03-15 Draft/related.tex
Revised Example Section
Revised Example, Related work, and background Section

@@
 
-% "In contrast" switch up the wording a little bit
-
-Our proposed approach touches a few research areas such as software verification,
-NLP in software engineering, and document augmentation.
+Our proposed approach touches a few research areas such as software verification, NLP in Software Engineering (SE), and document augmentation.
 We next discuss the relevant work pertinent to our proposed approach in these areas.
@@
 % Define temporal constraints distinction
-Formal specifications such as code contracts have been an active area of research.
-Notably, code contracts that are the heart of design by contract approach have been very influential in the area of software engineering.
-A significant amount of work has been done in automated inference of code contracts.
-Existing approaches statically or dynamically extract code contracts~\cite{csallner08dysy,NimmerE02:ISSTA,Tillmann:2006:DLM:2105385.2105433}.
-However, a combination of developer written and automatically inferred contracts seems to be the most effective approach~\cite{Polikarpova2009ISSTA,Flanagan2001:HAA}.
-Furthermore, there are existing approaches that infer code-contract-like specifications
-(such as behavioral model, algebraic specifications, and exception specifications) either dynamically\cite{Henkel07discoveringdocumentation,Ghezzi:2009:SIB:1555001.1555057,Henkel:2008:DDA:1363102.1363105} or statically~\cite{Flanagan2001:HAA,Buse:2008:ADI:1390630.1390664} from source code and binaries.
-In contrast, the approach presented in this work infers specifications from the natural language text in API documents,
+\textbf{Formal Specification}:
+Contracts have become an a well-known mechanism for formally specifying functional behavior of the software. 
+Contracts specify the behavior in terms of conditions that must hold before/after and during the execution of the method.
+A significant amount of work has been done in automated inference of contracts.
+Existing approaches use program analysis~\cite{csallner08dysy,NimmerE02:ISSTA,Tillmann:2006:DLM:2105385.2105433}
+as means to automatically infer contracts.
+However, recent studies~\cite{Polikarpova2009ISSTA,Flanagan2001:HAA} demonstrate that a combination of developer-written and automatically extracted
+contracts is the most effective approach for formally specifying the constraints on an API.
+Since  our approach infers temporal constraint from API documents, we believe our approach can work in conjunction with existing approaches
+to infer a compressive set of specifications.
+
+Furthermore, another set of approaches exist that infer code-contract-like specifications (such as behavioral model, algebraic specifications, and exception specifications) either dynamically\cite{Henkel07discoveringdocumentation,Ghezzi:2009:SIB:1555001.1555057,Henkel:2008:DDA:1363102.1363105} or statically~\cite{Flanagan2001:HAA,Buse:2008:ADI:1390630.1390664} from source code and binaries.
+In contrast, the approach presented in this report infers specifications from the natural language text in API documents,
 thus complementing these existing approaches when the source code or binaries of the API library is not available.
 
-\subsection{NLP in Software Engineering}
+\textbf{NLP in SE}:
+NLP techniques are being increasingly applied in the SE domain. 
+Tan et al.~\cite{TanSOSP07} were the first to apply Machine Learning (ML) and NLP on code comments to detect mismatches between the comments and the implementation.
+They rely on predefined rule templates targeted towards threading and lock related comments, thus limiting their scope both in terms of application area as well as language used in the comments.
+Furthermore, the constraints inferred by their approach are the restrictions imposed by the developer on the client code.
+In comparison, the temporal constraints inferred by our approach are the restriction imposed by the API library being used by the client code.
+Furthermore, approach presented in this report relies on generic natural language based templates thus relaxing the restriction on the style of the language used to describe specifications.
 
-NLP techniques are increasingly applied in the software engineering domain. 
-NLP techniques have been shown to be useful in requirements engineering ~\cite{Sinha2009,Sinha2010,Gervasi2005},
-usability of API documents~\cite{Dekel2009}, and other areas~\cite{Zhou2008,Little2009,pandita13:WHYPER}.
-We next describe the most relevant approaches.
+Zhong et al.~\cite{zhong09SE} leverage machine learning and type information to infer constraints on resources based on phases of resource usage: creating, manipulating, and releasing.
+However, temporal constraints are not limited to resource usage thus 
+Furthermore, the specifications inferred by their approach infers implicit specifications across multiple method descriptions,
+whereas the temporal constraints inferred by our approach infers explicit ordering information described in individual method descriptions.
+Furthermore, the performance of their approach is dependent on the quality of the training sets used for ML.
+In contrast, approach presented in this report is independent of such training set and thus can be easily extended to target respective problems addressed by them.
 
-\textit{1.
-Access Control Policies}: Xiao et al.~\cite{XiaoFSE2012} and Slankas et al.~\cite{johnSlankasPASSAT13} use shallow parsing techniques to infer Access Control Policy (ACP) rules from natural language text in use cases.
-The use of shallow parsing techniques works well on natural language texts in use cases, owing to well formed structure of sentences in use case descriptions.
-In contrast, often the sentences in API documents are not well formed.
+Xiao et al.~\cite{XiaoFSE2012} and Slankas et al.~\cite{johnSlankasPASSAT13} use shallow parsing techniques to infer Access Control Policy (ACP) rules from natural language text in use cases.
+The use of shallow parsing techniques works satisfactorily on natural language texts in use cases, owing to well-formed structure of sentences in use case descriptions.
+In contrast, often the sentences in API documents are not well-formed.
 Additionally, these approaches do not deal with programming keywords or identifiers, which are often mixed within the method descriptions in API documents.
 
-\textit{2. Resource Specifications}: Zhong et al.~\cite{zhong09SE} employ NLP and  Machine Learning (ML) techniques to infer resource specifications from API documents.
-Their approach uses machine learning to automatically classify such rules.
-In contrast, we attempt to parse sentences based on semantic templates and demonstrate that such an approach preforms reasonably well.
-Furthermore, the performance of the proposed approach is dependent on the quality of the training sets used for ML.
-In contrast, approach presented in this work is independent of such training set and thus can be easily extended to target respective problems addressed by them.
+Most closely related work to the approach presented here is Pandita et al.~\cite{pandita12:inferring} work on inferring parameter constraints from method descriptions in the API documents.
+Our proposed approach differs from the previous approach as follows.
+Our proposed approach addresses the problem of inferring temporal constraint, whereas the previous approach infers parameter constraints.
+Our proposed approach is a significant extension to the infrastructure used in the previous work in following areas.
+First, the proposed approach introduces hybrid shallow parsing that relies both on POS tags as well as Stanford-typed dependencies to construct intermediate representation.
+Second, the proposed approach introduces a new heuristics namely frequent phrase reduction to deal with the domain specific and ill-formed sentences in API documents.
+Finally, the proposed approach leverages the concept of semantic graphs constructed from class and method names in API to automatically infer the implicit method references in a sentence.
 
-\textit{3.
-Code Comments}: Tan et al.~\cite{TanSOSP07} and Hwei-Tan et al.~\cite{tcomment} applied an NLP and ML  based approach on code comments/ Javadoc comments to detect mismatches between these comments and implementations.
-They rely on predefined rule templates targeted towards method invocation and lock related comments, thus limiting their scope both in terms of application area as well as language used in the comments.
-In contrast, approach presented in this report relies on generic natural language based templates thus relaxing the restriction on the style of the language used to describe specifications.
-
-\textit{4.
-API Description}: Most closely related work to the approach presented here is Pandita et al.~\cite{pandita12:inferring} work on inferring parameter constraints from method descriptions in the API documents.
-In contrast this approach deals with the temporal constraints.
-The approach presented here is a significant extension to the infrastructure used in the previous work as documented in Section~\ref{sec:approach}.
-
-\subsection{Augmented Documentation}
-
-Another related field has been that of improving the documentation related to an software API~\cite{Dekel2009,tan2011acomment}.
-We next describe most relevant approaches.
-Dekel et al.~\cite{Dekel2009}, were the first to create a tool namely eMoose, an Eclipse~\footnote{\url{http://www.eclipse.org/}} based plug-in that allowed developers to create directives (way of marking the specification sentences) in the default API documentation.
+\textbf{Augmented Documentation}:
+Improving the documentation related to an software API~\cite{Dekel2009,tan2011acomment} is another related field of research.
+Dekel and Herbsleb~\cite{Dekel2009}, were the first to create a tool namely eMoose,
+an Eclipse~\footnote{\url{http://www.eclipse.org/}} based plug-in that allowed developers to create directives
+(way of marking the specification sentences) in the default API documentation.
 These directives are highlighted whenever they are displayed in the eclipse environment.
-Lee et al.~\cite{lee2012towards} improved upon their work by providing a formalism to the directives proposed by Dekel et al.~\cite{Dekel2009}, thus allowing tool based verification.
+Lee et al.~\cite{lee2012towards} improved upon their work by providing a formalism to the directives proposed by Dekel et al.~\cite{Dekel2009},
+thus allowing tool-based verification.
 However, a developer has to manually annotate such directives.

### 2014-03-15 Draft/abstract.tex
Fixing Partial Comments on Introduction
Revised Example, Related work, and background Section
Style Check
that and where left.

@@
 
-On the other hand, automatically inferring temporal constraints from API documents faces is challenging.
+On the other hand, automatically inferring temporal constraints from API documents is challenging.
 In particular, it is challenging to automatically 
@@
 
-To address the preceding challenge, we propose an natural-language-processing-based approach \tool,
+To address the preceding challenge, we propose a natural-language-processing-based approach \tool,
 to infer formal temporal constraints from natural language text of API documents. These constraints can be used (as input)
@@
 commonly used package \CodeIn{java.io} from JDK API and \amazonAPI.
-Our evaluation results are promising. In particular, \tool\ achieves an average of 65\% precision and 72\% recall
+Our evaluation results are promising.
+In particular, \tool\ achieves an average of 65\% precision and 72\% recall
 in inferring 63 temporal constraints from more than 3900 sentences of API documents.

### 2014-03-15 Draft/approach.tex
Minor Fixes
Revised Example, Related work, and background Section
Style Check
that and where left.

@@
-\section{\tool\ Design}
+\section{Approach Overview}
 \label{sec:approach}
@@
 
-In particular, we use n-gram based approach as means to achieve this reduction. 
+In particular, we use n-gram based approach to achieve this reduction. 
 In the fields of computational linguistics and probability, an n-gram is a contiguous sequence of n words from a given sequence of text or speech. 
@@
 We then prune the list of n-grams based on a subsumption. 
-We consider a n-gram of length k ($n_k$) to subsume n-gram of length k-1 ($n_{k-1}$) iff $n_{k-1}$ is a substring of ($n_k$) and the frequency of occurrence of $n_{k-1}$ equals frequency of occurrence of $n_{k}$.
+We consider an n-gram of length k ($n_k$) to subsume n-gram of length k-1 ($n_{k-1}$) iff $n_{k-1}$ is a substring of ($n_k$) and the frequency of occurrence of $n_{k-1}$ equals frequency of occurrence of $n_{k}$.
 Finally, we rank the list of n-grams based on the frequency of their occurrence in the text, and select top-k n-grams for reduction.
@@
 Apache Lucene is a high-performance, full-featured text search engine library written entirely in Java.
-It is a technology suitable for nearly any application that requires full-text search, especially cross-platform.
+Lucene is a technology suitable for nearly any application that requires full-text search, especially cross-platform.
 
@@
 From an implementation perspective, we chose the Stanford parser~\cite{Manning:01}.
-However, this component can be implemented using any other existing NLP libraries or approachs.
+However, this component can be implemented using any other existing NLP libraries or approaches.
 In particular, we annotate each sentence with POS tags, named-entity annotations and Stanford-typed dependencies.
@@
 	Typically, presence of temporal modifier is an indicator of presence of temporal information.  
-	\item If rules 2 and 3 don't apply then the sentences should be a conditional sentence, identified by the presence of keywords such as ``\textit{if}''.
+	\item If rules 2 and 3 don't apply then the sentences should be a conditional sentence, identified by the presence of keywords such as ``\textit{if}'' and ``\textit{whether}''.
 \end{enumerate}
@@
 Specification extractor then uses the semantic graph to determine
-if a candidate sentence is a specification sentence and if so extract
+whether a candidate sentence is a specification sentence and if so extract
 the action that should be performed prior to the method the sentence
@@
 the nodes representing methods in an API and the directed edges representing temporal constraints.
-First, a index is created based on the return types of the method (Line 2).
+First, an index is created based on the return types of the method (Line 2).
 Second, all methods in an API are added to an unconnected graph (Line 3-4).

### 2014-03-15 Draft/background.tex
Style Check
that and where left.

@@
 The Stanford typed dependencies representation  is designed to provide a simple description of grammatical relationships directed towards non-linguistics experts to perform NLP related tasks.
-It provides a hierarchical structure for the dependencies with precise definitions of what each dependency means, thus facilitating machine based manipulation of natural language text.
+It provides a hierarchical structure for the dependencies with precise definitions of what each dependency represents, thus facilitating machine based manipulation of natural language text.
 
@@
 \textbf{Noun Boosting}~\cite{pandita12:inferring}. Accurate annotation of POS tags in a sentence is fundamental to effectiveness of any advanced NLP technique.
-However, as mentioned previously, POS tagging works well on well written news articles which does not necessary entail that the tagging works well on domain specific text as well.
+However, as mentioned previously, POS tagging works satisfactorily on well written news articles which does not necessary entail that the tagging works satisfactorily on domain specific text as well.
 Thus, noun boosting is a necessary precursor to application of POS tagging on domain specific text.
-In particular, with respect to API documents certain words have a very different semantic meaning, in contrast to general linguistics that causes incorrect annotation of POS tags.
+In particular, with respect to API documents certain words have a different semantic meaning, in contrast to general linguistics that causes incorrect annotation of POS tags.
 
 Consider the word \CodeIn{POST} for instance. 
-The online Oxford dictionary\footnote{\url{http://oxforddictionaries.com/us/definition/american_english/post?q=POST}} has eight different definition of word \CodeIn{POST}, and none of them describes \CodeIn{POST} as a HTTP method\footnote{In HTTP vocabulary \CodeIn{POST} means: \textit{``Creates a new entry in the collection.
+The online Oxford dictionary\footnote{\url{http://oxforddictionaries.com/us/definition/american_english/post?q=POST}} has eight different definition of word \CodeIn{POST}, and none of them describes \CodeIn{POST} as an HTTP method\footnote{In HTTP vocabulary \CodeIn{POST} means: \textit{``Creates a new entry in the collection.
 The new entry's URI is assigned automatically and is usually returned by the operation''}}
@@
 In particular, WHYPER~\cite{pandita13:WHYPER} demonstrates the effectiveness of this technique, by constructing an intermediate representation generator based on shallow parsing~\cite{Branimir2000} techniques.
-The shallow parser itself is implemented as a sequence of cascading finite state machines based on the functions of stanford-typed dependencies~\cite{Marneffe06LREC,Marneffe08COLING,Klein03,KleinNIPS03}.
+The shallow parser itself is implemented as a sequence of cascading finite state machines based on the function of Stanford-typed dependencies~\cite{Marneffe06LREC,Marneffe08COLING,Klein03,KleinNIPS03}.
 

### 2014-03-15 Draft/evaluation.tex
Fixed bib entries and references
Minor Fixes
Style Check
that and where left.

@@
 
-\begin{tabular}{|l|c|c|c|c|c|c|c|c|c|c|c|c|}
-\hline API & Mtds & Sen & Sen$_C$ & Sen$_{ICON}$ & TP & FP & FN & P(\%) & R(\%) & F$_S$(\%) & Spec$_{ICON}$ & Acc(\%)\\
-\hline 
-\hline java.io &  & 2417 & 78 & 88 & 57 & 31 & 21 & 64.8 & 73.1 & 68.8 & 56 & 71.8\\ 
-\hline AMAZON S3 REST & 51 & 1492 & 12 & 12 & 8 & 4 & 4 & 66.7 & 66.7 & 66.7 & 7 & 58.3\\ 
-\hline Total &  & 3909 & 90 & 100 & 65 & 35 & 25 & 65.0$^*$ & 72.2$^*$ & 68.4$^*$ & 63 & 70.0$^*$\\ 
-\hline
+\begin{tabular}{lcccccccccccc}
+\topline
+\headcol API & Mtds & Sen & Sen$_C$ & Sen$_{ICON}$ & TP & FP & FN & P(\%) & R(\%) & F$_S$(\%) & Spec$_{ICON}$ & Acc(\%)\\
+\midline 
+java.io & 662 & 2417 & 78 & 88 & 57 & 31 & 21 & 64.8 & 73.1 & 68.8 & 56 & 71.8\\ 
+\rowcol AMAZON S3 REST & 51 & 1492 & 12 & 12 & 8 & 4 & 4 & 66.7 & 66.7 & 66.7 & 7 & 58.3\\ 
+Total & 713 & 3909 & 90 & 100 & 65 & 35 & 25 & 65.0$^*$ & 72.2$^*$ & 68.4$^*$ & 63 & 70.0$^*$\\ 
+\bottomlinec
 %----------------- END TABLE DATA ------------------------ 
@@
 For \CodeIn{java.io}, we define a type-enforced constraint as a constraint that mandates a method M accepting input parameter I of type T to be invoked after (at least one) a method M0 whose return value is of type T.
-Since there are no types in REST APIs, for \CodeIn{Amazon S3}, we consider a constraint as a type-enforced constraint if it is implicit in the \CodeIn{CRUD} naming convention followed by REST operations.
+Since there are no types in REST APIs, for \CodeIn{Amazon S3}, we consider a constraint as a type-enforced constraint if the constraint is implicit in the \CodeIn{CRUD} naming convention followed by REST operations.
 In particular, we consider a constraint as a type-enforced constraint, if the constraint mandates a DELETE, GET, or PUT operation on a resource to be invoked after a GET operation on the same resource.

### 2014-03-15 Draft/example.tex
Style Check
that and where left.

@@
 We suspect the reason for this phenomena is that the documentation is often verbose and the information is distributed across various pages.
-For instance, the PDF version of the documentation for \amazonAPI\footnote{\url{http://awsdocs.s3.amazonaws.com/S3/latest/s3-api.pdf}} spans 278 pages.
+For instance, the PDF version of the documentation for \amazonAPI\footnote{{\small \url{http://awsdocs.s3.amazonaws.com/S3/latest/s3-api.pdf}}} spans 278 pages.
 Developers often may not have time (and/or patience) to go through all the documentation and may overlook some temporal constraints of the API,
@@
 
-Consider the question asked in \textit{Stack Overflow}~\footnote{\url{http://stackoverflow.com/}} as shown in Figure~\ref{fig:Stackoverflow}.
+Consider the question asked in \textit{Stack Overflow}~\footnote{{\small \url{http://stackoverflow.com/}}} as shown in Figure~\ref{fig:Stackoverflow}.
 Stack Overflow is an online question and answer forum for professional and enthusiast programmers.
@@
 In particular, the issue was because the \CodeIn{S3Fox} developers overlooked the constraints in \amazon.
-The API document pertaining to the  delete bucket functionality clearly states that before deleting the bucket, the objects in the buckets must be deleted.
+The API document pertaining to the  delete bucket functionality states that before deleting the bucket, the objects in the buckets must be deleted.
 \textit{``All objects (including all objects versions and Delete Markers) in the bucket must be deleted before the bucket itself can be deleted''}.
@@
 The preceding issue can be easily detected using formal analysis tools.
-For instance, a specification rule (a temporal constraint) can be added to a static checker to verify
+For instance, a specification rule (temporal constraint) can be added to a static checker to verify
 the presence of a call to delete object functionality before the call to delete bucket functionality.

### 2014-03-15 Draft/introduction.tex
Style Check
that and where left.

@@
 For a method under consideration, an API document may describe both the constraints on that method parameters as well as the temporal constraints in terms of the methods must be invoked pre/post the method.
-We observed that a eminent portion (roughly 12\%) of the sentences (that describe some sort of constraints) in \amazonAPI\ documentations describe temporal constraints.
+We observed that an eminent portion (roughly 12\%) of the sentences (that describe some sort of constraints) in \amazonAPI\ documentations describe temporal constraints.
 Although API documents contain temporal constraints, existing formal analysis tools accept only formal constraints but not informal constraints written in natural language.

### 2014-03-15 Draft/related.tex
Style Check
that and where left.

@@
 \textbf{Formal Specification}:
-Contracts have become an a well-known mechanism for formally specifying functional behavior of the software. 
+Contracts have become a well-known mechanism for formally specifying functional behavior of the software. 
 Contracts specify the behavior in terms of conditions that must hold before/after and during the execution of the method.
@@
 Existing approaches use program analysis~\cite{csallner08dysy,NimmerE02:ISSTA,Tillmann:2006:DLM:2105385.2105433}
-as means to automatically infer contracts.
+to automatically infer contracts.
 However, recent studies~\cite{Polikarpova2009ISSTA,Flanagan2001:HAA} demonstrate that a combination of developer-written and automatically extracted
@@
 \textbf{Augmented Documentation}:
-Improving the documentation related to an software API~\cite{Dekel2009,tan2011acomment} is another related field of research.
+Improving the documentation related to a software API~\cite{Dekel2009,tan2011acomment} is another related field of research.
 Dekel and Herbsleb~\cite{Dekel2009}, were the first to create a tool namely eMoose,

### 2014-03-15 Draft/approach.tex
Revised Approach

@@
 \label{sec:approach}
-%\vspace{-2mm}
 
@@
 
-We next present our approach for inferring specifications from the method descriptions in API Documents.
+We next present our approach for inferring temporal constraints from the method descriptions in API Documents.
 Figure~\ref{fig:approachOverview} gives an overview of our approach.
-Our approach consists of five major components: a preprocessor, a text-analysis engine, a semantic graph generator, specification extractor, and a type analyzer.
+Our approach consists of five major components: a preprocessor, a text-analysis engine, a semantic graph generator, constraint extractor, and a type analyzer.
 
-The preprocessor accepts API documents and preprocesses the sentences in the method description, such as annotating sentence boundaries and reducing lexical tokens.
+The preprocessor accepts API documents and preprocesses the sentences in the method description,
+such as annotating sentence boundaries and reducing lexical tokens.
 The text-analysis engine accepts the pre-processed sentences and annotates them using an NLP parser.
 The text-analysis engine further transforms the annotated sentences into the first-order-logic (FOL) representation.
-The semantic graph generator accepts the API documents and generates the semantic graphs that are leveraged by specification extractor component.
+The semantic graph generator accepts the API documents and generates the semantic graphs that are leveraged by constraint extractor component.
 The type analyzer component infers temporal constraints encoded in the type system of a language by analyzing the API methods parameter and return types.
-Finally, the specification extractor then leverages the semantic graphs to infer temporal constraints from the FOL representation of a sentence.
+Finally, the constraint extractor leverages the semantic graphs to infer temporal constraints from the FOL representation of a sentence.
 We next describe each component in detail.
@@
 
-The preprocessor accepts the API documents and first extracts method descriptions from it.
+The preprocessor accepts the API documents and extracts method descriptions from it.
 In particular, the preprocessor extracts the following fields within method descriptions: 
@@
 
-This step is required to extract the desired descriptive text from the various presentation styles of the API documents.
+This step is required to extract the desired descriptive text from the API documents.
 In particular, different API documents may have different styles of presenting information to developers.
-This difference in style may include the difference in the level of detail presented to the developer.
+This difference in style may also include the difference in the level of detail presented to developers.
 Our approach thus relies on only basic fields that are trivially available for API methods across different presentation styles.
@@
 
-Although the previous techniques and heuristics significantly lower the number of lexical tokens in a sentence, some sentences may still contain a considerable number of lexical tokens to overwhelm the POS tagger.
-To address this issue, we propose a novel technique (\textit{`Frequent Phrases Reduction'}) to further reduce the number of lexical tokens in a sentence by annotating frequent phrases as a single lexical unit.
+Although the previous techniques and heuristics significantly lower the number of lexical tokens in a sentence,
+some sentences may still contain a considerable number of lexical tokens to overwhelm the POS tagger.
+To address this issue, we propose a new heuristic (\textit{`Frequent Phrases Reduction'})
+to further reduce the number of lexical tokens in a sentence by annotating frequent phrases as a single lexical unit.
 
-In particular, we use n-gram based approach to achieve this reduction. 
-In the fields of computational linguistics and probability, an n-gram is a contiguous sequence of n words from a given sequence of text or speech. 
-We first calculate the most frequently occurring n-grams in the text body. 
-In particular, we are interested in the n-grams of length 4 or greater to achieve a reasonable reduction. 
+In particular, we use n-gram~\cite{brown1992class} based approach to achieve this reduction. 
+In the fields of computational linguistics, an n-gram is a contiguous sequence of n words from a given text.
+In statistical NLP  and information theory, n-gram has been shown to be effective in computing the probability of occurrence of next word given a sequence of words.
+However, for our approach we use n-grams that always occur together in a given body of text.
+
+To achieve \textit{frequent phrases reduction}, we first calculate the most frequently occurring n-grams in the text body. 
+In particular, we are interested in the n-grams of length four or greater to achieve a reasonable reduction.
+We chose four as a threshold for n-grams because we observed that bigrams (size two) and trigrams (size three) frequently resulted in change of semantics
+of the sentence in comparison to n-grams of size four or grater.
 We then prune the list of n-grams based on a subsumption. 
@@
 Finally, we rank the list of n-grams based on the frequency of their occurrence in the text, and select top-k n-grams for reduction.
-For instance, \textit{Amazon Simple Storage Service}, \textit{an I/O Error Occurs}, and \textit{end of stream} are the examples of such n-grams detected by our approach.
-%\begin{figure}[t]
-%\begin{CodeOut}
-%\begin{alltt}
-%01: 
-%04:
-%\end{alltt}
-%\end{CodeOut}\vspace*{-2ex}
-%\caption{\label{fig:methodAPI} The method description of the \CodeIn{DefineObjectProperty} method in Facebook API}\vspace*{-4ex}
-%\end{figure}
-\\
-\textbf{Prototype Implementation.}
+For instance, \textit{Amazon Simple Storage Service}, \textit{an I/O Error Occurs}, and \textit{end of the stream} are the examples of such n-grams detected by our approach.
+
+%\textbf{Prototype Implementation.}
 Currently our prototype implementation works with online \amazon\ and JDK API. 
 However, almost all of the developer documents are provided online as structured webpages.
-Thus, current implementation of preprocessor can be easily extended to extract the desired information from any API developer documents.
+Thus, current prototype implementation of preprocessor can be easily extended to extract the desired information from any API developer documents.
 
-Additionally, in current implementation we have manually built the domain dictionaries for preprocessing using the glossary of terms collected from the websites pertaining to REST and Java API.
+Additionally, in current implementation we have manually built the dictionaries for preprocessing using the glossary of terms collected from the websites pertaining to REST and Java API.
 We further leveraged the HTML style information in \amazon\ to look for words that were highlighted in code like format.
@@
 
-Finally, to achieve  n-gram reduction we used Apache Lucene$^{\textregistered}$~\cite{lucene}.
-Apache Lucene is a high-performance, full-featured text search engine library written entirely in Java.
-Lucene is a technology suitable for nearly any application that requires full-text search, especially cross-platform.
-
-%Although a POS tagger can be retrained to achieve these pre-processing steps, we prefer annotations to make our approach independent of any specific NLP infrastructure, thus ensuring interoperability with various POS taggers.
+Finally, to achieve  n-gram reduction we used Apache Lucene~\cite{lucene}.
+Apache Lucene is a high-performance, full-featured text-search-engine library written entirely in Java,
+facilitating scalable cross-platform full-text search.
 
@@
 
-%\begin{figure}
-%	\centering
-%%		\includegraphics[scale=0.6]{StanfordAnnotated.eps}
-%	\caption{Sentence annotated with Stanford dependencies}
-%	\label{fig:standep}
-%\end{figure}
-%
-%Next we use an example to illustrate the annotations added by the NLP Parser.
-Consider the example sentence \textbf{\textit{``Also you can share the yoga exercise to your friends via Email and SMS.''}}, that indirectly refers to the READ\_CONTACTS permission.
+\begin{figure}
+	\centering
+		\includegraphics[scale=0.3]{StanfordAnnotated.eps}
+	\caption{Sentence annotated with Stanford dependencies}
+	\label{fig:standep}
+\end{figure}
+
+Next we use an example to illustrate the annotations added by the NLP Parser.
+Consider the sentence from the example section \textbf{\textit{`All objects (including all object versions and Delete Markers) in the bucket must be deleted before the bucket itself can be deleted.''}}.
 Figure~\ref{fig:standep} shows the sentence annotated with Stanford-typed dependencies.
@@
 In particular, we use semantic templates to logically break a sentences into smaller constituent sentences. 
-For instance, consider the sentence:
+For instance, consider the sentence which are then accurately annotated by the underlying NLP Parser:
 
@@
 
-The Stanford parser inaccurately annotates the Stanford-typed dependencies of the sentence because of presence of different clauses acting on different subject-object pairs.
+The Stanford parser finds it difficult to annotate accurately the Stanford-typed dependencies of the sentence because of presence of different clauses acting on different subject-object pairs.
+As shown in figure~\ref{fig:standep} the word including is annotated with Stanford-typed dependencies ``dep'' that is a catch all dependency.
 We thus break down the sentence into two smaller tractable sentences:
@@
 
-\subsection{Specification Extractor}
+\subsection{Constraint Extractor}
 \label{sub:SE}
@@
 then extracts the temporal constraints if present in a sentence.
-Specification Extractor then classifies the sentence as a specification 
+Constraint Extractor then classifies the sentence as a constraint 
 sentence (containing temporal constraint) candidate based on following ordered set of rules:
@@
 In particular, the semantic graph of the API class to which the candidate sentence belongs to selected.
+Since there is no concept of classes in REST API, semantic graphs of all resources described in the API are selected.
 A semantic graph constitutes the keyword representation of the classes and the corresponding applicable actions. 
-Figure~\ref{fig:knowledge} shows a sub-graph of  graph for \CodeIn{BufferedInputReader} class.
-The phrases in solid rectangles are synonyms of the class name \CodeIn{BufferedInputReader}.
-The phrases in rounded rectangle are the actions applicable on \CodeIn{BufferedInputReader} class.
+Figure~\ref{fig:knowledge} shows a graph for \CodeIn{Object} resource in \amazonAPI.
+The phrases in rounded rectangle are the actions applicable on \CodeIn{Object} resource.
 Section~\ref{sub:ACA} further describes how these graphs are generated.
 
-Specification extractor then uses the semantic graph to determine
-whether a candidate sentence is a specification sentence and if so extract
+Constraint extractor then uses the semantic graph to determine
+whether a candidate sentence is a constraint sentence and if so extract
 the action that should be performed prior to the method the sentence
@@
 of the candidate sentence to determine if a sentence
-describes a temporal specification. First, our algorithm
+describes a temporal constraint. First, our algorithm
 attempts to locate the occurrence of class name or its synonym
@@
 		\includegraphics[scale=0.4]{KnowledgeGraph.eps}
-	\caption{Semantic Graph for the \CodeIn{BufferedInputStream} class in Java}
+	\caption{Semantic Graph for the \CodeIn{Object} related operations in Amazon S3 REST API}
 	\label{fig:knowledge}
@@
 The verb phrases are used as the associated actions applicable on the object.
-For instance, \CodeIn{BufferedInputReader} defines operations available, close, mark, and so on.
-We associate these operations with the objects of type \CodeIn{BufferedInputReader}.
-Figure~\ref{fig:knowledge} shows a sub-graph of  graph for \CodeIn{BufferedInputReader} class.
-The phrases in solid rectangles are synonyms of the class name \CodeIn{BufferedInputReader}.
-The phrases in rounded rectangle are the actions applicable on \CodeIn{BufferedInputReader} class.
+In case of REST API we first identified the resources and then listed REST actions on those resources as applicable actions.
+Figure~\ref{fig:knowledge} shows the graph for \CodeIn{Object} resource in REST API.
+The phrases in rounded rectangle are the REST actions applicable on \CodeIn{Object} resource in \amazonAPI.
 

### 2014-03-16 Draft/evaluation.tex
Revised Evaluation

@@
 
-We conducted an evaluation to assess the effectiveness of \tool. In our evaluation, we address two main research questions:
+We next present the evaluation we conducted to assess the effectiveness of \tool. In our evaluation, we address three main research questions:
 
@@
 	\item\textbf{RQ1}: What are the precision and recall of \tool\ in identifying temporal constraints from sentences written in natural language?
+	Answer to this question quantifies the effectiveness of \tool\ in identifying constraint sentences.
 	\item\textbf{RQ2}: What is the accuracy of \tool\ in inferring temporal constraints from constraint sentences in the API documents?
-	\item\textbf{RQ3}: How do the constraints inferred by our approach compare with the typed-enforced temporal constraints?
+	Answer to this question quantifies the effectiveness of \tool\ in inferring temporal constraints from constraint sentences. 
+	\item\textbf{RQ3}: What is the degree of the overlap between the temporal constraints inferred from natural language text in comparison to the typed-enforced temporal constraints?
 
@@
 \begin{itemize}
-	\item{Amazon S3}.
-\amazon\ provides a REST based web services interface that can be used to store and retrieve data on the web.
+	\item \amazonAPI\: provides a REST based web services interface that can be used to store and retrieve data on the web.
 Furthermore, \CodeIn{Amazon S3} also empowers a developer with rich set of API methods to access a highly scalable, reliable, secure, fast, inexpensive infrastructure.
@@
 
-	\item{java.io}. \CodeIn{java.io} is a popular packacge in \CodeIn{Java} programming language that provides APIs for system input and output through data streams, serialization and the file system.
+	\item\CodeIn{java.io} : is one of a popular packages in \CodeIn{Java} programming language.
+The package provides APIs for system input and output through data streams, serialization and the file system, which are one of the fundamental functionalities provided by a programming language.
 \end{itemize}
@@
 The \CodeIn{cohen kappa} score of the two authors was .66 (on a scale of 0 to 1), 
-which denotes a statically significant agreement. 
+which denotes a statically significant agreement~\cite{carletta1996assessing}. 
 After the authors classified all the sentences, they 
 discussed with each other to reach a consensus on the sentences they classified differently. 
-We use this classified sentences as the golden set for calculating precision and recall.
+We use these classified sentences as the golden set for calculating precision and recall.
 
@@
 
-In statistical classification~\cite{Olson08}, $Precision$ is defined as a ratio of
+In statistical classification~\cite{Olson08}, \CodeIn{precision} is defined as a ratio of
 number of true positives to the total number of items reported to be true,
-$Recall$ is defined as a ratio of number of true positives to the total number
-of items that are true. $F-score$ is defined as the weighted harmonic mean of 
-$Precision$ and $Recall$. Higher value of $Precision$, $Recall$, and $F-Score$
+\CodeIn{recall} is defined as a ratio of number of true positives to the total number
+of items that are true. \CodeIn{F-Score} is defined as the weighted harmonic mean of 
+\CodeIn{precision} and \CodeIn{recall}. Higher value of \CodeIn{precision}, \CodeIn{recall}, and \CodeIn{F-Score}
 are indicative of higher quality of the constraint statements inferred using 
 \tool. based on the calculation of $TP$, $FP$, $TN$, and $FN$ of \tool\ defined
-previously we computed the $Precision$, $Recall$, and $F-Score$ of \tool\ as follows:
+previously we computed the \CodeIn{precision}, \CodeIn{recall}, and \CodeIn{F-Score} of \tool\ as follows:
 
@@
 
-To answer RQ2, we checked the temporal constraints inferred from constraint sentences by \tool.
-We measure $accuracy$ of \tool as the ratio of the total number of temporal constraints that
-are correctly inferred by \tool to the total number of constraint sentences.
+To answer RQ2, we manually verified the temporal constraints inferred from constraint sentences by \tool.
+However, we excluded the type-enforced temporal constraints inferred using Algorithm~\ref{alg:TypeAnalysis}, described in Section~\ref{sec:approach}.
+We excluded the type-enforced constraints because they are correct by construction and are by default enforced by modern IDE's such as eclipse. 
+We then measure $accuracy$ of \tool\ as the ratio of the total number of temporal constraints that
+are correctly inferred by \tool\ to the total number of constraint sentences. Two authors
+independently verified the correctness of the temporal constraints inferred by \tool.
+We define the \CodeIn{accuracy} of \tool\ as the ratio of constraint sentences with correctly inferred temporal constraints
+to the total number of constraint sentences. 
+Higher value of \CodeIn{accuracy} is indicative of effectiveness of \tool\ in inferring temporal constraints from constraint sentences.
+
+To answer RQ3, we counted the overlap in the temporal constraints inferred by \tool\ 
+from the natural language text in API documents to the type-enforced temporal constraints
+inferred using Algorithm~\ref{alg:TypeAnalysis}, described in Section~\ref{sec:approach}.
 
@@
 
-We next describe our evaluation results to demonstrate the effectiveness of \tool\ in identifying temporal constraints.
+%We next describe our evaluation results.
 
@@
 Columns ``P(\%)'', ``R(\%)'', and ``F$_S$(\%)'' list percentage values of \CodeIn{precision}, \CodeIn{recall}, and \CodeIn{F-score} respectively. 
-Our results show that, out of 3,909 sentences, \tool\ effectively identifies constraint sentences with the average precision, recall, and F-score of 65.0\%, 72.2\%, and 68.4\%, respectively.
+Our results show that, out of 3,909 sentences, \tool\ effectively identifies constraint sentences with the average \CodeIn{precision}, \CodeIn{recall}, and \CodeIn{F-score} of 65.0\%, 72.2\%, and 68.4\%, respectively.
 
@@
 
-Another major source of FPs is the incorrect parsing of sentences by the underlying NLP infrastructure and/or inadequacy of generic dictionaries for synonym analysis.
-For instance, consider the sentence ``\textit{If this stream has an associated channel then the channel is closed as well.}'' from the \CodeIn{close} method description from \CodeIn{FileOutputStream}.
+Another major source of FPs is the incorrect parsing of sentences by the underlying NLP infrastructure
+and/or inadequacy of generic dictionaries for synonym analysis.
+For instance, consider the sentence ``\textit{If this stream has an associated channel then the channel is closed as well.}''
+from the \CodeIn{close} method description from \CodeIn{FileOutputStream}.
 The sentence describes an effect that happens as a result of calling the \CodeIn{close} method and does not describe any temporal constraint.
 However, \tool\ annotates the sentence as a constraint sentence because underlying Wordnet dictionaries matches the word ``has'' as a synonym of ``get''.
-This incorrect matching in turn causes \tool\ to incorrectly annotate the sentence as constraint sentence because ``has'' is matched against \CodeIn(get) method in \CodeIn{FileOutputStream}.
+This incorrect matching in turn causes \tool\ to incorrectly annotate the sentence as constraint sentence
+because ``has'' is matched against \CodeIn(get) method in \CodeIn{FileOutputStream}.
 We observed 8 instances of previously described example in our results.
 
-If we manually fixed the Wordnet dictionaries to match ``has'' and ``get'' as synonyms, our precision is further increased to 70.8\% effectively increasing the F-Score of \tool\ to 71.2\%.
-We refrained from including such modifications for reporting the results to stay true to our proposed framework.
+If we manually fixed the Wordnet dictionaries to not match ``has'' and ``get'' as synonyms,
+our precision is further increased to 70.8\% effectively increasing the F-Score of \tool\ to 71.2\%.
+Although an easy fix, we refrained from including such modifications for reporting the results to stay true to our proposed framework.
 In the future, we plan to investigate techniques to construct better domain dictionaries for software API.
@@
 We next present an example to illustrate how \tool\ fails identify a constraint sentence (producing false negative).
-False negatives are undesirable in the context of our problem domain, because they can mislead the users of \tool\ into believing that no other temporal constraint exists in the API documents.
-Furthermore, an overwhelming number of false negatives works against the usefulness of \tool.
-For instance, consider the sentence ``\textit{This implementation of the PUT operation creates a copy of an object that is already stored in Amazon S3.}'' from  \CodeIn{PUT Object-Copy} method description in \amazonAPI.
-The sentence describes the constraint that the object must already be stored (invocation of \CodeIn{PUT Object}) before calling the current method.
+False negatives are undesirable in the context of our problem domain
+because they can mislead the users of \tool\ into believing that no other temporal constraint exists in the API documents.
+Furthermore, an overwhelming number of false negatives works against the practicality of \tool.
+For instance, consider the sentence ``\textit{This implementation of the PUT operation creates a copy of an object that is already stored in Amazon S3.}''
+from  \CodeIn{PUT Object-Copy} method description in \amazonAPI.
+The sentence describes the constraint that the object must already be stored (invocation of \CodeIn{PUT Object})
+before calling the current method.
 However, \tool cannot make the connection owing to the limitation of the semantic graphs that do not list ``already stored'' as a ``valid operation'' on object.  
+In the future, we plan to investigate techniques to further improve knowledge graphs to infer such implicit constraints.
 
 Another major source of false negatives (similar to reasons for false positives) is the incorrect parsing of sentences by the underlying NLP infrastructure.
-For instance, consider the sentence ``\textit{If any in-memory buffering is being done by the application (for example, by a BufferedOutputStream object), those buffers must be flushed into the FileDescriptor (for example, by invoking OutputStream.flush) before that data will be affected by sync.}'' The sentence describes that the \CodeIn{OutputStream.flush()} must be invoked before invoking the current method if in-memory buffering is performed.
-However, the length and complexity in terms of number of clauses causes the underlying Stanford parser to inaccurately annotate the dependencies, which eventually results into incorrect classification.
+For instance, consider the sentence ``\textit{If any in-memory buffering is being done by the application (for example, by a BufferedOutputStream object),
+those buffers must be flushed into the FileDescriptor (for example, by invoking OutputStream.flush) before that data will be affected by sync.}''
+The sentence describes that the \CodeIn{OutputStream.flush()} must be invoked before invoking the current method if in-memory buffering is performed.
+However, the length and complexity in terms of number of clauses causes the underlying Stanford parser to inaccurately annotate the dependencies,
+which eventually results into incorrect classification.
 
 Overall, a significant number of false positives and false negatives will be reduced as the current NLP research advances the underlying NLP infrastructure.
-Furthermore, use of domain specific dictionaries as opposed to generic dictionaries used in current prototype implementation will further improve the precision and recall of \tool.
+Furthermore, use of domain specific dictionaries as opposed to generic dictionaries
+sed in current prototype implementation will further improve the precision and recall of \tool.
 
@@
 
-In this section, we evaluate the effectiveness of \tool\ in inferring temporal constraints from the identified constraint sentences from API documents.
-To answer RQ2, we ran the sentences manually identified as constraint sentences against \tool.
-We then manually verified the correctness of temporal constraints inferred by our \tool.
-We define the \CodeIn{accuracy} of \tool\ as the ratio of constraint sentences with correctly inferred temporal constraints to the total number of constraint sentences.
-
-Table~\ref{tab:results} shows the effectiveness of \tool\ in inferring temporal constraints from the identified constraint sentences.
+In this section, we evaluate the effectiveness of \tool\ in inferring temporal constraints from the identified constraint sentences from API documents.Table~\ref{tab:results} shows the effectiveness of \tool\ in inferring temporal constraints from the identified constraint sentences.
 Column ``API'' lists the names of the subject API. 
@@
 We next present an example to illustrate how \tool\ incorrectly infers temporal constraints from a constraint sentence.
-Consider the sentence ``if the stream does not support seek, or if this input stream has been closed by invoking its close method, or an I/O error occurs.'' from \CodeIn{skip} method of \CodeIn{java.io.FilterInputStream} class.
-Although \tool\ correctly infers that close cannot be called before current method, \tool\ incorrectly associates the phrase ``support seek'' with method \CodeIn{markSupported} in the class.
+Consider the sentence ``\textit{if the stream does not support seek, or if this input stream has been closed by invoking its close method, or an I/O error occurs.}'' from \CodeIn{skip} method of \CodeIn{java.io.FilterInputStream} class.
+Although \tool\ correctly infers that method \CodeIn{close} cannot be called before current method, \tool\ incorrectly associates the phrase ``support seek'' with method \CodeIn{markSupported} in the class.
 The faulty association happens due to incorrect parsing of the sentence by the underlying NLP infrastructure.
@@
 Hence, for such types of constraints, we do not require sophisticated techniques like ICON. 
-For \CodeIn{java.io}, we define a type-enforced constraint as a constraint that mandates a method M accepting input parameter I of type T to be invoked after (at least one) a method M0 whose return value is of type T.
-Since there are no types in REST APIs, for \CodeIn{Amazon S3}, we consider a constraint as a type-enforced constraint if the constraint is implicit in the \CodeIn{CRUD} naming convention followed by REST operations.
+For \CodeIn{java.io}, we define a type-enforced constraint as a constraint that mandates a method $M$ accepting input parameter $I$ of type $T$ to be invoked after (at least one) a method $M'$ whose return value is of type $T$.
+Since there are no types in REST APIs, for \CodeIn{Amazon S3}, we consider a constraint as a type-enforced constraint
+if the constraint is implicit in the \CodeIn{CRUD} semantic followed by REST operations. 
+\CodeIn{CRUD} stands for resource manipulation semantic sequence create, retrieve, update, and delete.
 In particular, we consider a constraint as a type-enforced constraint, if the constraint mandates a DELETE, GET, or PUT operation on a resource to be invoked after a GET operation on the same resource.
@@
 To minimize the threat, we used API documents of two different API's: JDK \CodeIn{java.io} and \amazon.
-On one hand Java is a widely used programming language and \CodeIn{java.io} and is one of the main packages.
+On one hand, Java is a widely used programming language and \CodeIn{java.io} and is one of the main packages.
 In contrast, \amazon\ provides HTTP based access to online storage allowing developers the freedom to write clients applications in any programming language.
 Furthermore, the difference in the functionalities provided by the two API's also address the issue of over fitting our approach to a particular type of API.
-The threat can be further reduced by evaluating our approach on more subjects.
+The threat can be further reduced by evaluating our approach on more subjects API's.
 
-Threats to internal validity include the correctness of our implementation in extracting usage constraints and labeling a statement as a constraint statement.
+Threats to internal validity include the correctness of our prototype implementation in extracting temporal constraints and labeling a statement as a constraint statement.
 To reduce the threat, we manually inspected all the constraints inferred against the API method descriptions in our evaluation.
-Furthermore, we ensured that the results were individually verified and agreed upon by two authors.
+Furthermore, we ensured that the results were individually verified and agreed upon by two authors, using the \CodeIn{cohen kappa}~\cite{carletta1996assessing} score to statistically measure the inter-rater agreement.

### 2014-03-16 Draft/abstract.tex
Revised abstract and part of intro

@@
 \begin{abstract}
-Temporal specifications  or constraints of an Application Programming
-Interface (API) describe allowed sequence of invocations
-of methods within an API. These constraints govern the secure and robust
-operation of client software using these APIs.
-Despite being desirable for 
-software testing and verification (through formal analysis tools),
-most API's do not have formal temporal constraints.
-In contrast, API documents contain valuable information (including temporal constraints) about the usage in natural language.
-However, manually writing formal constraints based on natural language text in API documents
-can be prohibitively time consuming and error prone.
-
-On the other hand, automatically inferring temporal constraints from API documents is challenging.
-In particular, it is challenging to automatically 
-identify the methods referenced in the natural language text to infer temporal constraints.
+Temporal constraints of an Application Programming
+Interface (API) are the allowed sequences of invocations
+of methods from the API.
+These constraints govern the secure and robust
+operation of client software using the API.
+Typically, these constraints are described in natural language text
+of API documents and thus cannot be used by existing verification tools
+which typically accept only formal constraints.
+Because manually writing temporal constraints based on
+API documents can be prohibitively time consuming and error prone,
+we propose \tool: a Natural Language Processing (NLP) based approach
+to automatically infer temporal constraints.
+In particular, our approach includes novel techniques to reduce the number of lexical tokens
+as a way to make API documents amenable to existing NLP techniques
+(that are currently designed to work on well written news articles).
+Our approach also includes a novel technique of identifying method references in
+the natural language text by building domain-dictionaries systematically
+from API documents and generic English dictionaries.
+To evaluate our approach, we apply \tool\ to infer temporal constraints from 
+commonly used package \CodeIn{java.io} in the JDK API and from the \amazonAPI.
+Our results show that \tool\ effectively identifies constraint sentences (from over 3900 API sentences) with the average precision, recall, and F-score of 65.0\%, 72.2\%, and 68.4\%, respectively.
+Furthermore, \tool\ also achieves an accuracy of 70\% in inferring 63 temporal constraints from these sentences.
 
@@
 % within each phases.
-
-To address the preceding challenge, we propose a natural-language-processing-based approach \tool,
-to infer formal temporal constraints from natural language text of API documents. These constraints can be used (as input)
-by various software testing and verification tools to detect defects in client code the APIs.
-Our approach 
-addresses the preceding challenge by building (and leveraging) domain-dictionaries systematically from API
-documents and generic English dictionaries.
-To evaluate our proposed approach, we applied \tool\ to infer temporal constraints from 
-commonly used package \CodeIn{java.io} from JDK API and \amazonAPI.
-Our evaluation results are promising.
-In particular, \tool\ achieves an average of 65\% precision and 72\% recall
-in inferring 63 temporal constraints from more than 3900 sentences of API documents.
 

### 2014-03-16 Draft/conclusion.tex
Revised abstract and part of intro

@@
 
-Although highly desirable, most API's do not have formal specifications.
-In contrast documentation of methods contain detailed specifications of the usage in natural language text.
-However, formal analysis tools are not designed to work on specifications in natural languages.
+Although highly desirable, most API's do not have formal temporal constraints.
+In contrast, documentation of methods contain detailed specifications of the usage in natural language text.
 Manually writing formal specifications based on natural language text in API documents is prohibitively time consuming and error prone.
@@
 We applied \tool\ to infer temporal constraints from 
-commonly used package \CodeIn{java.io} from JDK API and Amazon S3 REST API.
-Our evaluation results show that \tool\ achieves an average of 65\% precision and 72\% recall
-in inferring 63 temporal constraints from more than 3900 sentences of API documents.
+commonly used package \CodeIn{java.io} in the JDK API and from the Amazon S3 REST API.
+Our evaluation results show that \tool\ effectively identifies sentences describing
+temporal constraints with an average 65\% precision and 72\% recall,
+from more than 3900 sentences in subject API documents.
+Furthermore,\tool\ also achieved an  accuracy of
+70\% in inferring 63 formal temporal constraints from these sentences.

### 2014-03-16 Draft/evaluation.tex
Revised abstract and part of intro

@@
 \CodeIn{CRUD} stands for resource manipulation semantic sequence create, retrieve, update, and delete.
-In particular, we consider a constraint as a type-enforced constraint, if the constraint mandates a DELETE, GET, or PUT operation on a resource to be invoked after a GET operation on the same resource.
+In particular, we consider a constraint as a type-enforced constraint, if the constraint mandates a DELETE, GET, or PUT operation on a resource to be invoked after a POST operation on the same resource.
 

### 2014-03-16 Draft/example.tex
Revised abstract and part of intro

@@
 The inquisitor complains about an issue in the delete bucket functionality of the \CodeIn{S3Fox}.
-In particular, the issue was because the \CodeIn{S3Fox} developers overlooked the constraints in \amazon.
+The \CodeIn{S3Fox} developers overlooked the constraints in \amazon, causing the issue.
 The API document pertaining to the  delete bucket functionality states that before deleting the bucket, the objects in the buckets must be deleted.
 \textit{``All objects (including all objects versions and Delete Markers) in the bucket must be deleted before the bucket itself can be deleted''}.
-Although the issue was fixed but one of the responses on the forum encouraged the person asking query to switch to another product,
-thus potentially resulting in a loss of revenue attributed to customer dissatisfaction.
+The issue was fixed.
+However, one of the forum responses contained a recommendation for the inquisitor to switch to another product.
+Customer dissatisfaction, such as was caused by this issue with the delete bucket functionality, can lead to a lose in revenue.
 
@@
 the presence of a call to delete object functionality before the call to delete bucket functionality.
-However, existing formal analysis accept only formal specifications but not informal constraints described in natural language.
-Thus, there is need for an approach to automatically translate the constraints described in natural language into a more formal notation.
+%However, existing formal analysis accept only formal specifications but not informal constraints described in natural language.
+%Thus, there is need for an approach to automatically translate the constraints described in natural language into a more formal notation.
 In next section, we briefly discuss the related work pertinent to our proposed approach.

### 2014-03-16 Draft/introduction.tex
Revised abstract and part of intro

--- 2014-03-15 Draft/introduction.tex
@@
 
-% Introduction needs to tightned up a bit
-% Paragraph about typed languages must be moved to background or methodology
-% Example might appropriately go in background as well
-% Try to fit the goal statement in the introduction
-% too long an abstract
-% Names of exact tools and citations to them for verification
-% Over use of however,
-% J2EE document seems to be out of place
+Temporal constraints~\cite{ball2002s} of an Application Programming Interface (API) 
+are the allowed sequences of invocations of methods within the API. 
+These constraints govern the secure and robust operation of client software using the API.
+If these constraints are formal (machine-readable such as linear temporal logic),
+they can be used as inputs to the formal analysis tools such 
+as model checker and runtime verifiers
+in detecting the violations of these temporal constraints as defects~\cite{lee2012towards}.
 
-Temporal specifications or constraints~\cite{ball2002s} of an Application Programming Interface (API) 
-describe allowed sequences of invocations of methods within an API. 
-These constraints govern the secure and robust operation of client software 
-using these APIs.
-If these constraints are formal (machine-readable such as linear temporal logic),
-they can be used  as a basis of formal analysis tools such 
-as model checker and runtime verifiers
-in detecting the violations of these temporal constraints as defects.
-
-%Specifications of using an Application Programming Interface (API) of a library play an important role in software reuse.
-%In addition to guiding the development process by outlining what and how to reuse, 
-%usage specifications also help in verification process by allowing quality assurance practitioners to test the expected outcome.
-%Furthermore, if the specifications are formal (machine-readable such as code-contracts),
-%they can be used in conjunction with the formal analysis tools such as model checkers and runtime verifiers
-%to automatically  reason about the quality of software.
-
-%Formal specifications of an Application Programming Interface (API) usage are highly desirable.
-%because they are the precursor to the formal analysis tools such as model checkers and runtime verifiers.
-
-Despite being desirable, most API's do not have formal constraints.
-In contrast, API developers commonly describe correct temporal usage in natural language text in API documents.
-Typically, such documents are provided to client-code developers through online access, or are shipped with the API code.
-%For example, J2EE's API documentation\footnote{\url{http:\\download.oracle.com/javaee/1.7/api/}} is one of the popular API documents.
-For a method under consideration, an API document may describe both the constraints on that method parameters as well as the temporal constraints in terms of the methods must be invoked pre/post the method.
-We observed that a eminent portion (roughly 12\%) of the sentences (that describe some sort of constraints) in \amazonAPI\ documentations describe temporal constraints.
-Although API documents contain temporal constraints, existing formal analysis tools accept only formal constraints but not informal constraints written in natural language.
+Typically, these constraints are described in natural language text of API documents.
+Such documents are provided to client-code developers through an online access, or are shipped with the API code.
+For a method under consideration, an API document may describe both the constraints on that method parameters
+as well as the temporal constraints in terms of methods that must be invoked pre/post that method.
+We observed that an considerable portion (roughly 12\%) of the sentences (that describe some sort of constraints)
+in \amazonAPI\ documentations describe temporal constraints.
+However, existing verification tools which typically accept only formal constraints
+cannot use the natural language constraints from API documents.
 
@@
 However, manually writing formal constraints based on natural language text in API documents can be prohibitively time consuming and error prone~\cite{wu2013inferring,RubingerWEB10}. 
-For instance, Wu et al.~\cite{wu2013inferring} report that it took one of the authors more than 10 hours to browse the documentation of one method of a web service API, even before they attempted to formalize the constraints on the method.
-
+For instance, Wu et al.~\cite{wu2013inferring} report that it took one of the authors hours to browse the documentation of one method of a web service API, even before they attempted to formalize the constraints on the method.
+To reduce the manual effort, we propose \tool: a Natural Language Processing (NLP) based approach
+to automatically infer formal temporal constraints. 
 %Strike out ``To address the aforementioned issue''
 %We propose a novel approach to infer temporal usage constraints from natural language text of API documents.
-To reduce the manual effort, we propose an automated approach that applies Natural Language Processing (NLP) techniques on natural language text in API documents to infer formal temporal constraints. 
+
 %In particular, we focus on specific type of constraints namely temporal constraints.
-A generic temporal constraint is defined as \textit{an interpropositional constraint that communicates the ordering in time of events or states.}
-In terms of API method constraints, we interpret temporal constraints as \textit{`the allowed sequence of invocations of methods'}.
-For example, consider the following statement in \amazonAPI\ ``You must initiate a multipart upload before you can upload any part.''
-We can interpret this sentence stating that a multipart-upload method must be invoked before invoking any part-upload method in the API.
+%A generic temporal constraint is defined as \textit{an interpropositional constraint that communicates the ordering in time of events or states.}
+%In terms of API method constraints, we interpret temporal constraints as \textit{`the allowed sequence of invocations of methods'}.
+%For example, consider the following statement in \amazonAPI\ ``You must initiate a multipart upload before you can upload any part.''
+%We can interpret this sentence stating that a multipart-upload method must be invoked before invoking any part-upload method in the API.
 

### 2014-03-16 Draft/related.tex
Revised abstract and part of intro

@@
 In contrast, often the sentences in API documents are not well-formed.
-Additionally, these approaches do not deal with programming keywords or identifiers, which are often mixed within the method descriptions in API documents.
+Additionally, their approaches do not deal with programming keywords or identifiers, which are often mixed within the method descriptions in API documents.
 
-Most closely related work to the approach presented here is Pandita et al.~\cite{pandita12:inferring} work on inferring parameter constraints from method descriptions in the API documents.
+Most closely related work to the approach presented here is our previous work on inferring parameter constraints from method descriptions in the API documents~\cite{pandita12:inferring}.
 Our proposed approach differs from the previous approach as follows.
@@
 Our proposed approach is a significant extension to the infrastructure used in the previous work in following areas.
-First, the proposed approach introduces hybrid shallow parsing that relies both on POS tags as well as Stanford-typed dependencies to construct intermediate representation.
+First, the proposed approach introduces hybrid shallow parsing that relies both on parts-of-speech tags as well as Stanford-typed dependencies to construct intermediate representation.
 Second, the proposed approach introduces a new heuristics namely frequent phrase reduction to deal with the domain specific and ill-formed sentences in API documents.
@@
 (way of marking the specification sentences) in the default API documentation.
-These directives are highlighted whenever they are displayed in the eclipse environment.
+These directives are highlighted whenever they are displayed in the Eclipse environment.
 Lee et al.~\cite{lee2012towards} improved upon their work by providing a formalism to the directives proposed by Dekel et al.~\cite{Dekel2009},

### 2014-03-17 Draft/abstract.tex
Dr. Xie's coments

@@
 Typically, these constraints are described in natural language text
-of API documents and thus cannot be used by existing verification tools
+of API documents and thus cannot be used by existing verification tools,
 which typically accept only formal constraints.
@@
 to automatically infer temporal constraints.
-In particular, our approach includes novel techniques to reduce the number of lexical tokens
+In particular, our approach includes a novel technique to reduce the number of lexical tokens
 as a way to make API documents amenable to existing NLP techniques
-(that are currently designed to work on well written news articles).
+(which are typically designed to work on well-written news articles).
 Our approach also includes a novel technique of identifying method references in
-the natural language text by building domain-dictionaries systematically
+the natural language text by building domain dictionaries systematically
 from API documents and generic English dictionaries.

### 2014-03-17 Draft/approach.tex
Dr. Xie's coments

@@
 The preprocessor accepts the API documents and extracts method descriptions from it.
-In particular, the preprocessor extracts the following fields within method descriptions: 
+In particular, the preprocessor extracts the following fields from the method descriptions: 
 1) \textit{Summary of the API method},
@@
 
-The NLP parser accepts the pre-processed documents and annotates every sentence within each document using core NLP techniques described in Section~\ref{sub:CoreNLPback}.
+The NLP parser accepts the pre-processed documents and annotates every sentence in each document using core NLP techniques described in Section~\ref{sub:CoreNLPback}.
 From an implementation perspective, we chose the Stanford parser~\cite{Manning:01}.
@@
 attempts to locate the occurrence of class name or its synonym
-within the leaf nodes of the FOL
+in the leaf nodes of the FOL
 representation of the sentence (Line 3). The method
@@
 
-A key way of identifying reference to a method within the API in our proposed approach is the employment of a semantic graph of an API.
+A key way of identifying reference to a method in the API by our approach is the employment of a semantic graph of an API.
 In particular, we propose to initially infer such graphs from API documents.

### 2014-03-17 Draft/conclusion.tex
Dr. Xie's coments

@@
 
-Although highly desirable, most API's do not have formal temporal constraints.
-In contrast, documentation of methods contain detailed specifications of the usage in natural language text.
+Despite being highly desirable, most APIs are not equipped with formal temporal constraints.
+In contrast, documentation of API methods contains detailed specifications of temporal constraints in natural language text.
 Manually writing formal specifications based on natural language text in API documents is prohibitively time consuming and error prone.
-To address this issue, we proposed a novel approach \tool\ to infer temporal constraints from natural language text of API documents.
+To address this issue, we have proposed a novel approach called \tool\ to infer temporal constraints from natural language text of API documents.
 We applied \tool\ to infer temporal constraints from 
-commonly used package \CodeIn{java.io} in the JDK API and from the Amazon S3 REST API.
+commonly used package \CodeIn{java.io} in the JDK API and from the \amazonAPI.
 Our evaluation results show that \tool\ effectively identifies sentences describing
@@
 from more than 3900 sentences in subject API documents.
-Furthermore,\tool\ also achieved an  accuracy of
+Furthermore, \tool\ also achieved an accuracy of
 70\% in inferring 63 formal temporal constraints from these sentences.

### 2014-03-17 Draft/introduction.tex
Dr. Xie's coments

@@
 Temporal constraints~\cite{ball2002s} of an Application Programming Interface (API) 
-are the allowed sequences of invocations of methods within the API. 
+are the allowed sequences of invocations of methods from the API. 
 These constraints govern the secure and robust operation of client software using the API.
-If these constraints are formal (machine-readable such as linear temporal logic),
-they can be used as inputs to the formal analysis tools such 
+If these constraints are in a formal specification language,
+they can be used as inputs to formal analysis tools such 
 as model checker and runtime verifiers
@@
 
-Typically, these constraints are described in natural language text of API documents.
+Typically, temporal constraints are described in natural language text of API documents.
 Such documents are provided to client-code developers through an online access, or are shipped with the API code.
-For a method under consideration, an API document may describe both the constraints on that method parameters
-as well as the temporal constraints in terms of methods that must be invoked pre/post that method.
-We observed that an considerable portion (roughly 12\%) of the sentences (that describe some sort of constraints)
-in \amazonAPI\ documentations describe temporal constraints.
-However, existing verification tools which typically accept only formal constraints
+For a method under consideration, an API document may describe both the constraints on the method parameters
+as well as the temporal constraints in terms of other methods that must be invoked pre/post invoking that method.
+We observe that a non-trivial portion (roughly 12\%) of the sentences (constraint-describing sentences)
+in \amazonAPI\ documentation describe temporal constraints.
+However, existing verification tools, which typically accept only formal constraints,
 cannot use the natural language constraints from API documents.
 
-One way of addressing the issue, is to manually convert the natural language API description into formal constraints. 
-However, manually writing formal constraints based on natural language text in API documents can be prohibitively time consuming and error prone~\cite{wu2013inferring,RubingerWEB10}. 
-For instance, Wu et al.~\cite{wu2013inferring} report that it took one of the authors hours to browse the documentation of one method of a web service API, even before they attempted to formalize the constraints on the method.
+Although natural language API description can be manually converted into formal constraints,
+manually writing formal constraints based on natural language text in API documents can be prohibitively time consuming and error prone~\cite{wu2013inferring,RubingerWEB10}. 
+For instance, Wu et al.~\cite{wu2013inferring} report that it took one person ten hours to browse the documentation of one method from a web service API, even before the person attempted to formalize the constraints on the method.
+
 To reduce the manual effort, we propose \tool: a Natural Language Processing (NLP) based approach
 to automatically infer formal temporal constraints. 
-%Strike out ``To address the aforementioned issue''
-%We propose a novel approach to infer temporal usage constraints from natural language text of API documents.
+However, inferring temporal constraints from the natural language text is challenging. 
+In particular, our approach addresses two major challenges to automatically infer specifications
+from natural language text in API documents.
+
+First, existing NLP techniques are initially designed towards well-written news articles.
+In contrast, API documents are domain-specific documents and are often not well formed.
+Furthermore, we observe that generic NLP techniques face problems with lengthy sentences (with a number of lexical tokens).
+Consider the description sentence ``All objects (including all object versions and Delete Markers) in the bucket must be deleted before the bucket itself can be delete.'' The length of the sentence may overwhelm an NLP parser, which then inaccurately extracts semantic relations between the words in the sentence.
+Our ICON approach includes a new technique called ``hybrid parsing'' to deal with the number of lexical tokens.
+Hybrid parsing automatically breaks lengthy sentences to smaller tractable sentences based on a function of parts-of-speech tags.
+
+Second, after API documents are made amenable to existing NLP techniques, a method referenced in the natural language text must be identified in order to infer temporal constraints on the method but such method referencing is often implicit.
+Consider the description sentence ``You must initiate a multipart upload before you can upload any part.''
+In this sentence, phrases ``multipart upload'' and ``upload any part'' refer to individual methods in the API.
+Identifying these phrases as method-invocation instances requires domain dictionaries.
+Ad-hoc construction of such dictionaries is prohibitively time and resource intensive.
+To address this challenge, we propose to build domain dictionaries systematically from API documents and generic English dictionaries.
+
+In summary, our \tool\ approach leverages natural language description of API's to infer temporal constraints of method invocations.
+As our approach analyzes API documents in natural language, it can be reused independent of the programming language of an API library.
+Additionally, our approach complements existing mining-based approaches~\cite{buse2012synthesizing, thummalapenta07parseweb, Wang:2013:MSR, Zhong:2009:MMR} that partially address the problem by mining for common usage patterns among client code reusing the API.
+This paper makes the following main contributions:
+%However, all of these approaches rely on the availability of the source code that use API methods under investigation.
+Furthermore, these approaches are limited by both the quantity as well as quality of data set (source code) available.
+To address the limitation we propose to extend the natural language infrastructure developed previously~\cite{pandita12:inferring,pandita2013whyper} to focus specifically on the temporal constraints.
+
+\begin{itemize}
+	\item An NLP-based approach that effectively infers temporal constraints of method invocations. 
+	To the best of our knowledge, our approach is the first one to apply NLP for inferring temporal constraints from API documents.
+	\item A prototype implementation of our approach based on extending the Stanford Parser~\cite{Klein03}, which is a natural language parser to derive the grammatical structure of sentences.
+	An open source implementation of the prototype is publicly available on our project website\footnote{\url{https://sites.google.com/site/temporalspec}}, along with the experimental subjects and the results.
+	\item An evaluation of our approach on commonly used package \CodeIn{java.io} from the JDK API and from \amazonAPI. 
+\end{itemize}
+
+The rest of the paper is organized as follows.
+Section~\ref{sec:example} presents a real-world example that motivates our approach.
+Section~\ref{sec:related} discusses related work.
+Section~\ref{sec:background} presents the  background on NLP techniques used in our approach.
+Section~\ref{sec:approach} presents our approach.
+Section~\ref{sec:evaluation} presents the evaluation of our approach.
+Section~\ref{sec:discussion} presents brief discussion and future work.
+Finally, Section~\ref{sec:conclusion} concludes.
 
 %In particular, we focus on specific type of constraints namely temporal constraints.
-%A generic temporal constraint is defined as \textit{an interpropositional constraint that communicates the ordering in time of events or states.}
-%In terms of API method constraints, we interpret temporal constraints as \textit{`the allowed sequence of invocations of methods'}.
-%For example, consider the following statement in \amazonAPI\ ``You must initiate a multipart upload before you can upload any part.''
-%We can interpret this sentence stating that a multipart-upload method must be invoked before invoking any part-upload method in the API.
+A generic temporal constraint is defined as \textit{an interpropositional constraint that communicates the ordering in time of events or states.} In terms of API method constraints, we interpret temporal constraints as \textit{`the allowed sequence of invocations of methods'}.
+For example, consider the following statement in \amazonAPI\ ``You must initiate a multipart upload before you can upload any part.'' We can interpret this sentence stating that a multipart-upload method must be invoked before invoking any part-upload method in the API.
 
-%Move this paragraph to later sections or may be push later in intro
-% make example flow in next paragraph
-% Make consistent terminology approach or technique
-
-%Background on out of how many sentences
-
-% Combine first two sentences
-% In contrast, temporal constraints are beyond these parameter constraints. may be use difficult to express using parameter constraints
-% Amazon S3 is popularly used web service for simple cloud based storage
-Although, existing approaches focus on inferring method pre-post conditions (in terms of parameter constraints) using either program analysis techniques~\cite{Henkel07discoveringdocumentation,Ghezzi:2009:SIB:1555001.1555057,Henkel:2008:DDA:1363102.1363105,Flanagan2001:HAA,Buse:2008:ADI:1390630.1390664} or NLP~\cite{pandita12:inferring, wu2013inferring}, temporal constraints are beyond these parameter constraints.
+%Although, existing approaches focus on inferring method pre-post conditions (in terms of parameter constraints) using either program analysis techniques~\cite{Henkel07discoveringdocumentation,Ghezzi:2009:SIB:1555001.1555057,Henkel:2008:DDA:1363102.1363105,Flanagan2001:HAA,Buse:2008:ADI:1390630.1390664} or NLP~\cite{pandita12:inferring, wu2013inferring}, temporal constraints are beyond these parameter constraints.
 Temporal constraints, in general focus on rules related to orchestration of methods within an API rather than focusing on the requirements on the input parameters of these methods.
 
-Apart from method specifications, Zhong et al.~\cite{zhong09SE} leverage machine learning and type information to infer constraints on resources based on phases of resource usage: creating, manipulating, and releasing.
+%Apart from method specifications, Zhong et al.~\cite{zhong09SE} leverage machine learning and type information to infer constraints on resources based on phases of resource usage: creating, manipulating, and releasing.
 However, temporal constraints are not limited to resource usage.
@@
 %First, relying just on type information will result in an incomplete list of temporal constraints.
-%In typed languages some temporal constraints are enforced by type system. 
-%For instances a method ($m$) accepting input parameter ($i$) of type ($t$) mandates that (at least one) method ($m'$) be invoked whose return value is of type ($t$).
-%However, temporal constraints are not limited by the type definitions (i.e, requirements on the type of input parameters), and are currently expressed mostly in natural language in API documents, as described in the example previously.
-%We propose to address the issue by augmenting the type definitions based temporal constraints with the constraints inferred from
-%the natural language text in API documents.
-%Furthermore, such constraints although valuable but are already checked by any advanced Integrated Development Environment(IDE) such as eclipse
-%for a strongly typed language.
-%The problem is exacerbated in web based API's such as \amazonAPI\ where most of the types are either \CodeIn{integer} or \CodeIn{strings}.
-%Our proposed approach extends the existing approaches to address the challenge.
-
-%identified in previous work~\cite{pandita12:inferring} delete and leave the reference
-% Add a sentence stating that we extend previous technique to address the issues 
-However, inferring temporal constraints from the natural language text is challenging. 
-There are existing challenges in NLP for software engineering domain namely \textit{ambiguity}, \textit{programming keywords}, and \textit{semantic equivalence} identified in previous work~\cite{pandita12:inferring}.
-In addition to these challenges, we have an added challenge of 
-implicit method referencing: identifying the method referenced in the natural language text to infer temporal constraint.
-Recall the description sentence ``You must initiate a multipart upload before you can upload any part.''
-In this sentence, phrases ``multipart upload'' and ``upload any part'' refer to individual methods in the API.
-Identifying these phrases as method invocation instances requires domain dictionaries.
-Ad-hoc construction of such dictionaries is prohibitively time and resources intensive.
-To address this challenge, we propose to build domain-dictionaries systematically from API documents and generic English dictionaries.
-
-% talk about mining approaches 
-In summary, the proposed work leverages natural language description of API's to infer temporal constraints of method invocations.
-As the proposed work analyzes API documents in natural language, it can be reused independent of the programming language of the API library.
-Additionally, our approach complements existing mining based approaches~\cite{buse2012synthesizing, thummalapenta07parseweb, Wang:2013:MSR, Zhong:2009:MMR} that partially address the problem by mining for common usage patterns among client software that use the API.
-The proposed work in general, makes the following contributions:
-%However, all of these approaches rely on the availability of the source code that use API methods under investigation.
-%Furthermore, these approaches are limited by both the quantity as well as quality of data set (source code) available.
-%To address the limitation we propose to extend the natural language infrastructure developed previously~\cite{pandita12:inferring,pandita2013whyper} to focus specifically on the temporal constraints.
-
-%Use consistent term technique or approach
-%Methodology for generating domain dictionaries 
-\begin{itemize}
-	\item An NLP based approach that infers temporal constraints of method invocations. 
-	To the best of our knowledge, our approach is the first one to apply NLP for the goal of inferring temporal constraints from API documents.
-	\item A prototype implementation of our approach based on extending the Stanford Parser~\cite{Klein03}, which is a natural language parser to derive the grammatical structure of sentences.
-	An open source implementation of the prototype is publicly available on our project website\footnote{\url{https://sites.google.com/site/temporalspec}}. 
-	\item An evaluation of proposed approach on commonly used package \CodeIn{java.io} from JDK API and \amazonAPI. 
-\end{itemize}
-
-The rest of the paper is organized as follows.
-Section~\ref{sec:example} presents real world examples that motivate our approach.
-Section~\ref{sec:related} discusses related work in this area.
-Section~\ref{sec:background} presents the  background on NLP techniques used in this work.
-Section~\ref{sec:approach} presents our approach.
-Section~\ref{sec:evaluation} presents evaluation of our approach.
-Section~\ref{sec:discussion} presents a brief discussion and future work.
-Finally, Section~\ref{sec:conclusion} concludes.
-
-% how well does the NLP based technique augument the type based temporal constraints
+In typed languages some temporal constraints are enforced by type system.
+For instances a method ($m$) accepting input parameter ($i$) of type ($t$) mandates that (at least one) method ($m'$) be invoked whose return value is of type ($t$).
+However, temporal constraints are not limited by the type definitions (i.e, requirements on the type of input parameters), and are currently expressed mostly in natural language in API documents, as described in the example previously.
+We propose to address the issue by augmenting the type definitions based temporal constraints with the constraints inferred from the natural language text in API documents.
+Furthermore, such constraints although valuable but are already checked by any advanced Integrated Development Environment(IDE) such as eclipse for a strongly typed language.
+The problem is exacerbated in web based API's such as \amazonAPI\ where most of the types are either \CodeIn{integer} or \CodeIn{strings}.
+Our proposed approach extends the existing approaches to address the challenge.

### 2014-03-17 Draft/related.tex
Dr. Xie's coments

@@
 
-Our proposed approach touches a few research areas such as software verification, NLP in Software Engineering (SE), and document augmentation.
-We next discuss the relevant work pertinent to our proposed approach in these areas.
+%Our proposed approach touches a few research areas such as software verification, NLP in Software Engineering (SE), and document augmentation.
+%We next discuss the relevant work pertinent to our proposed approach in these areas.
 
@@
 
-Zhong et al.~\cite{zhong09SE} leverage machine learning and type information to infer constraints on resources based on phases of resource usage: creating, manipulating, and releasing.
-However, temporal constraints are not limited to resource usage thus 
-Furthermore, the specifications inferred by their approach infers implicit specifications across multiple method descriptions,
-whereas the temporal constraints inferred by our approach infers explicit ordering information described in individual method descriptions.
+Zhong et al.~\cite{zhong09SE} leverage machine learning and type information to infer constraints on resources.
+Specifically, their approach infers resource constraints following template: resource creation methods followed by resource manipulation methods followed by resource release methods.
+However, temporal constraints may not be limited to such as template. 
 Furthermore, the performance of their approach is dependent on the quality of the training sets used for ML.
 In contrast, approach presented in this report is independent of such training set and thus can be easily extended to target respective problems addressed by them.
+Furthermore, the specifications inferred by their approach may ignore the explicit ordering information described in individual method descriptions as inferred by our approach.
 
@@
 In contrast, often the sentences in API documents are not well-formed.
-Additionally, their approaches do not deal with programming keywords or identifiers, which are often mixed within the method descriptions in API documents.
+Additionally, their approaches do not deal with programming keywords or identifiers, which are often mixed with the method descriptions in API documents.
 
 Most closely related work to the approach presented here is our previous work on inferring parameter constraints from method descriptions in the API documents~\cite{pandita12:inferring}.
-Our proposed approach differs from the previous approach as follows.
-Our proposed approach addresses the problem of inferring temporal constraint, whereas the previous approach infers parameter constraints.
-Our proposed approach is a significant extension to the infrastructure used in the previous work in following areas.
-First, the proposed approach introduces hybrid shallow parsing that relies both on parts-of-speech tags as well as Stanford-typed dependencies to construct intermediate representation.
-Second, the proposed approach introduces a new heuristics namely frequent phrase reduction to deal with the domain specific and ill-formed sentences in API documents.
-Finally, the proposed approach leverages the concept of semantic graphs constructed from class and method names in API to automatically infer the implicit method references in a sentence.
+\tool\ approach differs from the previous approach as follows.
+\tool\ approach addresses the problem of inferring temporal constraint, whereas the previous approach infers parameter constraints.
+\tool\ approach is a significant extension to the infrastructure used in the previous work in following areas.
+First, \tool\ approach introduces hybrid shallow parsing that relies both on parts-of-speech tags as well as Stanford-typed dependencies to construct intermediate representation, while the previous approach relies only on parts-of-speech tags.
+Second, the \tool\ approach introduces a new heuristics namely frequent phrase reduction to deal with the domain specific and ill-formed sentences in API documents.
+Finally, the \tool\ approach leverages the concept of semantic graphs constructed from class and method names in API to automatically infer the implicit method references in a sentence.
+In contrast, previous approach relies on predefined lists.
 
@@
 However, a developer has to manually annotate such directives.
-In contrast, our proposed approach both identifies the sentences pertaining to temporal constraints and infers the temporal constraints automatically.
+In contrast, our approach both identifies the sentences pertaining to temporal constraints and infers the temporal constraints automatically.
 

### 2014-03-17 Draft/related.tex
related wrk

@@
 Tan et al.~\cite{TanSOSP07} were the first to apply Machine Learning (ML) and NLP on code comments to detect mismatches between the comments and the implementation.
-They rely on predefined rule templates targeted towards threading and lock related comments, thus limiting their scope both in terms of application area as well as language used in the comments.
-Furthermore, the constraints inferred by their approach are the restrictions imposed by the developer on the client code.
+They rely on predefined rule templates targeted towards threading and lock related comments, and then apply machine learning to find comments following such rules.
+The constraints inferred by their approach are the restrictions imposed by the developer on the client code.
 In comparison, the temporal constraints inferred by our approach are the restriction imposed by the API library being used by the client code.

### 2014-10-28 Draft/abstract.tex
Updated Abstract and Intro for WWW

--- 2014-03-16 Draft/abstract.tex
@@
 \begin{abstract}
-Temporal constraints of an Application Programming
-Interface (API) are the allowed sequences of invocations
-of methods from the API.
-These constraints govern the secure and robust
+
+\textbf{Objective}: We propose \tool, an automated approach to infer
+temporal constraints from API documents.
+
+\textbf{Background}: Temporal constraints of an Application Programming
+Interface (API) are the allowed sequences of invocations of
+methods from the API. These constraints govern the secure and robust
 operation of client software using the API.
-Typically, these constraints are described in natural language text
-of API documents and thus cannot be used by existing verification tools
-which typically accept only formal constraints.
-Because manually writing temporal constraints based on
-API documents can be prohibitively time consuming and error prone,
-we propose \tool: a Natural Language Processing (NLP) based approach
-to automatically infer temporal constraints.
-In particular, our approach includes novel techniques to reduce the number of lexical tokens
-as a way to make API documents amenable to existing NLP techniques
-(that are currently designed to work on well written news articles).
-Our approach also includes a novel technique of identifying method references in
-the natural language text by building domain-dictionaries systematically
-from API documents and generic English dictionaries.
-To evaluate our approach, we apply \tool\ to infer temporal constraints from 
-commonly used package \CodeIn{java.io} in the JDK API and from the \amazonAPI.
-Our results show that \tool\ effectively identifies constraint sentences (from over 3900 API sentences) with the average precision, recall, and F-score of 65.0\%, 72.2\%, and 68.4\%, respectively.
-Furthermore, \tool\ also achieves an accuracy of 70\% in inferring 63 temporal constraints from these sentences.
+
+\textbf{Method}: \tool, is a Natural Language Processing (NLP) based
+approach thus complementing existing program-analysis-based approaches.
+In particular, \tool\ includes techniques to reduce the
+number of lexical tokens as a way to make API documents amenable
+to existing NLP techniques (which are typically designed to work
+on well-written news articles). Our approach also includes a novel
+technique of identifying method references (improvement over keyword-based
+techniques) in the natural language text by building domain
+dictionaries systematically from API documents and generic English
+dictionaries.
+
+\textbf{Results}: To evaluate our approach, we apply \tool to infer temporal
+constraints from commonly used package \CodeIn{java.io} in the
+JDK API and from the \amazonAPI. Our results show
+that \tool\ effectively identifies constraint sentences (from over
+3900 API sentences) with the average precision, recall, and F-score
+of 65.0\%, 72.2\%, and 68.4\%, respectively. Furthermore, \tool\
+also achieves an accuracy of 70\% in inferring 63 temporal constraints
+from these sentences.
+
+\textbf{Conclusion}: NLP based techniques offers a viable means to infer
+temporal constraints of an API.
+
+\textbf{Application}: Existing software engineering tools can leverage
+the inferred temporal constraints to effectively assist assist in development
+and verification activities.
+
+%Temporal constraints of an Application Programming
+%Interface (API) are the allowed sequences of invocations
+%of methods from the API.
+%These constraints govern the secure and robust
+%operation of client software using the API.
+%Typically, these constraints are described in natural language text
+%of API documents and thus cannot be used by existing verification tools,
+%which typically accept only formal constraints.
+%Because manually writing temporal constraints based on
+%API documents can be prohibitively time consuming and error prone,
+%we propose \tool: a Natural Language Processing (NLP) based approach
+%to automatically infer temporal constraints.
+%In particular, our approach includes a novel technique to reduce the number of lexical tokens
+%as a way to make API documents amenable to existing NLP techniques
+%(which are typically designed to work on well-written news articles).
+%Our approach also includes a novel technique of identifying method references in
+%the natural language text by building domain dictionaries systematically
+%from API documents and generic English dictionaries.
+%To evaluate our approach, we apply \tool\ to infer temporal constraints from 
+%commonly used package \CodeIn{java.io} in the JDK API and from the \amazonAPI.
+%Our results show that \tool\ effectively identifies constraint sentences (from over 3900 API sentences) with the average precision, recall, and F-score of 65.0\%, 72.2\%, and 68.4\%, respectively.
+%Furthermore, \tool\ also achieves an accuracy of 70\% in inferring 63 temporal constraints from these sentences.
 

### 2014-10-28 Draft/introduction.tex
Updated Abstract and Intro for WWW

@@
 
-Temporal constraints~\cite{ball2002s} of an Application Programming Interface (API) 
-are the allowed sequences of invocations of methods from the API. 
-These constraints govern the secure and robust operation of client software using the API.
-If these constraints are in a formal specification language,
-they can be used as inputs to formal analysis tools such 
-as model checker and runtime verifiers
-in detecting the violations of these temporal constraints as defects~\cite{lee2012towards}.
+The increasing reach of internet has fueled the growth of web
+Application Programming Interfaces (API). The ProgrammableWeb
+reports that the web APIs have doubled from Jan 2012 to Oct 2013\footnote{\url{http://www.programmableweb.com/api-research}}.
+These APIs are being combined in interesting ways by
+application developers creating third-party applications using
+these APIs to provide
+value added service. For instance, Netflix API leverages Facebook
+web API to assist users with finding movies that their friends are
+interested in.
+
+Web APIs, like traditional APIs have rules or constraints governing
+the use of the API that must be followed. One such type of
+constraints are temporal constraints [2], which are the allowed sequences
+of invocations of methods from the API. Non-compliance
+to such constraints can result in faulty applications that are unreliable
+to use and may even result in financial losses. Thus, formal
+analysis tools such as model checker and runtime verifiers are of
+high value in detecting the violations of the temporal constraints as
+defects~\cite{lee2012towards}.
 
 Typically, temporal constraints are described in natural language text of API documents.
-Such documents are provided to client-code developers through an online access, or are shipped with the API code.
+Such documents are provided to client-code developers through an online access, or are shipped with the API wrapper code.
 For a method under consideration, an API document may describe both the constraints on the method parameters

### 2014-10-28 Draft/abstract.tex
Space after ICON in abstract Removed duplicate assist

@@
 
-\textbf{Results}: To evaluate our approach, we apply \tool to infer temporal
+\textbf{Results}: To evaluate our approach, we apply \tool\ to infer temporal
 constraints from commonly used package \CodeIn{java.io} in the
@@
 \textbf{Application}: Existing software engineering tools can leverage
-the inferred temporal constraints to effectively assist assist in development
+the inferred temporal constraints to effectively assist in development
 and verification activities.

### 2014-10-28 Draft/introduction.tex
ignored generated files
Added context of type enforcement and search space explosion

@@
 %First, relying just on type information will result in an incomplete list of temporal constraints. 
-In typed languages some temporal constraints are enforced by type system.
-For instances a method ($m$) accepting input parameter ($i$) of type ($t$) mandates that (at least one) method ($m'$) be invoked whose return value is of type ($t$).
-However, temporal constraints are not limited by the type definitions (i.e, requirements on the type of input parameters), and are currently expressed mostly in natural language in API documents, as described in the example previously.
-We propose to address the issue by augmenting the type definitions based temporal constraints with the constraints inferred from the natural language text in API documents.
-Furthermore, such constraints although valuable but are already checked by any advanced Integrated Development Environment(IDE) such as eclipse for a strongly typed language.
-The problem is exacerbated in web based API's such as \amazonAPI\ where most of the types are either \CodeIn{integer} or \CodeIn{strings}.
+In traditional API, which are usually implemented in typed languages some temporal constraints are enforced by type system itself.
+Voilations are easily detected by the IDE's
+For instances a method ($m$) accepting input parameter ($i$) of type ($t$) mandates
+that (at least one) method ($m'$) be invoked whose return value is of type ($t$).
+However, using type system to detect temporal constraints in context of web APIs will result
+in a lot of false positives as web APIs work only on basic types such as
+\CodeIn{strings} and \CodeIn{numbers}.
+Use of basic datatype by web-apis result in search space explosion.
+Furthermore, we observed that temporal constraints re not limited to the type definitions
+
 Our proposed approach extends the existing approaches to address the challenge.
+
+However, temporal constraints are not limited by the type definitions
+(i.e, requirements on the type of input parameters),
+and are currently expressed mostly in natural language in API documents,
+as described in the example previously.
+We propose to address the issue by augmenting the type definitions based temporal constraints
+with the constraints inferred from the natural language text in API documents.
+Furthermore, such constraints although valuable but are already checked by any advanced 
+Integrated Development Environment(IDE) such as eclipse for a strongly typed language.

### 2014-10-28 Draft/evaluation.tex
included formal def

@@
 
-\subsection{Experimental Setup.} 
+\subsection{Evaluation Setup} 
 We first manually annotated the sentences in the API documents of the two APIs.
@@
 
-%We next describe our evaluation results.
+We next present our evaluation results.
 
@@
 \tool\ incorrectly identifies the action ``flush'' being performed before the action ``close''.
-However \tool\ fails to make the distinction that it happens internally (enforced within the body) in the method.
+However \tool\ fails to make the distinction that it happens internally (enforced in the body) in the method.
 \tool, thus incorrectly identifies the sentence as a constraint sentence.
@@
 our precision is further increased to 70.8\% effectively increasing the F-Score of \tool\ to 71.2\%.
-Although an easy fix, we refrained from including such modifications for reporting the results to stay true to our proposed framework.
+Although an easy fix, we refrained from including such modifications for reporting the results to stay true to our approach.
 In the future, we plan to investigate techniques to construct better domain dictionaries for software API.
@@
 \label{sub:threats_to_validity}
-Threats to external validity primarily include the degree to which the subject documents used in our evaluations are representative of true practice.
+Threats to external validity primarily include the degree to which the subject documents used in our evaluation are representative of true practice.
 To minimize the threat, we used API documents of two different API's: JDK \CodeIn{java.io} and \amazon.

### 2014-10-28 Draft/formal.tex
included formal def

\section{Temporal Specifications}
\label{sec:temporal}

In this section we describe various classes of temporal constraints using formal temporal logic.
In computer science, temporal Logic is a system of rules and symbols that are used to express and reason about prepositions pertaining to time.
We next present an extension to the temporal logic for API method invocation related rules proposed by Lo et al~\cite{lo2009mining}

\textbf{Method Invocation}: 
We adapt the definition of events proposed by Lo et al.~\cite{lo2009mining} as Method Invocation,
who define event as \textit{``any concrete or abstract representation of a program state''}. 
In particular, we propose the notion of method invocation analogous to the events as methods invocation,
where each method invocation is represented as a tuple which is an ordered set of strings. 
A method invocation is captured as the Tuple <$T$><\CodeIn{str1, str2, str3}...>, where \CodeIn{str1, str2, str3}... are string values,
that belong to set of all strings.
In particular, the method invocation tuple <$T$> captures information about the return value, enclosing type, name, and the parameter types of the method.
Thus Tuple[String, Bar, foo, Integer, Integer] represents a method \CodeIn{foo} enclosed by the type \CodeIn{Bar},
that accepts two parameters of type \CodeIn{Integer} and a return value of type \CodeIn{String}. 
For better readability mnemonic representation of the preceding tuple is \CodeIn{String<-Bar.foo(Integer, Integer);}

\textbf{Method Invocation Predicates}: We define method predicate as a predicate E over method invocations.
We reuse the notations proposed by Lo et al.~\cite{lo2009mining} $m \vdash \xi$ to denote that method invocation $m$ satisfies method Predicate $\xi$.
In context of \tool, method predicates combines a method name and the enclosing type with potential constraints on the return types and parameter types. 
In particular, the predicates are modeled after \textit{equality constraints predicates}, and are represented as \CodeIn{\$i=sym}, where \CodeIn{i} is a non-negative integer and \CodeIn{sym} is the primitive string value and defined as: a method invocation $m$ satisfies a predicates \CodeIn{\$i=sym} iff \CodeIn{m[i]=sym}. The simplest form of these predicates is of type \CodeIn{\$2 = sym} which refer to method invocations of name \CodeIn{sym}.

\textbf{Temporal Operators}: Temporal formulae (temporal constraints) are constructed by combining method invocation predicates using temporal operators. Lo et al.~\cite{lo2009mining}, proposed the following temporal operators

\begin{enumerate}

\item \textit{Forward Eventual Operator $\xi_1 \xrightarrow{*} \xi_2$}
occurrence of $\xi_1$ must be eventually followed by occurrence of $\xi_2$

\item \textit{Backward Eventual Operator $\xi_1 \xleftarrow{*} \xi_2$}
occurrence of $\xi_1$ must be preceded by occurrence of $\xi_2$

\item \textit{Forward Alternation Operator $\xi_1 \xrightarrow{a} \xi_2$}
occurrence of $\xi_1$ must be eventually followed by occurrence of $\xi_2$ and $\xi_1$ cannot occur in between

\item \textit{Backward Alternation Operator $\xi_1 \xleftarrow{a} \xi_2$}
occurrence of $\xi_1$ must be preceded by occurrence of $\xi_2$ and $\xi_1$ cannot occur in between
\end{enumerate}

In addition to these operators we propose two additional operators:
\begin{enumerate}
\item Forward Prohibition Operator $\xi_1 \nrightarrow \xi_2$
occurrence of $\xi_1$ cannot be followed by occurrence of $\xi_2$

\item Backward Prohibition Operator $\xi_1 \nleftarrow \xi_2$
occurrence of $\xi_1$ cannot be preceded by the occurrence of $\xi_2$
\end{enumerate}

The prohibition operators capture a different class of temporal constraints that cannot be expressed by the formulae constructed by previously proposed operators and their negations. For instance, the \textit{prohibition operators} on first glance seem to be negation of \textit{forward eventual operators} and \textit{backward eventual operators}. However, the negation of forward eventual operators is: not an invocation of e1 must be eventually followed by not an invocation of m2. In contrast, \textit{prohibition operators} either negates antecedent or consequent but not both.

\textbf{Quantification}: Quantification is used to introduce constraints involving parameter and return types of a method invocation. For instance, consider the constraint any method in an enclosing type \CodeIn{Obj} must not be invoked after method \CodeIn{foo} in the \CodeIn{Obj}.

$\forall$ \CodeIn{m <m in Obj> !=<foo in Obj>}

In summary, we extended the formalism for temporal rules previously proposed by Lo et al~\cite{lo2009mining} to express temporal constraints.
We obtain different classes of temporal constraints by varying: 1) the temporal operators allowed, b) the method-invocation predicates allowed, and 3) the degree of quantification allowed.

### 2014-10-29 Draft/abstract.tex
ignored generated files
Updated Introduction for flow Updated abstract with goal statement. Minor changes elsewhere.

@@
 
-\textbf{Objective}: We propose \tool, an automated approach to infer
-temporal constraints from API documents.
+%\textbf{Objective}: We propose \tool, an automated approach to infer
+%temporal constraints from API documents.
 
-\textbf{Background}: Temporal constraints of an Application Programming
-Interface (API) are the allowed sequences of invocations of
+\textbf{Objective}: The goal of this work is to assist developers construct
+web Application Programming Interface (API) clients that comply with 
+temporal constraints of the API thorough the inference and formalization of these constraints found in natural language text in API documents.
+
+\textbf{Background}: Temporal constraints of an API
+are the allowed sequences of invocations of
 methods from the API. These constraints govern the secure and robust
@@
 \textbf{Results}: To evaluate our approach, we apply \tool\ to infer temporal
-constraints from commonly used package \CodeIn{java.io} in the
-JDK API and from the \amazonAPI. Our results show
-that \tool\ effectively identifies constraint sentences (from over
+constraints from \amazonAPI, \paypalAPI and commonly used package \CodeIn{java.io} in the
+JDK API.
+Our results show that \tool\ effectively identifies constraint sentences (from over
 3900 API sentences) with the average precision, recall, and F-score

### 2014-10-29 Draft/formal.tex
Updated Introduction for flow Updated abstract with goal statement. Minor changes elsewhere.

@@
 In computer science, temporal Logic is a system of rules and symbols that are used to express and reason about prepositions pertaining to time.
-We next present an extension to the temporal logic for API method invocation related rules proposed by Lo et al~\cite{lo2009mining}
+We next present an extension to the temporal logic for API method invocation related rules proposed by Lo et al.~\cite{lo2009mining}
 
 \textbf{Method Invocation}: 
-We adapt the definition of events proposed by Lo et al.~\cite{lo2009mining} as Method Invocation,
-who define event as \textit{``any concrete or abstract representation of a program state''}. 
-In particular, we propose the notion of method invocation analogous to the events as methods invocation,
+We adapt the definition of events proposed by Lo et al.~\cite{lo2009mining} as method invocation.
+They define event as \textit{``any concrete or abstract representation of a program state''}. 
+We propose the notion of method invocation analogous to the events,
 where each method invocation is represented as a tuple which is an ordered set of strings. 
@@
 that belong to set of all strings.
-In particular, the method invocation tuple <$T$> captures information about the return value, enclosing type, name, and the parameter types of the method.
-Thus Tuple[String, Bar, foo, Integer, Integer] represents a method \CodeIn{foo} enclosed by the type \CodeIn{Bar},
+The method invocation tuple <$T$> captures information about the return value, enclosing type, name, and the parameter types of the method.
+Therefore a tuple <$T$><\CodeIn{String, Bar, foo, Integer, Integer}> represents a method \CodeIn{foo} enclosed by the type \CodeIn{Bar},
 that accepts two parameters of type \CodeIn{Integer} and a return value of type \CodeIn{String}. 
@@
 
-\textbf{Method Invocation Predicates}: We define method predicate as a predicate E over method invocations.
-We reuse the notations proposed by Lo et al.~\cite{lo2009mining} $m \vdash \xi$ to denote that method invocation $m$ satisfies method Predicate $\xi$.
+\textbf{Method Invocation Predicates}: We define method predicate as a predicate $E$ over method invocations.
+We reuse the notations proposed by Lo et al.~\cite{lo2009mining} $m \vdash \xi$ to denote that method invocation $m$ satisfies method predicate $\xi$.
 In context of \tool, method predicates combines a method name and the enclosing type with potential constraints on the return types and parameter types. 
-In particular, the predicates are modeled after \textit{equality constraints predicates}, and are represented as \CodeIn{\$i=sym}, where \CodeIn{i} is a non-negative integer and \CodeIn{sym} is the primitive string value and defined as: a method invocation $m$ satisfies a predicates \CodeIn{\$i=sym} iff \CodeIn{m[i]=sym}.
+The predicates are modeled after \textit{equality constraints predicates}, and are represented as \CodeIn{\$i=sym}, where \CodeIn{i} is a non-negative integer and \CodeIn{sym} is the primitive string value and defined as: a method invocation $m$ satisfies a predicates \CodeIn{\$i=sym} iff \CodeIn{m[i]=sym}.
 The simplest form of these predicates is of type \CodeIn{\$2 = sym} which refer to method invocations of name \CodeIn{sym}.
@@
 
-\item \textit{Forward Eventual Operator $\xi_1 \xrightarrow{*} \xi_2$}
+\item \textit{Forward Eventual Operator ($\xi_1 \xrightarrow{*} \xi_2$)}:
 occurrence of $\xi_1$ must be eventually followed by occurrence of $\xi_2$
 
-\item \textit{Backward Eventual Operator $\xi_1 \xleftarrow{*} \xi_2$}
+\item \textit{Backward Eventual Operator: ($\xi_1 \xleftarrow{*} \xi_2$)}:
 occurrence of $\xi_1$ must be preceded by occurrence of $\xi_2$
 
-\item \textit{Forward Alternation Operator $\xi_1 \xrightarrow{a} \xi_2$}
+\item \textit{Forward Alternation Operator ($\xi_1 \xrightarrow{a} \xi_2$)}:
 occurrence of $\xi_1$ must be eventually followed by occurrence of $\xi_2$ and $\xi_1$ cannot occur in between
 
-\item \textit{Backward Alternation Operator $\xi_1 \xleftarrow{a} \xi_2$}
+\item \textit{Backward Alternation Operator ($\xi_1 \xleftarrow{a} \xi_2$)}:
 occurrence of $\xi_1$ must be preceded by occurrence of $\xi_2$ and $\xi_1$ cannot occur in between
@@
 
-In addition to these operators we propose two additional operators:
+We extend these operators by proposing two additional operators:
 \begin{enumerate}
-\item Forward Prohibition Operator $\xi_1 \nrightarrow \xi_2$
+\item Forward Prohibition Operator ($\xi_1 \nrightarrow \xi_2$):
 occurrence of $\xi_1$ cannot be followed by occurrence of $\xi_2$
 
-\item Backward Prohibition Operator $\xi_1 \nleftarrow \xi_2$
+\item Backward Prohibition Operator ($\xi_1 \nleftarrow \xi_2$):
 occurrence of $\xi_1$ cannot be preceded by the occurrence of $\xi_2$
@@
 
-In summary, we extended the formalism for temporal rules previously proposed by Lo et al~\cite{lo2009mining} to express temporal constraints.
+In summary, we extended the formalism for temporal rules previously proposed by Lo et al.~\cite{lo2009mining} to express temporal constraints.
 We obtain different classes of temporal constraints by varying: 1) the temporal operators allowed, b) the method-invocation predicates allowed, and 3) the degree of quantification allowed.

### 2014-10-29 Draft/introduction.tex
Updated Introduction for flow Updated abstract with goal statement. Minor changes elsewhere.

@@
 
-The increasing reach of internet has fueled the growth of web
-Application Programming Interfaces (API). The ProgrammableWeb
-reports that the web APIs have doubled from Jan 2012 to Oct 2013\footnote{\url{http://www.programmableweb.com/api-research}}.
-These APIs are being combined in interesting ways by
-application developers creating third-party applications using
-these APIs to provide
-value added service. For instance, Netflix API leverages Facebook
-web API to assist users with finding movies that their friends are
-interested in.
+The increasing reach of internet has fueled the growth of web Application Programming Interfaces (API).
+The ProgrammableWeb reports that the web APIs have doubled from Jan 2012 to Oct 2013\footnote{\url{http://www.programmableweb.com/api-research}}.
+These APIs are being combined in interesting ways by application developers creating third-party applications using
+these APIs to provide value added service.
+For instance, many online stores leverage Paypal API to assist users with paying for the purchased commodities without actually
+providing financial information to the online store.
 
-Web APIs, like traditional APIs have rules or constraints governing
-the use of the API that must be followed. One such type of
-constraints are temporal constraints [2], which are the allowed sequences
-of invocations of methods from the API. Non-compliance
-to such constraints can result in faulty applications that are unreliable
-to use and may even result in financial losses. Thus, formal
-analysis tools such as model checker and runtime verifiers are of
-high value in detecting the violations of the temporal constraints as
-defects~\cite{lee2012towards}.
+Unlike most traditional API libraries that are in the format of locally stored binary files and are programming language specific,
+web API are designed to leverage the web server and web browser architecture and the implementation is programming language agnostic.
+However, Web APIs like traditional APIs have rules or constraints governing the proper  use of the API that must be followed.
+One such type of constraints are temporal constraints [2], which are the allowed sequences of invocations of methods from the API.
+Non-compliance to such constraints can result in faulty applications that are unreliable to use and may even result in financial losses.
 
-Typically, temporal constraints are described in natural language text of API documents.
+In traditional API, which are usually implemented in typed languages some temporal constraints are enforced by type system itself.
+For instances a method ($m$) accepting input parameter ($i$) of type ($t$) mandates
+that (at least one) method ($m'$) be invoked whose return value is of type ($t$).
+Thus compliance of such constraints are easily enforced by compilers.
+In contrast to traditional API libraries, web APIs work on basic parameter data types such as \CodeIn{strings} and \CodeIn{numbers}.
+Therefore enforcing temporal constraints through type system is ineffective in web APIs.
+Additionally temporal constraints are not entirely restricted to type definitions.
+
+Formal analysis tools such as model checker and runtime verifiers can assist in detection of the violations of the temporal constraints in web API clients as defects~\cite{lee2012towards}.
+However, such tools typically accept formal representation of the temporal constraints for detecting violations.
+In contrast, temporal constraints are typically described in natural language text of API documents.
 Such documents are provided to client-code developers through an online access, or are shipped with the API wrapper code.
@@
 in \amazonAPI\ documentation describe temporal constraints.
-However, existing verification tools, which typically accept only formal constraints,
-cannot use the natural language constraints from API documents.
 
@@
 Identifying these phrases as method-invocation instances requires domain dictionaries.
-Ad-hoc construction of such dictionaries is prohibitively time and resource intensive.
+Ad-hoc construction of such dictionaries is prohibitively resource intensive and error-prone.
 To address this challenge, we propose to build domain dictionaries systematically from API documents and generic English dictionaries.
@@
 	An open source implementation of the prototype is publicly available on our project website\footnote{\url{https://sites.google.com/site/temporalspec}}, along with the experimental subjects and the results.
-	\item An evaluation of our approach on commonly used package \CodeIn{java.io} from the JDK API and from \amazonAPI. 
+	\item An evaluation of our approach on \amazonAPI, \paypalAPI, and commonly used package \CodeIn{java.io} from the JDK API. 
 \end{itemize}
@@
 %First, relying just on type information will result in an incomplete list of temporal constraints. 
-In traditional API, which are usually implemented in typed languages some temporal constraints are enforced by type system itself.
-Voilations are easily detected by the IDE's
-For instances a method ($m$) accepting input parameter ($i$) of type ($t$) mandates
-that (at least one) method ($m'$) be invoked whose return value is of type ($t$).
-However, using type system to detect temporal constraints in context of web APIs will result
-in a lot of false positives as web APIs work only on basic types such as
-\CodeIn{strings} and \CodeIn{numbers}.
-Use of basic datatype by web-apis result in search space explosion.
-Furthermore, we observed that temporal constraints re not limited to the type definitions
-
-Our proposed approach extends the existing approaches to address the challenge.
-
-However, temporal constraints are not limited by the type definitions
-(i.e, requirements on the type of input parameters),
-and are currently expressed mostly in natural language in API documents,
-as described in the example previously.
-We propose to address the issue by augmenting the type definitions based temporal constraints
-with the constraints inferred from the natural language text in API documents.
-Furthermore, such constraints although valuable but are already checked by any advanced 
-Integrated Development Environment(IDE) such as eclipse for a strongly typed language.
+%In traditional API, which are usually implemented in typed languages some temporal constraints are enforced by type system itself.
+%Voilations are easily detected by the IDE's
+%For instances a method ($m$) accepting input parameter ($i$) of type ($t$) mandates
+%that (at least one) method ($m'$) be invoked whose return value is of type ($t$).
+%However, using type system to detect temporal constraints in context of web APIs will result
+%in a lot of false positives as web APIs work only on basic types such as
+%\CodeIn{strings} and \CodeIn{numbers}.
+%Use of basic datatype by web-apis result in search space explosion.
+%Furthermore, we observed that temporal constraints re not limited to the type definitions
+% 
+%Our proposed approach extends the existing approaches to address the challenge.
+%
+%However, temporal constraints are not limited by the type definitions
+%(i.e, requirements on the type of input parameters),
+%and are currently expressed mostly in natural language in API documents,
+%as described in the example previously.
+%We propose to address the issue by augmenting the type definitions based temporal constraints
+%with the constraints inferred from the natural language text in API documents.
+%Furthermore, such constraints although valuable but are already checked by any advanced 
+%Integrated Development Environment(IDE) such as eclipse for a strongly typed language.

### 2014-10-29 Draft/related.tex
Updated Introduction for flow Updated abstract with goal statement. Minor changes elsewhere.

@@
 Xiao et al.~\cite{XiaoFSE2012} and Slankas et al.~\cite{johnSlankasPASSAT13} use shallow parsing techniques to infer Access Control Policy (ACP) rules from natural language text in use cases.
-The use of shallow parsing techniques works satisfactorily on natural language texts in use cases, owing to well-formed structure of sentences in use case descriptions.
+The use of shallow parsing techniques works satisfactorily on natural language texts in use cases, owing to relative well-formed structure of sentences in use case descriptions.
 In contrast, often the sentences in API documents are not well-formed.

### 2014-10-29 Draft/related.tex
compressive -> comprehensive added Software Engineering(SE)

@@
 Since  our approach infers temporal constraint from API documents, we believe our approach can work in conjunction with existing approaches
-to infer a compressive set of specifications.
+to infer a comprehensive set of specifications.
 

### 2014-12-03 Draft/abstract.tex
Updated Draft for DSN
Updated Draft for DSN

--- 2014-10-28 Draft/abstract.tex
@@
 
-\textbf{Objective}: We propose \tool, an automated approach to infer
-temporal constraints from API documents.
+Temporal constraints of an Application Programming Interface (API)
+are the allowed sequences of method invocations in the API.
+These constraints govern the secure and robust operation of client software using the API.
+However, in practice, most API do not have formal temporal constraints.
+In contrast, these constraints are typically described
+informally in natural language API documents and therefore are not amenable
+to existing program analysis tools that require formal constraints.
+\textit{The goal of this work is to assist developers construct API clients that comply with 
+temporal constraints of the API through the inference and formalization of these constraints found in natural language text in API documents.}
+Since, API documents are often verbose manually writing formal temporal constraints can be prohibitively time consuming and error prone.
+To address this issue,
+we propose \tool, a Machine Learning (ML) and Natural Language Processing (NLP) based
+approach to identify and infer formal temporal constraints.
+To evaluate our approach, we apply \tool\ to infer and formalize temporal
+constraints from \amazonAPI, \paypalAPI\ and commonly used package \CodeIn{java.io} in the
+JDK API.
+Our results indicate that \tool\ is effective in identifying constraint sentences (from over
+4000 human-annotated API sentences) with the average precision, recall, and F-score
+of 65.0\%, 72.2\%, and 68.4\%, respectively.
+Furthermore, \tool\ also achieves an accuracy of 70\% in inferring 63 formal temporal constraints from these sentences.
 
-\textbf{Background}: Temporal constraints of an Application Programming
-Interface (API) are the allowed sequences of invocations of
-methods from the API. These constraints govern the secure and robust
-operation of client software using the API.
-
-\textbf{Method}: \tool, is a Natural Language Processing (NLP) based
-approach thus complementing existing program-analysis-based approaches.
-In particular, \tool\ includes techniques to reduce the
-number of lexical tokens as a way to make API documents amenable
-to existing NLP techniques (which are typically designed to work
-on well-written news articles). Our approach also includes a novel
-technique of identifying method references (improvement over keyword-based
-techniques) in the natural language text by building domain
-dictionaries systematically from API documents and generic English
-dictionaries.
-
-\textbf{Results}: To evaluate our approach, we apply \tool\ to infer temporal
-constraints from commonly used package \CodeIn{java.io} in the
-JDK API and from the \amazonAPI. Our results show
-that \tool\ effectively identifies constraint sentences (from over
-3900 API sentences) with the average precision, recall, and F-score
-of 65.0\%, 72.2\%, and 68.4\%, respectively. Furthermore, \tool\
-also achieves an accuracy of 70\% in inferring 63 temporal constraints
-from these sentences.
-
-\textbf{Conclusion}: NLP based techniques offers a viable means to infer
-temporal constraints of an API.
-
-\textbf{Application}: Existing software engineering tools can leverage
-the inferred temporal constraints to effectively assist in development
-and verification activities.
+%Our approach also includes a novel
+%technique of identifying method references (improvement over keyword-based
+%techniques) in the natural language text by building domain
+%dictionaries systematically from API documents and generic English
+%dictionaries.
+%
+%
+%Existing software engineering tools can leverage
+%the inferred formal temporal constraints to effectively assist in development
+%and verification activities.
 
@@
 
-% Goal Statement
-% Negating everything as we go along
-% Instead of despite 
-% need to explain why moving from formal specifications to temporal constraints
-% bridging
-% Goal statement
-% The goal of this research is to facilitate the correct usage API methods by identifying temporal constraints.
-% to support tool based verfication
-% Avoid starting the abstarct with a definition
-% bridge the gap
-% There is an order that API documents tell 
-% but they are 
-% Adhering to temporal constraints is mandatory for correct usage of API
-% However, it not starightforward to 
-% Motivation
-% Goal
-% Evaluation
-% Structured Abstract
-% what is the significance of this prescison i/p o/p
-% expresses 
-% makes end to end summary.
-
 % where do you loose precision and recall.

### 2014-12-03 Draft/approach.tex
Updated Draft for DSN
Updated Draft for DSN

@@
-\section{Approach Overview}
+\section{ICON Overview}
 \label{sec:approach}
@@
 
-We next present our approach for inferring temporal constraints from the method descriptions in API Documents.
-Figure~\ref{fig:approachOverview} gives an overview of our approach.
-Our approach consists of five major components: a preprocessor, a text-analysis engine, a semantic graph generator, constraint extractor, and a type analyzer.
+We next present our approach for inferring temporal constraints
+from the method descriptions in API Documents.
+Figure~\ref{fig:approachOverview} gives an overview of \tool\ approach.
+\tool\ consists of five major components: a preprocessor, a text-analysis engine, a semantic graph generator, constraint extractor, and a type analyzer.
+We next describe each component in detail.
 
-The preprocessor accepts API documents and preprocesses the sentences in the method description,
-such as annotating sentence boundaries and reducing lexical tokens.
-The text-analysis engine accepts the pre-processed sentences and annotates them using an NLP parser.
-The text-analysis engine further transforms the annotated sentences into the first-order-logic (FOL) representation.
-The semantic graph generator accepts the API documents and generates the semantic graphs that are leveraged by constraint extractor component.
-The type analyzer component infers temporal constraints encoded in the type system of a language by analyzing the API methods parameter and return types.
-Finally, the constraint extractor leverages the semantic graphs to infer temporal constraints from the FOL representation of a sentence.
-We next describe each component in detail.
+%The preprocessor accepts API documents and preprocesses the sentences in the method description,
+%such as annotating sentence boundaries and reducing lexical tokens.
+%The text-analysis engine accepts the pre-processed sentences and annotates them using an NLP parser.
+%The text-analysis engine further transforms the annotated sentences into the first-order-logic (FOL) representation.
+%The semantic graph generator accepts the API documents and generates the semantic graphs that are leveraged by constraint extractor component.
+%The type analyzer component infers temporal constraints encoded in the type system of a language by analyzing the API methods parameter and return types.
+%Finally, the constraint extractor leverages the semantic graphs to infer temporal constraints from the FOL representation of a sentence.
+%We next describe each component in detail.
 
@@
 3) \textit{Summary and type information of return values of the method}, and
-4) \textit{Summary and type information of exceptions thrown by the methods}.
+4) \textit{Summary and type information of exceptions thrown (or errors returned) by the methods}.
 
 This step is required to extract the desired descriptive text from the API documents.
-In particular, different API documents may have different styles of presenting information to developers.
+Different API documents may have different styles of presenting information to developers.
 This difference in style may also include the difference in the level of detail presented to developers.
-Our approach thus relies on only basic fields that are trivially available for API methods across different presentation styles.
+\tool\ thus relies on only basic fields that are generally available for API methods across different presentation styles.
 
@@
 The preprocessing steps are required to increase the accuracy of core NLP techniques (described in Section~\ref{sub:CoreNLPback}) that are used in the subsequent phases of \tool\ approach.
-In particular, the preprocessor first employs the noun boosting followed by heuristics listed under lexical token reduction, as introduced in Section~\ref{sub:SENLPback}.
+The preprocessor first employs the heuristics listed under lexical token reduction, as introduced in Section~\ref{sub:SENLPback}.
 
-Although the previous techniques and heuristics significantly lower the number of lexical tokens in a sentence,
-some sentences may still contain a considerable number of lexical tokens to overwhelm the POS tagger.
-To address this issue, we propose a new heuristic (\textit{`Frequent Phrases Reduction'})
-to further reduce the number of lexical tokens in a sentence by annotating frequent phrases as a single lexical unit.
-
-In particular, we use n-gram~\cite{brown1992class} based approach to achieve this reduction. 
-In the fields of computational linguistics, an n-gram is a contiguous sequence of n words from a given text.
-In statistical NLP  and information theory, n-gram has been shown to be effective in computing the probability of occurrence of next word given a sequence of words.
-However, for our approach we use n-grams that always occur together in a given body of text.
-
-To achieve \textit{frequent phrases reduction}, we first calculate the most frequently occurring n-grams in the text body. 
-In particular, we are interested in the n-grams of length four or greater to achieve a reasonable reduction.
-We chose four as a threshold for n-grams because we observed that bigrams (size two) and trigrams (size three) frequently resulted in change of semantics
-of the sentence in comparison to n-grams of size four or grater.
-We then prune the list of n-grams based on a subsumption. 
-We consider an n-gram of length k ($n_k$) to subsume n-gram of length k-1 ($n_{k-1}$) iff $n_{k-1}$ is a substring of ($n_k$) and the frequency of occurrence of $n_{k-1}$ equals frequency of occurrence of $n_{k}$.
-Finally, we rank the list of n-grams based on the frequency of their occurrence in the text, and select top-k n-grams for reduction.
-For instance, \textit{Amazon Simple Storage Service}, \textit{an I/O Error Occurs}, and \textit{end of the stream} are the examples of such n-grams detected by our approach.
+%Although the previous techniques and heuristics significantly lower the number of lexical tokens in a sentence,
+%some sentences may still contain a considerable number of lexical tokens to overwhelm the POS tagger.
+%To address this issue, we propose a new heuristic (\textit{`Frequent Phrases Reduction'})
+%to further reduce the number of lexical tokens in a sentence by annotating frequent phrases as a single lexical unit.
+%
+%In particular, we use n-gram~\cite{brown1992class} based approach to achieve this reduction. 
+%In the fields of computational linguistics, an n-gram is a contiguous sequence of n words from a given text.
+%In statistical NLP  and information theory, n-gram has been shown to be effective in computing the probability of occurrence of next word given a sequence of words.
+%However, for \tool\ we use n-grams that always occur together in a given body of text.
+%
+%
+%To achieve \textit{frequent phrases reduction}, we first calculate the most frequently occurring n-grams in the text body. 
+%In particular, we are interested in the n-grams of length four or greater to achieve a reasonable reduction.
+%We chose four as a threshold for n-grams because we observed that bigrams (size two) and trigrams (size three) frequently resulted in change of semantics
+%of the sentence in comparison to n-grams of size four or grater.
+%We then prune the list of n-grams based on a subsumption. 
+%We consider an n-gram of length k ($n_k$) to subsume n-gram of length k-1 ($n_{k-1}$) iff $n_{k-1}$ is a substring of ($n_k$) and the frequency of occurrence of $n_{k-1}$ equals frequency of occurrence of $n_{k}$.
+%Finally, we rank the list of n-grams based on the frequency of their occurrence in the text, and select top-k n-grams for reduction.
+%For instance, \textit{Amazon Simple Storage Service}, \textit{an I/O Error Occurs}, and \textit{end of the stream} are the examples of such n-grams detected by \tool.
 
 %\textbf{Prototype Implementation.}
-Currently our prototype implementation works with online \amazon\ and JDK API. 
-However, almost all of the developer documents are provided online as structured webpages.
-Thus, current prototype implementation of preprocessor can be easily extended to extract the desired information from any API developer documents.
-
-Additionally, in current implementation we have manually built the dictionaries for preprocessing using the glossary of terms collected from the websites pertaining to REST and Java API.
-We further leveraged the HTML style information in \amazon\ to look for words that were highlighted in code like format.
+%Currently our prototype implementation works with online \amazon\ and JDK API. 
+%However, almost all of the developer documents are provided online as structured webpages.
+%Thus, current prototype implementation of preprocessor can be easily extended to extract the desired information from any API developer documents.    
+%
+%Additionally, in current implementation we have manually built the dictionaries for preprocessing using the glossary of terms collected from the websites pertaining to REST and Java API.
+%We further leveraged the HTML style information in \amazon\ to look for words that were highlighted in code like format.
 We further leveraged WordNet to maintain a static lookup table of shorthand words to aid named entity handling and abbreviation handling.
-
-Finally, to achieve  n-gram reduction we used Apache Lucene~\cite{lucene}.
-Apache Lucene is a high-performance, full-featured text-search-engine library written entirely in Java,
-facilitating scalable cross-platform full-text search.
+% 
+%Finally, to achieve  n-gram reduction we used Apache Lucene~\cite{lucene}.
+%Apache Lucene is a high-performance, full-featured text-search-engine library written entirely in Java,
+%facilitating scalable cross-platform full-text search.
 
@@
 The NLP parser accepts the pre-processed documents and annotates every sentence in each document using core NLP techniques described in Section~\ref{sub:CoreNLPback}.
-From an implementation perspective, we chose the Stanford parser~\cite{Manning:01}.
-However, this component can be implemented using any other existing NLP libraries or approaches.
-In particular, we annotate each sentence with POS tags, named-entity annotations and Stanford-typed dependencies.
+%From an implementation perspective, we chose the Stanford parser~\cite{Manning:01}.
+%However, this component can be implemented using any other existing NLP libraries or approaches.
+In particular, each sentence is annotated with: \textit{1)POS tags, 2)named-entity annotations, and 3)Stanford-typed dependencies.}
 For more details on these techniques and their application, please refer to ~\cite{Marneffe06LREC, Marneffe08COLING, pandita12:inferring, pandita13:WHYPER, thummalapentaICSE12}.
@@
 Consider the sentence from the example section \textbf{\textit{`All objects (including all object versions and Delete Markers) in the bucket must be deleted before the bucket itself can be deleted.''}}.
-Figure~\ref{fig:standep} shows the sentence annotated with Stanford-typed dependencies.
-The words in red are the names of dependencies connecting the actual words of the sentence (in black).
-Each word is followed by the Part-Of-Speech (POS) tag of the word (in green).
-For more details on Stanford-typed dependencies and POS tags, please refer to ~\cite{Marneffe06LREC,Marneffe08COLING}.
+Figure~\ref{fig:standep} shows the sentence annotated by NLP parser.
+Each word (occurs first) is followed by the Part-Of-Speech (POS) tag of the word (in green), which is further followed by the name of Stanford dependency connecting the actual word of the sentence to its predecessor.
+%For more details on Stanford-typed dependencies and POS tags, please refer to ~\cite{Marneffe06LREC,Marneffe08COLING}.
+
+\subsection{Candidate Identifier}
+
+This component accepts the annotated sentence from the previous component,
+then using a trained model classifies whether a sentence describes a temporal constraint or not. We next describe the model construction.
+
+The goal of model construction is to use a small set of manually classified temporal constraint sentences of a representative API to construct a model to automatically classify the unlabeled sentences.
+Since \tool\ seeks to achieve a binary classification of the API sentences, we chose to train our model using na{\"i}ve Bayes classifier which is the simplest probabilistic classification methods  and is shown to be comparative other advanced classification methods given appropriate prepossessing~\cite{rennie2003tackling}.
+The model can be trained offline or else by the users of the approach if better accuracy is required for specific data.
+
+Feature selection is an important factor for the accuracy any classification method.
+Particularly, for na{\"i}ve Bayes classifier which assumes each feature independently contributes towards the final probability of classification.
+In the simplest form, each word occurring in a sentence is considered as a feature.
+However, such an approach may lead to overly specific models, and therefore \tool\ approach employs preprocessing for generic features.
+We next describe the features we chose for training our model along with the rationale for selecting such features.
+
+\begin{enumerate}
+
+	\item \textbf{Length of a Sentence}: The feature is the total number of words in  the sentence.
+The rationale is that shorter sentences (containing fewer words) are unlikely candidates for temporal constraint sentences.
+
+	\item \textbf{Sentence Type}: The context of sentence, whether the sentence appears as method summary, parameter summary, return value summary or exception/error summary as captured by pre-processor phase.
+The rationale is that a majority of the temporal constraint sentences are either summary or exception sentences.
+
+	\item \textbf{Lemmatization}: The feature is the base form of a word.
+In linguistic lemmatization is the reduction of operational form of a word to its base form.
+For instance ``invoking'', ``invokes'', and ``invoked'' are all reduced to invoke.
+The rationale for reducing the words to base form is to reduce the size of the feature set that otherwise considers every word as an independent feature.
+
+	\item \textbf{Stopword Reduction}: In linguistics stop words are the frequently occurring words that can easily be ignored and are often considered noise, such as ``the'' , ``of'', ``to'' etc...
+The rationale for filtering the stop words is to reduce the size of feature set that otherwise considers such word as an independent feature but are often noise.
+Stop word list is further augmented by adding to them the words that occur exactly once in the training corpus to avoid over-fitting of the model to the training corpus.
+
+	\item \textbf{Stanford Dependencies}: We add to the feature set by identifying the presence of specific Stanford typed dependencies pertaining to the temporal aspects of the sentence semantics.
+In particular we identify the presence of ``\textit{advcl}'', ``\textit{aux}'', ``\textit{auxpass}'', ``\textit{vmod}'', and ``\textit{tmod}''.
+For instance, the annotated sentence in Figure~\ref{fig:standep} contains both ``\textit{aux}'' and ``\textit{auxpass}'' dependencies.
+These are both added to the feature set.
+
+	\item \textbf{POS Tags}: We filter words whose part of speech tags are ``\textit{Noun}'', ``\textit{Determiner}'', ``\textit{Adjective}'', ``\textit{Cardinal Number}'', ``\textit{Foreign Word}'', ``\textit{Brackets}'', ``\textit{Coordinating Conjunction}'', and ``\textit{Personal Pronouns}''.
+The rationale for filtering based on POS tags is to remove the words that are unlikely to be specific to temporal constraints.
+For instance, presence or absence of determiners is unlikely to affect the outcome of classifier.
+We further, annotate the POS of word to further distinguish between the words used in different context.
+
+\end{enumerate}
+
+We use this feature set to train a classier to perform binary classification of temporal constraint sentence vs other sentences.
+The rationale of using ML based approach as opposed to a rule based approach is because: 1) rule-writing requires domain expertise, 2) rules-writing tends to quickly become ad hoc thus requires greater effort to generate generic rules, and 3) ML classifiers have shown to scale well with large volumes of data.
+
+%Constraint Extractor then classifies the sentence as a constraint 
+%sentence (containing temporal constraint) candidate based on following ordered set of rules:
+%
+%\begin{enumerate}
+%	\item The sentence is not from parameter summary or return variable summary.
+%	Typically such sentences describe pre-post conditions as opposed to temporal constraints \tool\ addresses.
+%	\item The sentences contains modal modifiers such as ``\textit{can, could, may, must, should}'' expressing necessity.
+%	Typically, presence of such modal modifier is a strong indicator of presence of constraints imposed by an API developer
+%	\item If the sentence does not contain modal modifiers described previously, sentence must contain temporal modifier relationship, identified by Stanford-typed dependency parser.
+%	Typically, presence of temporal modifier is an indicator of presence of temporal information.  
+%	\item If rules 2 and 3 don't apply then the sentences should be a conditional sentence, identified by the presence of keywords such as ``\textit{if}'' and ``\textit{whether}''.
+%\end{enumerate}
 
@@
 \label{sub:TAE}
-%
+
 %\begin{figure}
 %	\centering
-%	%	\includegraphics[scale=0.65]{taeRep.eps}
+%		\includegraphics[scale=0.65]{taeRep.eps}
 %	\caption{First-order logic representation of annotated sentence in Figure~\ref{fig:standep}}
@@
 
-The text analysis engine component accepts the annotated documents and creates an intermediate representation of each sentence.
+The text analysis engine component accepts the sentences identified as constraint sentences and creates an intermediate representation of each sentence.
 We define our representation as a tree structure that is essentially a FOL expression.
@@
 However, we observed that such implementation is overwhelmed by complex sentences.
-This limitation mandates the use of additional novel technique of \textit{`Frequent Phrases Reduction'} in preprocessing phase.
-We further improve the accuracy of intermediate-representation generation by proposing a hybrid approach, i.e. taking into consideration both the POS tags as well as Stanford-typed dependencies.
+We improve the accuracy of intermediate-representation generation by proposing a hybrid approach, i.e. taking into consideration both the POS tags as well as Stanford-typed dependencies.
 The POS tags which annotate the syntactical structure of a sentence are used to further simplify the constituent elements in a sentence. 
@@
 \textbf{Stanford-typed Dependencies}: This phase is equivalent to the intermediate-representation technique described in Section~\ref{sub:SENLPback}.
+Figure~\ref{fig:FOLTree} is the FOL representation of the sentence  \textit{``All objects in the bucket must be deleted before the bucket itself can be deleted''}.
+All the leaf nodes (entities) are represented as the bold words.
+For readability each node is appended with a number representing the in-order traversal index of the tree.
+
+\begin{figure}
+	\begin{CodeOut}
+		\begin{alltt}
+			01:before[6]
+			02:|->must be deleted[5]
+			03:\hspace*{0.2in}|->All[1]
+			04:\hspace*{0.2in}|\hspace*{0.2in}|->in[3]
+			05:\hspace*{0.2in}|\hspace*{0.4in}|->\textbf{objects}[2]
+			06:\hspace*{0.2in}|\hspace*{0.4in}|->\textbf{bucket}[4]
+			07:\hspace*{0.2in}|->can be deleted[8]
+			08:\hspace*{0.4in}|->\textbf{bucket}[7]
+			09:\hspace*{0.4in}|->\textbf{itself}[9]
+		\end{alltt}
+	\end{CodeOut}
+	\caption{\label{fig:FOLTree} FOL representation of the sentence \textit{``All objects in the bucket must be deleted before the bucket itself can be deleted.''}}
+\end{figure}
 
@@
 
-This component accepts the FOL representation of the sentence from the previous component,
-then extracts the temporal constraints if present in a sentence.
-Constraint Extractor then classifies the sentence as a constraint 
-sentence (containing temporal constraint) candidate based on following ordered set of rules:
+Constraint Extractor is responsible for inferring temporal constraint from the classified constraint sentences.
+\tool\ uses the formalism proposed by Lo et al.~\cite{lo2009mining} (introduced in Section~\ref{sec:background})
+for formalizing the constraints. 
+\tool\ extends the operators by proposing two additional operators:
 
 \begin{enumerate}
-	\item The sentence is not from parameter summary or return variable summary.
-	Typically such sentences describe pre-post conditions as opposed to temporal constraints this approach addresses.
-	\item The sentences contains modal modifiers such as ``\textit{can, could, may, must, should}'' expressing necessity.
-	Typically, presence of such modal modifier is a strong indicator of presence of constraints imposed by an API developer
-	\item If the sentence does not contain modal modifiers described previously, sentence must contain temporal modifier relationship, identified by Stanford-typed dependency parser.
-	Typically, presence of temporal modifier is an indicator of presence of temporal information.  
-	\item If rules 2 and 3 don't apply then the sentences should be a conditional sentence, identified by the presence of keywords such as ``\textit{if}'' and ``\textit{whether}''.
+	\item Forward Prohibition Operator ($\xi_1 \xrightarrow{-} \xi_2$):
+	occurrence of $\xi_1$ cannot be followed by occurrence of $\xi_2$
+
+	\item Backward Prohibition Operator ($\xi_1 \xleftarrow{-} \xi_2$):
+	occurrence of $\xi_1$ cannot be preceded by the occurrence of $\xi_2$
 \end{enumerate}
 
-Once a candidate sentence is identified, this component selects an semantic graph.
-In particular, the semantic graph of the API class to which the candidate sentence belongs to selected.
-Since there is no concept of classes in REST API, semantic graphs of all resources described in the API are selected.
-A semantic graph constitutes the keyword representation of the classes and the corresponding applicable actions. 
+The prohibition operators capture a different class of temporal constraints that cannot be
+expressed by the formulae constructed by previously proposed operators and their negations.
+For instance, the \textit{prohibition operators} seem to be negation of
+\textit{forward eventual operators} and \textit{backward eventual operators}.
+However, the negation of forward eventual operators is: not an invocation of $\xi_1$
+must be eventually followed by not an invocation of $\xi_2$. In contrast,
+\textit{prohibition operators} either negates antecedent or consequent but not both.
+In summary, we extended the formalism for temporal rules previously
+proposed by Lo et al.~\cite{lo2009mining} to express temporal constraints.
+
+\tool\ first identifies $\xi_1$ as the method whose description constraint sentence is part of.
+For instance the sentence in Figure~\ref{fig:standep} is part of Delete Bucket method description in \amazonAPI,
+$\xi_1$ is instantiated as Delete Bucket method.
+
+\tool\ next identifies $\xi_2$.
+Since, references to $\xi_2$ may not always be implicit we leverage the semantic graphs.
+A semantic graph is a representation of concepts of objects and the methods applicable on those objects.
 Figure~\ref{fig:knowledge} shows a graph for \CodeIn{Object} resource in \amazonAPI.
@@
 Section~\ref{sub:ACA} further describes how these graphs are generated.
-
-Constraint extractor then uses the semantic graph to determine
-whether a candidate sentence is a constraint sentence and if so extract
-the action that should be performed prior to the method the sentence
-belongs to. Algorithm~\ref{alg:SenAnnotaator} describes this action extraction
-process.
+\tool\ uses the Algorithm~\ref{alg:SenAnnotaator} to identify $\xi_2$.
 
@@
 
-Our algorithm systematically explores the FOL representation
-of the candidate sentence to determine if a sentence
-describes a temporal constraint. First, our algorithm
-attempts to locate the occurrence of class name or its synonym
+The algorithm systematically explores the FOL representation
+of the candidate sentence to identify $\xi_2$. First, the algorithm
+attempts to locate the occurrence of object name or its synonym
 in the leaf nodes of the FOL
@@
 findLeafContaining(r\_name\_list) explores the FOL representation
-to find a leaf node that contains either the class name
+to find a leaf node that contains either the object name
 or one of its synonyms.
-In particular, we use WordNet~\cite{wordnet} and Lemmatisation
-to deal with synonyms of a word in question to find appropriate
-matches. Once a leaf node is found, we systematically
+Once a leaf node is found, we systematically
 traverse the tree from the leaf node to the root,
@@
 predicates [Lines 5-16].
+Algorithm matches each of the traversed predicate
+with the actions associated with the object defined in
+semantic graph. 
+\tool\ further employs WordNet and Lemmatisation to deal with
+synonyms to find appropriate matches. If a match is
+found, then the matching action is returned as $\xi_2$.
+\tool\ does not consider self references, that is if $\xi_2 = \xi_1$, the identified method reference is discarded.
+In case of multiple matching actions \tool\ considers only the first match.
+For instance the sentence in Figure~\ref{fig:standep} algorithm identifies
+Delete Object method as $\xi_2$
 
-Our algorithm matches each of the traversed predicate
-with the actions associated with the class defined in
-semantic graph. Similar to matching entities, we also
-employ WordNet and Lemmatisation to deal with
-synonyms to find appropriate matches. If a match is
-found, then the matching action name is returned.
+\tool\ next identifies the direction (forward or backward) of the relationship by examining the tense of $\xi_2$ reference in the sentence.
+Past tense is considered as backward and other tenses are considered as forward.
+For instance, the sentence in Figure~\ref{fig:standep} since ``deleted'' is in past tense and therefore operator is backward and the constraint is
+Delete Object $\xleftarrow{*}$ Delete Method.
+
+The negation is identified by presence of negation verbs such as ``\textit{no}'', ``\textit{not}'', ``\textit{can't}'' ...
+etc.
+Another rule for negation operator is if the sentence is in exception/error description.
 
@@
 
-A key way of identifying reference to a method in the API by our approach is the employment of a semantic graph of an API.
-In particular, we propose to initially infer such graphs from API documents.
-Manually creating a semantic graph is prohibitively time consuming and may be error prone.
-We thus employ a systematic methodology (proposed previously in ~\cite{pandita13:WHYPER}) to infer such semantic graphs from API documents that can potentially be automated.
+A key way of identifying reference to a method in the API by \tool\ is the employment of a semantic graph of an API.
+We propose to initially infer such graphs from API documents.
+Ad hoc creation of semantic graph is prohibitively time consuming and may be error prone.
+We thus employ a systematic methodology (proposed previously by Pandita et al. ~\cite{pandita13:WHYPER}) to infer semantic graphs from API documents.
+
 We first consider the name of the class for the API document in question.
@@
 
-As mentioned earlier that some temporal constraints are enforced by the type system in typed Languages.
+Some temporal constraints are enforced by the type system in typed Languages.
 For instances a method ($m$) accepting input parameter ($i$) of type ($t$) mandates that (at least one) method ($m'$) be invoked whose return value is of type ($t$).
@@
 have the same type to the method in question (Line 14- 20).
-The algorithm does not take into consideration the basic parameter types such as integer, string (Line 15).
+The algorithm does not take into consideration the basic parameter types such as \CodeIn{integer}, \CodeIn{string} (Line 15).
 Additionally, an edge is created from the constructors of a class to the non static members methods of a class (Line 8 -13).

### 2014-12-03 Draft/background.tex
Dr. Xie's coments
Updated Introduction for flow Updated abstract with goal statement. Minor changes elsewhere.
compressive -> comprehensive added Software Engineering(SE)
Updated Draft for DSN
Updated Draft for DSN

@@
 
-In particular, this work proposes novel techniques on top of previously proposed techniques~\cite{pandita12:inferring, pandita13:WHYPER} to demonstrate the effectiveness of applying NLP on API documents.
+%In particular, this work proposes novel techniques on top of previously proposed techniques~\cite{pandita12:inferring, pandita13:WHYPER} to demonstrate the effectiveness of applying NLP on API documents.
 We next briefly introduce the techniques used in this work that have been grouped into broad categories.
 We first introduce the core NLP techniques used in this work.
-We then introduce the SE specific NLP techniques proposed in previous work~\cite{pandita12:inferring,pandita13:WHYPER} that are used in this work.
+We then introduce the SE specific NLP techniques proposed in related work~\cite{pandita12:inferring,pandita13:WHYPER} that are used in this work.
 
@@
 
+We next present Software Engineering (SE) specific NLP techniques.
+
 \subsection{SE specific NLP techniques}
@@
 
-\textbf{Noun Boosting}~\cite{pandita12:inferring}. Accurate annotation of POS tags in a sentence is fundamental to effectiveness of any advanced NLP technique.
-However, as mentioned previously, POS tagging works satisfactorily on well written news articles which does not necessary entail that the tagging works satisfactorily on domain specific text as well.
+\textbf{Programming keywords}~\cite{pandita12:inferring}. Accurate annotation of POS tags in a sentence is fundamental to effectiveness of any advanced NLP technique.
+However POS tagging works satisfactorily on well-written news articles which does not necessary entail that the tagging works satisfactorily on domain-specific text as well.
 Thus, noun boosting is a necessary precursor to application of POS tagging on domain specific text.
@@
 These are a group of generic preprocessing heuristics to further improve the accuracy of core NLP techniques.
-The accuracy of core NLP techniques is inversely proportional to the number of lexical tokens in a sentence.
+The accuracy of core NLP techniques is often inversely proportional to the number of lexical tokens in a sentence.
 Thus, the reduction in the number of lexical tokens greatly increases the accuracy of core NLP techniques. 
@@
 \textbf{Intermediate-Representation Generation}~\cite{pandita13:WHYPER}.
-This technique accepts the syntax-annotated sentences and builds a First-Order-Logic(FOL) representation of the sentence.
+This technique accepts the syntax-annotated sentences (grammatical and semantic) and builds a First-Order-Logic (FOL) representation of the sentence.
 Earlier researches have shown the adequacy using FOL for NLP related analysis tasks~\cite{Sinha2009,Sinha2010,pandita12:inferring}.
@@
 
-In next section we describe our proposed generic approach to infer constraints from API documents.
+In next section we describe our generic approach to infer temporal constraints from API documents.

### 2014-12-03 Draft/conclusion.tex
Updated Draft for DSN
Updated Draft for DSN

@@
 We applied \tool\ to infer temporal constraints from
-commonly used package \CodeIn{java.io} in the JDK API and from the \amazonAPI.
+\paypalAPI, \amazonAPI, and  
+commonly used package \CodeIn{java.io} in the JDK API.
 Our evaluation results show that \tool\ effectively identifies sentences describing
 temporal constraints with an average 65\% precision and 72\% recall,
-from more than 3900 sentences in subject API documents.
+from more than 4000 sentences in subject API documents.
 Furthermore, \tool\ also achieved an accuracy of

### 2014-12-03 Draft/evaluation.tex
Updated Draft for DSN
Updated Draft for DSN

@@
 \begin{itemize}
-	\item \amazonAPI\: provides a REST based web services interface that can be used to store and retrieve data on the web.
-Furthermore, \CodeIn{Amazon S3} also empowers a developer with rich set of API methods to access a highly scalable, reliable, secure, fast, inexpensive infrastructure.
+	\item \amazonAPI\: provides a REST based web services interface to store and retrieve data on the web.
+	Furthermore, \CodeIn{Amazon S3} also empowers a developer with rich set of API methods to access a highly scalable, reliable, secure, fast, and inexpensive infrastructure. 
 	\CodeIn{Amazon S3} is reported to store more than 2 trillion objects as of April 2013 and gets over 1.1 million requests per second at peak time~\cite{amazons3stats}.
+
+	\item \paypalAPI\: provides a REST based web service interface to facilitate online payments and money transfer.
+	\CodeIn{PayPal} reports to have handled \$56.6 billion(USD) worth of transactions (total value of transactions) in just the third quarter of 2014.
 
@@
 \end{itemize}
-We chose \CodeIn{Amazon S3} and \CodeIn{java.io} APIs as our subjects because they are popular and contain decent documentation.
+We chose \CodeIn{Amazon S3}, \CodeIn(PayPal) and \CodeIn{java.io} APIs as our subjects because they are popular and contain decent documentation.
 
@@
 java.io & 662 & 2417 & 78 & 88 & 57 & 31 & 21 & 64.8 & 73.1 & 68.8 & 56 & 71.8\\ 
-\rowcol AMAZON S3 REST & 51 & 1492 & 12 & 12 & 8 & 4 & 4 & 66.7 & 66.7 & 66.7 & 7 & 58.3\\ 
-Total & 713 & 3909 & 90 & 100 & 65 & 35 & 25 & 65.0$^*$ & 72.2$^*$ & 68.4$^*$ & 63 & 70.0$^*$\\ 
+\rowcol \amazonAPI & 51 & 1492 & 12 & 12 & 8 & 4 & 4 & 66.7 & 66.7 & 66.7 & 7 & 58.3\\ 
+\paypalAPI & 33	&	151 &  20 &  &  &  &  & &  &  &  & \\ 
+\rowcol Total & 746 & 4060 & 90 & 100 & 65 & 35 & 25 & 65.0$^*$ & 72.2$^*$ & 68.4$^*$ & 63 & 70.0$^*$\\ 
 \bottomlinec

### 2014-12-03 Draft/example.tex
included formal def
Updated Draft for DSN
Updated Draft for DSN

@@
 We next present a real world example to motivate our approach.
-In particular, through the example, we demonstrate that developers often ignore the temporal constraints of an API described in the documentation.
+Through the example, we demonstrate that developers often ignore the temporal constraints of an API described in the documentation.
 We suspect the reason for this phenomena is that the documentation is often verbose and the information is distributed across various pages.
 For instance, the PDF version of the documentation for \amazonAPI\footnote{{\small \url{http://awsdocs.s3.amazonaws.com/S3/latest/s3-api.pdf}}} spans 278 pages.
-Developers often may not have time (and/or patience) to go through all the documentation and may overlook some temporal constraints of the API,
+Often developers may not have time (and/or patience) to go through all the documentation and may overlook some temporal constraints of the API,
 resulting in defective client applications that invoke API methods in sequences prohibited by documentation.
@@
 \textit{``All objects (including all objects versions and Delete Markers) in the bucket must be deleted before the bucket itself can be deleted''}.
-The issue was fixed.
-However, one of the forum responses contained a recommendation for the inquisitor to switch to another product.
-Customer dissatisfaction, such as was caused by this issue with the delete bucket functionality, can lead to a lose in revenue.
+Although the issue was fixed, one of the forum responses contained a recommendation for the inquisitor to switch to another product.
+Customer dissatisfaction, such as the one was caused by this issue with the delete bucket functionality, can lead to a loss in revenue.
 
-The preceding issue can be easily detected using formal analysis tools.
+The presented issue can be easily detected using formal analysis tools.
 For instance, a specification rule (temporal constraint) can be added to a static checker to verify
@@
 %Thus, there is need for an approach to automatically translate the constraints described in natural language into a more formal notation.
-In next section, we briefly discuss the related work pertinent to our proposed approach.
+In next section, we briefly discuss the related work pertinent to our approach.

### 2014-12-03 Draft/formal.tex
Updated Draft for DSN
Updated Draft for DSN

@@
-\section{Temporal Specifications}
-\label{sec:temporal}
+\subsection{Temporal Specifications}
+\label{sub:temporal}
 
-In this section we describe various classes of temporal constraints using formal temporal logic.
-In computer science, temporal Logic is a system of rules and symbols that are used to express and reason about prepositions pertaining to time.
+We next describe various classes of temporal constraints using formal temporal logic.
+Temporal logic is a system of rules and symbols that are used to express and reason about prepositions pertaining to time.
 We next present an extension to the temporal logic for API method invocation related rules proposed by Lo et al.~\cite{lo2009mining}
@@
 where each method invocation is represented as a tuple which is an ordered set of strings. 
-A method invocation is captured as the Tuple <$T$><\CodeIn{str1, str2, str3}...>, where \CodeIn{str1, str2, str3}... are string values,
+A method invocation is captured as the Tuple \CodeIn{<T> <str1, str2, str3... >}, where \CodeIn{str1, str2, str3}... are string values,
 that belong to set of all strings.
-The method invocation tuple <$T$> captures information about the return value, enclosing type, name, and the parameter types of the method.
-Therefore a tuple <$T$><\CodeIn{String, Bar, foo, Integer, Integer}> represents a method \CodeIn{foo} enclosed by the type \CodeIn{Bar},
+The method invocation tuple \CodeIn{<T>} captures information about the return value, enclosing type, name, and the parameter types of the method.
+Therefore a tuple \CodeIn{<T> <String, Bar, foo, Integer, Integer>} represents a method \CodeIn{foo} enclosed by the type \CodeIn{Bar},
 that accepts two parameters of type \CodeIn{Integer} and a return value of type \CodeIn{String}. 
@@
 
-\textbf{Temporal Operators}: Temporal formulae (temporal constraints) are constructed by combining method invocation predicates using temporal operators.
-Lo et al.~\cite{lo2009mining}, proposed the following temporal operators
+\textbf{Temporal Operators}: Temporal constraints~\footnote{Temporal formulae} are constructed by combining method invocation predicates using temporal operators.
+Lo et al.~\cite{lo2009mining}, proposed the following temporal operators:
 
@@
 
-We extend these operators by proposing two additional operators:
-\begin{enumerate}
-\item Forward Prohibition Operator ($\xi_1 \nrightarrow \xi_2$):
-occurrence of $\xi_1$ cannot be followed by occurrence of $\xi_2$
-
-\item Backward Prohibition Operator ($\xi_1 \nleftarrow \xi_2$):
-occurrence of $\xi_1$ cannot be preceded by the occurrence of $\xi_2$
-\end{enumerate}
-
-The prohibition operators capture a different class of temporal constraints that cannot be expressed by the formulae constructed by previously proposed operators and their negations.
-For instance, the \textit{prohibition operators} on first glance seem to be negation of \textit{forward eventual operators} and \textit{backward eventual operators}.
-However, the negation of forward eventual operators is: not an invocation of e1 must be eventually followed by not an invocation of m2.
-In contrast, \textit{prohibition operators} either negates antecedent or consequent but not both.
-
 \textbf{Quantification}: Quantification is used to introduce constraints involving parameter and return types of a method invocation.
-For instance, consider the constraint any method in an enclosing type \CodeIn{Obj} must not be invoked after method \CodeIn{foo} in the \CodeIn{Obj}.
-
-$\forall$ \CodeIn{m <m in Obj> !=<foo in Obj>}
-
-In summary, we extended the formalism for temporal rules previously proposed by Lo et al.~\cite{lo2009mining} to express temporal constraints.
-We obtain different classes of temporal constraints by varying: 1) the temporal operators allowed, b) the method-invocation predicates allowed, and 3) the degree of quantification allowed.
+Formal representation of temporal constraints are obtained by varying: 1) the temporal operators allowed, b) the method-invocation predicates allowed, and 3) the degree of quantification allowed.
+For instance, consider the constraint any method in an enclosing type \CodeIn{Obj} must not be invoked after method \CodeIn{foo} in the \CodeIn{Obj}: $\forall$ \CodeIn{m <m in Obj> !=<foo in Obj>}.

### 2014-12-03 Draft/introduction.tex
Updated Draft for DSN
Updated Draft for DSN

@@
 
-The increasing reach of internet has fueled the growth of web Application Programming Interfaces (API).
+The increasing reach of the internet has fueled the growth of web Application Programming Interfaces (API).
 The ProgrammableWeb reports that the web APIs have doubled from Jan 2012 to Oct 2013\footnote{\url{http://www.programmableweb.com/api-research}}.
@@
 Unlike most traditional API libraries that are in the format of locally stored binary files and are programming language specific,
-web API are designed to leverage the web server and web browser architecture and the implementation is programming language agnostic.
+web APIs are designed to leverage the web server and web browser architecture and the implementation is programming language agnostic.
 However, Web APIs like traditional APIs have rules or constraints governing the proper  use of the API that must be followed.
@@
 
-In traditional API, which are usually implemented in typed languages some temporal constraints are enforced by type system itself.
-For instances a method ($m$) accepting input parameter ($i$) of type ($t$) mandates
+In traditional API, which are usually implemented in typed languages some temporal constraints are enforced by the type system itself.
+For instance, a method ($m$) accepting input parameter ($i$) of type ($t$) mandates
 that (at least one) method ($m'$) be invoked whose return value is of type ($t$).
@@
 Therefore enforcing temporal constraints through type system is ineffective in web APIs.
-Additionally temporal constraints are not entirely restricted to type definitions.
+Additionally, temporal constraints are not entirely restricted to type definitions.
 
@@
 manually writing formal constraints based on natural language text in API documents can be prohibitively time consuming and error prone~\cite{wu2013inferring,RubingerWEB10}. 
-For instance, Wu et al.~\cite{wu2013inferring} report that it took one person ten hours to browse the documentation of one method from a web service API, even before the person attempted to formalize the constraints on the method.
+For instance, Wu et al.~\cite{wu2013inferring} report that it took one person ten hours to browse the documentation of one method from a web API, even before the person attempted to formalize the constraints on the method.
 
@@
 to automatically infer formal temporal constraints. 
-However, inferring temporal constraints from the natural language text is challenging. 
 In particular, our approach addresses two major challenges to automatically infer specifications
@@
 
-First, existing NLP techniques are initially designed towards well-written news articles.
+First, existing NLP techniques are initially designed towards well-written generic news articles.
 In contrast, API documents are domain-specific documents and are often not well formed.
@@
 
-Second, after API documents are made amenable to existing NLP techniques, a method referenced in the natural language text must be identified in order to infer temporal constraints on the method but such method referencing is often implicit.
+Second, after API documents are made amenable to existing NLP techniques, a method referenced in the natural language text must be identified to infer temporal constraints on the method but such method referencing is often implicit.
 Consider the description sentence ``You must initiate a multipart upload before you can upload any part.''
@@
 \begin{itemize}
-	\item An NLP-based approach that effectively infers temporal constraints of method invocations. 
+	\item An NLP-based approach that effectively infers formal temporal constraints of method invocations. 
 	To the best of our knowledge, our approach is the first one to apply NLP for inferring temporal constraints from API documents.
@@
 Section~\ref{sec:evaluation} presents the evaluation of our approach.
-Section~\ref{sec:discussion} presents brief discussion and future work.
+Section~\ref{sec:discussion} presents brief discussion on the limitations and future work.
 Finally, Section~\ref{sec:conclusion} concludes.

### 2014-12-03 Draft/related.tex
Updated Draft for DSN
Updated Draft for DSN

--- 2014-03-17 Draft/related.tex
@@
 % Define temporal constraints distinction
+
 \textbf{Formal Specification}:
-Contracts have become a well-known mechanism for formally specifying functional behavior of the software. 
-Contracts specify the behavior in terms of conditions that must hold before/after and during the execution of the method.
+Contracts are a well-known mechanism for formally specifying functional behavior of the program. 
+Contracts specify the program behavior in terms of conditions that must hold before/after and/or during the execution of a method.
 A significant amount of work has been done in automated inference of contracts.
@@
 contracts is the most effective approach for formally specifying the constraints on an API.
-Since  our approach infers temporal constraint from API documents, we believe our approach can work in conjunction with existing approaches
-to infer a compressive set of specifications.
 
-Furthermore, another set of approaches exist that infer code-contract-like specifications (such as behavioral model, algebraic specifications, and exception specifications) either dynamically\cite{Henkel07discoveringdocumentation,Ghezzi:2009:SIB:1555001.1555057,Henkel:2008:DDA:1363102.1363105} or statically~\cite{Flanagan2001:HAA,Buse:2008:ADI:1390630.1390664} from source code and binaries.
-In contrast, the approach presented in this report infers specifications from the natural language text in API documents,
+Additionally, contracts are typically in the form of assertions on the state (member variables/ properties) of a program.
+In contrast, temporal constraints specify the ordering of method invocations and therefore are different.
+Furthermore, since \tool\ infers temporal constraint from API documents, we believe \tool\ can work in conjunction with existing approaches
+to infer a comprehensive set of program specifications.
+
+Furthermore, a different set of approaches exist that infer code-contract-like specifications (such as behavioral model, algebraic specifications, and exception specifications) either dynamically\cite{Henkel07discoveringdocumentation,Ghezzi:2009:SIB:1555001.1555057,Henkel:2008:DDA:1363102.1363105} or statically~\cite{Flanagan2001:HAA,Buse:2008:ADI:1390630.1390664} from source code and binaries.
+In contrast, \tool\ infers contracts from the natural language text in API documents,
 thus complementing these existing approaches when the source code or binaries of the API library is not available.
@@
 NLP techniques are being increasingly applied in the SE domain. 
-Tan et al.~\cite{TanSOSP07} were the first to apply Machine Learning (ML) and NLP on code comments to detect mismatches between the comments and the implementation.
-They rely on predefined rule templates targeted towards threading and lock related comments, and then apply machine learning to find comments following such rules.
+Tan et al.~\cite{TanSOSP07} were the first to apply ML and NLP on code comments to detect mismatches between the comments and the implementation.
+They rely on predefined rule templates targeted towards threading and lock related comments, and then apply ML-based approach to find comments following such rules.
 The constraints inferred by their approach are the restrictions imposed by the developer on the client code.
-In comparison, the temporal constraints inferred by our approach are the restriction imposed by the API library being used by the client code.
-Furthermore, approach presented in this report relies on generic natural language based templates thus relaxing the restriction on the style of the language used to describe specifications.
+In comparison, the temporal constraints inferred by \tool\ are the restriction imposed by the API library being used by the client code.
 
-Zhong et al.~\cite{zhong09SE} leverage machine learning and type information to infer constraints on resources.
+Zhong et al.~\cite{zhong09SE} also leverage ML along with type information to infer constraints on resources.
 Specifically, their approach infers resource constraints following template: resource creation methods followed by resource manipulation methods followed by resource release methods.
-However, temporal constraints may not be limited to such as template. 
-Furthermore, the performance of their approach is dependent on the quality of the training sets used for ML.
-In contrast, approach presented in this report is independent of such training set and thus can be easily extended to target respective problems addressed by them.
-Furthermore, the specifications inferred by their approach may ignore the explicit ordering information described in individual method descriptions as inferred by our approach.
+However, temporal constraints may not be limited to such templates. 
+Furthermore, the these approaches rely on specific templates for inferring constraints. In contrast, \tool\ works independent of such templates for identifying constraints.
+
+%In contrast, approach presented in this report is independent of such training set and thus can be easily extended to target respective problems addressed by them.
+Furthermore, the specifications inferred by their approach may ignore the explicit ordering information described in individual method descriptions as inferred by \tool\.
 
 Xiao et al.~\cite{XiaoFSE2012} and Slankas et al.~\cite{johnSlankasPASSAT13} use shallow parsing techniques to infer Access Control Policy (ACP) rules from natural language text in use cases.
-The use of shallow parsing techniques works satisfactorily on natural language texts in use cases, owing to well-formed structure of sentences in use case descriptions.
+The use of shallow parsing techniques works satisfactorily on natural language text in use cases, owing to relative well-formed structure of sentences in use case descriptions.
 In contrast, often the sentences in API documents are not well-formed.
@@
 
-Most closely related work to the approach presented here is our previous work on inferring parameter constraints from method descriptions in the API documents~\cite{pandita12:inferring}.
-\tool\ approach differs from the previous approach as follows.
-\tool\ approach addresses the problem of inferring temporal constraint, whereas the previous approach infers parameter constraints.
-\tool\ approach is a significant extension to the infrastructure used in the previous work in following areas.
-First, \tool\ approach introduces hybrid shallow parsing that relies both on parts-of-speech tags as well as Stanford-typed dependencies to construct intermediate representation, while the previous approach relies only on parts-of-speech tags.
-Second, the \tool\ approach introduces a new heuristics namely frequent phrase reduction to deal with the domain specific and ill-formed sentences in API documents.
+Pandita et al.~\cite{pandita12:inferring} proposed an NLP based approach on inferring parameter constraints from method descriptions in the API documents.
+\tool\ differs from the their work as follows.
+\tool\ addresses the problem of inferring temporal constraint, which is not addressed by the previous approach.
+\tool\ significantly extends the infrastructure used by Pandita et al.~\cite{pandita12:inferring} in following dimensions.
+First, \tool\ relies on ML to identify the temporal constraint sentences.
+The lower frequency of occurrence of temporal constraint sentences in comparison to parameter constraint sentences, make them harder to detect.
+Second, approach introduces hybrid shallow parsing that relies both on parts-of-speech tags as well as Stanford-typed dependencies to construct intermediate representation, while the previous approach relies only on parts-of-speech tags only.
 Finally, the \tool\ approach leverages the concept of semantic graphs constructed from class and method names in API to automatically infer the implicit method references in a sentence.
-In contrast, previous approach relies on predefined lists.
 
@@
 However, a developer has to manually annotate such directives.
-In contrast, our approach both identifies the sentences pertaining to temporal constraints and infers the temporal constraints automatically.
+In contrast, \tool\ both identifies the sentences pertaining to temporal constraints and infers the temporal constraints automatically.
 
-In next section, we briefly introduce the NLP techniques used by our approach.
+In next section, we briefly introduce the NLP techniques used by \tool.

### 2014-12-03 Draft/introduction.tex
updated Intro

@@
 
-The increasing reach of the internet has fueled the growth of web Application Programming Interfaces (API).
-The ProgrammableWeb reports that the web APIs have doubled from Jan 2012 to Oct 2013\footnote{\url{http://www.programmableweb.com/api-research}}.
-These APIs are being combined in interesting ways by application developers creating third-party applications using
-these APIs to provide value added service.
-For instance, many online stores leverage Paypal API to assist users with paying for the purchased commodities without actually
-providing financial information to the online store.
+%Application Programming Interface (API) facilateas software 
+%The increasing reach of the internet has fueled the growth of
+%web Application Programming Interfaces (API).
+%The ProgrammableWeb reports that the web APIs have doubled
+%from Jan 2012 to Oct 2013\footnote{\url{http://www.programmableweb.com/api-research}}.
 
-Unlike most traditional API libraries that are in the format of locally stored binary files and are programming language specific,
-web APIs are designed to leverage the web server and web browser architecture and the implementation is programming language agnostic.
-However, Web APIs like traditional APIs have rules or constraints governing the proper  use of the API that must be followed.
+%Application Programming Interface (API) facilitate creation of diverse and complex applications using 
+%these APIs to provide value added service.
+%For instance, many online stores leverage Paypal API to assist users with paying for the purchased commodities without actually
+%providing financial information to the online store.
+
+Application Programming Interface (API) has evolved from traditional libraries that are in the format of locally stored binary files and are programming language specific,
+to web APIs that are designed to leverage the web server and web browser architecture and the implementation is programming language agnostic.
+However, APIs (whether traditional or web-based) have some rules or constraints governing the proper use of the API that must be followed.
 One such type of constraints are temporal constraints [2], which are the allowed sequences of invocations of methods from the API.
-Non-compliance to such constraints can result in faulty applications that are unreliable to use and may even result in financial losses.
+Non-compliance to such constraints will often result in faulty applications that are unreliable to use and may even result in financial losses.
 
-In traditional API, which are usually implemented in typed languages some temporal constraints are enforced by the type system itself.
-For instance, a method ($m$) accepting input parameter ($i$) of type ($t$) mandates
-that (at least one) method ($m'$) be invoked whose return value is of type ($t$).
-Thus compliance of such constraints are easily enforced by compilers.
-In contrast to traditional API libraries, web APIs work on basic parameter data types such as \CodeIn{strings} and \CodeIn{numbers}.
-Therefore enforcing temporal constraints through type system is ineffective in web APIs.
-Additionally, temporal constraints are not entirely restricted to type definitions.
+%In traditional API, which are usually implemented in typed languages some temporal constraints are enforced by the type system itself.
+%For instance, a method ($m$) accepting input parameter ($i$) of type ($t$) mandates
+%that (at least one) method ($m'$) be invoked whose return value is of type ($t$).
+%Thus compliance to a part of these constraints are enforced by compilers. 
+%However temporal constraints are not entirely restricted to type definitions.
+%In contrast to traditional API libraries, web APIs work on basic parameter data types such as \CodeIn{strings} and \CodeIn{numbers}.
+%Therefore enforcing temporal constraints through type system is ineffective in web APIs.
+%\textbf{TODO plug that temporal constraints go beyond type system}
 
-Formal analysis tools such as model checker and runtime verifiers can assist in detection of the violations of the temporal constraints in web API clients as defects~\cite{lee2012towards}.
+Formal analysis tools such as model checker and runtime verifiers can assist in detection of the violations of the temporal constraints in API clients as defects~\cite{lee2012towards}.
 However, such tools typically accept formal representation of the temporal constraints for detecting violations.
@@
 as well as the temporal constraints in terms of other methods that must be invoked pre/post invoking that method.
-We observe that a non-trivial portion (roughly 12\%) of the sentences (constraint-describing sentences)
-in \amazonAPI\ documentation describe temporal constraints.
+%We observe that a non-trivial portion (roughly 12\%) of the sentences (constraint-describing sentences)
+%in \amazonAPI\ documentation describe temporal constraints.
+
+\textit{The goal of this work is to assist developers construct API clients that comply with
+	temporal constraints of the API through the inference and formalization of these constraints found in natural language text in API documents.}
 
@@
 For instance, Wu et al.~\cite{wu2013inferring} report that it took one person ten hours to browse the documentation of one method from a web API, even before the person attempted to formalize the constraints on the method.
+Also, the PDF version of the documentation for \amazonAPI\footnote{{\small \url{http://awsdocs.s3.amazonaws.com/S3/latest/s3-api.pdf}}} spans 278 pages.
 
-To reduce the manual effort, we propose \tool: a Natural Language Processing (NLP) based approach
+To reduce the manual effort, we propose \tool: a Machine Learning (ML) and Natural Language Processing (NLP) based approach
 to automatically infer formal temporal constraints. 
-In particular, our approach addresses two major challenges to automatically infer specifications
-from natural language text in API documents.
+We propose to employ ML as a means to identify temporal constraint sentences from rest and then use NLP techniques to infer formal constraints from identified sentences. 
+Besides the generic challenges of applying NLP techniques on software related artifacts~\cite{pandita12:inferring},
+our approach addresses two major challenges to automatically infer specifications from natural language text in API documents
 
-First, existing NLP techniques are initially designed towards well-written generic news articles.
-In contrast, API documents are domain-specific documents and are often not well formed.
-Furthermore, we observe that generic NLP techniques face problems with lengthy sentences (with a number of lexical tokens).
-Consider the description sentence ``All objects (including all object versions and Delete Markers) in the bucket must be deleted before the bucket itself can be delete.'' The length of the sentence may overwhelm an NLP parser, which then inaccurately extracts semantic relations between the words in the sentence.
-Our ICON approach includes a new technique called ``hybrid parsing'' to deal with the number of lexical tokens.
-Hybrid parsing automatically breaks lengthy sentences to smaller tractable sentences based on a function of parts-of-speech tags.
+First, classifying temporal constraint sentences is difficult.
+A keyword-based filtering or rule-based approach for identifying constraint sentences is often unsatisfactory, because the method names (and synonyms) are part of the keywords themselves, thus resulting an exponential number of keywords.
+To, address this challenge, we propose to train a classification model based on generic semantic and syntactic features instead of the keywords-based features.
 
-Second, after API documents are made amenable to existing NLP techniques, a method referenced in the natural language text must be identified to infer temporal constraints on the method but such method referencing is often implicit.
+Second, a method referenced in the natural language text must be identified to infer temporal constraints on the method but such method referencing is often implicit.
 Consider the description sentence ``You must initiate a multipart upload before you can upload any part.''
@@
 This paper makes the following main contributions:
-%However, all of these approaches rely on the availability of the source code that use API methods under investigation.
-Furthermore, these approaches are limited by both the quantity as well as quality of data set (source code) available.
-To address the limitation we propose to extend the natural language infrastructure developed previously~\cite{pandita12:inferring,pandita2013whyper} to focus specifically on the temporal constraints.
 
 \begin{itemize}
-	\item An NLP-based approach that effectively infers formal temporal constraints of method invocations. 
-	To the best of our knowledge, our approach is the first one to apply NLP for inferring temporal constraints from API documents.
+	\item An ML and NLP-based approach that effectively infers formal temporal constraints of method invocations. 
+	%To the best of our knowledge, our approach is the first one to apply NLP for inferring temporal constraints from API documents.
 	\item A prototype implementation of our approach based on extending the Stanford Parser~\cite{Klein03}, which is a natural language parser to derive the grammatical structure of sentences.
@@
 Finally, Section~\ref{sec:conclusion} concludes.
-
-%In particular, we focus on specific type of constraints namely temporal constraints.
-A generic temporal constraint is defined as \textit{an interpropositional constraint that communicates the ordering in time of events or states.} In terms of API method constraints, we interpret temporal constraints as \textit{`the allowed sequence of invocations of methods'}.
-For example, consider the following statement in \amazonAPI\ ``You must initiate a multipart upload before you can upload any part.'' We can interpret this sentence stating that a multipart-upload method must be invoked before invoking any part-upload method in the API.
-
-%Although, existing approaches focus on inferring method pre-post conditions (in terms of parameter constraints) using either program analysis techniques~\cite{Henkel07discoveringdocumentation,Ghezzi:2009:SIB:1555001.1555057,Henkel:2008:DDA:1363102.1363105,Flanagan2001:HAA,Buse:2008:ADI:1390630.1390664} or NLP~\cite{pandita12:inferring, wu2013inferring}, temporal constraints are beyond these parameter constraints.
-Temporal constraints, in general focus on rules related to orchestration of methods within an API rather than focusing on the requirements on the input parameters of these methods.
-
-%Apart from method specifications, Zhong et al.~\cite{zhong09SE} leverage machine learning and type information to infer constraints on resources based on phases of resource usage: creating, manipulating, and releasing.
-However, temporal constraints are not limited to resource usage.
-Furthermore, their approach fails to make the finer grained distinction on the ordering of the methods within a phase.
-For the description mentioned in previously, assuming that the method calls are associated with resource ``part'', both the methods referenced are logically associated with the creation phase of resource.
-Zhong et al.~\cite{zhong09SE} approach fails to make a distinction in ordering of such methods.
-In contrast our proposed approach leverages natural language processing to infer generic temporal constraints (not limited to resource related constraints) and also improves upon existing work for making finer grained distinction between ordering of methods within a phase of a resource.
-
-%First, relying just on type information will result in an incomplete list of temporal constraints. 
-%In traditional API, which are usually implemented in typed languages some temporal constraints are enforced by type system itself.
-%Voilations are easily detected by the IDE's
-%For instances a method ($m$) accepting input parameter ($i$) of type ($t$) mandates
-%that (at least one) method ($m'$) be invoked whose return value is of type ($t$).
-%However, using type system to detect temporal constraints in context of web APIs will result
-%in a lot of false positives as web APIs work only on basic types such as
-%\CodeIn{strings} and \CodeIn{numbers}.
-%Use of basic datatype by web-apis result in search space explosion.
-%Furthermore, we observed that temporal constraints re not limited to the type definitions
-% 
-%Our proposed approach extends the existing approaches to address the challenge.
-%
-%However, temporal constraints are not limited by the type definitions
-%(i.e, requirements on the type of input parameters),
-%and are currently expressed mostly in natural language in API documents,
-%as described in the example previously.
-%We propose to address the issue by augmenting the type definitions based temporal constraints
-%with the constraints inferred from the natural language text in API documents.
-%Furthermore, such constraints although valuable but are already checked by any advanced 
-%Integrated Development Environment(IDE) such as eclipse for a strongly typed language.

### 2014-12-06 Draft/evaluation.tex
updated table structure

@@
 
-\caption{Evaluation Results}
+\caption{Evaluation Results (Identification)}
 
-\begin{tabular}{lcccccccccccc}
+\begin{tabular}{rlccccccccc}
 \topline
-\headcol API & Mtds & Sen & Sen$_C$ & Sen$_{ICON}$ & TP & FP & FN & P(\%) & R(\%) & F$_S$(\%) & Spec$_{ICON}$ & Acc(\%)\\
+\headcol S. No. & Trainer	& P$_{wrd}$	& R$_{wrd}$	& F$_{wrd}$	& P$_{ftr}$	& R$_{ftr}$	& F$_{ftr}$	& P$_{\Delta}$	& R$_{\Delta}$	& F$_{\Delta}$	\\
 \midline 
-java.io & 662 & 2417 & 78 & 88 & 57 & 31 & 21 & 64.8 & 73.1 & 68.8 & 56 & 71.8\\ 
-\rowcol \amazonAPI & 51 & 1492 & 12 & 12 & 8 & 4 & 4 & 66.7 & 66.7 & 66.7 & 7 & 58.3\\ 
-\paypalAPI & 33	&	151 &  20 &  &  &  &  & &  &  &  & \\ 
-\rowcol Total & 746 & 4060 & 90 & 100 & 65 & 35 & 25 & 65.0$^*$ & 72.2$^*$ & 68.4$^*$ & 63 & 70.0$^*$\\ 
+		 1 		& 				& 662 	& 2417 		& 78 		& 88 		& 57 		& 31 		& 21 			& 64.8 			& 73.1 			\\ 
+\rowcol  2		& \amazonAPI 	& 662 	& 2417 		& 78 		& 88 		& 57 		& 31 		& 21 			& 64.8 			& 73.1 			\\ 
+		 3		& \paypalAPI 	& 662 	& 2417 		& 78 		& 88 		& 57 		& 31 		& 21 			& 64.8 			& 73.1 			\\ 
+\rowcol 		& Average 		& 662 	& 2417 		& 78 		& 88 		& 57 		& 31 		& 21 			& 64.8 			& 73.1 			\\ 
 \bottomlinec
 %----------------- END TABLE DATA ------------------------ 
-\multicolumn{13}{p{6.5in}}{\small
-$^*$ Column average;
-Mtds: Total no. of Methods; Sen: Total no. of Sentences; Sen$_C$: Total no. of constraint Sentences;
-Sen$_{ICON}$: Total no. of constraint Sentences identified by \tool; 
-TP: Total no. of True Positives; FP: Total no. of False Positives; FN: Total no. of False Negatives;
-P: Precision; R: Recall; F$_S$: F-Score; Acc: Accuracy
+\multicolumn{11}{p{6.5in}}{\small
+All values are average over 10-fold cross validation;
+P: Precision; R: Recall; F: F-Score;
+$_{wrd}$: No features used for training;
+$_{ftr}$: features used for training;
+$_{\Delta}$: improvement factor ($_{ftr}$ - $_{wrd}$)} \\ 
+\end{tabular}
+\label{tab:results}
+\end{center}
+\end{table*}
+
+\begin{table}
+\begin{center}
+
+\caption{Evaluation Results (Inference)}
+
+\begin{tabular}{lccccc}
+\topline
+\headcol 	API 		& Mtds 	& Sen 	& Sen$_C$ 	& Spec$_{ICON}$ 	& Acc(\%)\\
+\midline 
+			java.io 	& 662 	& 2417 	& 78 		& 56 				& 71.8\\ 
+\rowcol 	Amazon S3 REST 	& 51 	& 1492 	& 12		& 7 				& 58.3\\ 
+			Paypal REST 	& 33	& 151 	& 20 		& 					& \\ 
+\rowcol 	Total 		& 746 	& 4060 	& 90		& 63 				& 70.0$^*$\\ 
+\bottomlinec
+%----------------- END TABLE DATA ------------------------ 
+\multicolumn{6}{p{3.25in}}{\small
+$^*$ Average;
+Mtds: Total no. of Methods; Sen: Total no. of Sentences; Sen$_C$: Total no. of constraint Sentences; Acc: Accuracy
 Spec$_{ICON}$: Total no. of temporal constraint correctly identified by \tool;
@@
 \end{center}
-\end{table*}
+\end{table}
 

### 2014-12-06 Draft/approach.tex
updated formalism

@@
 Figure~\ref{fig:approachOverview} gives an overview of \tool\ approach.
-\tool\ consists of five major components: a preprocessor, a text-analysis engine, a semantic graph generator, constraint extractor, and a type analyzer.
+\tool\ consists of following major components: a preprocessor, a candidate identifier, a text-analysis engine, a semantic graph generator, constraint extractor, and a type analyzer.
 We next describe each component in detail.
@@
 \subsection{Constraint Extractor}
-\label{sub:SE}
+\label{sub:ConsExtract}
 
 Constraint Extractor is responsible for inferring temporal constraint from the classified constraint sentences.
-\tool\ uses the formalism proposed by Lo et al.~\cite{lo2009mining} (introduced in Section~\ref{sec:background})
-for formalizing the constraints. 
-\tool\ extends the operators by proposing two additional operators:
+
+Temporal constraints are expressed as temporal formulae involving: 1) \textit{Predicates} $\xi$ representing method calls and 2) \textit{Temporal operators}: backward ($\leftarrow$) \& forward ($\rightarrow$) and their negations $\xleftarrow{-}$ \& $\xrightarrow{-}$.
+We define following four constraints:
+
+%
+%
+%To express temporal constraints between two methods $\xi_1,\xi_2$, there two basic constatins 
+%
+%\tool\ uses the formalism proposed by Lo et al.~\cite{lo2009mining} (introduced in Section~\ref{sec:background})
+%for formalizing the constraints. 
+%\tool\ extends the operators by proposing two additional operators:
 
 \begin{enumerate}
-	\item Forward Prohibition Operator ($\xi_1 \xrightarrow{-} \xi_2$):
-	occurrence of $\xi_1$ cannot be followed by occurrence of $\xi_2$
-
-	\item Backward Prohibition Operator ($\xi_1 \xleftarrow{-} \xi_2$):
-	occurrence of $\xi_1$ cannot be preceded by the occurrence of $\xi_2$
+	\item \textit{Forward Operator ($\xi_1 \rightarrow \xi_2$)}: method call $\xi_1$ must be succeeded by method call $\xi_2$. 
+	\item \textit{Backward Operator ($\xi_1 \leftarrow \xi_2$)}: method call $\xi_1$ must be preceded by method call $\xi_2$.
+	\item \textit{Negative Forward Operator ($\xi_1 \xrightarrow{-} \xi_2$)}: method call $\xi_1$ cannot be succeeded by method call $\xi_2$
+	\item \textit{Negative Backward Operator ($\xi_1 \xleftarrow{-} \xi_2$)}: method call $\xi_1$ cannot be preceded by the method call of $\xi_2$
 \end{enumerate}
 
-The prohibition operators capture a different class of temporal constraints that cannot be
-expressed by the formulae constructed by previously proposed operators and their negations.
-For instance, the \textit{prohibition operators} seem to be negation of
-\textit{forward eventual operators} and \textit{backward eventual operators}.
-However, the negation of forward eventual operators is: not an invocation of $\xi_1$
-must be eventually followed by not an invocation of $\xi_2$. In contrast,
-\textit{prohibition operators} either negates antecedent or consequent but not both.
-In summary, we extended the formalism for temporal rules previously
-proposed by Lo et al.~\cite{lo2009mining} to express temporal constraints.
+%The prohibition operators capture a different class of temporal constraints that cannot be
+%expressed by the formulae constructed by previously proposed operators and their negations.
+%For instance, the \textit{prohibition operators} seem to be negation of
+%\textit{forward eventual operators} and \textit{backward eventual operators}.
+%However, the negation of forward eventual operators is: not an invocation of $\xi_1$
+%must be eventually followed by not an invocation of $\xi_2$. In contrast,
+%\textit{prohibition operators} either negates antecedent or consequent but not both.
+%In summary, we extended the formalism for temporal rules previously
+%proposed by Lo et al.~\cite{lo2009mining} to express temporal constraints.
 
+We next show how \tool\ identifies the terms of the constraint formula:
+
+\textbf{$\xi_1$}:
 \tool\ first identifies $\xi_1$ as the method whose description constraint sentence is part of.
@@
 
+\textbf{$\xi_2$}:
 \tool\ next identifies $\xi_2$.
@@
 
+\textbf{Temporal Operator}:
 \tool\ next identifies the direction (forward or backward) of the relationship by examining the tense of $\xi_2$ reference in the sentence.
@@
 For instance, the sentence in Figure~\ref{fig:standep} since ``deleted'' is in past tense and therefore operator is backward and the constraint is
-Delete Object $\xleftarrow{*}$ Delete Method.
+Delete Bucket $\leftarrow$ Delete Object.
 

### 2014-12-06 Draft/background.tex
updated formalism

@@
 
-Natural language is well suited for human communication, but converting natural language into unambiguous specifications that can be processed and understood by computers is difficult.
-However, research advances~\cite{Marneffe06LREC,Marneffe08COLING,Klein03,KleinNIPS03} have increased the accuracy of existing NLP techniques to annotate the grammatical structure of a sentence.
-These advances in NLP have inspired researchers/ practitioners~\cite{pandita12:inferring, pandita13:WHYPER, johnSlankasPASSAT13, XiaoFSE2012, thummalapentaICSE12} to adapt/apply NLP techniques to solve problems in SE domain.
+%Natural language is well suited for human communication, but converting natural language into unambiguous specifications that can be processed and understood by computers is difficult.
+%However, research advances~\cite{Marneffe06LREC,Marneffe08COLING,Klein03,KleinNIPS03} have increased the accuracy of existing NLP techniques to annotate the grammatical structure of a sentence.
+%These advances in NLP have inspired researchers/ practitioners~\cite{pandita12:inferring, pandita13:WHYPER, johnSlankasPASSAT13, XiaoFSE2012, thummalapentaICSE12} to adapt/apply NLP techniques to solve problems in SE domain.
 

### 2014-12-06 Draft/example.tex
updated formalism

@@
 \textit{``All objects (including all objects versions and Delete Markers) in the bucket must be deleted before the bucket itself can be deleted''}.
-Although the issue was fixed, one of the forum responses contained a recommendation for the inquisitor to switch to another product.
-Customer dissatisfaction, such as the one was caused by this issue with the delete bucket functionality, can lead to a loss in revenue.
+Although the issue was fixed, one of the forum responses recommended the inquisitor to switch to another product.
+Customer dissatisfaction caused by such issues with the delete bucket functionality, can lead to a loss in revenue.
 

### 2014-12-06 Draft/formal.tex
updated formalism

@@
-\subsection{Temporal Specifications}
-\label{sub:temporal}
-
-We next describe various classes of temporal constraints using formal temporal logic.
-Temporal logic is a system of rules and symbols that are used to express and reason about prepositions pertaining to time.
-We next present an extension to the temporal logic for API method invocation related rules proposed by Lo et al.~\cite{lo2009mining}
-
-\textbf{Method Invocation}: 
-We adapt the definition of events proposed by Lo et al.~\cite{lo2009mining} as method invocation.
-They define event as \textit{``any concrete or abstract representation of a program state''}. 
-We propose the notion of method invocation analogous to the events,
-where each method invocation is represented as a tuple which is an ordered set of strings. 
-A method invocation is captured as the Tuple \CodeIn{<T> <str1, str2, str3... >}, where \CodeIn{str1, str2, str3}... are string values,
-that belong to set of all strings.
-The method invocation tuple \CodeIn{<T>} captures information about the return value, enclosing type, name, and the parameter types of the method.
-Therefore a tuple \CodeIn{<T> <String, Bar, foo, Integer, Integer>} represents a method \CodeIn{foo} enclosed by the type \CodeIn{Bar},
-that accepts two parameters of type \CodeIn{Integer} and a return value of type \CodeIn{String}. 
-For better readability mnemonic representation of the preceding tuple is \CodeIn{String<-Bar.foo(Integer, Integer);}
-
-\textbf{Method Invocation Predicates}: We define method predicate as a predicate $E$ over method invocations.
-We reuse the notations proposed by Lo et al.~\cite{lo2009mining} $m \vdash \xi$ to denote that method invocation $m$ satisfies method predicate $\xi$.
-In context of \tool, method predicates combines a method name and the enclosing type with potential constraints on the return types and parameter types. 
-The predicates are modeled after \textit{equality constraints predicates}, and are represented as \CodeIn{\$i=sym}, where \CodeIn{i} is a non-negative integer and \CodeIn{sym} is the primitive string value and defined as: a method invocation $m$ satisfies a predicates \CodeIn{\$i=sym} iff \CodeIn{m[i]=sym}.
+%\subsection{Temporal Specifications}
+%\label{sub:temporal}
+%
+%We next describe various classes of temporal constraints using formal temporal logic.
+%Temporal logic is a system of rules and symbols that are used to express and reason about prepositions pertaining to time.
+%We next present an extension to the temporal logic for API method invocation related rules proposed by Lo et al.~\cite{lo2009mining}
+%
+%\textbf{Method Invocation}: 
+%We adapt the definition of events proposed by Lo et al.~\cite{lo2009mining} as method invocation.
+%They define event as \textit{``any concrete or abstract representation of a program state''}. 
+%We propose the notion of method invocation analogous to the events,
+%where each method invocation is represented as a tuple which is an ordered set of strings. 
+%A method invocation is captured as the Tuple \CodeIn{<T> <str1, str2, str3... >}, where \CodeIn{str1, str2, str3}... are string values,
+%that belong to set of all strings.
+%The method invocation tuple \CodeIn{<T>} captures information about the return value, enclosing type, name, and the parameter types of the method.
+%Therefore a tuple \CodeIn{<T> <String, Bar, foo, Integer, Integer>} represents a method \CodeIn{foo} enclosed by the type \CodeIn{Bar},
+%that accepts two parameters of type \CodeIn{Integer} and a return value of type \CodeIn{String}. 
+%For better readability mnemonic representation of the preceding tuple is \CodeIn{String<-Bar.foo(Integer, Integer);}
+%
+%
+%\textbf{Method Invocation Predicates}: We define method predicate as a predicate $E$ over method invocations.
+%We reuse the notations proposed by Lo et al.~\cite{lo2009mining} $m \vdash \xi$ to denote that method invocation $m$ satisfies method predicate $\xi$.
+%In context of \tool, method predicates combines a method name and the enclosing type with potential constraints on the return types and parameter types. 
+%The predicates are modeled after \textit{equality constraints predicates}, and are represented as \CodeIn{\$i=sym}, where \CodeIn{i} is a non-negative integer and \CodeIn{sym} is the primitive string value and defined as: a method invocation $m$ satisfies a predicates \CodeIn{\$i=sym} iff \CodeIn{m[i]=sym}.
 The simplest form of these predicates is of type \CodeIn{\$2 = sym} which refer to method invocations of name \CodeIn{sym}.
-
-\textbf{Temporal Operators}: Temporal constraints~\footnote{Temporal formulae} are constructed by combining method invocation predicates using temporal operators.
+%
+%\textbf{Temporal Operators}: Temporal constraints~\footnote{Temporal formulae} are constructed by combining method invocation predicates using temporal operators.
 Lo et al.~\cite{lo2009mining}, proposed the following temporal operators:
-
-\begin{enumerate}
-
-\item \textit{Forward Eventual Operator ($\xi_1 \xrightarrow{*} \xi_2$)}:
-occurrence of $\xi_1$ must be eventually followed by occurrence of $\xi_2$
-
-\item \textit{Backward Eventual Operator: ($\xi_1 \xleftarrow{*} \xi_2$)}:
-occurrence of $\xi_1$ must be preceded by occurrence of $\xi_2$
-
-\item \textit{Forward Alternation Operator ($\xi_1 \xrightarrow{a} \xi_2$)}:
-occurrence of $\xi_1$ must be eventually followed by occurrence of $\xi_2$ and $\xi_1$ cannot occur in between
-
-\item \textit{Backward Alternation Operator ($\xi_1 \xleftarrow{a} \xi_2$)}:
-occurrence of $\xi_1$ must be preceded by occurrence of $\xi_2$ and $\xi_1$ cannot occur in between
-\end{enumerate}
-
-\textbf{Quantification}: Quantification is used to introduce constraints involving parameter and return types of a method invocation.
+%
+%\begin{enumerate}
+%
+%\item \textit{Forward Eventual Operator ($\xi_1 \xrightarrow{*} \xi_2$)}:
+%occurrence of $\xi_1$ must be eventually followed by occurrence of $\xi_2$
+%
+%\item \textit{Backward Eventual Operator: ($\xi_1 \xleftarrow{*} \xi_2$)}:
+%occurrence of $\xi_1$ must be preceded by occurrence of $\xi_2$
+%
+%\item \textit{Forward Alternation Operator ($\xi_1 \xrightarrow{a} \xi_2$)}:
+%occurrence of $\xi_1$ must be eventually followed by occurrence of $\xi_2$ and $\xi_1$ cannot occur in between
+%
+%\item \textit{Backward Alternation Operator ($\xi_1 \xleftarrow{a} \xi_2$)}:
+%occurrence of $\xi_1$ must be preceded by occurrence of $\xi_2$ and $\xi_1$ cannot occur in between
+%\end{enumerate}
+%
+%\textbf{Quantification}: Quantification is used to introduce constraints involving parameter and return types of a method invocation.
 Formal representation of temporal constraints are obtained by varying: 1) the temporal operators allowed, b) the method-invocation predicates allowed, and 3) the degree of quantification allowed.

### 2014-12-06 Draft/introduction.tex
updated formalism

@@
 
-Application Programming Interface (API) has evolved from traditional libraries that are in the format of locally stored binary files and are programming language specific,
+Application Programming Interfaces (APIs) have evolved from traditional libraries that are in the format of locally stored binary files and are programming language specific,
 to web APIs that are designed to leverage the web server and web browser architecture and the implementation is programming language agnostic.
@@
 to automatically infer formal temporal constraints. 
-We propose to employ ML as a means to identify temporal constraint sentences from rest and then use NLP techniques to infer formal constraints from identified sentences. 
+We propose to first employ ML for identifying temporal constraint sentences and then use NLP techniques to infer formal constraints from the identified sentences. 
 Besides the generic challenges of applying NLP techniques on software related artifacts~\cite{pandita12:inferring},
@@
 First, classifying temporal constraint sentences is difficult.
-A keyword-based filtering or rule-based approach for identifying constraint sentences is often unsatisfactory, because the method names (and synonyms) are part of the keywords themselves, thus resulting an exponential number of keywords.
+A keyword-based filtering or rule-based approach for identifying constraint sentences is often unsatisfactory, because the method names (and synonyms) are part of the keywords themselves, thus resulting an large number of keywords.
+Furthermore, keywords often have confounding effects that inversely affects accuracy.
 To, address this challenge, we propose to train a classification model based on generic semantic and syntactic features instead of the keywords-based features.
@@
 
-In summary, our \tool\ approach leverages natural language description of API's to infer temporal constraints of method invocations.
+In summary, \tool\ approach leverages natural language description of API's to infer temporal constraints of method invocations.
 As our approach analyzes API documents in natural language, it can be reused independent of the programming language of an API library.

### 2014-12-06 Draft/related.tex
updated formalism

@@
 In contrast, temporal constraints specify the ordering of method invocations and therefore are different.
-Furthermore, since \tool\ infers temporal constraint from API documents, we believe \tool\ can work in conjunction with existing approaches
+Furthermore, since \tool\ infers temporal constraint from API documents, we envision \tool\ to work in conjunction with existing approaches
 to infer a comprehensive set of program specifications.
@@
 
-\textbf{NLP in SE}:
-NLP techniques are being increasingly applied in the SE domain. 
+\textbf{NLP in Software Engineering (SE)}:
+
+Research advances~\cite{Marneffe08COLING,KleinNIPS03} in the accuracy of existing NLP techniques have inspired researchers/ practitioners~\cite{pandita12:inferring, pandita13:WHYPER, johnSlankasPASSAT13, XiaoFSE2012, thummalapentaICSE12} to adapt/apply NLP techniques to solve problems in SE domain.
 Tan et al.~\cite{TanSOSP07} were the first to apply ML and NLP on code comments to detect mismatches between the comments and the implementation.

### 2014-12-07 Draft/abstract.tex
updated Intro
Updated RQ1

@@
 4000 human-annotated API sentences) with the average precision, recall, and F-score
-of 65.0\%, 72.2\%, and 68.4\%, respectively.
+of 77.0\%, 60.0\%, and 65.0\%, respectively.
 Furthermore, \tool\ also achieves an accuracy of 70\% in inferring 63 formal temporal constraints from these sentences.
 
-%Our approach also includes a novel
-%technique of identifying method references (improvement over keyword-based
-%techniques) in the natural language text by building domain
-%dictionaries systematically from API documents and generic English
-%dictionaries.
-%
-%
-%Existing software engineering tools can leverage
-%the inferred formal temporal constraints to effectively assist in development
-%and verification activities.
-
-%Temporal constraints of an Application Programming
-%Interface (API) are the allowed sequences of invocations
-%of methods from the API.
-%These constraints govern the secure and robust
-%operation of client software using the API.
-%Typically, these constraints are described in natural language text
-%of API documents and thus cannot be used by existing verification tools,
-%which typically accept only formal constraints.
-%Because manually writing temporal constraints based on
-%API documents can be prohibitively time consuming and error prone,
-%we propose \tool: a Natural Language Processing (NLP) based approach
-%to automatically infer temporal constraints.
-%In particular, our approach includes a novel technique to reduce the number of lexical tokens
-%as a way to make API documents amenable to existing NLP techniques
-%(which are typically designed to work on well-written news articles).
-%Our approach also includes a novel technique of identifying method references in
-%the natural language text by building domain dictionaries systematically
-%from API documents and generic English dictionaries.
-%To evaluate our approach, we apply \tool\ to infer temporal constraints from 
-%commonly used package \CodeIn{java.io} in the JDK API and from the \amazonAPI.
-%Our results show that \tool\ effectively identifies constraint sentences (from over 3900 API sentences) with the average precision, recall, and F-score of 65.0\%, 72.2\%, and 68.4\%, respectively.
-%Furthermore, \tool\ also achieves an accuracy of 70\% in inferring 63 temporal constraints from these sentences.
-
-% There are existing techniques that infer from API documents resource specifications 
-% (such as constraints based on phases: creating, manipulating, and releasing resources).
-% However, such techniques are limited to finding temporal specification of resources.
-% Furthermore, such techniques do not make a distinction between explicit ordering of methods
-% within each phases.
-
-% where do you loose precision and recall.
 \end{abstract}

### 2014-12-07 Draft/approach.tex
Updated RQ1

@@
 The goal of model construction is to use a small set of manually classified temporal constraint sentences of a representative API to construct a model to automatically classify the unlabeled sentences.
-Since \tool\ seeks to achieve a binary classification of the API sentences, we chose to train our model using na{\"i}ve Bayes classifier which is the simplest probabilistic classification methods  and is shown to be comparative other advanced classification methods given appropriate prepossessing~\cite{rennie2003tackling}.
+We can any of the standard off-the-shelf classifiers to train the model, since \tool\ seeks to achieve only a binary classification of the API sentences.
+For instance, model can be trained using na{\"i}ve Bayes classifier which is the simplest probabilistic classification methods  and is shown to be comparative other advanced classification methods given appropriate prepossessing~\cite{rennie2003tackling}.
 The model can be trained offline or else by the users of the approach if better accuracy is required for specific data.
@@
 Feature selection is an important factor for the accuracy any classification method.
-Particularly, for na{\"i}ve Bayes classifier which assumes each feature independently contributes towards the final probability of classification.
+For instance, na{\"i}ve Bayes classifier assumes each feature independently contributes towards the final probability of classification.
 In the simplest form, each word occurring in a sentence is considered as a feature.

### 2014-12-07 Draft/conclusion.tex
Updated RQ1

@@
 Our evaluation results show that \tool\ effectively identifies sentences describing
-temporal constraints with an average 65\% precision and 72\% recall,
+temporal constraints with an average 77\% precision and 60\% recall,
 from more than 4000 sentences in subject API documents.

### 2014-12-07 Draft/evaluation.tex
Updated RQ1

@@
 \subsection{Evaluation Setup} 
-We first manually annotated the sentences in the API documents of the two APIs.
-Two authors manually labeled each sentence in the API documentation as sentence containing 
+We first manually annotated the sentences in the API documents of the subject APIs.
+First two authors manually labeled each sentence in the Java API documentation as sentence containing 
 temporal constraints or not.
@@
 which denotes a statically significant agreement~\cite{carletta1996assessing}. 
+Based on the discussions first author annotated the rest of the subject APIs. 
 After the authors classified all the sentences, they 
 discussed with each other to reach a consensus on the sentences they classified differently. 
-We use these classified sentences as the golden set for calculating precision and recall.
+We use these classified sentences as the golden set for evaluating effectiveness of \tool.
+Table~\ref{tab:results} lists the subject statistics.
 
-To answer RQ1, we measure the number of true positives ($TP$), false positives ($FP$), true negative ($TN$), and false negatives ($FN$)
+To answer RQ1, we first measure the number of true positives ($TP$), false positives ($FP$), true negative ($TN$), and false negatives ($FN$)
 in identifying the constraint sentences by \tool.
@@
 of items that are true. \CodeIn{F-Score} is defined as the weighted harmonic mean of 
-\CodeIn{precision} and \CodeIn{recall}. Higher value of \CodeIn{precision}, \CodeIn{recall}, and \CodeIn{F-Score}
-are indicative of higher quality of the constraint statements inferred using 
-\tool. based on the calculation of $TP$, $FP$, $TN$, and $FN$ of \tool\ defined
+\CodeIn{precision} and \CodeIn{recall}.
+Based on the calculation of $TP$, $FP$, $TN$, and $FN$ of \tool\ defined
 previously we computed the \CodeIn{precision}, \CodeIn{recall}, and \CodeIn{F-Score} of \tool\ as follows:
@@
 \end{center}
+
+We then use these measures to identify relative effectiveness of \tool by executing multiple classifiers on the annotated sentences.
+We tested the classifiers using a stratified n-fold cross-validation approach,
+using 10 as the value n (10-fold) as recommended by Han et al.~\cite{han2006data}
+The cross validation ensures that every sentence is used for training and testing,
+thus producing low bias and variance.
+In particular, we execute the classifiers in two different configurations.
+First we execute the classifiers using the words in the sentnces as features and measure \CodeIn{precision}, \CodeIn{recall}, and \CodeIn{F-Score} as P$_{wrd}$, R$_{wrd}$, and F$_{wrd}$.
+We next execute the classifiers on the features proposed by \tool\ approach and measure \CodeIn{precision}, \CodeIn{recall}, and \CodeIn{F-Score} as P$_{ftr}$, R$_{ftr}$, and F$_{ftr}$.
+We next calculate relative gain in \CodeIn{precision}, \CodeIn{recall}, and \CodeIn{F-Score} as P$_{\Delta}$ (P$_{ftr}$- P$_{wrd}$), R$_{\Delta}$ (R$_{ftr}$ - R$_{wrd}$), and F$_{\Delta}$ (F$_{ftr}$ - F$_{wrd}$).
+Higher values of P$_{\Delta}$, R$_{\Delta}$, and F$_{\Delta}$ are are indicative of effectiveness of the constraint statements inferred using \tool.
 
@@
 \midline 
-		 1 		& 				& 662 	& 2417 		& 78 		& 88 		& 57 		& 31 		& 21 			& 64.8 			& 73.1 			\\ 
-\rowcol  2		& \amazonAPI 	& 662 	& 2417 		& 78 		& 88 		& 57 		& 31 		& 21 			& 64.8 			& 73.1 			\\ 
-		 3		& \paypalAPI 	& 662 	& 2417 		& 78 		& 88 		& 57 		& 31 		& 21 			& 64.8 			& 73.1 			\\ 
-\rowcol 		& Average 		& 662 	& 2417 		& 78 		& 88 		& 57 		& 31 		& 21 			& 64.8 			& 73.1 			\\ 
+1	& AdaBoost	& 0.52	& 0.81	& 0.61	& 0.7	& 0.78	& 0.74	& 0.18	& -0.03	& 0.13	\\
+\rowcol2	& NaiveBayes	& 0.49	& 0.67	& 0.56	& 0.74	& 0.65	& 0.69	& 0.25	& -0.02	& 0.13	\\
+3	& Balanced Winnow	& 0.77	& 0.76	& 0.76	& 0.78	& 0.77	& 0.77	& 0.01	& 0.01	& 0.01	\\
+\rowcol4	& Decision Tree	& 0.82	& 0.58	& 0.66	& 0.92	& 0.41	& 0.56	& 0.1	& -0.17	& -0.1	\\
+5	& Winnow	& 0.19	& 0.41	& 0.15	& 0.8	& 0.51	& 0.59	& 0.61	& 0.1	& 0.44	\\
+\rowcol6	& MaxEnt	& 0.69	& 0.48	& 0.55	& 0.76	& 0.46	& 0.56	& 0.07	& -0.02	& 0.01	\\
+	& Total	& 0.59	& 0.62	& 0.55	& 0.77	& 0.6	& 0.65	& 0.19	& -0.02	& 0.1	\\
 \bottomlinec
 %----------------- END TABLE DATA ------------------------ 
-\multicolumn{11}{p{6.5in}}{\small
+\multicolumn{11}{p{5in}}{\small
 All values are average over 10-fold cross validation;
@@
 \end{tabular}
-\label{tab:results}
+\label{tab:resultsRQ1}
 \end{center}
@@
 In this section, we quantify the effectiveness of \tool\ in identifying constraint sentences by answering RQ1.
-Table~\ref{tab:results} shows the effectiveness of \tool\ in identifying constraint sentences.
-Column ``API'' lists the names of the subject API. 
-Columns ``Mtds'' and ``Sen'' lists the number of methods and sentences in each subject API's.
-Column ``Sen$_C$'' list the number of manually identified constraint sentences.
-Column ``Sen$_{ICON}$'' lists the number of sentences identified by \tool\ as constraint sentences. 
-Columns ``TP'', ``FP'', ``TN'', and ``FN'' represent the number of \CodeIn{true positives}, \CodeIn{false positives}, \CodeIn{true negatives}, and \CodeIn{false negatives}, respectively. 
-Columns ``P(\%)'', ``R(\%)'', and ``F$_S$(\%)'' list percentage values of \CodeIn{precision}, \CodeIn{recall}, and \CodeIn{F-score} respectively. 
-Our results show that, out of 3,909 sentences, \tool\ effectively identifies constraint sentences with the average \CodeIn{precision}, \CodeIn{recall}, and \CodeIn{F-score} of 65.0\%, 72.2\%, and 68.4\%, respectively.
+Table~\ref{tab:results} shows the effectiveness of \tool\ in inferring temporal constraints from the identified constraint sentences using various classifiers.
+Column ``Trainer'' lists the names of the classifiers used to train the model for classifications in \tool.
+Columns P$_{wrd}$, R$_{wrd}$, and F$_{wrd}$ list the \CodeIn{precision}, \CodeIn{recall}, and \CodeIn{F-score} of classifiers trained without the features proposed by \tool.
+Columns P$_{ftr}$, R$_{ftr}$, and F$_{ftr}$ list the \CodeIn{precision}, \CodeIn{recall}, and \CodeIn{F-score} of classifiers trained with the features proposed by \tool.
+Finally, columns P$_{\Delta}$, R$_{\Delta}$, and F$_{\Delta}$ list the improvement factors in\CodeIn{precision}, \CodeIn{recall}, and \CodeIn{F-score} respectively.
+
+For our evaluation we used following well known classifiers: AdaBoost (or adaptive boosting), Na{\"i}ve Bayes, Winnow, Balanced Winnow, Decision Tree, and Max Entropy.
+We used Na{\"i}ve Bayes as the weaker classifier with AdaBoost.
+We used \CodeIn{Mallet}~\cite{mallet} implementation of these classifiers for our experiments.
+
+Our results show that, \tool\ effectively identifies constraint sentences with the average (across different classifiers) \CodeIn{precision}, \CodeIn{recall}, and \CodeIn{F-score} of 77.0\%, 60.0\%, and 65.0\%, respectively.
+Balanced Winnow performed best, with an average \CodeIn{precisoin} and \CodeIn{recall} of 78\% and 77\% respectively. 
+Furthermore, our results also show the features proposed by \tool\ improves the precision of classification algorithms by an average of 19\%, without significant reduction in the recall (average 2\%).
 
 %We next present an example to illustrate how \tool\ incorrectly identifies a sentence as a constraint sentence. \textbf{A example goes here}
-We next present an example to illustrate how \tool\ incorrectly identifies a sentence as a constraint sentence (producing false positives).
-For instance, consider the sentence ``\textit{This is done by flushing the stream and then closing the underlying output stream.}'' from  \CodeIn{close} method description from \CodeIn{PrintStream} class.
-\tool\ incorrectly identifies the action ``flush'' being performed before the action ``close''.
-However \tool\ fails to make the distinction that it happens internally (enforced in the body) in the method.
-\tool, thus incorrectly identifies the sentence as a constraint sentence.
-
-Another major source of FPs is the incorrect parsing of sentences by the underlying NLP infrastructure
-and/or inadequacy of generic dictionaries for synonym analysis.
-For instance, consider the sentence ``\textit{If this stream has an associated channel then the channel is closed as well.}''
-from the \CodeIn{close} method description from \CodeIn{FileOutputStream}.
-The sentence describes an effect that happens as a result of calling the \CodeIn{close} method and does not describe any temporal constraint.
-However, \tool\ annotates the sentence as a constraint sentence because underlying Wordnet dictionaries matches the word ``has'' as a synonym of ``get''.
-This incorrect matching in turn causes \tool\ to incorrectly annotate the sentence as constraint sentence
-because ``has'' is matched against \CodeIn(get) method in \CodeIn{FileOutputStream}.
-We observed 8 instances of previously described example in our results.
-
-If we manually fixed the Wordnet dictionaries to not match ``has'' and ``get'' as synonyms,
-our precision is further increased to 70.8\% effectively increasing the F-Score of \tool\ to 71.2\%.
-Although an easy fix, we refrained from including such modifications for reporting the results to stay true to our approach.
-In the future, we plan to investigate techniques to construct better domain dictionaries for software API.
-
-We next present an example to illustrate how \tool\ fails identify a constraint sentence (producing false negative).
-False negatives are undesirable in the context of our problem domain
-because they can mislead the users of \tool\ into believing that no other temporal constraint exists in the API documents.
-Furthermore, an overwhelming number of false negatives works against the practicality of \tool.
-For instance, consider the sentence ``\textit{This implementation of the PUT operation creates a copy of an object that is already stored in Amazon S3.}''
-from  \CodeIn{PUT Object-Copy} method description in \amazonAPI.
-The sentence describes the constraint that the object must already be stored (invocation of \CodeIn{PUT Object})
-before calling the current method.
-However, \tool cannot make the connection owing to the limitation of the semantic graphs that do not list ``already stored'' as a ``valid operation'' on object.  
-In the future, we plan to investigate techniques to further improve knowledge graphs to infer such implicit constraints.
-
-Another major source of false negatives (similar to reasons for false positives) is the incorrect parsing of sentences by the underlying NLP infrastructure.
-For instance, consider the sentence ``\textit{If any in-memory buffering is being done by the application (for example, by a BufferedOutputStream object),
-those buffers must be flushed into the FileDescriptor (for example, by invoking OutputStream.flush) before that data will be affected by sync.}''
-The sentence describes that the \CodeIn{OutputStream.flush()} must be invoked before invoking the current method if in-memory buffering is performed.
-However, the length and complexity in terms of number of clauses causes the underlying Stanford parser to inaccurately annotate the dependencies,
-which eventually results into incorrect classification.
-
-Overall, a significant number of false positives and false negatives will be reduced as the current NLP research advances the underlying NLP infrastructure.
-Furthermore, use of domain specific dictionaries as opposed to generic dictionaries
-sed in current prototype implementation will further improve the precision and recall of \tool.
+%We next present an example to illustrate how \tool\ incorrectly identifies a sentence as a constraint sentence (producing false positives).
+%For instance, consider the sentence ``\textit{This is done by flushing the stream and then closing the underlying output stream.}'' from  \CodeIn{close} method description from \CodeIn{PrintStream} class.
+%\tool\ incorrectly identifies the action ``flush'' being performed before the action ``close''.
+%However \tool\ fails to make the distinction that it happens internally (enforced in the body) in the method.
+%\tool, thus incorrectly identifies the sentence as a constraint sentence.   
+%
+%
+%Another major source of FPs is the incorrect parsing of sentences by the underlying NLP infrastructure
+%and/or inadequacy of generic dictionaries for synonym analysis.
+%For instance, consider the sentence ``\textit{If this stream has an associated channel then the channel is closed as well.}''
+%from the \CodeIn{close} method description from \CodeIn{FileOutputStream}.
+%The sentence describes an effect that happens as a result of calling the \CodeIn{close} method and does not describe any temporal constraint.
+%However, \tool\ annotates the sentence as a constraint sentence because underlying Wordnet dictionaries matches the word ``has'' as a synonym of ``get''.
+%This incorrect matching in turn causes \tool\ to incorrectly annotate the sentence as constraint sentence
+%because ``has'' is matched against \CodeIn(get) method in \CodeIn{FileOutputStream}.
+%We observed 8 instances of previously described example in our results.
+%
+%If we manually fixed the Wordnet dictionaries to not match ``has'' and ``get'' as synonyms,
+%our precision is further increased to 70.8\% effectively increasing the F-Score of \tool\ to 71.2\%.
+%Although an easy fix, we refrained from including such modifications for reporting the results to stay true to our approach.
+%In the future, we plan to investigate techniques to construct better domain dictionaries for software API. 
+%
+%We next present an example to illustrate how \tool\ fails identify a constraint sentence (producing false negative).
+%False negatives are undesirable in the context of our problem domain
+%because they can mislead the users of \tool\ into believing that no other temporal constraint exists in the API documents.
+%Furthermore, an overwhelming number of false negatives works against the practicality of \tool.
+%For instance, consider the sentence ``\textit{This implementation of the PUT operation creates a copy of an object that is already stored in Amazon S3.}''
+%from  \CodeIn{PUT Object-Copy} method description in \amazonAPI.
+%The sentence describes the constraint that the object must already be stored (invocation of \CodeIn{PUT Object})
+%before calling the current method.
+%However, \tool cannot make the connection owing to the limitation of the semantic graphs that do not list ``already stored'' as a ``valid operation'' on object.  
+%In the future, we plan to investigate techniques to further improve knowledge graphs to infer such implicit constraints. 
+%
+%Another major source of false negatives (similar to reasons for false positives) is the incorrect parsing of sentences by the underlying NLP infrastructure.
+%For instance, consider the sentence ``\textit{If any in-memory buffering is being done by the application (for example, by a BufferedOutputStream object),
+%those buffers must be flushed into the FileDescriptor (for example, by invoking OutputStream.flush) before that data will be affected by sync.}''
+%The sentence describes that the \CodeIn{OutputStream.flush()} must be invoked before invoking the current method if in-memory buffering is performed.
+%However, the length and complexity in terms of number of clauses causes the underlying Stanford parser to inaccurately annotate the dependencies,
+%which eventually results into incorrect classification. 
+%
+%Overall, a significant number of false positives and false negatives will be reduced as the current NLP research advances the underlying NLP infrastructure.
+%Furthermore, use of domain specific dictionaries as opposed to generic dictionaries
+%used in current prototype implementation will further improve the precision and recall of \tool.
 
@@
 In this section, we evaluate the effectiveness of \tool\ in inferring temporal constraints from the identified constraint sentences from API documents.Table~\ref{tab:results} shows the effectiveness of \tool\ in inferring temporal constraints from the identified constraint sentences.
-Column ``API'' lists the names of the subject API. 
+Column ``Trainer'' lists the names of the subject API. 
 Columns ``Mtds'' and ``Sen'' list the number of methods and sentences in each subject API's.

### 2014-12-07 Draft/abstract.tex
Laurie's Comments

@@
 In contrast, these constraints are typically described
-informally in natural language API documents and therefore are not amenable
+informally in natural language API documents, and therefore are not amenable
 to existing program analysis tools that require formal constraints.
@@
 temporal constraints of the API through the inference and formalization of these constraints found in natural language text in API documents.}
-Since, API documents are often verbose manually writing formal temporal constraints can be prohibitively time consuming and error prone.
+Since, API documents are often verbose, manually writing formal temporal constraints can be prohibitively time consuming and error prone.
 To address this issue,
 we propose \tool, a Machine Learning (ML) and Natural Language Processing (NLP) based
-approach to identify and infer formal temporal constraints.
+approach for identifying and inferring formal temporal constraints.
 To evaluate our approach, we apply \tool\ to infer and formalize temporal
-constraints from \amazonAPI, \paypalAPI\ and commonly used package \CodeIn{java.io} in the
+constraints from \amazonAPI, \paypalAPI\ and \CodeIn{java.io} package in the
 JDK API.

### 2014-12-07 Draft/introduction.tex
Laurie's Comments

@@
 to web APIs that are designed to leverage the web server and web browser architecture and the implementation is programming language agnostic.
-However, APIs (whether traditional or web-based) have some rules or constraints governing the proper use of the API that must be followed.
+However, APIs (whether traditional or web-based) have some constraints governing the proper use of the API that must be followed.
 One such type of constraints are temporal constraints [2], which are the allowed sequences of invocations of methods from the API.
@@
 
-Formal analysis tools such as model checker and runtime verifiers can assist in detection of the violations of the temporal constraints in API clients as defects~\cite{lee2012towards}.
-However, such tools typically accept formal representation of the temporal constraints for detecting violations.
-In contrast, temporal constraints are typically described in natural language text of API documents.
+Formal analysis tools, such as model checker and runtime verifiers can assist in detection of the violations of the temporal constraints in API clients as defects~\cite{lee2012towards}.
+These tools typically accept formal representation of the temporal constraints for detecting violations.
+However, temporal constraints are typically described in natural language text of API documents.
 Such documents are provided to client-code developers through an online access, or are shipped with the API wrapper code.
@@
 To reduce the manual effort, we propose \tool: a Machine Learning (ML) and Natural Language Processing (NLP) based approach
-to automatically infer formal temporal constraints. 
-We propose to first employ ML for identifying temporal constraint sentences and then use NLP techniques to infer formal constraints from the identified sentences. 
+to automatically identify and infer formal temporal constraints. 
+We propose to first employ ML for identifying temporal constraint sentences and then use NLP techniques to infer formal temporal constraints from the identified sentences.
+
 Besides the generic challenges of applying NLP techniques on software related artifacts~\cite{pandita12:inferring},
@@
 
-First, classifying temporal constraint sentences is difficult.
-A keyword-based filtering or rule-based approach for identifying constraint sentences is often unsatisfactory, because the method names (and synonyms) are part of the keywords themselves, thus resulting an large number of keywords.
+First, identifying temporal constraint sentences is difficult.
+A keyword-based filtering or rule-based approach for identifying constraint sentences is often unsatisfactory, because the method names (and synonyms) are part of the keywords themselves, thus resulting in a large number of keywords.
 Furthermore, keywords often have confounding effects that inversely affects accuracy.

### 2014-12-08 Draft/abstract.tex
updated based on Dr. Xie's Comments

@@
 informally in natural language API documents, and therefore are not amenable
-to existing program analysis tools that require formal constraints.
+to existing tools for checking formal temporal constraints.
 \textit{The goal of this work is to assist developers construct API clients that comply with 
-temporal constraints of the API through the inference and formalization of these constraints found in natural language text in API documents.}
-Since, API documents are often verbose, manually writing formal temporal constraints can be prohibitively time consuming and error prone.
+temporal constraints of the API through the inference and formalization of these constraints found in natural language API documents.}
+Since API documents are often verbose, manually identifying and writing formal temporal constraints can be prohibitively time-consuming and error-prone.
 To address this issue,
-we propose \tool, a Machine Learning (ML) and Natural Language Processing (NLP) based
-approach for identifying and inferring formal temporal constraints.
+we propose \tool: an approach based on Machine Learning (ML) and Natural Language Processing (NLP) for identifying and inferring formal temporal constraints.
 To evaluate our approach, we apply \tool\ to infer and formalize temporal
-constraints from \amazonAPI, \paypalAPI\ and \CodeIn{java.io} package in the
+constraints from \amazonAPI, \paypalAPI\ and the \CodeIn{java.io} package in the
 JDK API.
-Our results indicate that \tool\ is effective in identifying constraint sentences (from over
+Our results indicate that \tool\ is effective in identifying temporal
+constraint sentences (from over
 4000 human-annotated API sentences) with the average precision, recall, and F-score
-of 77.0\%, 60.0\%, and 65.0\%, respectively.
-Furthermore, \tool\ also achieves an accuracy of 70\% in inferring 63 formal temporal constraints from these sentences.
+of 79.0\%, 60.0\%, and 65.0\%, respectively.
+Furthermore, our evaluation also demonstrate that \tool\ achieves an accuracy of 70\% in inferring and formalizing 77 temporal constraints from these temporal constraint sentences.
 

### 2014-12-08 Draft/approach.tex
updated based on Dr. Xie's Comments

--- 2014-12-06 Draft/approach.tex
@@
 Figure~\ref{fig:approachOverview} gives an overview of \tool\ approach.
-\tool\ consists of following major components: a preprocessor, a candidate identifier, a text-analysis engine, a semantic graph generator, constraint extractor, and a type analyzer.
+\tool\ consists of following six major components: a preprocessor, a candidate identifier, a text-analysis engine, a semantic graph generator, constraint extractor, and a type analyzer.
+Additionally, there is an optional model trainer component and external NLP parser component.
 We next describe each component in detail.
@@
 
-The preprocessor accepts the API documents and extracts method descriptions from it.
+The preprocessor accepts the API documents and extracts method descriptions.
 In particular, the preprocessor extracts the following fields from the method descriptions: 
@@
 Different API documents may have different styles of presenting information to developers.
-This difference in style may also include the difference in the level of detail presented to developers.
-\tool\ thus relies on only basic fields that are generally available for API methods across different presentation styles.
+This difference in style may also include the difference in the level of the details presented to developers.
+\tool\ relies only on basic fields that are generally available for API methods across different presentation styles.
 
@@
 %However, this component can be implemented using any other existing NLP libraries or approaches.
-In particular, each sentence is annotated with: \textit{1)POS tags, 2)named-entity annotations, and 3)Stanford-typed dependencies.}
-For more details on these techniques and their application, please refer to ~\cite{Marneffe06LREC, Marneffe08COLING, pandita12:inferring, pandita13:WHYPER, thummalapentaICSE12}.
+In particular, each sentence is annotated with: \textit{1) POS tags, 2) named-entity annotations, and 3) Stanford-typed dependencies.}
+For more details on these techniques and their application, please to ~\cite{Marneffe06LREC, Marneffe08COLING, pandita12:inferring, pandita13:WHYPER, thummalapentaICSE12}.
 
@@
 Each word (occurs first) is followed by the Part-Of-Speech (POS) tag of the word (in green), which is further followed by the name of Stanford dependency connecting the actual word of the sentence to its predecessor.
-%For more details on Stanford-typed dependencies and POS tags, please refer to ~\cite{Marneffe06LREC,Marneffe08COLING}.
+From an implementation perspective, this component can be implemented using any existing NLP libraries or approaches such as Stanford Parser~\cite{SNLP1}.
 
@@
 The goal of model construction is to use a small set of manually classified temporal constraint sentences of a representative API to construct a model to automatically classify the unlabeled sentences.
-Since \tool\ seeks to achieve a binary classification of the API sentences, we chose to train our model using na{\"i}ve Bayes classifier which is the simplest probabilistic classification methods  and is shown to be comparative other advanced classification methods given appropriate prepossessing~\cite{rennie2003tackling}.
-The model can be trained offline or else by the users of the approach if better accuracy is required for specific data.
+From an implementation perspective, we can use any of the standard off-the-shelf classifiers to train the model, since \tool\ seeks to achieve only a binary classification of the API sentences.
+For instance, model can be trained using na{\"i}ve Bayes classifier which is the simplest probabilistic classification methods and is shown to be comparative to other advanced classification methods given appropriate prepossessing~\cite{rennie2003tackling}.
+The model can be trained offline or else by the users of the approach if better accuracy is desired for domain-specific data.
 
 Feature selection is an important factor for the accuracy any classification method.
-Particularly, for na{\"i}ve Bayes classifier which assumes each feature independently contributes towards the final probability of classification.
+%For instance, na{\"i}ve Bayes classifier assumes each feature independently contributes towards the final probability of classification.
 In the simplest form, each word occurring in a sentence is considered as a feature.
@@
 
-	\item \textbf{Sentence Type}: The context of sentence, whether the sentence appears as method summary, parameter summary, return value summary or exception/error summary as captured by pre-processor phase.
+	\item \textbf{Sentence Type}: The context of sentence, whether the sentence appears as method summary, parameter summary, return value summary, or exception/error summary as captured by pre-processor phase.
 The rationale is that a majority of the temporal constraint sentences are either summary or exception sentences.
@@
 	\item \textbf{Lemmatization}: The feature is the base form of a word.
-In linguistic lemmatization is the reduction of operational form of a word to its base form.
-For instance ``invoking'', ``invokes'', and ``invoked'' are all reduced to invoke.
+In linguistic, lemmatization is the reduction of operational form of a word to its base form.
+For instance, ``invoking'', ``invokes'', and ``invoked'' are all reduced to invoke.
 The rationale for reducing the words to base form is to reduce the size of the feature set that otherwise considers every word as an independent feature.
 
-	\item \textbf{Stopword Reduction}: In linguistics stop words are the frequently occurring words that can easily be ignored and are often considered noise, such as ``the'' , ``of'', ``to'' etc...
-The rationale for filtering the stop words is to reduce the size of feature set that otherwise considers such word as an independent feature but are often noise.
-Stop word list is further augmented by adding to them the words that occur exactly once in the training corpus to avoid over-fitting of the model to the training corpus.
+	\item \textbf{Stopword Reduction}: In linguistics, stopwords are the frequently occurring words that can be ignored and are often considered noise, such as ``the'' , ``of'', ``to'' etc...
+The rationale for filtering the stopwords is to reduce the size of feature set that otherwise considers such words (despite being noise) as an independent features.
+Stopword list is further augmented by adding to them the words that occur exactly once in the training corpus to avoid over-fitting of the model to the training corpus.
 
 	\item \textbf{Stanford Dependencies}: We add to the feature set by identifying the presence of specific Stanford typed dependencies pertaining to the temporal aspects of the sentence semantics.
-In particular we identify the presence of ``\textit{advcl}'', ``\textit{aux}'', ``\textit{auxpass}'', ``\textit{vmod}'', and ``\textit{tmod}''.
+In particular, we identify the presence of ``\textit{advcl}'', ``\textit{aux}'', ``\textit{auxpass}'', ``\textit{vmod}'', and ``\textit{tmod}''.
 For instance, the annotated sentence in Figure~\ref{fig:standep} contains both ``\textit{aux}'' and ``\textit{auxpass}'' dependencies.
@@
 As shown in figure~\ref{fig:standep} the word including is annotated with Stanford-typed dependencies ``dep'' that is a catch all dependency.
+A catch all dependency is selected by a parser when no other appropriate dependency can be selected.
 We thus break down the sentence into two smaller tractable sentences:
@@
 
-Table~\ref{tab:semanticTemplates} shows a list the semantic templates used in this phase.
-Column ``Template'' describes conditions where the template is applicable and Column ``Summary'' describes the action taken by our shallow parser when the template is applicable.
-All of these semantic templates are publicly available on our project website\footnote{\url{https://sites.google.com/site/temporalspec}}.
+Table~\ref{tab:semanticTemplates} lists the semantic templates used in this phase.
+Column ``Template'' describes conditions where the template is applicable and Column ``Summary'' describes the action taken by \tool\ when the template is applicable.
+%All of these semantic templates are publicly available on our project website\footnote{\url{https://sites.google.com/site/temporalspec}}.
 With respect to the previous example the template 3 \textit{( A noun phrase followed by another noun/pronoun/verb phrase in brackets)} is applicable.
@@
 
-\textbf{Stanford-typed Dependencies}: This phase is equivalent to the intermediate-representation technique described in Section~\ref{sub:SENLPback}.
+\textbf{Stanford-typed Dependencies}: After complex sentences (whenever applicable) have been broken to simple sentnces, this phase generates an intermediate (FOL) representation of the sentences.
+This phase is equivalent to the intermediate-representation technique described in Section~\ref{sub:SENLPback}.
 Figure~\ref{fig:FOLTree} is the FOL representation of the sentence  \textit{``All objects in the bucket must be deleted before the bucket itself can be deleted''}.
@@
 Ad hoc creation of semantic graph is prohibitively time consuming and may be error prone.
-We thus employ a systematic methodology (proposed previously by Pandita et al. ~\cite{pandita13:WHYPER}) to infer semantic graphs from API documents.
+We thus employ a systematic methodology (proposed by Pandita et al. ~\cite{pandita13:WHYPER}) to infer semantic graphs from API documents.
 

### 2014-12-08 Draft/background.tex
updated based on Dr. Xie's Comments

@@
 %In particular, this work proposes novel techniques on top of previously proposed techniques~\cite{pandita12:inferring, pandita13:WHYPER} to demonstrate the effectiveness of applying NLP on API documents.
-We next briefly introduce the techniques used in this work that have been grouped into broad categories.
+We next briefly introduce the techniques used in this work that have been grouped into two broad categories.
 We first introduce the core NLP techniques used in this work.
-We then introduce the SE specific NLP techniques proposed in related work~\cite{pandita12:inferring,pandita13:WHYPER} that are used in this work.
+We then introduce the SE specific NLP techniques proposed in related work~\cite{pandita12:inferring,pandita13:WHYPER} that are leveraged in this work.
 
@@
 The most commonly used technique is to train a classification parser over a previously known data set.
-Current state of the art approaches have demonstrated to be effective in classifying POS tags for well written news articles.
+Current state-of-the-art approaches have demonstrated to be effective in classifying POS tags for well-written news articles.
 
@@
 Also known as chunking, this technique divides a sentence into a constituent set of words (or phrases) that logically belong together (such as a Noun Phrase and Verb Phrase).
-Chunking thus further enhances the syntax of a sentence on top of POS tagging.
-Current state-of-the-art approaches can effectively classify phrases and clauses over well written news articles.
+Chunking further enhances the syntax of a sentence in addition to POS tagging.
+Current state-of-the-art approaches can effectively classify phrases and clauses over well-written news articles.
 
@@
 
-We next present Software Engineering (SE) specific NLP techniques.
+We next present SE specific NLP techniques.
 
@@
 
-Consider the word \CodeIn{POST} for instance. 
+For instance, consider the word \CodeIn{POST}. 
 The online Oxford dictionary\footnote{\url{http://oxforddictionaries.com/us/definition/american_english/post?q=POST}} has eight different definition of word \CodeIn{POST}, and none of them describes \CodeIn{POST} as an HTTP method\footnote{In HTTP vocabulary \CodeIn{POST} means: \textit{``Creates a new entry in the collection.
@@
 
-Noun Boosting identifies such words from the sentences based on a domain-specific dictionaries, and annotates them appropriately.
-The annotation assists the POS tagger to accurately annotate the POS tags of the words thus in turn increasing accuracy of advanced NLP techniques such as chunking and typed dependency annotation.
+Noun boosting identifies such words from the sentences based on a domain-specific dictionaries, and annotates them appropriately.
+The annotation assists the POS tagger to accurately annotate the POS tags of the words thus increasing accuracy of advanced NLP techniques such as chunking and typed dependency annotation.
 
 \textbf{Lexical Token Reduction}~\cite{pandita13:WHYPER}.
-These are a group of generic preprocessing heuristics to further improve the accuracy of core NLP techniques.
+These are a collection of generic preprocessing heuristics to further improve the accuracy of core NLP techniques.
 The accuracy of core NLP techniques is often inversely proportional to the number of lexical tokens in a sentence.
 Thus, the reduction in the number of lexical tokens greatly increases the accuracy of core NLP techniques. 
-In particular, following heuristics have been used in previous work to achieve the desired reduction of lexical tokens:
+In particular, following heuristics have been used in related work~\cite{pandita12:inferring,pandita13:WHYPER} to achieve the desired reduction of lexical tokens:
 
@@
 \item \textbf{Period Handling}.
-Besides marking the end of a sentence in simplistic English, the character period (`.') has other legal usages as well such as decimal representation (periods between numbers).
+Besides marking the end of a sentence in generic English, the character period (`.') has other legal usages as well, such as decimal representation (periods between numbers).
 Although legal, such usage hinder detection of sentence boundaries, thus causing core NLP techniques to return incorrect or imprecise results.
@@
 
-\item \textbf{Abbreviation Handling}. Natural-language sentences often consist of abbreviations mixed with text.
-This phenomenon can result in subsequent components to incorrectly parse a sentence.
+\item \textbf{Abbreviation Handling}. Natural-language sentences often consist of abbreviations interleaved with text.
+This interleaving may result in POS tagger to incorrectly parse a sentence.
 This heuristic finds such instances and annotates them as a single lexical unit.
@@
 Earlier researches have shown the adequacy using FOL for NLP related analysis tasks~\cite{Sinha2009,Sinha2010,pandita12:inferring}.
-In particular, WHYPER~\cite{pandita13:WHYPER} demonstrates the effectiveness of this technique, by constructing an intermediate representation generator based on shallow parsing~\cite{Branimir2000} techniques.
-The shallow parser itself is implemented as a sequence of cascading finite state machines based on the function of Stanford-typed dependencies~\cite{Marneffe06LREC,Marneffe08COLING,Klein03,KleinNIPS03}.
+Particularly, WHYPER~\cite{pandita13:WHYPER} demonstrates the effectiveness of this technique, by constructing an intermediate representation generator from semantically annotated sentences. 
+The component is implemented as a sequence of cascading finite state machines based on the function of annotated Stanford-typed dependencies~\cite{Marneffe06LREC,Marneffe08COLING,Klein03,KleinNIPS03}.
 

### 2014-12-08 Draft/conclusion.tex
updated based on Dr. Xie's Comments

@@
 Our evaluation results show that \tool\ effectively identifies sentences describing
-temporal constraints with an average 77\% precision and 60\% recall,
+temporal constraints with an average 79\% precision and 60\% recall,
 from more than 4000 sentences in subject API documents.
 Furthermore, \tool\ also achieved an accuracy of
-70\% in inferring 63 formal temporal constraints from these sentences.
+70\% in inferring 77 formal temporal constraints from these sentences.

### 2014-12-08 Draft/evaluation.tex
updated based on Dr. Xie's Comments

@@
 
-We used the API documents of the following two libraries as subjects for our evaluation. 
+We used the API documents of the following three libraries as subjects for our evaluation. 
 \begin{itemize}
@@
 	\item\CodeIn{java.io} : is one of a popular packages in \CodeIn{Java} programming language.
-The package provides APIs for system input and output through data streams, serialization and the file system, which are one of the fundamental functionalities provided by a programming language.
+The package provides APIs for system input and output through data streams, serialization and the file system, which are one of the fundamental functionalities provided by any programming language.
 \end{itemize}
-We chose \CodeIn{Amazon S3}, \CodeIn(PayPal) and \CodeIn{java.io} APIs as our subjects because they are popular and contain decent documentation.
+We chose \CodeIn{Amazon S3}, \CodeIn{PayPal payment}, and \CodeIn{java.io} APIs as our subjects because they are popular and contain decent documentation.
 
@@
 which denotes a statically significant agreement~\cite{carletta1996assessing}. 
-Based on the discussions first author annotated the rest of the subject APIs. 
 After the authors classified all the sentences, they 
@@
 Table~\ref{tab:results} lists the subject statistics.
+Based on the discussions with regards to annotation of \CodeIn{java.io} API, first author annotated the rest of the subject APIs.
 
@@
 
-We then use these measures to identify relative effectiveness of \tool by executing multiple classifiers on the annotated sentences.
+We then use these measures to identify relative effectiveness of \tool\ by executing multiple classifiers on the annotated sentences.
 We tested the classifiers using a stratified n-fold cross-validation approach,
-using 10 as the value n (10-fold) as recommended by Han et al.~\cite{han2006data}
+using 10 as the value n (10-fold) as recommended by Han et al.~\cite{han2006data}.
 The cross validation ensures that every sentence is used for training and testing,
@@
 In particular, we execute the classifiers in two different configurations.
-First we execute the classifiers using the words in the sentnces as features and measure \CodeIn{precision}, \CodeIn{recall}, and \CodeIn{F-Score} as P$_{wrd}$, R$_{wrd}$, and F$_{wrd}$.
-We next execute the classifiers on the features proposed by \tool\ approach and measure \CodeIn{precision}, \CodeIn{recall}, and \CodeIn{F-Score} as P$_{ftr}$, R$_{ftr}$, and F$_{ftr}$.
+First we executed the classifiers using the words in the sentences as features and measure \CodeIn{precision}, \CodeIn{recall}, and \CodeIn{F-Score} as P$_{wrd}$, R$_{wrd}$, and F$_{wrd}$.
+We next executed the classifiers on the features proposed by \tool\ approach and measure \CodeIn{precision}, \CodeIn{recall}, and \CodeIn{F-Score} as P$_{ftr}$, R$_{ftr}$, and F$_{ftr}$.
 We next calculate relative gain in \CodeIn{precision}, \CodeIn{recall}, and \CodeIn{F-Score} as P$_{\Delta}$ (P$_{ftr}$- P$_{wrd}$), R$_{\Delta}$ (R$_{ftr}$ - R$_{wrd}$), and F$_{\Delta}$ (F$_{ftr}$ - F$_{wrd}$).
-Higher values of P$_{\Delta}$, R$_{\Delta}$, and F$_{\Delta}$ are are indicative of effectiveness of the constraint statements inferred using \tool.
+Higher values of P$_{\Delta}$, R$_{\Delta}$, and F$_{\Delta}$ are indicative of effectiveness of the constraint statements inferred using the features proposed by \tool\ approach.
 
@@
 			1	& AdaBoost			& 0.52	& 0.81	& 0.61	& 0.7	& 0.78	& 0.74	& 0.18	& -0.03	& 0.13	\\
-\rowcol2	& NaiveBayes	& 0.49	& 0.67	& 0.56	& 0.74	& 0.65	& 0.69	& 0.25	& -0.02	& 0.13	\\
+\rowcol		2	& NaiveBayes		& 0.49	& 0.67	& 0.56	& 0.74	& 0.65	& 0.69	& 0.25	& -0.02	& 0.13	\\
 			3	& Balanced Winnow	& 0.77	& 0.76	& 0.76	& 0.78	& 0.77	& 0.77	& 0.01	& 0.01	& 0.01	\\
-\rowcol4	& Decision Tree	& 0.82	& 0.58	& 0.66	& 0.92	& 0.41	& 0.56	& 0.1	& -0.17	& -0.1	\\
+\rowcol		4	& Decision Tree		& 0.82	& 0.58	& 0.66	& 0.92	& 0.41	& 0.56	& 0.1	& -0.17	& -0.1	\\
 			5	& Winnow			& 0.19	& 0.41	& 0.15	& 0.8	& 0.51	& 0.59	& 0.61	& 0.1	& 0.44	\\
-\rowcol6	& MaxEnt	& 0.69	& 0.48	& 0.55	& 0.76	& 0.46	& 0.56	& 0.07	& -0.02	& 0.01	\\
-	& Total	& 0.59	& 0.62	& 0.55	& 0.77	& 0.6	& 0.65	& 0.19	& -0.02	& 0.1	\\
+\rowcol		6	& MaxEnt			& 0.69	& 0.48	& 0.55	& 0.76	& 0.46	& 0.56	& 0.07	& -0.02	& 0.01	\\
+			7	& c45				& 0.78	& 0.4	& 0.52	& 0.82	& 0.59	& 0.67	& 0.04	& 0.19	& 0.15	\\
+\midline
+			& Average			& 0.61	& 0.59	& 0.54	& 0.79	& 0.6	& 0.65	& 0.18	& 0.01	& 0.11	\\
 \bottomlinec
@@
 \rowcol 	Amazon S3 REST 	& 51 	& 1492 	& 12		& 7 				& 58.3\\ 
-			Paypal REST 	& 33	& 151 	& 20 		& 					& \\ 
-\rowcol 	Total 		& 746 	& 4060 	& 90		& 63 				& 70.0$^*$\\ 
+			Paypal REST 	& 33	& 151 	& 20 		& 14				& 70.0\\ 
+\rowcol 	Total 			& 746 	& 4060 	& 110		& 77 				& 70.0$^*$\\ 
 \bottomlinec
@@
 In this section, we quantify the effectiveness of \tool\ in identifying constraint sentences by answering RQ1.
-Table~\ref{tab:results} shows the effectiveness of \tool\ in inferring temporal constraints from the identified constraint sentences using various classifiers.
+Table~\ref{tab:resultsRQ1} shows the effectiveness of \tool\ in inferring temporal constraints from the identified constraint sentences using various classifiers.
 Column ``Trainer'' lists the names of the classifiers used to train the model for classifications in \tool.
@@
 Columns P$_{ftr}$, R$_{ftr}$, and F$_{ftr}$ list the \CodeIn{precision}, \CodeIn{recall}, and \CodeIn{F-score} of classifiers trained with the features proposed by \tool.
-Finally, columns P$_{\Delta}$, R$_{\Delta}$, and F$_{\Delta}$ list the improvement factors in\CodeIn{precision}, \CodeIn{recall}, and \CodeIn{F-score} respectively.
+Finally, columns P$_{\Delta}$, R$_{\Delta}$, and F$_{\Delta}$ list the improvement factors in \CodeIn{precision}, \CodeIn{recall}, and \CodeIn{F-score} respectively.
 
-For our evaluation we used following well known classifiers: AdaBoost (or adaptive boosting), Na{\"i}ve Bayes, Winnow, Balanced Winnow, Decision Tree, and Max Entropy.
+For our evaluation we used following well known classifiers: AdaBoost (or adaptive boosting), Na{\"i}ve Bayes, Winnow, Balanced Winnow, Decision Tree, Max Entropy, and c45.
 We used Na{\"i}ve Bayes as the weaker classifier with AdaBoost.
@@
 
-Our results show that, \tool\ effectively identifies constraint sentences with the average (across different classifiers) \CodeIn{precision}, \CodeIn{recall}, and \CodeIn{F-score} of 77.0\%, 60.0\%, and 65.0\%, respectively.
+Our results show that, \tool\ effectively identifies constraint sentences with the average (across different classifiers) \CodeIn{precision}, \CodeIn{recall}, and \CodeIn{F-score} of 79.0\%, 60.0\%, and 65.0\%, respectively.
 Balanced Winnow performed best, with an average \CodeIn{precisoin} and \CodeIn{recall} of 78\% and 77\% respectively. 
-Furthermore, our results also show the features proposed by \tool\ improves the precision of classification algorithms by an average of 19\%, without significant reduction in the recall (average 2\%).
+Furthermore, our results also show the features proposed by \tool\ improves the precision of classification algorithms by an average of 18\%.
+There is also a slight increase in the recall (average 1\% gain).
 
@@
 %
-%We next present an example to illustrate how \tool\ fails identify a constraint sentence (producing false negative).
-%False negatives are undesirable in the context of our problem domain
-%because they can mislead the users of \tool\ into believing that no other temporal constraint exists in the API documents.
-%Furthermore, an overwhelming number of false negatives works against the practicality of \tool.
-%For instance, consider the sentence ``\textit{This implementation of the PUT operation creates a copy of an object that is already stored in Amazon S3.}''
-%from  \CodeIn{PUT Object-Copy} method description in \amazonAPI.
-%The sentence describes the constraint that the object must already be stored (invocation of \CodeIn{PUT Object})
-%before calling the current method.
-%However, \tool cannot make the connection owing to the limitation of the semantic graphs that do not list ``already stored'' as a ``valid operation'' on object.  
-%In the future, we plan to investigate techniques to further improve knowledge graphs to infer such implicit constraints. 
+
 %
@@
 
-Another, major cause of failure for \tool\ in inferring temporal constraints from sentences is the failure to identify the sentence as a constraint sentences at the first place (false negatives).
+We next present an example to illustrate how \tool\ fails infer constraints from a constraint sentence.
+%False negatives are undesirable in the context of our problem domain
+%because they can mislead the users of \tool\ into believing that no other temporal constraint exists in the API documents.
+%Furthermore, an overwhelming number of false negatives works against the practicality of \tool.
+For instance, consider the sentence ``\textit{This implementation of the PUT operation creates a copy of an object that is already stored in Amazon S3.}''
+from  \CodeIn{PUT Object-Copy} method description in \amazonAPI.
+The sentence describes the constraint that the object must already be stored (invocation of \CodeIn{PUT Object})
+before calling the current method.
+However, \tool cannot make the connection owing to the limitation of the semantic graphs that do not list ``already stored'' as a ``valid operation'' on object.  
+In the future, we plan to investigate techniques to further improve knowledge graphs to infer such implicit constraints.
+
+%Another, major cause of failure for \tool\ in inferring temporal constraints from sentences is the failure to identify the sentence as a constraint sentences at the first place (false negatives).
 Overall, accuracy of \tool\ can be significantly improved by lowering the false negative rate in identifying the constraint sentences.
@@
 
-In summary, we demonstrate that \tool\ effectively identifies constraint sentences (from over 3900 API sentences) with the average precision, recall, and F-score of 65.0\%, 72.2\%, and 68.4\% respectively.
-Furthermore, we also show that \tool\ infers temporal constraints from the constraint sentences an average accuracy of 70\%.
-Furthermore, also provide discussion that a false positives rate and false negatives rate can be further improved by improving the underlying NLP infrastructure.
+In summary, we demonstrate that \tool\ effectively identifies constraint sentences (from over 3900 API sentences) with the average precision, recall, and F-score of 79.0\%, 60\%, and 65\% respectively.
+We also show that \tool\ infers temporal constraints from the constraint sentences an average accuracy of 70\%.
+Furthermore, also provide discussion on why \tool\ does not or incorrectly infers temporal constraints.
 Finally, we provide a comparison of the temporal constraints inferred from natural language description against the temporal constraints enforced by a type system.
@@
 Threats to external validity primarily include the degree to which the subject documents used in our evaluation are representative of true practice.
-To minimize the threat, we used API documents of two different API's: JDK \CodeIn{java.io} and \amazon.
+To minimize the threat, we used API documents of three different API's: JDK \CodeIn{java.io}, \amazonAPI, \paypalAPI.
 On one hand, Java is a widely used programming language and \CodeIn{java.io} and is one of the main packages.
-In contrast, \amazon\ provides HTTP based access to online storage allowing developers the freedom to write clients applications in any programming language.
-Furthermore, the difference in the functionalities provided by the two API's also address the issue of over fitting our approach to a particular type of API.
+In contrast, \amazonAPI\ provides HTTP based access to online storage allowing developers the freedom to write clients applications in any programming language.
+Finally, \paypalAPI\ provides a REST support for online financial transactions.
+The difference in the functionalities provided by the three API's also address the issue of over-fitting our approach to a particular type of API.
 The threat can be further reduced by evaluating our approach on more subjects API's.
@@
 To reduce the threat, we manually inspected all the constraints inferred against the API method descriptions in our evaluation.
-Furthermore, we ensured that the results were individually verified and agreed upon by two authors, using the \CodeIn{cohen kappa}~\cite{carletta1996assessing} score to statistically measure the inter-rater agreement.
+Furthermore, we ensured that the results were individually verified and agreed upon by two authors independently.

### 2014-12-08 Draft/example.tex
updated based on Dr. Xie's Comments

@@
 Through the example, we demonstrate that developers often ignore the temporal constraints of an API described in the documentation.
-We suspect the reason for this phenomena is that the documentation is often verbose and the information is distributed across various pages.
-For instance, the PDF version of the documentation for \amazonAPI\footnote{{\small \url{http://awsdocs.s3.amazonaws.com/S3/latest/s3-api.pdf}}} spans 278 pages.
+We suspect the reason for this behavior is that the documentation is often verbose and the information is distributed across various pages.
+%For instance, the PDF version of the documentation for \amazonAPI\footnote{{\small \url{http://awsdocs.s3.amazonaws.com/S3/latest/s3-api.pdf}}} spans 278 pages.
 Often developers may not have time (and/or patience) to go through all the documentation and may overlook some temporal constraints of the API,
@@
 
-Consider the question asked in \textit{Stack Overflow}~\footnote{{\small \url{http://stackoverflow.com/}}} as shown in Figure~\ref{fig:Stackoverflow}.
+Consider the question asked in \textit{Stack Overflow}~\footnote{{\small \url{http://stackoverflow.com/questions/27267/delete-amazon-s3-buckets}}} as shown in Figure~\ref{fig:Stackoverflow}.
 Stack Overflow is an online question and answer forum for professional and enthusiast programmers.
@@
 The inquisitor complains about an issue in the delete bucket functionality of the \CodeIn{S3Fox}.
-The \CodeIn{S3Fox} developers overlooked the constraints in \amazon, causing the issue.
+The \CodeIn{S3Fox} developers overlooked the constraints in \amazonAPI\ developer documents, causing the issue.
 The API document pertaining to the  delete bucket functionality states that before deleting the bucket, the objects in the buckets must be deleted.
@@
 Although the issue was fixed, one of the forum responses recommended the inquisitor to switch to another product.
-Customer dissatisfaction caused by such issues with the delete bucket functionality, can lead to a loss in revenue.
+Customer dissatisfaction caused by such issues with the delete bucket functionality can lead to a loss in revenue.
 
@@
 %Thus, there is need for an approach to automatically translate the constraints described in natural language into a more formal notation.
-In next section, we briefly discuss the related work pertinent to our approach.
+We next briefly discuss the related work pertinent to our approach.

### 2014-12-08 Draft/introduction.tex
updated based on Dr. Xie's Comments

@@
 
-Application Programming Interfaces (APIs) have evolved from traditional libraries that are in the format of locally stored binary files and are programming language specific,
-to web APIs that are designed to leverage the web server and web browser architecture and the implementation is programming language agnostic.
-However, APIs (whether traditional or web-based) have some constraints governing the proper use of the API that must be followed.
+Application Programming Interfaces (APIs) facilitates software reuse
+by providing standardized mechanism to access API components.
+However, APIs have some constraints governing the proper use of the API that must be followed.
 One such type of constraints are temporal constraints [2], which are the allowed sequences of invocations of methods from the API.
 Non-compliance to such constraints will often result in faulty applications that are unreliable to use and may even result in financial losses.
+
+%Recently, the increasing reach of the internet has fueled the growth of
+%web API's, which are designed to leverage the web server and web
+%browser architecture and ar eprogramming language agnostic.
 
@@
 However, temporal constraints are typically described in natural language text of API documents.
-Such documents are provided to client-code developers through an online access, or are shipped with the API wrapper code.
-For a method under consideration, an API document may describe both the constraints on the method parameters
+Such documents are provided to client-code developers through an online access, or are shipped with the API code.
+For a method under consideration, API document may describe both the constraints on the method parameters
 as well as the temporal constraints in terms of other methods that must be invoked pre/post invoking that method.
@@
 \textit{The goal of this work is to assist developers construct API clients that comply with
-	temporal constraints of the API through the inference and formalization of these constraints found in natural language text in API documents.}
+	temporal constraints of the API through the inference and formalization of these constraints found in natural language API documents.}
 
 Although natural language API description can be manually converted into formal constraints,
-manually writing formal constraints based on natural language text in API documents can be prohibitively time consuming and error prone~\cite{wu2013inferring,RubingerWEB10}. 
-For instance, Wu et al.~\cite{wu2013inferring} report that it took one person ten hours to browse the documentation of one method from a web API, even before the person attempted to formalize the constraints on the method.
-Also, the PDF version of the documentation for \amazonAPI\footnote{{\small \url{http://awsdocs.s3.amazonaws.com/S3/latest/s3-api.pdf}}} spans 278 pages.
+manually identifying and writing formal constraints based on natural language text in API documents can be prohibitively time-consuming and error-prone~\cite{wu2013inferring,RubingerWEB10}. 
+%For instance, Wu et al.~\cite{wu2013inferring} report that it took one person ten hours to browse the documentation of one method from a web API, even before the person attempted to formalize the constraints on the method.
+For instance, the PDF version of the documentation for \amazonAPI\footnote{{\small \url{http://awsdocs.s3.amazonaws.com/S3/latest/s3-api.pdf}}} spans 278 pages describing 51 methods.
 
 To reduce the manual effort, we propose \tool: a Machine Learning (ML) and Natural Language Processing (NLP) based approach
-to automatically identify and infer formal temporal constraints. 
+for identifying and inferring formal temporal constraints. 
 We propose to first employ ML for identifying temporal constraint sentences and then use NLP techniques to infer formal temporal constraints from the identified sentences.
@@
 First, identifying temporal constraint sentences is difficult.
-A keyword-based filtering or rule-based approach for identifying constraint sentences is often unsatisfactory, because the method names (and synonyms) are part of the keywords themselves, thus resulting in a large number of keywords.
-Furthermore, keywords often have confounding effects that inversely affects accuracy.
-To, address this challenge, we propose to train a classification model based on generic semantic and syntactic features instead of the keywords-based features.
+A naive approach is to perform a keyword-based search.
+For instance, consider the sentences from \paypalAPI: 1) ``\textit{Use this call to refund a completed payment.}'' 2) ``\textit{Use this call to complete a payment.}''
+Sentence 1 indicates the temporal constraint that a payment must be completed before the refund call is initiated.
+In contrast, sentence 2 is a descriptive statement about complete payment method.
+Since these sentences are not significantly different in terms of words (sentence 1 contains refund), a simple keyword based approach will fail to distinguish between the two.  
+Another problem with keyword based search is that the method names (and synonyms) are part of the keywords themselves, thus resulting in a large number of keywords to be searched.
+The large number of keywords often negatively affects accuracy.
+%Furthermore, keywords often have confounding effects that inversely affects accuracy.
+To address this challenge, we propose to train a classification model based on generic semantic and syntactic features instead of the keywords-based features.
 
 Second, a method referenced in the natural language text must be identified to infer temporal constraints on the method but such method referencing is often implicit.
-Consider the description sentence ``You must initiate a multipart upload before you can upload any part.''
+Consider the description sentence from \amazonAPI: ``\textit{You must initiate a multipart upload before you can upload any part.}''
 In this sentence, phrases ``multipart upload'' and ``upload any part'' refer to individual methods in the API.
@@
 Additionally, our approach complements existing mining-based approaches~\cite{buse2012synthesizing, thummalapenta07parseweb, Wang:2013:MSR, Zhong:2009:MMR} that partially address the problem by mining for common usage patterns among client code reusing the API.
+Our results indicate that \tool\ is effective in identifying temporal
+constraint sentences (from over
+4000 human-annotated API sentences) with the average precision, recall, and F-score
+of 79.0\%, 60.0\%, and 65.0\%, respectively.
+Furthermore, our evaluation also demonstrate that \tool\ achieves an accuracy of 70\% in inferring 77 formal temporal constraints from these sentences.
 This paper makes the following main contributions:

### 2014-12-08 Draft/related.tex
updated based on Dr. Xie's Comments

--- 2014-12-03 Draft/related.tex
@@
 Additionally, contracts are typically in the form of assertions on the state (member variables/ properties) of a program.
-In contrast, temporal constraints specify the ordering of method invocations and therefore are different.
-Furthermore, since \tool\ infers temporal constraint from API documents, we believe \tool\ can work in conjunction with existing approaches
-to infer a comprehensive set of program specifications.
+In contrast, temporal constraints specify the ordering of method invocations, therefore are different.
+Furthermore, since \tool\ infers temporal constraints from API documents, we envision \tool\ to work in conjunction with existing approaches
+to infer a comprehensive formal specification.
 
-Furthermore, a different set of approaches exist that infer code-contract-like specifications (such as behavioral model, algebraic specifications, and exception specifications) either dynamically\cite{Henkel07discoveringdocumentation,Ghezzi:2009:SIB:1555001.1555057,Henkel:2008:DDA:1363102.1363105} or statically~\cite{Flanagan2001:HAA,Buse:2008:ADI:1390630.1390664} from source code and binaries.
+A different set of approaches exist that infer code-contract-like specifications (such as behavioral model, algebraic specifications, and exception specifications) either dynamically\cite{Henkel07discoveringdocumentation,Ghezzi:2009:SIB:1555001.1555057,Henkel:2008:DDA:1363102.1363105} or statically~\cite{Flanagan2001:HAA,Buse:2008:ADI:1390630.1390664} from source code and binaries.
 In contrast, \tool\ infers contracts from the natural language text in API documents,
-thus complementing these existing approaches when the source code or binaries of the API library is not available.
+thus complementing existing approaches when the source code or binaries of the API library is not available.
 
-\textbf{NLP in SE}:
-NLP techniques are being increasingly applied in the SE domain. 
+\textbf{NLP in Software Engineering (SE)}:
+
+Research advances~\cite{Marneffe08COLING,KleinNIPS03} in the accuracy of existing NLP techniques have inspired researchers and practitioners~\cite{pandita12:inferring, pandita13:WHYPER, johnSlankasPASSAT13, XiaoFSE2012, thummalapentaICSE12} to adapt and(/or) apply NLP techniques to solve problems in SE domain.
 Tan et al.~\cite{TanSOSP07} were the first to apply ML and NLP on code comments to detect mismatches between the comments and the implementation.
@@
 
-Zhong et al.~\cite{zhong09SE} also leverage ML along with type information to infer constraints on resources.
-Specifically, their approach infers resource constraints following template: resource creation methods followed by resource manipulation methods followed by resource release methods.
-However, temporal constraints may not be limited to such templates. 
+Zhong et al.~\cite{zhong09SE} also leverage ML along with type information to infer constraints on resources from API documents.
+Specifically, their approach infers resource constraints following the template - ``\textit{resource creation methods} followed by \textit{resource manipulation methods} followed by \textit{resource release methods}''.
+However, temporal constraints are often not be limited to such template. 
 Furthermore, the these approaches rely on specific templates for inferring constraints. In contrast, \tool\ works independent of such templates for identifying constraints.
@@
 Xiao et al.~\cite{XiaoFSE2012} and Slankas et al.~\cite{johnSlankasPASSAT13} use shallow parsing techniques to infer Access Control Policy (ACP) rules from natural language text in use cases.
-The use of shallow parsing techniques works satisfactorily on natural language text in use cases, owing to relative well-formed structure of sentences in use case descriptions.
-In contrast, often the sentences in API documents are not well-formed.
-Additionally, their approaches do not deal with programming keywords or identifiers, which are often mixed with the method descriptions in API documents.
-
-Pandita et al.~\cite{pandita12:inferring} proposed an NLP based approach on inferring parameter constraints from method descriptions in the API documents.
-\tool\ differs from the their work as follows.
+In contrast, \tool\ approach works with API documents.
+%The use of shallow parsing techniques works satisfactorily on natural language text in use cases, owing to relative well-formed structure of sentences in use case descriptions.
+%In contrast, often the sentences in API documents are not well-formed.
+%Additionally, their approaches do not deal with programming keywords or identifiers, which are often mixed with the method descriptions in API documents.
+Pandita et al.~\cite{pandita12:inferring} proposed an NLP-based approach on inferring parameter constraints from method descriptions in the API documents. \tool\ differs from their work as follows.
 \tool\ addresses the problem of inferring temporal constraint, which is not addressed by the previous approach.
@@
 The lower frequency of occurrence of temporal constraint sentences in comparison to parameter constraint sentences, make them harder to detect.
-Second, approach introduces hybrid shallow parsing that relies both on parts-of-speech tags as well as Stanford-typed dependencies to construct intermediate representation, while the previous approach relies only on parts-of-speech tags only.
+Second, \tool\ approach introduces hybrid shallow parsing that relies both on parts-of-speech tags as well as Stanford-typed dependencies to construct intermediate representation, while the previous approach relies only on parts-of-speech tags.
 Finally, the \tool\ approach leverages the concept of semantic graphs constructed from class and method names in API to automatically infer the implicit method references in a sentence.

### 2014-12-09 Draft/evaluation.tex
Updated Intro based on Dr. Xie's structure, Minor changes on Evaluation
=> Discuss motivations of the problem
=> Discuss existing approaches to this problem and their limitations
(e.g., "keyword-based filtering or rule-based approach") [in the
current writing, you never explicitly talk about what these existing
approaches are like]
=> Discuss challenges faced by these existing approaches (here you
don't need to include those sentences in the end as in the current
writing "To address this challenge..."
=> Start with your paragraph with "To address these challenges along
with general challenges

@@
 
-In summary, we demonstrate that \tool\ effectively identifies constraint sentences (from over 3900 API sentences) with the average precision, recall, and F-score of 79.0\%, 60\%, and 65\% respectively.
+In summary, we demonstrate that \tool\ effectively identifies constraint sentences (from over 4000 API sentences) with the average precision, recall, and F-score of 79.0\%, 60\%, and 65\% respectively.
 We also show that \tool\ infers temporal constraints from the constraint sentences an average accuracy of 70\%.

### 2014-12-09 Draft/introduction.tex
Updated Intro based on Dr. Xie's structure, Minor changes on Evaluation
=> Discuss motivations of the problem
=> Discuss existing approaches to this problem and their limitations
(e.g., "keyword-based filtering or rule-based approach") [in the
current writing, you never explicitly talk about what these existing
approaches are like]
=> Discuss challenges faced by these existing approaches (here you
don't need to include those sentences in the end as in the current
writing "To address this challenge..."
=> Start with your paragraph with "To address these challenges along
with general challenges

@@
 \label{sec:introduction}
-
-%Application Programming Interface (API) facilateas software 
-%The increasing reach of the internet has fueled the growth of
-%web Application Programming Interfaces (API).
-%The ProgrammableWeb reports that the web APIs have doubled
-%from Jan 2012 to Oct 2013\footnote{\url{http://www.programmableweb.com/api-research}}.
-
-%Application Programming Interface (API) facilitate creation of diverse and complex applications using 
-%these APIs to provide value added service.
-%For instance, many online stores leverage Paypal API to assist users with paying for the purchased commodities without actually
-%providing financial information to the online store.
 
@@
 
-%Recently, the increasing reach of the internet has fueled the growth of
-%web API's, which are designed to leverage the web server and web
-%browser architecture and ar eprogramming language agnostic.
-
-%In traditional API, which are usually implemented in typed languages some temporal constraints are enforced by the type system itself.
-%For instance, a method ($m$) accepting input parameter ($i$) of type ($t$) mandates
-%that (at least one) method ($m'$) be invoked whose return value is of type ($t$).
-%Thus compliance to a part of these constraints are enforced by compilers. 
-%However temporal constraints are not entirely restricted to type definitions.
-%In contrast to traditional API libraries, web APIs work on basic parameter data types such as \CodeIn{strings} and \CodeIn{numbers}.
-%Therefore enforcing temporal constraints through type system is ineffective in web APIs.
-%\textbf{TODO plug that temporal constraints go beyond type system}
-
-Formal analysis tools, such as model checker and runtime verifiers can assist in detection of the violations of the temporal constraints in API clients as defects~\cite{lee2012towards}.
+Formal analysis tools, such as model checker and runtime verifiers 
+can assist in detection of the violations of the temporal constraints
+in API clients as defects~\cite{lee2012towards}.
 These tools typically accept formal representation of the temporal constraints for detecting violations.
@@
 
-\textit{The goal of this work is to assist developers construct API clients that comply with
-	temporal constraints of the API through the inference and formalization of these constraints found in natural language API documents.}
-
 Although natural language API description can be manually converted into formal constraints,
@@
 
-To reduce the manual effort, we propose \tool: a Machine Learning (ML) and Natural Language Processing (NLP) based approach
+\textit{The goal of this work is to assist developers construct API clients that comply with
+	temporal constraints of the API through the inference and formalization of these constraints found in natural language API documents.}
+
+First step towards formalizing temporal constraints is to identify the sentences describing such constraints.
+A naive approach to identify the constraint sentences is to perform keyword-based search on API documents.
+However, the effectiveness of such approach is limited by the quality of the keywords used.
+Furthermore, sentences involving temporal constraints oftentimes may not have have uniquely identifiable keywords.
+
+For instance, consider the sentences from \paypalAPI:
+1) ``\textit{Use this call to complete a payment.}'' 
+2) ``\textit{Use this method to refund a completed payment.}''
+Sentence 1 indicates the temporal constraint that a payment must be completed before the refund call is initiated.
+In contrast, sentence 2 is a descriptive statement about complete payment method.
+Since these sentences are not significantly different in terms of words, a simple keyword-based search will fail to distinguish between the two. 
+Another problem with keyword-based search is that the method names (and synonyms) are part of the keywords themselves, thus resulting in a large number of keywords to be searched.
+The large number of keywords further negatively affects accuracy.
+
+Even after a sentence has been identified as a constraint sentence, an approach has to infer the references to the method in the sentences, which may often not be implicit.
+Consider Sentence 2 in preceding paragraph.
+The phrase \textit{``completed payment''} refers to the ``Execute Payment'' method in the API.
+
+To address these issues, we propose \tool: an approach based on Machine Learning (ML) and Natural Language Processing (NLP)
 for identifying and inferring formal temporal constraints.
@@
 
-Besides the generic challenges of applying NLP techniques on software related artifacts~\cite{pandita12:inferring},
-our approach addresses two major challenges to automatically infer specifications from natural language text in API documents
-
-First, identifying temporal constraint sentences is difficult.
-A naive approach is to perform a keyword-based search.
-For instance, consider the sentences from \paypalAPI: 1) ``\textit{Use this call to refund a completed payment.}'' 2) ``\textit{Use this call to complete a payment.}''
-Sentence 1 indicates the temporal constraint that a payment must be completed before the refund call is initiated.
-In contrast, sentence 2 is a descriptive statement about complete payment method.
-Since these sentences are not significantly different in terms of words (sentence 1 contains refund), a simple keyword based approach will fail to distinguish between the two.  
-Another problem with keyword based search is that the method names (and synonyms) are part of the keywords themselves, thus resulting in a large number of keywords to be searched.
-The large number of keywords often negatively affects accuracy.
-%Furthermore, keywords often have confounding effects that inversely affects accuracy.
-To address this challenge, we propose to train a classification model based on generic semantic and syntactic features instead of the keywords-based features.
-
-Second, a method referenced in the natural language text must be identified to infer temporal constraints on the method but such method referencing is often implicit.
-Consider the description sentence from \amazonAPI: ``\textit{You must initiate a multipart upload before you can upload any part.}''
-In this sentence, phrases ``multipart upload'' and ``upload any part'' refer to individual methods in the API.
-Identifying these phrases as method-invocation instances requires domain dictionaries.
-Ad-hoc construction of such dictionaries is prohibitively resource intensive and error-prone.
-To address this challenge, we propose to build domain dictionaries systematically from API documents and generic English dictionaries.
+A ML based approach for identifying the temporal constraint sentences addresses the limitations of keyword-based search by automatically learning patterns of temporal constraint sentences.
+Furthermore, we propose to use a combination of words, syntax (parts of speech) of a sentence, and semantics (relationship between words) of a sentence as the features for learning patterns.
+This combination allows our approach to make a finer grained distinction between the example sentences described earlier.
+To identify the phrases as method-invocation instances, we propose to build domain dictionaries systematically from API documents and generic English dictionaries.
 

### 2014-12-09 Draft/abstract.tex
Laurie's comments

@@
 to existing tools for checking formal temporal constraints.
-\textit{The goal of this work is to assist developers construct API clients that comply with 
+\textit{The goal of this work is to assist developers to construct API clients that comply with 
 temporal constraints of the API through the inference and formalization of these constraints found in natural language API documents.}

### 2014-12-09 Draft/approach.tex
Laurie's comments

@@
 		\includegraphics[scale=0.45]{approach.eps}
-	\caption{Overview of \tool\ approach}
+	\caption{Overview of the \tool\ approach}
 	\label{fig:approachOverview}
@@
 from the method descriptions in API Documents.
-Figure~\ref{fig:approachOverview} gives an overview of \tool\ approach.
+Figure~\ref{fig:approachOverview} gives an overview of the \tool\ approach.
 \tool\ consists of following six major components: a preprocessor, a candidate identifier, a text-analysis engine, a semantic graph generator, constraint extractor, and a type analyzer.
 Additionally, there is an optional model trainer component and external NLP parser component.
+
+First, the preprocessor accepts API documents and preprocesses the sentences in the method description.
+%such as annotating sentence boundaries and reducing lexical tokens.
+Next, an NLP parser annotates the syntax and semantics of preprocessed sentences.   
+The annotated sentences are accepted by candidate identifier component to classify temporal constraint sentences,
+using the model trained by the model trainer component.
+The text-analysis engine further transforms the identified constraint sentences into the first-order-logic (FOL) representation.
+Finally, the constraint extractor leverages the semantic graphs to infer temporal constraints from the FOL representation of a sentence.
+The type analyzer component infers temporal constraints encoded in the type system of a language by analyzing the API methods parameter and return types.
 We next describe each component in detail.
-
-%The preprocessor accepts API documents and preprocesses the sentences in the method description,
-%such as annotating sentence boundaries and reducing lexical tokens.
-%The text-analysis engine accepts the pre-processed sentences and annotates them using an NLP parser.
-%The text-analysis engine further transforms the annotated sentences into the first-order-logic (FOL) representation.
-%The semantic graph generator accepts the API documents and generates the semantic graphs that are leveraged by constraint extractor component.
-%The type analyzer component infers temporal constraints encoded in the type system of a language by analyzing the API methods parameter and return types.
-%Finally, the constraint extractor leverages the semantic graphs to infer temporal constraints from the FOL representation of a sentence.
-%We next describe each component in detail.
 
@@
 In particular, the preprocessor extracts the following fields from the method descriptions: 
-1) \textit{Summary of the API method},
-2) \textit{Summary and type information of parameters of the API method}, 
-3) \textit{Summary and type information of return values of the method}, and
-4) \textit{Summary and type information of exceptions thrown (or errors returned) by the methods}.
+1) Summary of the API method,
+2) Summary and type information of parameters of the API method, 
+3) Summary and type information of return values of the method, and
+4) Summary and type information of exceptions thrown (or errors returned) by the methods.
 
@@
 After extracting desired information, the natural language text is further preprocessed to be analyzed by subsequent components.
-The preprocessing steps are required to increase the accuracy of core NLP techniques (described in Section~\ref{sub:CoreNLPback}) that are used in the subsequent phases of \tool\ approach.
+The preprocessing steps are required to increase the accuracy of core NLP techniques (described in Section~\ref{sub:CoreNLPback}) that are used in the subsequent phases of the \tool\ approach.
 The preprocessor first employs the heuristics listed under lexical token reduction, as introduced in Section~\ref{sub:SENLPback}.
@@
 
-The NLP parser accepts the pre-processed documents and annotates every sentence in each document using core NLP techniques described in Section~\ref{sub:CoreNLPback}.
+The NLP parser accepts the pre-processed documents and annotates every sentence in each document using core NLP techniques~\cite{Marneffe06LREC, Marneffe08COLING, pandita12:inferring, pandita13:WHYPER, thummalapentaICSE12} described in Section~\ref{sub:CoreNLPback}.
 %From an implementation perspective, we chose the Stanford parser~\cite{Manning:01}.
@@
 In particular, each sentence is annotated with: \textit{1) POS tags, 2) named-entity annotations, and 3) Stanford-typed dependencies.}
-For more details on these techniques and their application, please to ~\cite{Marneffe06LREC, Marneffe08COLING, pandita12:inferring, pandita13:WHYPER, thummalapentaICSE12}.
 
@@
 This component accepts the annotated sentence from the previous component,
-then using a trained model classifies whether a sentence describes a temporal constraint or not. We next describe the model construction.
+then using a trained ML model classifies whether a sentence describes a temporal constraint or not. We next describe the model construction.
 
-The goal of model construction is to use a small set of manually classified temporal constraint sentences of a representative API to construct a model to automatically classify the unlabeled sentences.
-From an implementation perspective, we can use any of the standard off-the-shelf classifiers to train the model, since \tool\ seeks to achieve only a binary classification of the API sentences.
+The goal of model construction is to use a small set of manually classified temporal constraint sentences of a representative API classify the unlabeled sentences as being temporal constraints or not.
+From an implementation perspective, we can use any of the standard off-the-shelf classifiers to train the ML model, since \tool\ seeks to achieve only a binary classification of the API sentences.
 For instance, model can be trained using na{\"i}ve Bayes classifier which is the simplest probabilistic classification methods and is shown to be comparative to other advanced classification methods given appropriate prepossessing~\cite{rennie2003tackling}.
-The model can be trained offline or else by the users of the approach if better accuracy is desired for domain-specific data.
+The ML model can be trained offline or else by the users of the approach if better accuracy is desired for domain-specific data.
 
@@
 In the simplest form, each word occurring in a sentence is considered as a feature.
-However, such an approach may lead to overly specific models, and therefore \tool\ approach employs preprocessing for generic features.
-We next describe the features we chose for training our model along with the rationale for selecting such features.
+However, such an approach may lead to overly specific ML models, and therefore the \tool\ approach extracts generic features from sentences.
+We next describe the features we chose for training our ML model along with the rationale for selecting such features.
 
@@
 
+	\item \textbf{Sentence Structure}: The feature is the ordered sequence of chunking tags~\cite{Klein03,KleinNIPS03} in a sentence.
+Chunking seeks to divide a sentence into a constituent set of words (or phrases) that logically belong together (such as a Noun Phrase and Verb Phrase).
+Thus chunking captures the structure of a sentence.
+Rationale for selecting ordered sequence of chunking tags is to incorporate structure of a sentence as a feature.
+
 \end{enumerate}
 
-We use this feature set to train a classier to perform binary classification of temporal constraint sentence vs other sentences.
-The rationale of using ML based approach as opposed to a rule based approach is because: 1) rule-writing requires domain expertise, 2) rules-writing tends to quickly become ad hoc thus requires greater effort to generate generic rules, and 3) ML classifiers have shown to scale well with large volumes of data.
+We use the described feature set to train a classier to perform binary classification of temporal constraint sentence vs other sentences.
+The rationale of using ML based approach as opposed to a rule based approach is because: 1) rule-writing requires domain expertise; 2) rules-writing tends to quickly become ad hoc thus requires greater effort to generate generic rules; and 3) ML classifiers have shown to scale well with large volumes of data.
 
@@
 The text analysis engine component accepts the sentences identified as constraint sentences and creates an intermediate representation of each sentence.
+This intermediate representation is leveraged by subsequent component to infer formal constraints.
 We define our representation as a tree structure that is essentially a FOL expression.
@@
 The Stanford parser finds it difficult to annotate accurately the Stanford-typed dependencies of the sentence because of presence of different clauses acting on different subject-object pairs.
-As shown in figure~\ref{fig:standep} the word including is annotated with Stanford-typed dependencies ``dep'' that is a catch all dependency.
+As shown in Figure~\ref{fig:standep} the word including is annotated with Stanford-typed dependencies ``dep'' that is a catch all dependency.
 A catch all dependency is selected by a parser when no other appropriate dependency can be selected.
-We thus break down the sentence into two smaller tractable sentences:
+The \tool\ approach thus automatically break down the sentence into two smaller tractable sentences:
 
@@
 %All of these semantic templates are publicly available on our project website\footnote{\url{https://sites.google.com/site/temporalspec}}.
-With respect to the previous example the template 3 \textit{( A noun phrase followed by another noun/pronoun/verb phrase in brackets)} is applicable.
+With respect to the previous example the template 3 \textit{(A noun phrase followed by another noun/pronoun/verb phrase in brackets)} is applicable.
 Thus our shallow parser breaks the sentence into two individual sentences.
@@
 
-\textbf{Stanford-typed Dependencies}: After complex sentences (whenever applicable) have been broken to simple sentnces, this phase generates an intermediate (FOL) representation of the sentences.
+\textbf{Stanford-typed Dependencies}: After complex sentences (whenever applicable) have been broken to simple sentences, this phase generates an intermediate (FOL) representation of the sentences.
 This phase is equivalent to the intermediate-representation technique described in Section~\ref{sub:SENLPback}.

### 2014-12-09 Draft/evaluation.tex
Laurie's comments

@@
 
-	\item\CodeIn{java.io} : is one of a popular packages in \CodeIn{Java} programming language.
+	\item\CodeIn{java.io} : is one of the widely used packages in \CodeIn{Java} programming language.
 The package provides APIs for system input and output through data streams, serialization and the file system, which are one of the fundamental functionalities provided by any programming language.
 \end{itemize}
-We chose \CodeIn{Amazon S3}, \CodeIn{PayPal payment}, and \CodeIn{java.io} APIs as our subjects because they are popular and contain decent documentation.
+We chose \CodeIn{Amazon S3}, \CodeIn{PayPal payment}, and \CodeIn{java.io} APIs as our subjects because they are widely used and contain relevant documentation.
 
@@
 We first manually annotated the sentences in the API documents of the subject APIs.
-First two authors manually labeled each sentence in the Java API documentation as sentence containing 
-temporal constraints or not.
+The first two authors manually labeled each sentence (2417 total) in the Java API documentation as being a temporal constraint sentence or not.
 We used \CodeIn{cohen kappa}~\cite{carletta1996assessing} score to statistically measure
@@
 First we executed the classifiers using the words in the sentences as features and measure \CodeIn{precision}, \CodeIn{recall}, and \CodeIn{F-Score} as P$_{wrd}$, R$_{wrd}$, and F$_{wrd}$.
-We next executed the classifiers on the features proposed by \tool\ approach and measure \CodeIn{precision}, \CodeIn{recall}, and \CodeIn{F-Score} as P$_{ftr}$, R$_{ftr}$, and F$_{ftr}$.
+We next executed the classifiers on the features proposed by the \tool\ approach and measure \CodeIn{precision}, \CodeIn{recall}, and \CodeIn{F-Score} as P$_{ftr}$, R$_{ftr}$, and F$_{ftr}$.
 We next calculate relative gain in \CodeIn{precision}, \CodeIn{recall}, and \CodeIn{F-Score} as P$_{\Delta}$ (P$_{ftr}$- P$_{wrd}$), R$_{\Delta}$ (R$_{ftr}$ - R$_{wrd}$), and F$_{\Delta}$ (F$_{ftr}$ - F$_{wrd}$).
-Higher values of P$_{\Delta}$, R$_{\Delta}$, and F$_{\Delta}$ are indicative of effectiveness of the constraint statements inferred using the features proposed by \tool\ approach.
+Higher values of P$_{\Delta}$, R$_{\Delta}$, and F$_{\Delta}$ are indicative of effectiveness of the constraint statements inferred using the features proposed by the \tool\ approach.
 
@@
 However, we excluded the type-enforced temporal constraints inferred using Algorithm~\ref{alg:TypeAnalysis}, described in Section~\ref{sec:approach}.
-We excluded the type-enforced constraints because they are correct by construction and are by default enforced by modern IDE's such as eclipse. 
+We excluded the type-enforced constraints because they are correct by construction and are by default enforced by modern IDE's such as the Eclipse. 
 We then measure $accuracy$ of \tool\ as the ratio of the total number of temporal constraints that

### 2014-12-09 Draft/introduction.tex
Laurie's comments

@@
 
-\textit{The goal of this work is to assist developers construct API clients that comply with
-	temporal constraints of the API through the inference and formalization of these constraints found in natural language API documents.}
+\textit{The goal of this work is to assist developers to construct API clients that comply with temporal constraints of the API through the inference and formalization of these constraints found in natural language API documents.}
 
-First step towards formalizing temporal constraints is to identify the sentences describing such constraints.
+The first step towards formalizing temporal constraints is to identify the sentences describing such constraints.
 A naive approach to identify the constraint sentences is to perform keyword-based search on API documents.
 However, the effectiveness of such approach is limited by the quality of the keywords used.
-Furthermore, sentences involving temporal constraints oftentimes may not have have uniquely identifiable keywords.
+Furthermore, sentences involving temporal constraints often the time may not have uniquely identifiable keywords.
 
 For instance, consider the sentences from \paypalAPI:
-1) ``\textit{Use this call to complete a payment.}'' 
-2) ``\textit{Use this method to refund a completed payment.}''
-Sentence 1 indicates the temporal constraint that a payment must be completed before the refund call is initiated.
-In contrast, sentence 2 is a descriptive statement about complete payment method.
+1) ``\textit{Use this call to complete a payment.}'' from \CodeIn{execute payment} method.
+2) ``\textit{Use this call to refund a completed payment.}'' from \CodeIn{refund sale} method.
+Sentence 1 is a descriptive statement about complete payment method.
+In contrast, Sentence 1 indicates the temporal constraint that a payment must be completed before the refund call is initiated.
 Since these sentences are not significantly different in terms of words, a simple keyword-based search will fail to distinguish between the two. 
@@
 Consider Sentence 2 in preceding paragraph.
-The phrase \textit{``completed payment''} refers to the ``Execute Payment'' method in the API.
+The phrase \textit{``completed payment''} refers to the \CodeIn{execute payment} method in the API.
 
@@
 Furthermore, we propose to use a combination of words, syntax (parts of speech) of a sentence, and semantics (relationship between words) of a sentence as the features for learning patterns.
-This combination allows our approach to make a finer grained distinction between the example sentences described earlier.
-To identify the phrases as method-invocation instances, we propose to build domain dictionaries systematically from API documents and generic English dictionaries.
+This combination allows \tool\ to make a finer grained distinction between the example sentences described earlier.
+Furthermore, to identify the phrases as implicit method-invocation references, we propose to leverage domain dictionaries that are systematically created from API documents and generic English dictionaries.
 
-In summary, \tool\ approach leverages natural language description of API's to infer temporal constraints of method invocations.
+In summary, the \tool\ approach leverages natural language description of API's to infer temporal constraints of method invocations.
 As our approach analyzes API documents in natural language, it can be reused independent of the programming language of an API library.

### 2014-12-09 Draft/related.tex
Laurie's comments

@@
 Xiao et al.~\cite{XiaoFSE2012} and Slankas et al.~\cite{johnSlankasPASSAT13} use shallow parsing techniques to infer Access Control Policy (ACP) rules from natural language text in use cases.
-In contrast, \tool\ approach works with API documents.
+In contrast, the \tool\ approach works with API documents.
 %The use of shallow parsing techniques works satisfactorily on natural language text in use cases, owing to relative well-formed structure of sentences in use case descriptions.
@@
 The lower frequency of occurrence of temporal constraint sentences in comparison to parameter constraint sentences, make them harder to detect.
-Second, \tool\ approach introduces hybrid shallow parsing that relies both on parts-of-speech tags as well as Stanford-typed dependencies to construct intermediate representation, while the previous approach relies only on parts-of-speech tags.
+Second, the \tool\ approach introduces hybrid shallow parsing that relies both on parts-of-speech tags as well as Stanford-typed dependencies to construct intermediate representation, while the previous approach relies only on parts-of-speech tags.
 Finally, the \tool\ approach leverages the concept of semantic graphs constructed from class and method names in API to automatically infer the implicit method references in a sentence.

### 2014-12-09 Draft/abstract.tex
Dr. Xie's cmnts on Abstract, Intro, and Conclusion

@@
 These constraints govern the secure and robust operation of client software using the API.
-However, in practice, most API do not have formal temporal constraints.
+However, in practice, most APIs do not come with formal temporal constraints.
 In contrast, these constraints are typically described
@@
 To evaluate our approach, we apply \tool\ to infer and formalize temporal
-constraints from \amazonAPI, \paypalAPI\ and the \CodeIn{java.io} package in the
+constraints from the \amazonAPI, the \paypalAPI\, and the \CodeIn{java.io} package in the
 JDK API.
@@
 of 79.0\%, 60.0\%, and 65.0\%, respectively.
-Furthermore, our evaluation also demonstrate that \tool\ achieves an accuracy of 70\% in inferring and formalizing 77 temporal constraints from these temporal constraint sentences.
+Furthermore, our evaluation also demonstrates that \tool\ achieves an accuracy of 70\% in inferring and formalizing 77 temporal constraints from these temporal constraint sentences.
 

### 2014-12-09 Draft/conclusion.tex
Laurie's comments
Dr. Xie's cmnts on Abstract, Intro, and Conclusion

@@
 
-Despite being highly desirable, most APIs are not equipped with formal temporal constraints.
+Despite being highly desirable, formal temporal constraints are missing from most APIs.
 In contrast, documentation of API methods contains detailed specifications of temporal constraints in natural language text.
-Manually writing formal specifications based on natural language text in API documents is prohibitively time consuming and error prone.
+Manually writing formal specifications based on natural language text in API documents is prohibitively time-consuming and error-prone.
 To address this issue, we have proposed a novel approach called \tool\ to infer temporal constraints from natural language text of API documents.
 We applied \tool\ to infer temporal constraints from
-\paypalAPI, \amazonAPI, and  
+the \paypalAPI, the \amazonAPI, and the 
 commonly used package \CodeIn{java.io} in the JDK API.
@@
 Furthermore, \tool\ also achieved an accuracy of
-70\% in inferring 77 formal temporal constraints from these sentences.
+70\% in inferring 77 formal temporal constraints from these temporal constraint sentences.

### 2014-12-09 Draft/introduction.tex
Dr. Xie's cmnts on Abstract, Intro, and Conclusion

@@
 by providing standardized mechanism to access API components.
-However, APIs have some constraints governing the proper use of the API that must be followed.
+However, an API has some constraints governing the proper use of the API that must be followed.
 One such type of constraints are temporal constraints [2], which are the allowed sequences of invocations of methods from the API.
-Non-compliance to such constraints will often result in faulty applications that are unreliable to use and may even result in financial losses.
+Non-compliance to such constraints will often result in faulty applications that are unreliable to use. % and may even result in financial losses.
 
-Formal analysis tools, such as model checker and runtime verifiers 
-can assist in detection of the violations of the temporal constraints
+Formal analysis tools, such as model checkers and runtime verifiers 
+can assist in detecting violations of the temporal constraints
 in API clients as defects~\cite{lee2012towards}.
@@
 
-Although natural language API description can be manually converted into formal constraints,
+Although natural language API descriptions can be manually converted to formal constraints,
 manually identifying and writing formal constraints based on natural language text in API documents can be prohibitively time-consuming and error-prone~\cite{wu2013inferring,RubingerWEB10}. 
@@
 
-For instance, consider the sentences from \paypalAPI:
-1) ``\textit{Use this call to complete a payment.}'' from \CodeIn{execute payment} method.
-2) ``\textit{Use this call to refund a completed payment.}'' from \CodeIn{refund sale} method.
-Sentence 1 is a descriptive statement about complete payment method.
-In contrast, Sentence 1 indicates the temporal constraint that a payment must be completed before the refund call is initiated.
+For instance, consider the sentences from the \paypalAPI:
+1) ``\textit{Use this call to complete a payment.}'' from the \CodeIn{execute payment} method.
+2) ``\textit{Use this call to refund a completed payment.}'' from the \CodeIn{refund sale} method.
+Sentence 1 is a descriptive statement about the \CodeIn{execute payment} method.
+In contrast, Sentence 2 indicates the temporal constraint that a payment must be completed before the refund call is initiated.
 Since these sentences are not significantly different in terms of words, a simple keyword-based search will fail to distinguish between the two. 
@@
 
-Even after a sentence has been identified as a constraint sentence, an approach has to infer the references to the method in the sentences, which may often not be implicit.
-Consider Sentence 2 in preceding paragraph.
+Even after a sentence has been identified as a constraint sentence, an approach has to infer the references to the method in the sentences, which often may not be explicit.
+Consider Sentence 2 in the preceding paragraph.
 The phrase \textit{``completed payment''} refers to the \CodeIn{execute payment} method in the API.
@@
 
-A ML based approach for identifying the temporal constraint sentences addresses the limitations of keyword-based search by automatically learning patterns of temporal constraint sentences.
+An ML based approach for identifying the temporal constraint sentences addresses the limitations of keyword-based search by automatically learning patterns of temporal constraint sentences.
 Furthermore, we propose to use a combination of words, syntax (parts of speech) of a sentence, and semantics (relationship between words) of a sentence as the features for learning patterns.
@@
 
-In summary, the \tool\ approach leverages natural language description of API's to infer temporal constraints of method invocations.
+In summary, the \tool\ approach leverages natural language description of an API to infer temporal constraints of method invocations.
 As our approach analyzes API documents in natural language, it can be reused independent of the programming language of an API library.
@@
 of 79.0\%, 60.0\%, and 65.0\%, respectively.
-Furthermore, our evaluation also demonstrate that \tool\ achieves an accuracy of 70\% in inferring 77 formal temporal constraints from these sentences.
+Furthermore, our evaluation also demonstrates that \tool\ achieves an accuracy of 70\% in inferring 77 formal temporal constraints from these sentences.
 This paper makes the following main contributions:
@@
 	An open source implementation of the prototype is publicly available on our project website\footnote{\url{https://sites.google.com/site/temporalspec}}, along with the experimental subjects and the results.
-	\item An evaluation of our approach on \amazonAPI, \paypalAPI, and commonly used package \CodeIn{java.io} from the JDK API. 
+	\item An evaluation of our approach on the \amazonAPI, the \paypalAPI, and the commonly used package \CodeIn{java.io} from the JDK API. 
 \end{itemize}

### 2014-12-09 Draft/introduction.tex
minor

@@
 	\item A prototype implementation of our approach based on extending the Stanford Parser~\cite{Klein03}, which is a natural language parser to derive the grammatical structure of sentences.
-	An open source implementation of the prototype is publicly available on our project website\footnote{\url{https://sites.google.com/site/temporalspec}}, along with the experimental subjects and the results.
+	All our experimental subjects, results, and artifacts are publicly available on our project website\footnote{\url{https://sites.google.com/site/temporalspec}}. 
 	\item An evaluation of our approach on the \amazonAPI, the \paypalAPI, and the commonly used package \CodeIn{java.io} from the JDK API. 

### 2015-05-11 Draft/approach.tex
ASE Changes

@@
 From an implementation perspective, we can use any of the standard off-the-shelf classifiers to train the ML model, since \tool\ seeks to achieve only a binary classification of the API sentences.
-For instance, model can be trained using na{\"i}ve Bayes classifier which is the simplest probabilistic classification methods and is shown to be comparative to other advanced classification methods given appropriate prepossessing~\cite{rennie2003tackling}.
+For instance, model can be trained using na{\"i}ve Bayes classifier which is the simplest probabilistic classification methods and is shown to be comparative to other advanced classification methods given appropriate preprocessing~\cite{rennie2003tackling}.
 The ML model can be trained offline or else by the users of the approach if better accuracy is desired for domain-specific data.

### 2015-05-11 Draft/background.tex
ASE Changes

@@
 \textbf{Parts Of Speech (POS) tagging}~\cite{Klein03,KleinNIPS03}.
-Also known as \textit{`word tagging'}, \textit{`grammatical tagging'} and \textit{`word-sense disambiguation'}, these techniques aim to identify the part of speech (such as noun, verbs, etc.), a particular word in a sentence belongs to.
+Also known as \textit{`word tagging'} and \textit{`grammatical tagging'}, these techniques aim to identify the part of speech (such as noun, verbs, etc.), a particular word in a sentence belongs to.
 The most commonly used technique is to train a classification parser over a previously known data set.

### 2015-05-11 Draft/evaluation.tex
Dr. Xie's cmnts on Abstract, Intro, and Conclusion
ASE Changes

@@
 
-$F-Score$ = $\frac{2 X Precison X Recall}{Precision + Recall}$
+$F-Score$ = $\frac{2 X Precision X Recall}{Precision + Recall}$
 \end{center}
@@
 Mtds: Total no. of Methods; Sen: Total no. of Sentences; Sen$_C$: Total no. of constraint Sentences; Acc: Accuracy
-Spec$_{ICON}$: Total no. of temporal constraint correctly identified by \tool;
+Spec$_{ICON}$: Total no. of temporal constraints correctly identified by \tool;
 } \\ 
@@
 In this section, we evaluate the effectiveness of \tool\ in inferring temporal constraints from the identified constraint sentences from API documents.Table~\ref{tab:results} shows the effectiveness of \tool\ in inferring temporal constraints from the identified constraint sentences.
-Column ``Trainer'' lists the names of the subject API. 
+Column ``API'' lists the names of the subject API. 
 Columns ``Mtds'' and ``Sen'' list the number of methods and sentences in each subject API's.
@@
 To minimize the threat, we used API documents of three different API's: JDK \CodeIn{java.io}, \amazonAPI, \paypalAPI.
-On one hand, Java is a widely used programming language and \CodeIn{java.io} and is one of the main packages.
+On one hand, Java is a widely used programming language and \CodeIn{java.io} is one of the main packages.
 In contrast, \amazonAPI\ provides HTTP based access to online storage allowing developers the freedom to write clients applications in any programming language.

### 2015-05-11 Draft/related.tex
Edited Related Work

@@
 
-%Our proposed approach touches a few research areas such as software verification, NLP in Software Engineering (SE), and document augmentation.
-%We next discuss the relevant work pertinent to our proposed approach in these areas.
-
-%\subsection{Code Contracts - Formal Specifications}
-% Define temporal constraints distinction
-
 \textbf{Formal Specification}:
-Contracts are a well-known mechanism for formally specifying functional behavior of the program. 
-Contracts specify the program behavior in terms of conditions that must hold before/after and/or during the execution of a method.
+Contracts formally specify the program behavior in terms of conditions that must hold before/after and/or during the execution of a method.
 A significant amount of work has been done in automated inference of contracts.
@@
 to automatically infer contracts.
-However, recent studies~\cite{Polikarpova2009ISSTA,Flanagan2001:HAA} demonstrate that a combination of developer-written and automatically extracted
+However, studies~\cite{Polikarpova2009ISSTA,Flanagan2001:HAA} demonstrate that a combination of developer-written and automatically extracted
 contracts is the most effective approach for formally specifying the constraints on an API.
@@
 
-A different set of approaches exist that infer code-contract-like specifications (such as behavioral model, algebraic specifications, and exception specifications) either dynamically\cite{Henkel07discoveringdocumentation,Ghezzi:2009:SIB:1555001.1555057,Henkel:2008:DDA:1363102.1363105} or statically~\cite{Flanagan2001:HAA,Buse:2008:ADI:1390630.1390664} from source code and binaries.
-In contrast, \tool\ infers contracts from the natural language text in API documents,
+Another set of approaches infer code-contract-like specifications (such as behavioral model, algebraic specifications, and exception specifications) either dynamically\cite{Henkel07discoveringdocumentation,Ghezzi:2009:SIB:1555001.1555057,Henkel:2008:DDA:1363102.1363105} or statically~\cite{Flanagan2001:HAA,Buse:2008:ADI:1390630.1390664} from source code and binaries.
+In contrast, \tool\ infers specifications from the natural language text in API documents,
 thus complementing existing approaches when the source code or binaries of the API library is not available.
@@
 
-%In contrast, approach presented in this report is independent of such training set and thus can be easily extended to target respective problems addressed by them.
-Furthermore, the specifications inferred by their approach may ignore the explicit ordering information described in individual method descriptions as inferred by \tool\.
-
 Xiao et al.~\cite{XiaoFSE2012} and Slankas et al.~\cite{johnSlankasPASSAT13} use shallow parsing techniques to infer Access Control Policy (ACP) rules from natural language text in use cases.
 In contrast, the \tool\ approach works with API documents.
-%The use of shallow parsing techniques works satisfactorily on natural language text in use cases, owing to relative well-formed structure of sentences in use case descriptions.
-%In contrast, often the sentences in API documents are not well-formed.
-%Additionally, their approaches do not deal with programming keywords or identifiers, which are often mixed with the method descriptions in API documents.
 Pandita et al.~\cite{pandita12:inferring} proposed an NLP-based approach on inferring parameter constraints from method descriptions in the API documents. \tool\ differs from their work as follows.
@@
 In contrast, \tool\ both identifies the sentences pertaining to temporal constraints and infers the temporal constraints automatically.
-
-In next section, we briefly introduce the NLP techniques used by \tool.

### 2015-05-13 Draft/background.tex
Added Related Gabel and Su in Related work
Cleaned Related Work and Background

Closes #3

@@
 
-%Natural language is well suited for human communication, but converting natural language into unambiguous specifications that can be processed and understood by computers is difficult.
-%However, research advances~\cite{Marneffe06LREC,Marneffe08COLING,Klein03,KleinNIPS03} have increased the accuracy of existing NLP techniques to annotate the grammatical structure of a sentence.
-%These advances in NLP have inspired researchers/ practitioners~\cite{pandita12:inferring, pandita13:WHYPER, johnSlankasPASSAT13, XiaoFSE2012, thummalapentaICSE12} to adapt/apply NLP techniques to solve problems in SE domain.
-
-%In particular, this work proposes novel techniques on top of previously proposed techniques~\cite{pandita12:inferring, pandita13:WHYPER} to demonstrate the effectiveness of applying NLP on API documents.
 We next briefly introduce the techniques used in this work that have been grouped into two broad categories.
@@
 
-\textbf{Parts Of Speech (POS) tagging}~\cite{Klein03,KleinNIPS03}.
-Also known as \textit{`word tagging'} and \textit{`grammatical tagging'}, these techniques aim to identify the part of speech (such as noun, verbs, etc.), a particular word in a sentence belongs to.
-The most commonly used technique is to train a classification parser over a previously known data set.
-Current state-of-the-art approaches have demonstrated to be effective in classifying POS tags for well-written news articles.
+\textit{Parts Of Speech (POS) tagging}~\cite{Klein03,KleinNIPS03}: Also known as \textit{`word tagging'} and \textit{`grammatical tagging'}, these techniques aim to identify the part of speech (such as noun, verbs, etc.), a particular word in a sentence belongs to.
 
-\textbf{Phrase and Clause Parsing}.
-Also known as chunking, this technique divides a sentence into a constituent set of words (or phrases) that logically belong together (such as a Noun Phrase and Verb Phrase).
+\textit{Phrase and Clause Parsing}: Also known as chunking, this technique divides a sentence into a constituent set of words (or phrases) that logically belong together (such as a Noun Phrase and Verb Phrase).
 Chunking further enhances the syntax of a sentence in addition to POS tagging.
-Current state-of-the-art approaches can effectively classify phrases and clauses over well-written news articles.
 
-\textbf{Typed Dependencies}~\cite{Marneffe06LREC,Marneffe08COLING}.
-The Stanford typed dependencies representation  is designed to provide a simple description of grammatical relationships directed towards non-linguistics experts to perform NLP related tasks.
-It provides a hierarchical structure for the dependencies with precise definitions of what each dependency represents, thus facilitating machine based manipulation of natural language text.
+\textit{Typed Dependencies}~\cite{Marneffe06LREC,Marneffe08COLING}: The Stanford typed dependencies representation  is designed to provide a simple description of grammatical relationships directed towards non-linguistics experts to perform NLP related tasks.
+The representation provides a hierarchical structure for the dependencies with precise definitions of what each dependency represents, thus facilitating machine based manipulation of natural language text.
 
@@
 
-We next present SE specific NLP techniques.
+%We next present SE specific NLP techniques.
 
@@
 
-\textbf{Programming keywords}~\cite{pandita12:inferring}. Accurate annotation of POS tags in a sentence is fundamental to effectiveness of any advanced NLP technique.
-However POS tagging works satisfactorily on well-written news articles which does not necessary entail that the tagging works satisfactorily on domain-specific text as well.
-Thus, noun boosting is a necessary precursor to application of POS tagging on domain specific text.
+\textit{Programming Keywords}~\cite{pandita12:inferring}: Accurate annotation of POS tags in a sentence is fundamental to effectiveness of any advanced NLP technique.
+However POS tagging developed for well written news articles, often performs unsatisfactorily on domain-specific text.
 In particular, with respect to API documents certain words have a different semantic meaning, in contrast to general linguistics that causes incorrect annotation of POS tags.
@@
 Noun boosting identifies such words from the sentences based on a domain-specific dictionaries, and annotates them appropriately.
-The annotation assists the POS tagger to accurately annotate the POS tags of the words thus increasing accuracy of advanced NLP techniques such as chunking and typed dependency annotation.
+The annotation directs the POS tagger to correctly annotate the POS tags of the domain specific words thus increasing accuracy of subsequent NLP techniques such as chunking and typed dependency annotation.
 
-\textbf{Lexical Token Reduction}~\cite{pandita13:WHYPER}.
-These are a collection of generic preprocessing heuristics to further improve the accuracy of core NLP techniques.
+\textit{Lexical Token Reduction}~\cite{pandita13:WHYPER}:
 The accuracy of core NLP techniques is often inversely proportional to the number of lexical tokens in a sentence.
-Thus, the reduction in the number of lexical tokens greatly increases the accuracy of core NLP techniques. 
+Thus, reduction in the number of lexical tokens greatly improves the accuracy of core NLP techniques. 
 In particular, following heuristics have been used in related work~\cite{pandita12:inferring,pandita13:WHYPER} to achieve the desired reduction of lexical tokens:
+%These are a collection of generic preprocessing heuristics to further improve the accuracy of core NLP techniques.
 
@@
 
-\item \textbf{Period Handling}.
-Besides marking the end of a sentence in generic English, the character period (`.') has other legal usages as well, such as decimal representation (periods between numbers).
+\item \textit{Period Handling}: Besides marking the end of a sentence in generic English, the character period (`.') has other legal usages as well, such as decimal representation (periods between numbers).
 Although legal, such usage hinder detection of sentence boundaries, thus causing core NLP techniques to return incorrect or imprecise results.
@@
 
-\item \textbf{Named Entity Handling}. Sometimes a sequence of words correspond to the name of entities that have a specific meaning collectively.
+\item \textit{Named Entity Handling}: Sometimes a sequence of words correspond to the name of entities that have a specific meaning collectively.
 For instance, consider the phrases \textit{``Amazon S3'', ``Amazon simple storage service''}, which are the names of the service.
-Further resolution of these phrases using grammatical syntax is unnecessary and would not bring forth any semantic value.
+Further resolution of such phrases using grammatical syntax may not bring forth any semantic value.
 Also these phrases contribute to length of a sentence that in turn negatively affects the accuracy of core NLP techniques.
@@
 
-\item \textbf{Abbreviation Handling}. Natural-language sentences often consist of abbreviations interleaved with text.
+\item \textit{Abbreviation Handling}: Natural-language sentences often consist of abbreviations interleaved with text.
 This interleaving may result in POS tagger to incorrectly parse a sentence.
@@
 
-\textbf{Intermediate-Representation Generation}~\cite{pandita13:WHYPER}.
-This technique accepts the syntax-annotated sentences (grammatical and semantic) and builds a First-Order-Logic (FOL) representation of the sentence.
+\textit{Intermediate-Representation Generation}~\cite{pandita13:WHYPER}:
+This technique accepts the syntax-annotated sentences (grammatical and semantic) and builds a First-Order-Logic (FOL) like representation of the sentence.
 Earlier researches have shown the adequacy using FOL for NLP related analysis tasks~\cite{Sinha2009,Sinha2010,pandita12:inferring}.
-Particularly, WHYPER~\cite{pandita13:WHYPER} demonstrates the effectiveness of this technique, by constructing an intermediate representation generator from semantically annotated sentences. 
+Particularly, WHYPER~\cite{pandita13:WHYPER} demonstrates the effectiveness of this representation, by constructing an intermediate representation generator from semantically annotated sentences. 
 The component is implemented as a sequence of cascading finite state machines based on the function of annotated Stanford-typed dependencies~\cite{Marneffe06LREC,Marneffe08COLING,Klein03,KleinNIPS03}.
-
-In next section we describe our generic approach to infer temporal constraints from API documents.

### 2015-05-13 Draft/introduction.tex
ASE Changes
Added Related Gabel and Su in Related work
Cleaned Related Work and Background

Closes #3

@@
 
-Application Programming Interfaces (APIs) facilitates software reuse
+Application Programming Interfaces (APIs) facilitate software reuse
 by providing standardized mechanism to access API components.
@@
 
-The rest of the paper is organized as follows.
-Section~\ref{sec:example} presents a real-world example that motivates our approach.
-Section~\ref{sec:related} discusses related work.
-Section~\ref{sec:background} presents the  background on NLP techniques used in our approach.
-Section~\ref{sec:approach} presents our approach.
-Section~\ref{sec:evaluation} presents the evaluation of our approach.
-Section~\ref{sec:discussion} presents brief discussion on the limitations and future work.
-Finally, Section~\ref{sec:conclusion} concludes.
+%The rest of the paper is organized as follows.
+%Section~\ref{sec:example} presents a real-world example that motivates our approach.
+%Section~\ref{sec:related} discusses related work.
+%Section~\ref{sec:background} presents the  background on NLP techniques used in our approach.
+%Section~\ref{sec:approach} presents our approach.
+%Section~\ref{sec:evaluation} presents the evaluation of our approach.
+%Section~\ref{sec:discussion} presents brief discussion on the limitations and future work.
+%Finally, Section~\ref{sec:conclusion} concludes.

### 2015-05-13 Draft/related.tex
Added Related Gabel and Su in Related work
Cleaned Related Work and Background

Closes #3

@@
 Another set of approaches infer code-contract-like specifications (such as behavioral model, algebraic specifications, and exception specifications) either dynamically\cite{Henkel07discoveringdocumentation,Ghezzi:2009:SIB:1555001.1555057,Henkel:2008:DDA:1363102.1363105} or statically~\cite{Flanagan2001:HAA,Buse:2008:ADI:1390630.1390664} from source code and binaries.
+Among mining based approaches Gable and Su~\cite{gabel2008javert} proposed to learn  
+\textit{micropatterns} of temporal properties from runtime traces and then combining them into larger specifications depicted as finite state automata.
 In contrast, \tool\ infers specifications from the natural language text in API documents,
@@
 \textbf{Augmented Documentation}:
-Improving the documentation related to a software API~\cite{Dekel2009,tan2011acomment} is another related field of research.
 Dekel and Herbsleb~\cite{Dekel2009}, were the first to create a tool namely eMoose,

### 2015-05-13 Draft/approach.tex
Refined Approach

@@
 	\centering
-		\includegraphics[scale=0.3]{StanfordAnnotated.eps}
+		\includegraphics[scale=0.25]{StanfordAnnotated.eps}
 	\caption{Sentence annotated with Stanford dependencies}
@@
 From an implementation perspective, we can use any of the standard off-the-shelf classifiers to train the ML model, since \tool\ seeks to achieve only a binary classification of the API sentences.
-For instance, model can be trained using na{\"i}ve Bayes classifier which is the simplest probabilistic classification methods and is shown to be comparative to other advanced classification methods given appropriate preprocessing~\cite{rennie2003tackling}.
+%For instance, model can be trained using na{\"i}ve Bayes classifier which is the simplest probabilistic classification methods and is shown to be comparative to other advanced classification methods given appropriate preprocessing~\cite{rennie2003tackling}.
 The ML model can be trained offline or else by the users of the approach if better accuracy is desired for domain-specific data.
@@
 
-\begin{enumerate}
-
-	\item \textbf{Length of a Sentence}: The feature is the total number of words in  the sentence.
+1) \textbf{Length of a Sentence}: The feature is the total number of words in  the sentence.
 The rationale is that shorter sentences (containing fewer words) are unlikely candidates for temporal constraint sentences.
 
-	\item \textbf{Sentence Type}: The context of sentence, whether the sentence appears as method summary, parameter summary, return value summary, or exception/error summary as captured by pre-processor phase.
+2) \textbf{Sentence Type}: The context of sentence, whether the sentence appears as method summary, parameter summary, return value summary, or exception/error summary as captured by pre-processor phase.
 The rationale is that a majority of the temporal constraint sentences are either summary or exception sentences.
 
-	\item \textbf{Lemmatization}: The feature is the base form of a word.
+3) \textbf{Lemmatization}: The feature is the base form of a word.
 In linguistic, lemmatization is the reduction of operational form of a word to its base form.
 For instance, ``invoking'', ``invokes'', and ``invoked'' are all reduced to invoke.
-The rationale for reducing the words to base form is to reduce the size of the feature set that otherwise considers every word as an independent feature.
+The rationale for reducing the words to base form is to reduce the size of the feature set that otherwise considers every word form as an independent feature.
 
-	\item \textbf{Stopword Reduction}: In linguistics, stopwords are the frequently occurring words that can be ignored and are often considered noise, such as ``the'' , ``of'', ``to'' etc...
+4) \textbf{Stopword Reduction}: In linguistics, stopwords are the frequently occurring words that can be ignored and are often considered noise, such as ``the'' , ``of'', ``to'' etc...
 The rationale for filtering the stopwords is to reduce the size of feature set that otherwise considers such words (despite being noise) as an independent features.
@@
 
-	\item \textbf{Stanford Dependencies}: We add to the feature set by identifying the presence of specific Stanford typed dependencies pertaining to the temporal aspects of the sentence semantics.
+5) \textbf{Stanford Dependencies}: We add to the feature set by identifying the presence of specific Stanford typed dependencies pertaining to the temporal aspects of the sentence semantics.
 In particular, we identify the presence of ``\textit{advcl}'', ``\textit{aux}'', ``\textit{auxpass}'', ``\textit{vmod}'', and ``\textit{tmod}''.
@@
 
-	\item \textbf{POS Tags}: We filter words whose part of speech tags are ``\textit{Noun}'', ``\textit{Determiner}'', ``\textit{Adjective}'', ``\textit{Cardinal Number}'', ``\textit{Foreign Word}'', ``\textit{Brackets}'', ``\textit{Coordinating Conjunction}'', and ``\textit{Personal Pronouns}''.
+6) \textbf{POS Tags}: We filter words whose part of speech tags are ``\textit{Noun}'', ``\textit{Determiner}'', ``\textit{Adjective}'', ``\textit{Cardinal Number}'', ``\textit{Foreign Word}'', ``\textit{Brackets}'', ``\textit{Coordinating Conjunction}'', and ``\textit{Personal Pronouns}''.
 The rationale for filtering based on POS tags is to remove the words that are unlikely to be specific to temporal constraints.
@@
 
-	\item \textbf{Sentence Structure}: The feature is the ordered sequence of chunking tags~\cite{Klein03,KleinNIPS03} in a sentence.
+7) \textbf{Sentence Structure}: The feature is the ordered sequence of chunking tags~\cite{Klein03,KleinNIPS03} in a sentence.
 Chunking seeks to divide a sentence into a constituent set of words (or phrases) that logically belong together (such as a Noun Phrase and Verb Phrase).
@@
 
-\end{enumerate}
-
-We use the described feature set to train a classier to perform binary classification of temporal constraint sentence vs other sentences.
-The rationale of using ML based approach as opposed to a rule based approach is because: 1) rule-writing requires domain expertise; 2) rules-writing tends to quickly become ad hoc thus requires greater effort to generate generic rules; and 3) ML classifiers have shown to scale well with large volumes of data.
+We use the described feature set to train a classifier to perform binary classification of sentence as either temporal constraint describing or not.
+The rationale of using ML based approach as opposed to a rule based approach is because: 1) rule-writing requires domain expertise; 2) rules-writing tends to quickly become ad hoc thus requires greater effort to generate generic rules to avoid over-fitting; and 3) ML classifiers have shown to scale well with large volumes of data.
 
@@
 This intermediate representation is leveraged by subsequent component to infer formal constraints.
-We define our representation as a tree structure that is essentially a FOL expression.
+We define our representation as a tree structure that is mimics a FOL expression.
 Research literature provides evidence of the adequacy of using FOL for NLP related analysis tasks~\cite{Sinha2009,Sinha2010,pandita12:inferring, pandita13:WHYPER}.
@@
 
-As described in Section~\ref{sub:SENLPback} the intermediate representation generation technique is based on the principle of shallow parsing~\cite{Branimir2000}. 
-In particular, the intermediate-representation technique is implemented as a function of Stanford-typed dependencies~\cite{Marneffe06LREC,Marneffe08COLING,KleinNIPS03}, to leverage the semantic information encoded in Stanford-typed dependencies.
+As described in Section~\ref{sub:SENLPback} the intermediate representation generation technique is implemented as a function of Stanford-typed dependencies~\cite{Marneffe06LREC,Marneffe08COLING,KleinNIPS03}, to leverage the semantic information encoded in Stanford-typed dependencies.
 
@@
 The POS tags which annotate the syntactical structure of a sentence are used to further simplify the constituent elements in a sentence. 
-We then use the Stanford-typed dependencies that annotate the grammatical relationships between words to construct our FOL representation.
-Thus, the intermediate representation generator used in this work is a two phase process as opposed to previous work~\cite{pandita12:inferring, pandita13:WHYPER}. 
+We then use the Stanford-typed dependencies that annotate the grammatical relationships between words to construct our FOL like representation.
+Thus, the intermediate representation generator used in this work is a two phase process as opposed to single phase in previous work~\cite{pandita12:inferring, pandita13:WHYPER}. 
 We next describe these two phases:
@@
 Constraint Extractor is responsible for inferring temporal constraint from the classified constraint sentences.
-
-Temporal constraints are expressed as temporal formulae involving: 1) \textit{Predicates} $\xi$ representing method calls and 2) \textit{Temporal operators}: backward ($\leftarrow$) \& forward ($\rightarrow$) and their negations $\xleftarrow{-}$ \& $\xrightarrow{-}$.
+Temporal constraints are expressed as temporal formulae involving: a) \textit{Predicates} $\xi$ representing method calls and b) \textit{Temporal operators}: backward ($\leftarrow$) \& forward ($\rightarrow$) and their negations $\xleftarrow{-}$ \& $\xrightarrow{-}$.
 We define following four constraints:
@@
 
-\begin{enumerate}
-	\item \textit{Forward Operator ($\xi_1 \rightarrow \xi_2$)}: method call $\xi_1$ must be succeeded by method call $\xi_2$. 
-	\item \textit{Backward Operator ($\xi_1 \leftarrow \xi_2$)}: method call $\xi_1$ must be preceded by method call $\xi_2$.
-	\item \textit{Negative Forward Operator ($\xi_1 \xrightarrow{-} \xi_2$)}: method call $\xi_1$ cannot be succeeded by method call $\xi_2$
-	\item \textit{Negative Backward Operator ($\xi_1 \xleftarrow{-} \xi_2$)}: method call $\xi_1$ cannot be preceded by the method call of $\xi_2$
-\end{enumerate}
+1) \textit{Forward Operator ($\xi_1 \rightarrow \xi_2$)}: method call $\xi_1$ must be succeeded by method call $\xi_2$.
+
+2) \textit{Backward Operator ($\xi_1 \leftarrow \xi_2$)}: method call $\xi_1$ must be preceded by method call $\xi_2$.
+
+3) \textit{Negative Forward Operator ($\xi_1 \xrightarrow{-} \xi_2$)}: method call $\xi_1$ cannot be succeeded by method call $\xi_2$
+
+4) \textit{Negative Backward Operator ($\xi_1 \xleftarrow{-} \xi_2$)}: method call $\xi_1$ cannot be preceded by the method call of $\xi_2$
 
@@
 Section~\ref{sub:ACA} further describes how these graphs are generated.
-\tool\ uses the Algorithm~\ref{alg:SenAnnotaator} to identify $\xi_2$.
+%\tool\ uses the Algorithm~\ref{alg:SenAnnotaator} to identify $\xi_2$.
 
-\algsetup{indent=1em}
-\begin{algorithm}[t!]
-\begin{algorithmic}[1]
-\begin{scriptsize}
-\REQUIRE K\_Graph $g$, FOL\_rep $rep$ 
-\ENSURE String $action$
-\STATE $String\ action\ =\ \phi$
-\STATE $List\ r\_name\_list\ =\ g.resource\_Names$
-\STATE $FOL\_rep\ r'\ =\ rep.findLeafContaining(r\_nam\_list)$
-\STATE $List\ actionList\ =\ g.actionList$
-\WHILE{$(r'.hasParent)$}
-	\IF{$actionList.contains(r'.parent.predicate)$}
-		\STATE $action\ =\ actionList.matching(r'.parent.predicate)$
-		\STATE $break$
-	\ELSE
-		\IF{$actionList.contains(r'.leftSibling.predicate)$}
-			\STATE $action\ =\ actionList.matching(r'.leftSibling.predicate)$
-			\STATE $break$
-		\ENDIF
-	\ENDIF
-	\STATE $r'\ =\ r'.parent$
-\ENDWHILE
-\RETURN $action$
-\end{scriptsize}
-\end{algorithmic}
-\caption{Action\_Extractor}
-\label{alg:SenAnnotaator}
-\end{algorithm}
+%\algsetup{indent=1em}
+%\begin{algorithm}[t!]
+%\begin{algorithmic}[1]
+%\begin{scriptsize}
+%\REQUIRE K\_Graph $g$, FOL\_rep $rep$ 
+%\ENSURE String $action$
+%\STATE $String\ action\ =\ \phi$
+%\STATE $List\ r\_name\_list\ =\ g.resource\_Names$
+%\STATE $FOL\_rep\ r'\ =\ rep.findLeafContaining(r\_nam\_list)$
+%\STATE $List\ actionList\ =\ g.actionList$
+%\WHILE{$(r'.hasParent)$}
+%	\IF{$actionList.contains(r'.parent.predicate)$}
+%		\STATE $action\ =\ actionList.matching(r'.parent.predicate)$
+%		\STATE $break$
+%	\ELSE
+%		\IF{$actionList.contains(r'.leftSibling.predicate)$}
+%			\STATE $action\ =\ actionList.matching(r'.leftSibling.predicate)$
+%			\STATE $break$
+%		\ENDIF
+%	\ENDIF
+%	\STATE $r'\ =\ r'.parent$
+%\ENDWHILE
+%\RETURN $action$
+%\end{scriptsize}
+%\end{algorithmic}
+%\caption{Action\_Extractor}
+%\label{alg:SenAnnotaator}
+%\end{algorithm}
 
-The algorithm systematically explores the FOL representation
-of the candidate sentence to identify $\xi_2$. First, the algorithm
+\tool\ systematically explores the intermediate representation
+of the candidate sentence to identify $\xi_2$. First, this component
 attempts to locate the occurrence of object name or its synonym
-in the leaf nodes of the FOL
-representation of the sentence (Line 3). The method
-findLeafContaining(r\_name\_list) explores the FOL representation
-to find a leaf node that contains either the object name
-or one of its synonyms.
-Once a leaf node is found, we systematically
-traverse the tree from the leaf node to the root,
+in the leaf nodes (entity) of the intermediate
+representation of the sentence.
+Once a leaf node is found, this component systematically
+traverses the tree from the leaf node to the root,
 matching all parent predicates as well as immediate child
-predicates [Lines 5-16].
-Algorithm matches each of the traversed predicate
+predicates.
+This component matches each of the traversed predicate
 with the actions associated with the object defined in

### 2015-05-13 Draft/related.tex
Added Reference to another related work

@@
 
-Another set of approaches infer code-contract-like specifications (such as behavioral model, algebraic specifications, and exception specifications) either dynamically\cite{Henkel07discoveringdocumentation,Ghezzi:2009:SIB:1555001.1555057,Henkel:2008:DDA:1363102.1363105} or statically~\cite{Flanagan2001:HAA,Buse:2008:ADI:1390630.1390664} from source code and binaries.
+Another set of approaches infer code-contract-like specifications (such as behavioral model, algebraic specifications, and exception specifications) either dynamically\cite{Henkel07discoveringdocumentation,Ghezzi:2009:SIB:1555001.1555057,Henkel:2008:DDA:1363102.1363105} or statically~\cite{Flanagan2001:HAA,Buse:2008:ADI:1390630.1390664,wasylkowski2011mining} from source code and binaries.
 Among mining based approaches Gable and Su~\cite{gabel2008javert} proposed to learn  

### 2015-05-13 Draft/approach.tex
Updated Approach
Removed Algorithms to save space

@@
 Ad hoc creation of semantic graph is prohibitively time consuming and may be error prone.
-We thus employ a systematic methodology (proposed by Pandita et al. ~\cite{pandita13:WHYPER}) to infer semantic graphs from API documents.
+We thus employ a systematic methodology (proposed previously in Whyper ~\cite{pandita13:WHYPER}) to infer semantic graphs from API documents.
 
@@
 We then find the synonyms terms used refer to the class in question.
-The synonym terms are listed as by breaking down the camel-case notation in the class name.
-This list is further augmented by listing the name of the parent classes and implemented interfaces if any.
-
-\begin{figure}
-	\centering
-		\includegraphics[scale=0.4]{KnowledgeGraph.eps}
-	\caption{Semantic Graph for the \CodeIn{Object} related operations in Amazon S3 REST API}
-	\label{fig:knowledge}
-\end{figure}
-
+The synonym terms are listed as by splitting the camel-case notation in the class name.
+This list is further augmented with the name of the parent classes and implemented interfaces if any.
 We then systematically inspect the member methods to identify actions applicable to the objects represented by the class.
@@
 
+\begin{figure}
+	\centering
+	\includegraphics[scale=0.3]{KnowledgeGraph.eps}
+	\caption{Semantic Graph for the \CodeIn{Object} related operations in Amazon S3 REST API}
+	\label{fig:knowledge}
+\end{figure}
+
 \subsection{Type Analysis}
@@
 To extend the temporal constraints inferred by the analyzing the natural language text, this component infers additional constraints that are encoded
-in the type system. Algorithm~\ref{alg:TypeAnalysis} lists the steps followed to infer type based temporal constraints.
+in the type system. %Algorithm~\ref{alg:TypeAnalysis} lists the steps followed to infer type based temporal constraints.
 
-The algorithm accepts the list of methods as an input produces a graph with
-the nodes representing methods in an API and the directed edges representing temporal constraints.
-First, an index is created based on the return types of the method (Line 2).
-Second, all methods in an API are added to an unconnected graph (Line 3-4).
-Then, for every public method in the input list, the algorithm checks the types
-of the input parameters and constructs and directed edge from all the methods whose return value
-have the same type to the method in question (Line 14- 20).
-The algorithm does not take into consideration the basic parameter types such as \CodeIn{integer}, \CodeIn{string} (Line 15).
-Additionally, an edge is created from the constructors of a class to the non static members methods of a class (Line 8 -13).
-The resultant graph is then returned by the algorithm.
-
-The temporal constraints based on the type information can be extracted by querying the graph. 
+%The algorithm accepts the list of methods as an input produces a graph with
+%the nodes representing methods in an API and the directed edges representing temporal constraints.
+First, an index list ($L_{mtd}$) of the public methods in an API is created based on the return types of the method.
+Next, all public methods in the API are added as nodes ($m_1,m_2...m_k$) in an unconnected graph ($G$).
+Next, for every method ($m$) in $L_{mtd}$, we identify the types
+of the input parameters ($t_1,t_2...t_k$).
+We then add a directed edge from all the methods in ($G$), where the return type of the method matches any of the types in ($t_1,t_2...t_k$). 
+Additionally, an edge is created from the object creation methods (constructors) of a class to the non-static members methods of a class, because a member methods are invoked after objects creation. 
+The temporal constraints based on the type information is extracted by querying $G$. 
 The incoming edges to a node denoting a method represents the set of pre-requisite methods.
@@
 
-\begin{algorithm}[t!]
-\begin{algorithmic}[1]
-\begin{scriptsize}
-\REQUIRE List $methodList$ 
-\ENSURE Graph $seq\_Graph$
-\STATE $Graph\ seq\_Graph\ =\ \phi$
-\STATE $Map\ idx\ = createIdx(methodList)$
-
-\FORALL{$Method\ mtd\ in\ methodList$} 
-	\STATE $seq\_Graph.addVertex(mtd)$
-\ENDFOR
-
-\FORALL{$Method\ mtd\ in\ methodList$} 
-	\IF{$mtd.isPublic()$}
-		\IF{$!mtd.isStatic()$}
-			\STATE $List\ preList\ =\ idx.query(mtd.declaringType)$
-			\FORALL{$Method\ mtd'\ in\ preList$}
-				\STATE $seq\_Graph.addEdge(mtd',mtd)$
-			\ENDFOR
-		\ENDIF
-		\FORALL{$Parameter\ param\ in\ mtd.getParameters()$}
-			\IF{$!isBasicType(param.Type)$}
-				\STATE $List\ preList\ =\ idx.query(paramType)$
-				\FORALL{$Method\ mtd'\ in\ preList$}
-					\STATE $seq\_Graph.addEdge(mtd',mtd)$
-				\ENDFOR				
-			\ENDIF
-		\ENDFOR
-	\ENDIF
-\ENDFOR
-\RETURN $seq\_Graph$
-\end{scriptsize}
-\end{algorithmic}
-\caption{Type\_Sequence\_Builder}
-\label{alg:TypeAnalysis}
-\end{algorithm}
+%\begin{algorithm}[t!]
+%\begin{algorithmic}[1]
+%\begin{scriptsize}
+%\REQUIRE List $methodList$ 
+%\ENSURE Graph $seq\_Graph$
+%\STATE $Graph\ seq\_Graph\ =\ \phi$
+%\STATE $Map\ idx\ = createIdx(methodList)$
+%
+%\FORALL{$Method\ mtd\ in\ methodList$} 
+%	\STATE $seq\_Graph.addVertex(mtd)$
+%\ENDFOR
+%
+%\FORALL{$Method\ mtd\ in\ methodList$} 
+%	\IF{$mtd.isPublic()$}
+%		\IF{$!mtd.isStatic()$}
+%			\STATE $List\ preList\ =\ idx.query(mtd.declaringType)$
+%			\FORALL{$Method\ mtd'\ in\ preList$}
+%				\STATE $seq\_Graph.addEdge(mtd',mtd)$
+%			\ENDFOR
+%		\ENDIF
+%		\FORALL{$Parameter\ param\ in\ mtd.getParameters()$}
+%			\IF{$!isBasicType(param.Type)$}
+%				\STATE $List\ preList\ =\ idx.query(paramType)$
+%				\FORALL{$Method\ mtd'\ in\ preList$}
+%					\STATE $seq\_Graph.addEdge(mtd',mtd)$
+%				\ENDFOR				
+%			\ENDIF
+%		\ENDFOR
+%	\ENDIF
+%\ENDFOR
+%\RETURN $seq\_Graph$
+%\end{scriptsize}
+%\end{algorithmic}
+%\caption{Type\_Sequence\_Builder}
+%\label{alg:TypeAnalysis}
+%\end{algorithm}

### 2015-05-13 Draft/evaluation.tex
Updated Approach
Removed Algorithms to save space

@@
 Our results show that, \tool\ effectively identifies constraint sentences with the average (across different classifiers) \CodeIn{precision}, \CodeIn{recall}, and \CodeIn{F-score} of 79.0\%, 60.0\%, and 65.0\%, respectively.
-Balanced Winnow performed best, with an average \CodeIn{precisoin} and \CodeIn{recall} of 78\% and 77\% respectively. 
+Balanced Winnow performed best, with an average \CodeIn{precision} and \CodeIn{recall} of 78\% and 77\% respectively. 
 Furthermore, our results also show the features proposed by \tool\ improves the precision of classification algorithms by an average of 18\%.
@@
 Threats to external validity primarily include the degree to which the subject documents used in our evaluation are representative of true practice.
-To minimize the threat, we used API documents of three different API's: JDK \CodeIn{java.io}, \amazonAPI, \paypalAPI.
+To minimize the threat, we used API documents of three different APIs: JDK \CodeIn{java.io}, \amazonAPI, \paypalAPI.
 On one hand, Java is a widely used programming language and \CodeIn{java.io} is one of the main packages.
@@
 Finally, \paypalAPI\ provides a REST support for online financial transactions.
-The difference in the functionalities provided by the three API's also address the issue of over-fitting our approach to a particular type of API.
-The threat can be further reduced by evaluating our approach on more subjects API's.
+The difference in the functionality provided by the three APIs also address the issue of over-fitting our approach to a particular type of API.
+The threat can be further reduced by evaluating our approach on more subjects APIs.
 

### 2015-05-13 Draft/approach.tex
Removed unnecessary background

@@
 
-\textbf{POS Tags}: We first parse a sentence based on the function of POS tags. 
+{\small $\bullet$} \textbf{POS Tags}: We first parse a sentence based on the function of POS tags. 
 In particular, we use semantic templates to logically break a sentences into smaller constituent sentences. 
@@
 
-The Stanford parser finds it difficult to annotate accurately the Stanford-typed dependencies of the sentence because of presence of different clauses acting on different subject-object pairs.
+The Stanford parser faces difficulty to annotate accurately the Stanford-typed dependencies of the sentence because of presence of various clauses acting on various subject-object pairs.
 As shown in Figure~\ref{fig:standep} the word including is annotated with Stanford-typed dependencies ``dep'' that is a catch all dependency.
@@
 
-\textbf{Stanford-typed Dependencies}: After complex sentences (whenever applicable) have been broken to simple sentences, this phase generates an intermediate (FOL) representation of the sentences.
+{\small $\bullet$} \textbf{Stanford-typed Dependencies}: After complex sentences (whenever applicable) have been broken to simple sentences, this phase generates an intermediate (FOL) representation of the sentences.
 This phase is equivalent to the intermediate-representation technique described in Section~\ref{sub:SENLPback}.

### 2015-05-13 Draft/background.tex
Removed unnecessary background

@@
 
-\textit{Parts Of Speech (POS) tagging}~\cite{Klein03,KleinNIPS03}: Also known as \textit{`word tagging'} and \textit{`grammatical tagging'}, these techniques aim to identify the part of speech (such as noun, verbs, etc.), a particular word in a sentence belongs to.
+{\small $\bullet$} \textbf{Parts Of Speech (POS) tagging}~\cite{Klein03,KleinNIPS03}: Also known as \textit{`word tagging'} and \textit{`grammatical tagging'}, these techniques aim to identify the part of speech (such as noun, verbs, etc.), a particular word in a sentence belongs to.
 
-\textit{Phrase and Clause Parsing}: Also known as chunking, this technique divides a sentence into a constituent set of words (or phrases) that logically belong together (such as a Noun Phrase and Verb Phrase).
+{\small $\bullet$} \textbf{Phrase and Clause Parsing}: Also known as chunking, this technique divides a sentence into a constituent set of words (or phrases) that logically belong together (such as a Noun Phrase and Verb Phrase).
 Chunking further enhances the syntax of a sentence in addition to POS tagging.
 
-\textit{Typed Dependencies}~\cite{Marneffe06LREC,Marneffe08COLING}: The Stanford typed dependencies representation  is designed to provide a simple description of grammatical relationships directed towards non-linguistics experts to perform NLP related tasks.
+{\small $\bullet$} \textbf{Typed Dependencies}~\cite{Marneffe06LREC,Marneffe08COLING}: The Stanford typed dependencies representation  is designed to provide a simple description of grammatical relationships directed towards non-linguistics experts to perform NLP related tasks.
 The representation provides a hierarchical structure for the dependencies with precise definitions of what each dependency represents, thus facilitating machine based manipulation of natural language text.
@@
 
-\textit{Programming Keywords}~\cite{pandita12:inferring}: Accurate annotation of POS tags in a sentence is fundamental to effectiveness of any advanced NLP technique.
+{\small $\bullet$} \textbf{Programming Keywords}~\cite{pandita12:inferring}: Accurate annotation of POS tags in a sentence is fundamental to effectiveness of any advanced NLP technique.
 However POS tagging developed for well written news articles, often performs unsatisfactorily on domain-specific text.
@@
 For instance, consider the word \CodeIn{POST}. 
-The online Oxford dictionary\footnote{\url{http://oxforddictionaries.com/us/definition/american_english/post?q=POST}} has eight different definition of word \CodeIn{POST}, and none of them describes \CodeIn{POST} as an HTTP method\footnote{In HTTP vocabulary \CodeIn{POST} means: \textit{``Creates a new entry in the collection.
+The online Oxford dictionary %\footnote{\url{http://oxforddictionaries.com/us/definition/american_english/post?q=POST}}
+has eight different definition of word \CodeIn{POST}, and none of them describes \CodeIn{POST} as an HTTP method\footnote{In HTTP vocabulary \CodeIn{POST} means: \textit{``Creates a new entry in the collection.
 The new entry's URI is assigned automatically and is usually returned by the operation''}}
@@
 
-\textit{Lexical Token Reduction}~\cite{pandita13:WHYPER}:
+{\small $\bullet$} \textbf{Lexical Token Reduction}~\cite{pandita13:WHYPER}:
 The accuracy of core NLP techniques is often inversely proportional to the number of lexical tokens in a sentence.
@@
 
+%\item \textit{Period Handling}: Besides marking the end of a sentence in generic English, the character period (`.') has other legal usages as well, such as decimal representation (periods between numbers).
+%Although legal, such usage hinder detection of sentence boundaries, thus causing core NLP techniques to return incorrect or imprecise results.
+%The text is pre-processed by annotating these usages for accurate detection of sentence boundaries.
+\vspace*{-1.5ex}
 \begin{itemize}
-
-\item \textit{Period Handling}: Besides marking the end of a sentence in generic English, the character period (`.') has other legal usages as well, such as decimal representation (periods between numbers).
-Although legal, such usage hinder detection of sentence boundaries, thus causing core NLP techniques to return incorrect or imprecise results.
-The text is pre-processed by annotating these usages for accurate detection of sentence boundaries.
 
@@
 
-\textit{Intermediate-Representation Generation}~\cite{pandita13:WHYPER}:
+{\small $\bullet$} \textbf{Intermediate-Representation Generation}~\cite{pandita13:WHYPER}:
 This technique accepts the syntax-annotated sentences (grammatical and semantic) and builds a First-Order-Logic (FOL) like representation of the sentence.

### 2015-05-13 Draft/related.tex
Removed unnecessary background

@@
 
-\textbf{Formal Specification}:
+{\small $\bullet$} \textbf{Formal Specification}:
 Contracts formally specify the program behavior in terms of conditions that must hold before/after and/or during the execution of a method.
@@
 
-\textbf{NLP in Software Engineering (SE)}:
-
+{\small $\bullet$} \textbf{NLP in Software Engineering (SE)}:
 Research advances~\cite{Marneffe08COLING,KleinNIPS03} in the accuracy of existing NLP techniques have inspired researchers and practitioners~\cite{pandita12:inferring, pandita13:WHYPER, johnSlankasPASSAT13, XiaoFSE2012, thummalapentaICSE12} to adapt and(/or) apply NLP techniques to solve problems in SE domain.
@@
 In contrast, the \tool\ approach works with API documents.
-Pandita et al.~\cite{pandita12:inferring} proposed an NLP-based approach on inferring parameter constraints from method descriptions in the API documents. \tool\ differs from their work as follows.
-\tool\ addresses the problem of inferring temporal constraint, which is not addressed by the previous approach.
-\tool\ significantly extends the infrastructure used by Pandita et al.~\cite{pandita12:inferring} in following dimensions.
+Our previous work~\cite{pandita12:inferring} proposed an NLP-based approach on inferring parameter constraints from method descriptions in the API documents.
+\tool\ differs from previous work as follows.
+\tool\ addresses the problem of inferring temporal constraint, which is not addressed by the previous approach. \tool\ significantly extends the infrastructure in following dimensions.
 First, \tool\ relies on ML to identify the temporal constraint sentences.
@@
 
-\textbf{Augmented Documentation}:
+{\small $\bullet$} \textbf{Augmented Documentation}:
 Dekel and Herbsleb~\cite{Dekel2009}, were the first to create a tool namely eMoose,
-an Eclipse~\footnote{\url{http://www.eclipse.org/}} based plug-in that allowed developers to create directives
+an Eclipse IDE based plug-in that allowed developers to create directives
 (way of marking the specification sentences) in the default API documentation.

### 2015-05-13 Draft/background.tex
Minor gramatical edits

@@
 Thus, reduction in the number of lexical tokens greatly improves the accuracy of core NLP techniques. 
-In particular, following heuristics have been used in related work~\cite{pandita12:inferring,pandita13:WHYPER} to achieve the desired reduction of lexical tokens:
+In particular, following heuristics have been used in our previous work~\cite{pandita12:inferring,pandita13:WHYPER} to achieve the desired reduction of lexical tokens:
 %These are a collection of generic preprocessing heuristics to further improve the accuracy of core NLP techniques.
@@
 %The text is pre-processed by annotating these usages for accurate detection of sentence boundaries.
-\vspace*{-1.5ex}
+
 \begin{itemize}
@@
 For instance, consider the phrases \textit{``Amazon S3'', ``Amazon simple storage service''}, which are the names of the service.
-Further resolution of such phrases using grammatical syntax may not bring forth any semantic value.
-Also these phrases contribute to length of a sentence that in turn negatively affects the accuracy of core NLP techniques.
-This heuristic annotates the phrase representing the name of the entities as a single lexical token.
+Further resolution of such phrases using grammatical syntax is redundant for inference needs.
+This heuristic annotates the phrase representing the name of an entity as a single lexical token,
+to improve accuracy of core NLP techniques.
 

### 2015-05-13 Draft/related.tex
Minor gramatical edits

@@
 Among mining based approaches Gable and Su~\cite{gabel2008javert} proposed to learn  
-\textit{micropatterns} of temporal properties from runtime traces and then combining them into larger specifications depicted as finite state automata.
+\textit{micro-patterns} of temporal properties from runtime traces and then combining them into larger specifications depicted as finite state automata.
 In contrast, \tool\ infers specifications from the natural language text in API documents,

### 2015-05-14 Draft/abstract.tex
Updated Brittnay's feedback

@@
 we propose \tool: an approach based on Machine Learning (ML) and Natural Language Processing (NLP) for identifying and inferring formal temporal constraints.
-To evaluate our approach, we apply \tool\ to infer and formalize temporal
+To evaluate our approach, we use \tool\ to infer and formalize temporal
 constraints from the \amazonAPI, the \paypalAPI\, and the \CodeIn{java.io} package in the
 JDK API.
-Our results indicate that \tool\ is effective in identifying temporal
+Our results indicate that \tool\ can effectively identify temporal
 constraint sentences (from over

### 2015-05-14 Draft/approach.tex
Updated Brittnay's feedback

@@
 Figure~\ref{fig:approachOverview} gives an overview of the \tool\ approach.
-\tool\ consists of following six major components: a preprocessor, a candidate identifier, a text-analysis engine, a semantic graph generator, constraint extractor, and a type analyzer.
+\tool\ consists of six major components: a preprocessor, a candidate identifier, a text-analysis engine, a semantic graph generator, constraint extractor, and a type analyzer.
 Additionally, there is an optional model trainer component and external NLP parser component.
@@
 This component accepts the annotated sentence from the previous component,
-then using a trained ML model classifies whether a sentence describes a temporal constraint or not. We next describe the model construction.
+then using a trained ML model classifies whether each sentence as a temporal constraint sentence or not. We next describe the model construction.
 
@@
 
-3) \textbf{Lemmatization}: The feature is the base form of a word.
+3) \textbf{Lemmatization}: The features are the lemma of a words occurring in the sentences.
 In linguistic, lemmatization is the reduction of operational form of a word to its base form.
@@
 
-5) \textbf{Stanford Dependencies}: We add to the feature set by identifying the presence of specific Stanford typed dependencies pertaining to the temporal aspects of the sentence semantics.
+5) \textbf{Stanford Dependencies}: We add to the feature set by identifying the presence of specific Stanford-typed dependencies pertaining to the temporal aspects of the sentence semantics.
 In particular, we identify the presence of ``\textit{advcl}'', ``\textit{aux}'', ``\textit{auxpass}'', ``\textit{vmod}'', and ``\textit{tmod}''.
@@
 Constraint Extractor is responsible for inferring temporal constraint from the classified constraint sentences.
-Temporal constraints are expressed as temporal formulae involving: a) \textit{Predicates} $\xi$ representing method calls and b) \textit{Temporal operators}: backward ($\leftarrow$) \& forward ($\rightarrow$) and their negations $\xleftarrow{-}$ \& $\xrightarrow{-}$.
-We define following four constraints:
+Temporal constraints are expressed as temporal formulae involving: 
+a) \textit{Predicates} $\xi$ representing method calls and 
+b) \textit{Temporal operators}: backward ($\leftarrow$) \& forward ($\rightarrow$) and their negations $\xleftarrow{-}$ \& $\xrightarrow{-}$.
+We define the following four constraints:
 
@@
 \textbf{$\xi_1$}:
-\tool\ first identifies $\xi_1$ as the method whose description constraint sentence is part of.
+\tool\ first identifies $\xi_1$ as the method whose description the constraint sentence is part of.
 For instance the sentence in Figure~\ref{fig:standep} is part of Delete Bucket method description in \amazonAPI,
@@
 \textbf{$\xi_2$}:
-\tool\ next identifies $\xi_2$.
-Since, references to $\xi_2$ may not always be implicit we leverage the semantic graphs.
-A semantic graph is a representation of concepts of objects and the methods applicable on those objects.
+\tool\ next identifies $\xi_2$. Since, references to $\xi_2$ may not always be implicit we leverage the semantic graphs. 
+A semantic graph is a representation of objects and the methods applicable on those objects.
 Figure~\ref{fig:knowledge} shows a graph for \CodeIn{Object} resource in \amazonAPI.
@@
 
-The negation is identified by presence of negation verbs such as ``\textit{no}'', ``\textit{not}'', ``\textit{can't}'' ...
-etc.
+The negation is identified by presence of the negation verbs such as ``\textit{no}'', ``\textit{not}'', ``\textit{can't}'' ... etc.
 Another rule for negation operator is if the sentence is in exception/error description.
@@
 \subsection{Type Analysis}
+\label{sub:typeAnalysis}
 
 Some temporal constraints are enforced by the type system in typed Languages.
-For instances a method ($m$) accepting input parameter ($i$) of type ($t$) mandates that (at least one) method ($m'$) be invoked whose return value is of type ($t$).
+For instance, a method ($m$) accepting input parameter ($i$) of type ($t$) mandates that (at least one) method ($m'$) be invoked whose return value is of type ($t$).
 To extend the temporal constraints inferred by the analyzing the natural language text, this component infers additional constraints that are encoded

### 2015-05-14 Draft/background.tex
Updated Brittnay's feedback

@@
 
-We next briefly introduce the techniques used in this work that have been grouped into two broad categories.
-We first introduce the core NLP techniques used in this work.
-We then introduce the SE specific NLP techniques proposed in related work~\cite{pandita12:inferring,pandita13:WHYPER} that are leveraged in this work.
+We next briefly introduce the NLP techniques used in this work that have been grouped into two broad categories.
+We first introduce the core NLP techniques.
+We then introduce the SE specific NLP techniques proposed in related work~\cite{pandita12:inferring,pandita13:WHYPER}.
 
@@
 {\small $\bullet$} \textbf{Typed Dependencies}~\cite{Marneffe06LREC,Marneffe08COLING}: The Stanford typed dependencies representation is designed to provide a simple description of grammatical relationships directed towards non-linguistics experts to perform NLP related tasks.
-The representation provides a hierarchical structure for the dependencies with precise definitions of what each dependency represents, thus facilitating machine based manipulation of natural language text.
+The representation provides a hierarchical structure for the dependencies with precise definitions of what each dependency represents, thus facilitating machine-based manipulation of natural language text.
 

### 2015-05-14 Draft/evaluation.tex
Updated Brittnay's feedback

@@
 The first two authors manually labeled each sentence (2417 total) in the Java API documentation as being a temporal constraint sentence or not.
-We used \CodeIn{cohen kappa}~\cite{carletta1996assessing} score to statistically measure
+We used cohen kappa~\cite{carletta1996assessing} score to statistically measure
 the inter-rater agreement.
@@
 To answer RQ2, we manually verified the temporal constraints inferred from constraint sentences by \tool.
-However, we excluded the type-enforced temporal constraints inferred using Algorithm~\ref{alg:TypeAnalysis}, described in Section~\ref{sec:approach}.
+However, we excluded the type-enforced temporal constraints described in Section~\ref{sub:typeAnalysis}.
 We excluded the type-enforced constraints because they are correct by construction and are by default enforced by modern IDE's such as the Eclipse. 
@@
 from the natural language text in API documents to the type-enforced temporal constraints
-inferred using Algorithm~\ref{alg:TypeAnalysis}, described in Section~\ref{sec:approach}.
+inferred using the method in Section~\ref{sub:typeAnalysis}.We next present our evaluation results.
 
 \subsection{Results}
-
-We next present our evaluation results.
 
@@
 
-Our results show that, \tool\ effectively identifies constraint sentences with the average (across different classifiers) \CodeIn{precision}, \CodeIn{recall}, and \CodeIn{F-score} of 79.0\%, 60.0\%, and 65.0\%, respectively.
+Our results show that \tool\ effectively identifies constraint sentences with the average (across different classifiers) \CodeIn{precision}, \CodeIn{recall}, and \CodeIn{F-score} of 79.0\%, 60.0\%, and 65.0\%, respectively.
 Balanced Winnow performed best, with an average \CodeIn{precision} and \CodeIn{recall} of 78\% and 77\% respectively. 
@@
 
-In this section, we evaluate the effectiveness of \tool\ in inferring temporal constraints from the identified constraint sentences from API documents.Table~\ref{tab:results} shows the effectiveness of \tool\ in inferring temporal constraints from the identified constraint sentences.
+%In this section, we evaluate the effectiveness of \tool\ in inferring temporal constraints from the identified constraint sentences from API documents.
+Table~\ref{tab:results} shows the effectiveness of \tool\ in inferring temporal constraints from the identified constraint sentences.
 Column ``API'' lists the names of the subject API. 
@@
 before calling the current method.
-However, \tool cannot make the connection owing to the limitation of the semantic graphs that do not list ``already stored'' as a ``valid operation'' on object.  
+However, \tool\ cannot make the connection due to the limitation of the semantic graphs that do not list ``already stored'' as a ``valid operation'' on object.  
 In the future, we plan to investigate techniques to further improve knowledge graphs to infer such implicit constraints.
@@
 
-To address this question, we manually inspect each of the constraints reported by ICON and classify it as a type-enforced constraint or a non type-enforced constraint. 
+To address this question, we manually inspected each of the constraints reported by ICON and classify it as a type-enforced constraint or a non type-enforced constraint. 
 We observed that none of the constraints inferred by our \tool\ from natural language text were classified as a type-enforced constraint.
@@
 
-In summary, we demonstrate that \tool\ effectively identifies constraint sentences (from over 4000 API sentences) with the average precision, recall, and F-score of 79.0\%, 60\%, and 65\% respectively.
-We also show that \tool\ infers temporal constraints from the constraint sentences an average accuracy of 70\%.
+In summary, we demonstrate that \tool\ effectively identifies constraint sentences (from over 4000 API sentences) with the average precision, recall, and F-score of 79.0\%, 60\%, and 65\% respectively [RQ1].
+We also show that \tool\ infers temporal constraints from the constraint sentences an average accuracy of 70\% [RQ2].
 Furthermore, also provide discussion on why \tool\ does not or incorrectly infers temporal constraints.
-Finally, we provide a comparison of the temporal constraints inferred from natural language description against the temporal constraints enforced by a type system.
+Finally, we provide a comparison of the temporal constraints inferred from natural language description against the temporal constraints enforced by a type system [RQ3].
 

### 2015-05-14 Draft/introduction.tex
Minor gramatical edits
Updated Brittnay's feedback

@@
 Application Programming Interfaces (APIs) facilitate software reuse
-by providing standardized mechanism to access API components.
+by providing a standardized mechanism to access API components.
 However, an API has some constraints governing the proper use of the API that must be followed.
 One such type of constraints are temporal constraints [2], which are the allowed sequences of invocations of methods from the API.
-Non-compliance to such constraints will often result in faulty applications that are unreliable to use. % and may even result in financial losses.
+Non-compliance to such constraints will often result in faulty applications that are unreliable. % and may even result in financial losses.
 
-Formal analysis tools, such as model checkers and runtime verifiers 
+Formal analysis tools, such as model checkers and runtime verifiers, 
 can assist in detecting violations of the temporal constraints
 in API clients as defects~\cite{lee2012towards}.
-These tools typically accept formal representation of the temporal constraints for detecting violations.
+These tools typically accept a formal representation of the temporal constraints for detecting violations.
 However, temporal constraints are typically described in natural language text of API documents.
 Such documents are provided to client-code developers through an online access, or are shipped with the API code.
-For a method under consideration, API document may describe both the constraints on the method parameters
+For a method under consideration, an API document may describe both the constraints on the method parameters
 as well as the temporal constraints in terms of other methods that must be invoked pre/post invoking that method.
@@
 A naive approach to identify the constraint sentences is to perform keyword-based search on API documents.
-However, the effectiveness of such approach is limited by the quality of the keywords used.
+However, the effectiveness of such an approach is limited by the quality of the keywords used.
 Furthermore, sentences involving temporal constraints often the time may not have uniquely identifiable keywords.
@@
 
-An ML based approach for identifying the temporal constraint sentences addresses the limitations of keyword-based search by automatically learning patterns of temporal constraint sentences.
+An ML-based approach for identifying the temporal constraint sentences addresses the limitations of keyword-based search by automatically learning patterns of temporal constraint sentences.
 Furthermore, we propose to use a combination of words, syntax (parts of speech) of a sentence, and semantics (relationship between words) of a sentence as the features for learning patterns.
@@
 \begin{itemize}
-	\item An ML and NLP-based approach that effectively infers formal temporal constraints of method invocations. 
+	\item A ML- and NLP-based approach that effectively infers formal temporal constraints of method invocations. 
 	%To the best of our knowledge, our approach is the first one to apply NLP for inferring temporal constraints from API documents.
 	\item A prototype implementation of our approach based on extending the Stanford Parser~\cite{Klein03}, which is a natural language parser to derive the grammatical structure of sentences.
-	All our experimental subjects, results, and artifacts are publicly available on our project website\footnote{\url{https://sites.google.com/site/temporalspec}}. 
+	All our experimental subjects, results, and artifacts are publicly available on our project website.~\footnote{\url{https://sites.google.com/site/temporalspec}} 
 	\item An evaluation of our approach on the \amazonAPI, the \paypalAPI, and the commonly used package \CodeIn{java.io} from the JDK API. 

### 2015-05-14 Draft/approach.tex
Formatted to fit in 10 page format
Closes #8

@@
 		\includegraphics[scale=0.45]{approach.eps}
+	\vspace*{-2ex}
 	\caption{Overview of the \tool\ approach}
 	\label{fig:approachOverview}
+	\vspace*{-4ex}
 \end{figure}
@@
 		\includegraphics[scale=0.25]{StanfordAnnotated.eps}
+	\vspace*{-2.5ex}
 	\caption{Sentence annotated with Stanford dependencies}
 	\label{fig:standep}
+	\vspace*{-3ex}	
 \end{figure}
@@
 
-2) \textbf{Sentence Type}: The context of sentence, whether the sentence appears as method summary, parameter summary, return value summary, or exception/error summary as captured by pre-processor phase.
-The rationale is that a majority of the temporal constraint sentences are either summary or exception sentences.
+2) \textbf{Sentence Type}: The context of sentence, whether the sentence appears as under method, parameter, return value, or exception/error summary as captured by pre-processor phase.
+The rationale is that a majority of the temporal constraint sentences are either method or exception summary sentences.
 
@@
 
-As described in Section~\ref{sub:SENLPback} the intermediate representation generation technique is implemented as a function of Stanford-typed dependencies~\cite{Marneffe06LREC,Marneffe08COLING,KleinNIPS03}, to leverage the semantic information encoded in Stanford-typed dependencies.
-
+Section~\ref{sub:SENLPback} the intermediate representation generation technique implemented as a function of Stanford-typed dependencies~\cite{Marneffe06LREC,Marneffe08COLING,KleinNIPS03}, to leverage the semantic information encoded in Stanford-typed dependencies.
 However, we observed that such implementation is overwhelmed by complex sentences.
@@
 
-{\small $\bullet$} \textbf{POS Tags}: We first parse a sentence based on the function of POS tags. 
-In particular, we use semantic templates to logically break a sentences into smaller constituent sentences. 
+{\small $\bullet$} \textbf{POS Tags}: We first split a sentence into smaller constituent sentences based on the function of POS tags. 
 For instance, consider the sentence which are then accurately annotated by the underlying NLP Parser:
@@
 The Stanford parser faces difficulty to annotate accurately the Stanford-typed dependencies of the sentence because of presence of various clauses acting on various subject-object pairs.
-As shown in Figure~\ref{fig:standep} the word including is annotated with Stanford-typed dependencies ``dep'' that is a catch all dependency.
+As shown in Figure~\ref{fig:standep} the word ``including'' is annotated with Stanford-typed dependencies ``dep'' that is a catch all dependency.
 A catch all dependency is selected by a parser when no other appropriate dependency can be selected.
-The \tool\ approach thus automatically break down the sentence into two smaller tractable sentences:
+The \tool\ approach thus automatically break down the sentence into two smaller tractable sentences, which are accurately annotated:
 
@@
 \begin{center}
+\vspace*{-3ex}
+\caption{Semantic Templates}
+\vspace*{-1ex}
 
-\caption{Semantic Templates}
     \begin{tabular}{  l  p{5cm} p{10cm} }
@@
 	\label{tab:semanticTemplates}
+	\vspace*{-4ex}
 \end{center}
@@
 		\begin{alltt}
-			01:before[6]
-			02:|->must be deleted[5]
-			03:\hspace*{0.2in}|->All[1]
-			04:\hspace*{0.2in}|\hspace*{0.2in}|->in[3]
-			05:\hspace*{0.2in}|\hspace*{0.4in}|->\textbf{objects}[2]
-			06:\hspace*{0.2in}|\hspace*{0.4in}|->\textbf{bucket}[4]
-			07:\hspace*{0.2in}|->can be deleted[8]
-			08:\hspace*{0.4in}|->\textbf{bucket}[7]
-			09:\hspace*{0.4in}|->\textbf{itself}[9]
+			\hspace*{0.8in}01:before[6]
+			\hspace*{0.8in}02:|->must be deleted[5]
+			\hspace*{0.8in}03:\hspace*{0.2in}|->All[1]
+			\hspace*{0.8in}04:\hspace*{0.2in}|\hspace*{0.2in}|->in[3]
+			\hspace*{0.8in}05:\hspace*{0.2in}|\hspace*{0.4in}|->\textbf{objects}[2]
+			\hspace*{0.8in}06:\hspace*{0.2in}|\hspace*{0.4in}|->\textbf{bucket}[4]
+			\hspace*{0.8in}07:\hspace*{0.2in}|->can be deleted[8]
+			\hspace*{0.8in}08:\hspace*{0.4in}|->\textbf{bucket}[7]
+			\hspace*{0.8in}09:\hspace*{0.4in}|->\textbf{itself}[9]
 		\end{alltt}
 	\end{CodeOut}
-	\caption{\label{fig:FOLTree} FOL representation of the sentence \textit{``All objects in the bucket must be deleted before the bucket itself can be deleted.''}}
+	\vspace*{-3ex}
+	\caption{\label{fig:FOLTree} FOL-like representation of the sentence \textit{``All objects in the bucket must be deleted before the bucket itself can be deleted.''}}
+	\vspace*{-3ex}
+
 \end{figure}
@@
 
-1) \textit{Forward Operator ($\xi_1 \rightarrow \xi_2$)}: method call $\xi_1$ must be succeeded by method call $\xi_2$.
+\begin{enumerate}
+\item \textit{Forward Operator ($\xi_1 \rightarrow \xi_2$)}: method call $\xi_1$ must be succeeded by method call $\xi_2$.
 
-2) \textit{Backward Operator ($\xi_1 \leftarrow \xi_2$)}: method call $\xi_1$ must be preceded by method call $\xi_2$.
+\item \textit{Backward Operator ($\xi_1 \leftarrow \xi_2$)}: method call $\xi_1$ must be preceded by method call $\xi_2$.
 
-3) \textit{Negative Forward Operator ($\xi_1 \xrightarrow{-} \xi_2$)}: method call $\xi_1$ cannot be succeeded by method call $\xi_2$
+\item \textit{Negative Forward Operator ($\xi_1 \xrightarrow{-} \xi_2$)}: method call $\xi_1$ cannot be succeeded by method call $\xi_2$
 
-4) \textit{Negative Backward Operator ($\xi_1 \xleftarrow{-} \xi_2$)}: method call $\xi_1$ cannot be preceded by the method call of $\xi_2$
-
+\item \textit{Negative Backward Operator ($\xi_1 \xleftarrow{-} \xi_2$)}: method call $\xi_1$ cannot be preceded by the method call of $\xi_2$
+\end{enumerate}
 %The prohibition operators capture a different class of temporal constraints that cannot be
@@
 
-We next show how \tool\ identifies the terms of the constraint formula:
+We next describe how \tool\ identifies the terms of the constraint formula:
 
@@
 Delete Bucket $\leftarrow$ Delete Object.
-
-The negation is identified by presence of the negation verbs such as ``\textit{no}'', ``\textit{not}'', ``\textit{can't}'' ... etc.
+Negation is identified by presence of the negation verbs such as ``\textit{no}'', ``\textit{not}'', ``\textit{can't}'' ... etc.
 Another rule for negation operator is if the sentence is in exception/error description.
@@
 	\includegraphics[scale=0.3]{KnowledgeGraph.eps}
-	\caption{Semantic Graph for the \CodeIn{Object} related operations in Amazon S3 REST API}
+	\vspace*{-2.5ex}
+	\caption{Semantic Graph for the \CodeIn{Object} method in Amazon S3 REST API}
 	\label{fig:knowledge}
+	\vspace*{-3ex}
 \end{figure}

### 2015-05-14 Draft/background.tex
Fixes #9
Formatted to fit in 10 page format
Closes #8

@@
 We first introduce the core NLP techniques.
-We then introduce the SE specific NLP techniques proposed in related work~\cite{pandita12:inferring,pandita13:WHYPER}.
+We then introduce the SE specific NLP techniques proposed in previous work~\cite{pandita12:inferring,pandita13:WHYPER}.
 
@@
 The online Oxford dictionary %\footnote{\url{http://oxforddictionaries.com/us/definition/american_english/post?q=POST}}
-has eight different definition of word \CodeIn{POST}, and none of them describes \CodeIn{POST} as an HTTP method\footnote{In HTTP vocabulary \CodeIn{POST} means: \textit{``Creates a new entry in the collection.
+has eight generic definition of word \CodeIn{POST}, and none of them describes \CodeIn{POST} as an HTTP method\footnote{In HTTP vocabulary \CodeIn{POST} means: \textit{``Creates a new entry in the collection.
 The new entry's URI is assigned automatically and is usually returned by the operation''}}
 supported by REST API.
-Thus existing POS tagging techniques fail to accurately annotate the POS tags of the sentences involving word \CodeIn{POST}.
+Existing POS tagging techniques that are trained on generic documents fail to accurately annotate the POS tags of the sentences involving word \CodeIn{POST}.
 

### 2015-05-14 Draft/conclusion.tex
Formatted to fit in 10 page format
Closes #8

@@
 \label{sec:conclusion}
-
+\vspace*{-1ex}
 Despite being highly desirable, formal temporal constraints are missing from most APIs.
@@
 To address this issue, we have proposed a novel approach called \tool\ to infer temporal constraints from natural language text of API documents.
-We applied \tool\ to infer temporal constraints from
+We used \tool\ to infer temporal constraints from
 the \paypalAPI, the \amazonAPI, and the 

### 2015-05-14 Draft/evaluation.tex
Formatted to fit in 10 page format
Closes #8

@@
 \begin{center}
-
+\vspace*{-3ex}
 \caption{Evaluation Results (Identification)}
-
+\vspace*{-1ex}
 \begin{tabular}{rlccccccccc}
@@
 \label{tab:resultsRQ1}
+\vspace*{-5ex}
 \end{center}
@@
 \begin{center}
-
 \caption{Evaluation Results (Inference)}
-
+\vspace*{-1ex}
 \begin{tabular}{lccccc}
@@
 \label{tab:results}
+\vspace*{-5ex}
 \end{center}
@@
 
-In this section, we compared the temporal constraints inferred from the natural language API descriptions to those enforced by the type-system (referred to as type-enforced constraint).
+In this section, we compare the temporal constraints inferred from the natural language API descriptions to those enforced by the type-system (referred to as type-enforced constraint).
 The constraints that are enforced by the type-system can be enforced by IDEs.

### 2015-05-14 Draft/example.tex
Formatted to fit in 10 page format
Closes #8

@@
 	\end{center}
-	\caption{\label{fig:Stackoverflow} The Query posted on Stack Overflow forum regrading Amazon S3 REST API}
+	\vspace*{-3ex}
+	\caption{\label{fig:Stackoverflow} Query posted on StackOverflow forum about Amazon S3 REST API}
+	\vspace*{-3ex}
 \end{figure}
 
-Consider the question asked in \textit{Stack Overflow}~\footnote{{\small \url{http://stackoverflow.com/questions/27267/delete-amazon-s3-buckets}}} as shown in Figure~\ref{fig:Stackoverflow}.
+Consider the question asked in \textit{Stack Overflow}~\footnote{ \url{http://stackoverflow.com/questions/27267/delete-amazon-s3-buckets}} as shown in Figure~\ref{fig:Stackoverflow}.
 Stack Overflow is an online question and answer forum for professional and enthusiast programmers.

### 2015-05-14 Draft/evaluation.tex
Made best values bold in Table 2
Closes #6
Incorporated Feedback by Maria

@@
 \begin{itemize}
-	\item\textbf{RQ1}: What are the precision and recall of \tool\ in identifying temporal constraints from sentences written in natural language?
+	\item\textbf{RQ1}: What are the precision and recall of \tool\ in identifying natural language sentences describing temporal constraints?
 	Answer to this question quantifies the effectiveness of \tool\ in identifying constraint sentences.
@@
 \midline 
-			1	& AdaBoost			& 0.52	& 0.81	& 0.61	& 0.7	& 0.78	& 0.74	& 0.18	& -0.03	& 0.13	\\
+			1	& AdaBoost			& 0.52	& \textbf{0.81}	& 0.61	& 0.7	& \textbf{0.78}	& 0.74	& 0.18	& -0.03	& 0.13	\\
 \rowcol		2	& NaiveBayes		& 0.49	& 0.67	& 0.56	& 0.74	& 0.65	& 0.69	& 0.25	& -0.02	& 0.13	\\
-			3	& Balanced Winnow	& 0.77	& 0.76	& 0.76	& 0.78	& 0.77	& 0.77	& 0.01	& 0.01	& 0.01	\\
-\rowcol		4	& Decision Tree		& 0.82	& 0.58	& 0.66	& 0.92	& 0.41	& 0.56	& 0.1	& -0.17	& -0.1	\\
-			5	& Winnow			& 0.19	& 0.41	& 0.15	& 0.8	& 0.51	& 0.59	& 0.61	& 0.1	& 0.44	\\
+			3	& Balanced Winnow	& 0.77	& 0.76	& \textbf{0.76}	& 0.78	& 0.77	& \textbf{0.77}	& 0.01	& 0.01	& \textbf{0.01}	\\
+\rowcol		4	& Decision Tree		& \textbf{0.82}	& 0.58	& 0.66	& \textbf{0.92}	& 0.41	& 0.56	& 0.1	& -0.17	& -0.1	\\
+			5	& Winnow			& 0.19	& 0.41	& 0.15	& 0.8	& 0.51	& 0.59	& \textbf{0.61}	& 0.1	& \textbf{0.44}	\\
 \rowcol		6	& MaxEnt			& 0.69	& 0.48	& 0.55	& 0.76	& 0.46	& 0.56	& 0.07	& -0.02	& 0.01	\\
@@
 To address this question, we manually inspected each of the constraints reported by ICON and classify it as a type-enforced constraint or a non type-enforced constraint. 
-We observed that none of the constraints inferred by our \tool\ from natural language text were classified as a type-enforced constraint.
+We observed that none of the constraints inferred by \tool\ from natural language text were classified as a type-enforced constraint.
 Hence, the constraints detected by \tool\ are not trivial enough to be enforced by a type system.

### 2015-05-16 Draft/abstract.tex
Updated Dr. Xie's Comments

@@
 To evaluate our approach, we use \tool\ to infer and formalize temporal
-constraints from the \amazonAPI, the \paypalAPI\, and the \CodeIn{java.io} package in the
+constraints from the \amazonAPI, the \paypalAPI, and the \CodeIn{java.io} package in the
 JDK API.

### 2015-05-16 Draft/conclusion.tex
Updated Dr. Xie's Comments

@@
 \vspace*{-1ex}
-Despite being highly desirable, formal temporal constraints are missing from most APIs.
+Despite being highly desirable, formal temporal constraints are absent in most APIs.
 In contrast, documentation of API methods contains detailed specifications of temporal constraints in natural language text.
@@
 from more than 4000 sentences in subject API documents.
-Furthermore, \tool\ also achieved an accuracy of
+Furthermore, \tool\ also achieves an accuracy of
 70\% in inferring 77 formal temporal constraints from these temporal constraint sentences.

### 2015-05-16 Draft/introduction.tex
Incorporated Feedback by Maria
Updated Dr. Xie's Comments

@@
 by providing a standardized mechanism to access API components.
-However, an API has some constraints governing the proper use of the API that must be followed.
+However, an API has some constraints (governing the proper use of the API) that must be followed.
 One such type of constraints are temporal constraints [2], which are the allowed sequences of invocations of methods from the API.
-Non-compliance to such constraints will often result in faulty applications that are unreliable. % and may even result in financial losses.
+Non-compliance to such constraints often results in faulty applications that are unreliable. % and may even result in financial losses.
 
@@
 %For instance, Wu et al.~\cite{wu2013inferring} report that it took one person ten hours to browse the documentation of one method from a web API, even before the person attempted to formalize the constraints on the method.
-For instance, the PDF version of the documentation for \amazonAPI\footnote{{\small \url{http://awsdocs.s3.amazonaws.com/S3/latest/s3-api.pdf}}} spans 278 pages describing 51 methods.
+For instance, the PDF version of the documentation for the \amazonAPI\footnote{{\small \url{http://awsdocs.s3.amazonaws.com/S3/latest/s3-api.pdf}}} spans 278 pages describing 51 methods.
 
@@
 The first step towards formalizing temporal constraints is to identify the sentences describing such constraints.
-A naive approach to identify the constraint sentences is to perform keyword-based search on API documents.
-However, the effectiveness of such an approach is limited by the quality of the keywords used.
+A straightforward approach to identify the constraint sentences is to perform keyword-based search on API documents.
+However, the effectiveness of such an approach is limited by the quality of the used keywords.
 Furthermore, sentences involving temporal constraints often the time may not have uniquely identifiable keywords.
@@
 For instance, consider the sentences from the \paypalAPI:
-1) ``\textit{Use this call to complete a payment.}'' from the \CodeIn{execute payment} method.
+1) ``\textit{Use this call to complete a payment.}'' from the \CodeIn{execute payment} method;
 2) ``\textit{Use this call to refund a completed payment.}'' from the \CodeIn{refund sale} method.
@@
 
-Even after a sentence has been identified as a constraint sentence, an approach has to infer the references to the method in the sentences, which often may not be explicit.
-Consider Sentence 2 in the preceding paragraph.
+Even after a sentence has been identified as a constraint sentence, there is strong need to infer the references to the method in the sentences, which often may not be explicit.
+Consider Sentence 2 in the preceding example.
 The phrase \textit{``completed payment''} refers to the \CodeIn{execute payment} method in the API.
@@
 Furthermore, we propose to use a combination of words, syntax (parts of speech) of a sentence, and semantics (relationship between words) of a sentence as the features for learning patterns.
-This combination allows \tool\ to make a finer grained distinction between the example sentences described earlier.
-Furthermore, to identify the phrases as implicit method-invocation references, we propose to leverage domain dictionaries that are systematically created from API documents and generic English dictionaries.
+This combination allows \tool\ to make a finer-grained distinction between the example sentences described earlier.
+Furthermore, to identify phrases as implicit method-invocation references, we propose to leverage domain dictionaries that are systematically created from API documents and generic English dictionaries.
 
@@
 \begin{itemize}
-	\item A ML- and NLP-based approach that effectively infers formal temporal constraints of method invocations. 
+	\item An ML- and NLP-based approach that effectively infers formal temporal constraints of method invocations. 
 	%To the best of our knowledge, our approach is the first one to apply NLP for inferring temporal constraints from API documents.
 	\item A prototype implementation of our approach based on extending the Stanford Parser~\cite{Klein03}, which is a natural language parser to derive the grammatical structure of sentences.
-	All our experimental subjects, results, and artifacts are publicly available on our project website.~\footnote{\url{https://sites.google.com/site/temporalspec}} 
 	\item An evaluation of our approach on the \amazonAPI, the \paypalAPI, and the commonly used package \CodeIn{java.io} from the JDK API.
+	All our experimental subjects, results, and artifacts are publicly available on our project website.\footnote{\url{https://sites.google.com/site/temporalspec}}.
 \end{itemize}
